### 2020-04-03 manuscript/manuscript_outline.Rmd
Started manuscript, as well as:
- Added section of code to replace "0m" value with composition from trapLoc
- Started section of code to make collinearity figure with AAFC geo data

---
title: "Landscape composition and beneficial insects"
author: "Sam Robinson, Paul Galpern, others"
date: "03/04/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

* Arthropod diversity is important to understand in agricultural systems
  + Pests can cause large amounts of damage
  + Beneficial insects can offset this
  + Important for global biodiversity - insects may be declining globally
  + Agriculture is ~36% of land worldwide
  + Potential for win-win scenarios

* We don't have a good understanding of what drives arthropod abundance
  + Bees are generally driven by flower/nest abundance
  + Limited understanding of other arthropods
  + Beetles are limited by water, food, oviposition sites, etc.
  + Arachnids are similarly limited by food, shelter

* Landscape structure can influence abundance of beneficial arthropods in agricultural areas
  + No-till agriculture 
  + How can we design landscapes to benefit both farmers and insects?

* Point estimates of abundance are influenced by spatio-temporal processes 
  + Arthropods move between landscape components depending on their life history
  + e.g. Carabid beetles are thought to reproduce in field margins, but adults feed in fields (Desender and Alderweireldt 1988, J. of App. Ent.)
  + Counts are a proxy of activity density, not necessarily abundance
  + Nevertheless, this is an OK measure (_need to justify this_)

* In this study, we used pitfall trap counts of three species of beneficial arthropod to determine how landscape composition affects activity density of arthropods
  + We hypothesized that:
  1. Abundance of semi-natural land would result in increased arthropod abundance
  2. Other things...

# Methods

* We used a system of pitfall traps located in southern Alberta in 2017

# Results

# Discussion

### 2020-04-03 extractGeoData.R

@@ -238,6 +238,13 @@ par(mfrow=c(1,1))
 #Save list of matrices
 save(oRingMat2,file='./data/geoDataAAFC.Rdata')
 
+# Collinearity plots for different land cover classes ---------------------
+
+#Problem: some land cover types are collinear with each other, but differs based on distances. Need to create a figure to properly visualize this
+
+
+
+
 # Other code snippets -----------------------
 
 # Create new shapefiles for 2018 data

### 2020-04-03 frAnalysis.R

@@ -93,26 +93,12 @@ tempTrap <- trap %>% filter(startYear==2017,grepl('PF',BTID)) %>%
 #When using trap location, canola clearly has the most 
 #Is this a "cultural" species?
 
-# #Function for optimizing range values for gp models
-# rAIC <- function(r,t){
-#   f1 <- gam(count~offset(log(trapdays))+
-#               s(endjulian,bs='gp',k=20,m=c(2,exp(r[1])))+ #Gaussian process basis function (powExp correlation)
-#               s(easting,northing,bs='gp',m=c(2,exp(r[2])))+
-#               ti(northing,easting,endjulian)+
-#               trapLoc,
-#             # s(BLID,bs='re')
-#             # s(grass)+s(wetlands)+
-#             data=t,family='nb',method='ML')
-#   return(f1$aic)
-# }
-# optR <- optim(c(6,1),rAIC,t=tempTrap)
-
 mod1 <- gam(count~offset(log(trapdays))+
               # s(endjulian,bs='gp',k=10,m=c(2,80))+ #Gaussian process basis function (powExp correlation)
               # s(easting,northing,bs='gp',k=30,m=c(2,5))+
               s(endjulian,bs='ts',k=10)+ #Thin plate spline with shrinkage
               s(easting,northing,bs='ts',k=100)+
-              ti(northing,easting,endjulian,bs='ts')+
+              ti(northing,easting,endjulian,bs='ts')+ #Spatiotemporal interaction   
               trapLoc,
               # s(BLID,bs='re')
               # s(grass)+s(wetlands)+
@@ -220,9 +206,7 @@ summary(mod2); AIC(mod2)
 plot(mod2,scheme=2,pages=1,resid=T)
 par(mfrow=c(2,2)); gam.check(mod2); par(mfrow=c(1,1))
 
-
 #Model of landscape effect (ring composition from AAFC rasters)
-
 #Proportion area within each ring
 oRingMat2Prop <-  lapply(oRingMat2,function(x) x/Reduce('+',oRingMat2))
 
@@ -231,6 +215,22 @@ oRingMat2Prop <- lapply(oRingMat2Prop,function(x){
   x %>% as.data.frame() %>% rownames_to_column('ID') %>% 
[…]

### 2020-04-06 frSim.R
Added simple simulation of vector-on-scalar functional regression

@@ -1,0 +1,94 @@
+#Simple example of functional regression
+#Sam Robinson, Spring 2020
+
+# Functions ---------------------------------------------------------------
+
+library(mgcv)
+logit <- function(x) log(x/(1-x))
+invLogit <- function(x) exp(x)/(1+exp(x))
+
+# Simulate data -----------------------------------------------------------
+
+#Goal: fit yield data to time series of NDVI (or other indices)
+
+set.seed(1)
+
+Ndays <- 100 #Number of days of data (columns of matrix)
+Nsamp <- 1000 #Number of samples (rows of matrix)
+
+#Say that the "true" effect of NDVI on yield is something like this:
+coefFun <- function(t) 3*exp(-0.03*t)
+curve(coefFun,0,100,xlab='Day',ylab='Coefficient')
+#i.e the effect of NDVI is positive early on, and zero later on
+
+#Generate some NDVI data - double logistic function from doi:10.1016/j.rse.2005.10.021
+ndviFun <- function(t,min,max,mS,mA,S,A){
+  #t = day, min/max = min/max NDVI,
+  #mS = spring slope, mA = autumn slope, S = spring start, A = autumn start
+  a <- 1/(1+exp(-mS*(t-S))) #Part 1
+  b <- 1/(1+exp(mA*(t-A))) #Part 2
+  min + (max-min)*(a+b-1)
+}
+#Example
+curve(ndviFun(x,min=0.1,max=1,mS=0.2,mA=0.4,S=20,A=80),0,100,xlab='Day',y='NDVI')
+
+#Parameters for NDVI generation
+ndviPars <- c(0.1,1,0.2,0.4,20,80)
+
+#"True" NDVI values
+ndviTrue <- replicate(Nsamp,{
+  sapply(1:Ndays,ndviFun,min=ndviPars[1],
+         max=ndviPars[2]-1/(1+exp(rnorm(1,2,2))), #Add some variation in max NDVI
+         mS=ndviPars[3], mA=ndviPars[4], 
+         S=ndviPars[5] + rnorm(1,0,5), #Add variation in start time
+         A=ndviPars[6])
+},simplify=F)
+
+#Received NDVI values (white noise added)
+ndvi <- lapply(ndviTrue,function(x){
+  invLogit(logit(x)+rnorm(length(x),0,0.5))
+})
+
+#Convert both into matrices
[…]

### 2020-04-16 manuscript/manuscript_outline.Rmd
Created correlation plots, and started looking into multicollinearity

@@
   + Counts are a proxy of activity density, not necessarily abundance
-  + Nevertheless, this is an OK measure (_need to justify this_)
+  + Nevertheless, this is probably an OK measure (_need to justify this_)
 
@@
 
-* We used a system of pitfall traps located in southern Alberta in 2017
+##Data collection
+
+* We used a system of pitfall traps installed in ditches, field margins, wetlands, and in-field sites across southern Alberta in 2017 (_need a map here_)
+  + Traps at in-field sites were installed 20, 100, 200m (?) along a transect from the nearest non-crop feature (wetland, grassland, pivot)
+  +
+
+* To characterize landscape composition surrounding the traps, we used classified landscape data from AAFC
+  + Classifications are very accurate for fields (~90%), but less accurate for non-crop areas (~70%)
+  + Landscape studies often use the landscape composition within a circle of a fixed radius surrounding each point
+  + However, the radius of the circle depends on the grain of the landscape that is relevant to the abundance of a given organism.
+  + We used a novel method 
+  + Instead, we divided the landscape into annuli (rings) surrounding each trap location.
+  + Each annulus was 30 m thick, and had inner radii ranging from 30 to 1470m, in increments of 30m.
+
+##Statistics
 

### 2020-04-16 extractGeoData.R

@@ -244,8 +244,10 @@ load('./data/geoDataAAFC.Rdata')
 #Problem: some land cover types are collinear with each other, but differs based on distances. Need to create a figure to properly visualize this
 
 #Function to examine correlation between % landscape categories at different distances
-corplot <- function(l,nam,tVal=F,xlabel=NULL){ #Requires list of matrices, names to use, and whether to use t-values or r values
-  if(tVal){
+corplot <- function(l,nam,value=NULL,xlabel=NULL){ #Requires list of matrices, names to use, and whether to use t-values or r values
+  if(is.null(value)) stop('Type of correlation value not found')
+  
+  if(value=='t'){
     slopes <- sapply(1:ncol(l[[1]]),function(x) { #Linear slope estimate
       coefs <- summary(lm(l[[nam[1]]][,x]~l[[nam[2]]][,x]))$coefficients #Get t-value of slope term (if possible)
       if(nrow(coefs)==2) return(coefs[2,3]) else return(0)
@@ -257,10 +259,15 @@ corplot <- function(l,nam,tVal=F,xlabel=NULL){ #Requires list of matrices, names
          type='b')
     abline(h=c(-2,0,2),lty=c('dashed','solid','dashed'),col=c('red','black','red')) #Standard deviations
   } else {
+    corvals <- lapply(1:ncol(l[[1]]),function(x) cor.test(l[[nam[1]]][,x],l[[nam[2]]][,x],method=value)) #Kendall correlation
+    y <- sapply(corvals,function(x) x$statistic)
+    sig <- sapply(corvals,function(x) x$p.value<0.05)
+    
     plot(as.numeric(gsub('d','',colnames(l[[1]]))),
-         sapply(1:ncol(l[[1]]),function(x) cor(l[[nam[1]]][,x],l[[nam[2]]][,x],method='kendall')), #Correlation
-         # zPrime <- 0.5*log((1+r)/(1-r))
-         xlab=xlabel,ylab='Correlation',main=paste0(nam[1],':',nam[2]),pch=19,type='b')
+         y,
+         xlab=xlabel,ylab=corvals[[1]]$method,main=paste0(nam[1],':',nam[2]),
+         pch=ifelse(sig,19,1),
[…]

### 2020-04-16 frAnalysis.R

@@ -12,11 +12,20 @@ library(beepr)
 # Functions --------------------------------------------------------
 
 #Function to display matrix (m) with row/column names (nam)
-matrixplot <- function(m,nam){
-  par(mfrow=c(1,1))
+matrixplot <- function(m,nam=NULL,mar=NULL,showNums=T){
+  if(ncol(m)!=nrow(m)) stop('Matrix not square')
+  if(!is.null(nam)){
+    if(ncol(m)!=length(nam)) stop('Length of name vector != matrix dimension')
+  } else {
+    nam <- rep('',ncol(m))
+  }
+  n <- ncol(m) #Matrix dimensions
+  savepar <- par()
+  if(is.null(mar)) mar <- c(1,5,5,1)
+  par(mfrow=c(1,1),mar=mar)
   #Dark colours indicate high multicollinearity
-  image(m,axes=F,col=gray.colors(12,start=0.2,end=1,rev=T))
-  mtext(text=nam, side=2, line=0.3, at=seq(0,1,length.out=nrow(m)), las=1, cex=0.8)
+  image(m[1:n,n:1],axes=F,col=gray.colors(12,start=0.2,end=1,rev=T))
+  mtext(text=nam[n:1], side=2, line=0.3, at=seq(0,1,length.out=nrow(m)), las=1, cex=0.8)
   mtext(text=nam, side=3, line=0.3, at=seq(0,1,length.out=nrow(m)), las=2, cex=0.8)
   
   # #shadowtext trick from:
@@ -26,23 +35,28 @@ matrixplot <- function(m,nam){
   # x0 <- r*strwidth('0')
   # y0 <- r*strheight('0')
 
-  for(i in 1:nrow(m)){ #Add row text
-    (rpos <- (i-1)/(nrow(m)-1)) #Row position
-    # for(j in 1:ncol(m)){
-    j <- 1:ncol(m)
-    (cpos <- (j-1)/(ncol(m)-1)) #Column position
-    # #White background text
-    # for(k in 1:length(theta)){
-    #   text(cpos+cos(k)*x0,rpos+sin(k)*y0,round(m[j,i],2),col='white')
-    # }
-    #Actual text
-    text(cpos,rpos,round(m[j,i],2),col='darkred')
-    # }
+  if(showNums){
+    #Add row text
+    for(i in 1:n){ #Column of matrix to access
+      cpos <- (i-1)/(n-1) #Col position in figure
+      j <- 1:n #Rows of matrix to access
[…]

### 2020-04-18 manuscript/manuscript_outline.Rmd
Decided on spatiotemporal smoothing structure
- Shrinkage splines use 1 less term, so smoother terms easier to interpret
- Less correlation problem (?)

@@
   + Traps at in-field sites were installed 20, 100, 200m (?) along a transect from the nearest non-crop feature (wetland, grassland, pivot)
-  +
+  + Specimens were collected from the traps every 14 days, on average (SD: 2.9), and were identified to species
 
@@
   + However, the radius of the circle depends on the grain of the landscape that is relevant to the abundance of a given organism.
-  + We used a novel method 
   + Instead, we divided the landscape into annuli (rings) surrounding each trap location.
   + Each annulus was 30 m thick, and had inner radii ranging from 30 to 1470m, in increments of 30m.
+  + Using functional regression (see below), we were able to incorporate landscape information at different distance, allowing us to assess the impact of both local and regional landscape composition
 
 ##Statistics
+
+* Function-on-scalar (FOS) regression is a special type of linear model ($\hat{y}=X\beta$), where the values of the coefficients ($\beta$) are defined by a smooth function
+  + In our case, the coefficients represent the effect of a given type of landscape cover, and are a smooth function of distance from the trap (i.e. $\beta_i = f(distance_i)$)
+  + This technique has been used by other authors; Galpern et al. called this ``onion-skin regression"
+  + We fit our functional regression models using _mgcv_ version XXX.
 

### 2020-04-18 frAnalysis.R

@@ -12,7 +12,7 @@ library(beepr)
 # Functions --------------------------------------------------------
 
 #Function to display matrix (m) with row/column names (nam)
-matrixplot <- function(m,nam=NULL,mar=NULL,showNums=T){
+matrixplot <- function(m,nam=NULL,mar=NULL,numSize=1,numCol='red'){
   if(ncol(m)!=nrow(m)) stop('Matrix not square')
   if(!is.null(nam)){
     if(ncol(m)!=length(nam)) stop('Length of name vector != matrix dimension')
@@ -35,7 +35,7 @@ matrixplot <- function(m,nam=NULL,mar=NULL,showNums=T){
   # x0 <- r*strwidth('0')
   # y0 <- r*strheight('0')
 
-  if(showNums){
+  if(numSize>0){
     #Add row text
     for(i in 1:n){ #Column of matrix to access
       cpos <- (i-1)/(n-1) #Col position in figure
@@ -45,7 +45,7 @@ matrixplot <- function(m,nam=NULL,mar=NULL,showNums=T){
       # for(k in 1:length(theta)){
       #   text(cpos+cos(k)*x0,rpos+sin(k)*y0,round(m[j,i],2),col='white')
       # }
-      text(cpos,rpos,round(m[j,i],2),col='darkred') #Text
+      text(cpos,rpos,round(m[j,i],2),col=numCol,cex=numSize) #Text
       # }
     }
   }
@@ -56,7 +56,8 @@ matrixplot <- function(m,nam=NULL,mar=NULL,showNums=T){
 #Takes a df of arthropod counts at each site (unique to each spp), then runs 4 landscape-level models of abundance
 #mod3Vars = vector of landscape cover types contained in oRingMat2
 #mod4Var = name of "noncrop" cover type to use
-runMods <- function(tempArth,trap,nnDistMat,oRingMat2,Kvals=NULL,mod3Vars=NULL,mod4Var=NULL){
+runMods <- function(tempArth,trap,nnDistMat,oRingMat2,Kvals=NULL,mod3Vars=NULL,mod4Var=NULL,
+                    fitMethod='REML',fitFam='nb',basisFun='ts',doublePenalize=F){
[…]

### 2020-05-04 frAnalysis.R
Reran models with spatial + temporal + interaction FR

@@ -157,6 +157,46 @@ firstUpper <- function(x){
   paste0(toupper(substring(x,1,1)),substring(x,2,nchar(x)))
 }
 
+#Extract data for partial effects plots of smoothing terms
+# dat = dataframe of predictor data (think "newdata" from predict.gam) + column of ones with title of "by" matrix (if doing functional regression)
+#   * must have the same name as predictors
+# m = GAM model
+# whichSmooth = smoothing terms (numeric) to use; all terms are aggregated (useful for interaction plots)
+# ci = multiplicitive factor for SE bounds (default = 1.96)
+smoothPred <- function(dat,m,whichSmooth,ci=1.96){ 
+  #Predictor matrices
+  predMat <- lapply(whichSmooth,function(i) PredictMat(m$smooth[[i]],data=dat)) #Get predictor matrices from each smoother, using dat
+  predMat <- do.call('cbind',predMat) #Amalgamate into single matrix
+  #Coefficients
+  coefRange <- do.call('c',lapply(m$smooth[whichSmooth],function(x) x$first.para:x$last.para)) #Get coefficients to use
+  coefs <- coef(m)[coefRange] #Extract coefficient values
+  #Predicted value - predictor matrix X coefficients
+  dat$pred <- predMat %*% coefs
+  #SE - swiped from plot.gam code
+  dat$se <- sqrt(pmax(0,rowSums(predMat %*% m$Vp[coefRange,coefRange] * predMat)))
+  #Confidence intervals
+  dat$upr <- dat$pred + dat$se*ci; dat$lwr <- dat$pred - dat$se*ci 
+  return(dat) #Return entire dataframe
+}
+
+#Helper ggplot function to plot functional regression effects
+#Optional legend, and different colours
+effectPlot <- function(dat,leg=T,cols=NULL){
+  if(sum(is.na(dat$y))==nrow(dat)){ #B/W version
+    dat$y <- 'a'
+    cols <- 'black'
+  }
+  p <- ggplot(data=dat,aes(x=x,y=pred))+
+    geom_ribbon(aes(ymax=upr,ymin=lwr,fill=y),alpha=0.3,show.legend=leg)+
+    geom_line(aes(col=y),show.legend=leg)+
[…]

### 2020-05-06 manuscript/manuscript_outline.Rmd
Worked on outline, esp. figures and citations

@@
 title: "Landscape composition and beneficial insects"
-author: "Sam Robinson, Paul Galpern, others"
+author: "Sam Robinson, Paul Galpern, et al."
 date: "03/04/2020"
 output: html_document
+bibliography: "/home/samuel/Documents/bibtexRefs/references.bib"
+csl: ecology-letters.csl
 ---
@@
 knitr::opts_chunk$set(echo = TRUE)
+library(knitr)
 ```
@@
 
-* We don't have a good understanding of what drives arthropod abundance
-  + Bees are generally driven by flower/nest abundance
+* We don't have a good understanding of what drives beneficial arthropod abundance
+  + Bees are generally driven by flower/nest substrate availability [@roulston2011]
   + Limited understanding of other arthropods
-  + Beetles are limited by water, food, oviposition sites, etc.
+  + Beetles are limited by water, food, and oviposition sites [@lovei1996]
   + Arachnids are similarly limited by food, shelter
 
-* Landscape structure can influence abundance of beneficial arthropods in agricultural areas
-  + No-till agriculture 
+* Landscape structure can influence abundance of beneficial arthropods in agricultural areas [@albrecht2010]
+  + No-till agriculture is better for some ground beetles [@busch_Msc]
   + How can we design landscapes to benefit both farmers and insects?
@@
   + Arthropods move between landscape components depending on their life history
-  + e.g. Carabid beetles are thought to reproduce in field margins, but adults feed in fields (Desender and Alderweireldt 1988, J. of App. Ent.)
-  + Counts are a proxy of activity density, not necessarily abundance
-  + Nevertheless, this is probably an OK measure (_need to justify this_)
-
+  + e.g. Carabid beetles are thought to reproduce in field margins, but adults feed in fields [@desender1988]
+  + Counts in pitfall traps are a proxy of activity density (not actual density), but this is probably an OK measure, at least within fields [@lang2000]
 * In this study, we used pitfall trap counts of three species of beneficial arthropod to determine how landscape composition affects activity density of arthropods
   + We hypothesized that:
-  1. Abundance of semi-natural land would result in increased arthropod abundance
-  2. Other things...
+  1. Abundance of semi-natural land (SNL) would result in increased arthropod abundance
+  2. Nearby SNL acts as a source of arthropods earlier in the season, and act as a sink later on, as arthropods migrate into margins to reproduce
 
@@
 
-##Data collection
+## Data collection
 
@@
 * To characterize landscape composition surrounding the traps, we used classified landscape data from AAFC
-  + Classifications are very accurate for fields (~90%), but less accurate for non-crop areas (~70%)
+  + Classifications are very accurate for fields (~90%), but less accurate for non-crop areas (~70%, [@AAFC_data])
   + Landscape studies often use the landscape composition within a circle of a fixed radius surrounding each point
@@
 
-##Statistics
+## Statistics
 
@@
   + In our case, the coefficients represent the effect of a given type of landscape cover, and are a smooth function of distance from the trap (i.e. $\beta_i = f(distance_i)$)
-  + This technique has been used by other authors; Galpern et al. called this ``onion-skin regression"
-  + We fit our functional regression models using _mgcv_ version XXX.
+  + This technique has been used by other authors; @galpern2020 called this ``onion-skin regression"
+  + We fit our functional regression models using _mgcv_ version 1.8-31.
+  + @ockinger2007 is a test
 
@@
 
+## _Pterostichus melanarius_
+
+![Landscape influence on _P. melanarius_ activity density](../figures/Pterostichus_melanarius_fixeff.png)
+
+## _Pardosa distincta_
+
+![Landscape influence on _P. distincta_ activity density](../figures/Pardosa_distincta_fixeff.png)
+
+## _Phalangium opilio_
+
+![Landscape influence on _P. opilio_ activity density](../figures/Opiliones_fixeff.png)
+
 # Discussion
+
+# References

### 2020-05-06 frAnalysis.R

@@ -306,8 +306,9 @@ p1 <- data.frame(day=min(datList$day):max(datList$day)) %>%
   labs(x='Day of Year',y='Activity')
 
 #Spatial smoother
-p2 <- with(datList,expand.grid(E=seq(from=min(E),to=max(E),length.out=100),N=seq(from=min(N),to=max(N),length.out=100))) %>% 
+p2 <- with(datList,expand.grid(E=seq(from=min(E)-5,to=max(E)+5,length.out=100),N=seq(from=min(N)-5,to=max(N)+5,length.out=100))) %>%
   smoothPred(mod3,whichSmooth=2) %>% 
+  filter(!exclude.too.far(E,N,datList$E,datList$N,0.1)) %>% 
   ggplot(aes(x=E,y=N))+geom_raster(aes(fill=pred))+
   geom_point(data=tempTrap,aes(x=easting,y=northing))+
   scale_fill_gradient(low='blue',high='red')+
@@ -426,6 +427,7 @@ p1 <- data.frame(day=min(datList$day):max(datList$day)) %>%
 #Spatial smoother
 p2 <- with(datList,expand.grid(E=seq(from=min(E),to=max(E),length.out=100),N=seq(from=min(N),to=max(N),length.out=100))) %>% 
   smoothPred(mod3,whichSmooth=2) %>% 
+  filter(!exclude.too.far(E,N,datList$E,datList$N,0.1)) %>% 
   ggplot(aes(x=E,y=N))+geom_raster(aes(fill=pred))+
   geom_point(data=tempTrap,aes(x=easting,y=northing))+
   scale_fill_gradient(low='blue',high='red')+
@@ -532,6 +534,7 @@ p1 <- data.frame(day=min(datList$day):max(datList$day)) %>%
 #Spatial smoother
 p2 <- with(datList,expand.grid(E=seq(from=min(E),to=max(E),length.out=100),N=seq(from=min(N),to=max(N),length.out=100))) %>% 
   smoothPred(mod3,whichSmooth=2) %>% 
+  filter(!exclude.too.far(E,N,datList$E,datList$N,0.1)) %>% 
   ggplot(aes(x=E,y=N))+geom_raster(aes(fill=pred))+
   geom_point(data=tempTrap,aes(x=easting,y=northing))+
   scale_fill_gradient(low='blue',high='red')+

### 2020-05-06 manuscript/manuscript_outline.Rmd
Continued on Results section

@@
 library(knitr)
+library(tidyverse)
+
+#Helper functions
+firstUpper <- function(x){
+  paste0(toupper(substring(x,1,1)),substring(x,2,nchar(x)))
+}
+
+#Rounds to dig, converts to character, anything 
+roundLess <- function(x,dig){
+  x <- as.character(round(x,dig))
+  x[x=='0'] <- paste0('<0.',strrep('0',dig-1),'1',collapse='')
+  return(x)
+}
+
 ```
@@
   + We fit our functional regression models using _mgcv_ version 1.8-31.
-  + @ockinger2007 is a test
 
@@
 
+* _P. melanarius_ activity density was strongly influenced by trap location and landscape composition.
+  + Canola crops had a higher activity density of _P. melanarius_ than any other trap location, indicating that (comparitively) low-density stands may allow faster movement of ground beetles.
+  + Ditches had the lowest level of activity density
+  + In landscape composition, proportion of urban land cover (roadside right-of-way) was the strongest predictor of activity density, and this varied across the season, with early-season (June) urban land acting as a sink, but becoming a source in the mid-season (July)
+  + trees and shrubs, pulse crops, and pasture.
+  + Overall wetland cover had a negative influence on _P. melanarius_ abundance, but only after mid-July, indicating that wetlands may act as a sink for _P. melanarius_ populations later in the season
+  + Finally, _P. melanarius_ had a very strong spatial component
+
+```{r PteMelCoefs, echo=FALSE, message=FALSE}
+load('../data/PteMelMod.Rdata')
+pmelRes <- summary(PteMelMod$mod3)
+linTerms <- pmelRes$p.table %>% as.data.frame() %>% 
+  rownames_to_column('loc') %>% 
+  mutate(loc=firstUpper(gsub('trapLoc','',loc))) %>% 
+  rename(p='Pr(>|z|)') %>% mutate(p=roundLess(p,3))
+
+smTerms <- pmelRes$s.table %>% as.data.frame() %>% 
+  rownames_to_column('Smoother') %>% 
+  rename(p='p-value') %>% mutate(p=roundLess(p,3)) %>% mutate_at(vars(2:3),roundLess,dig=2) 
+kable(linTerms,caption='Linear terms for _Pterostichus melanarius_',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
+        digits=c(1,2,2,2,2),align='rrrrl')
+kable(smTerms[c(1,2,4,5)],caption='Smooth terms for _Pterostichus melanarius_',col.names=c('Smoothing term','E.D.F.','$\\chi^2$','p'),
+        digits=c(1,2,2,2),align='rrll')
+
+```
+
 ![Landscape influence on _P. melanarius_ activity density](../figures/Pterostichus_melanarius_fixeff.png)
+
+![Temporal and spatial components of _P. melanarius_ activity density](../figures/Pterostichus_melanarius_raneff.png)
 
@@
 ![Landscape influence on _P. distincta_ activity density](../figures/Pardosa_distincta_fixeff.png)
+![Temporal and spatial components of _P. distincta_ activity density](../figures/Pardosa_distincta_raneff.png)
 
@@
 
+![Temporal and spatial components of _P. opilio_ activity density](../figures/Opiliones_raneff.png)
+
 # Discussion

### 2020-05-13 helperFunctions.R
Created helper function script

@@ -1,0 +1,187 @@
+# Helper functions for project
+
+#Function to display matrix (m) with row/column names (nam)
+# Useful for looking at correlation matrices
+matrixplot <- function(m,nam=NULL,mar=NULL,numSize=1,numCol='red'){
+  if(ncol(m)!=nrow(m)) stop('Matrix not square')
+  if(!is.null(nam)){
+    if(ncol(m)!=length(nam)) stop('Length of name vector != matrix dimension')
+  } else {
+    nam <- rep('',ncol(m))
+  }
+  n <- ncol(m) #Matrix dimensions
+  savepar <- par()
+  if(is.null(mar)) mar <- c(1,5,5,1)
+  par(mfrow=c(1,1),mar=mar)
+  #Dark colours indicate high multicollinearity
+  image(m[1:n,n:1],axes=F,col=gray.colors(12,start=0.2,end=1,rev=T))
+  mtext(text=nam[n:1], side=2, line=0.3, at=seq(0,1,length.out=nrow(m)), las=1, cex=0.8)
+  mtext(text=nam, side=3, line=0.3, at=seq(0,1,length.out=nrow(m)), las=2, cex=0.8)
+  
+  # #shadowtext trick from:
+  # #https://stackoverflow.com/questions/25631216/r-plots-is-there-any-way-to-draw-border-shadow-or-buffer-around-text-labels/39002911
+  # theta <-  seq(0, 2*pi, length.out=60) #Vector of angles to use
+  # r <- 0.15 #Proportion of character size to extend
+  # x0 <- r*strwidth('0')
+  # y0 <- r*strheight('0')
+  
+  if(numSize>0){
+    #Add row text
+    for(i in 1:n){ #Column of matrix to access
+      cpos <- (i-1)/(n-1) #Col position in figure
+      j <- 1:n #Rows of matrix to access
+      rpos <- ((j-1)/(n-1))[n:1] #Column position in figure
+      # #White background text
+      # for(k in 1:length(theta)){
+      #   text(cpos+cos(k)*x0,rpos+sin(k)*y0,round(m[j,i],2),col='white')
+      # }
+      text(cpos,rpos,round(m[j,i],2),col=numCol,cex=numSize) #Text
+      # }
+    }
+  }
+  par(mfrow=savepar$mfrow,mar=savepar$mar)
+}
+
+#Takes a df of arthropod counts at each site (unique to each spp), then runs 4 landscape-level models of abundance
[…]

### 2020-05-13 manuscript/manuscript_outline.Rmd
Added other figures, updated cross-refs

--- 2020-05-06 manuscript/manuscript_outline.Rmd
@@
 author: "Sam Robinson, Paul Galpern, et al."
-date: "03/04/2020"
-output: html_document
+date: "Spring 2020"
+output: bookdown::html_document2 
 bibliography: "/home/samuel/Documents/bibtexRefs/references.bib"
@@
 library(knitr)
+library(tidyverse)
+
+#Helper functions
+
+#Capitalize
+firstUpper <- function(x){
+  paste0(toupper(substring(x,1,1)),substring(x,2,nchar(x)))
+}
+
+#Rounds to dig digits, converts to character, anything less than digits becomes "<0.xx1"
+# Useful for tables
+roundLess <- function(x,dig){
+  x <- as.character(round(x,dig))
+  x[x=='0'] <- paste0('<0.',strrep('0',dig-1),'1',collapse='')
+  return(x)
+}
+
+#Adds ** around text (makes it bold in RMarkdown)
+boldRMD <- function(x) paste0('**',x,'**')
+
+#Load models
+load('../data/PteMelMod.Rdata')
+load('../data/ParDisMod.Rdata')
+load('../data/OpilioMod.Rdata')
+
 ```
@@
 
-![Landscape influence on _P. melanarius_ activity density](../figures/Pterostichus_melanarius_fixeff.png)
+* _P. melanarius_ activity density was strongly influenced by trap location and landscape composition (Tables \@ref(tab:PteMelCoefs-linTerms), \@ref(tab:PteMelCoefs-smoothTerms))
+  + Canola crops had a higher activity density of _P. melanarius_ than any other trap location, while roadside ditches had the lowest (Figure \@ref(fig:PteMelCoefs-fixeff)a)
+  + This indicates that low-density stands of canola may allow faster movement of ground beetles.
+  + In landscape composition, proportion of urban land cover (roadside right-of-way) was the strongest predictor of activity density, and this varied across the season, with urban land acting as a sink during June, but becoming a source during July (Figure \@ref(fig:PteMelCoefs-fixeff)f); trees and shrubs followed a similar pattern (Figure \@ref(fig:PteMelCoefs-fixeff)d)
+  + Wetland cover had a negative influence on _P. melanarius_ abundance, but only after mid-July, indicating that wetlands may act as a sink for _P. melanarius_ populations later in the season
+
+```{r PteMelCoefs-linTerms, echo=FALSE, warning=FALSE}
+pmelRes <- summary(PteMelMod$mod3)
+linTerms <- pmelRes$p.table %>% as.data.frame() %>% 
+  rownames_to_column('loc') %>% 
+  mutate(loc=firstUpper(gsub('trapLoc','',loc))) %>% 
+  rename(p='Pr(>|z|)') %>% mutate(p=roundLess(p,3)) %>% 
+  mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
+  mutate(p=ifelse(sig,boldRMD(p),p)) %>% select(-sig) #Make text bold
+kable(linTerms,caption='\\label{tab:PteMelCoefs-linTerms} Linear terms for _Pterostichus melanarius_. Line',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
+        digits=c(1,2,2,2,2),align='rrrrl')
+```
+
+```{r PteMelCoefs-smoothTerms, echo=FALSE, warning=FALSE}
+pmelRes <- summary(PteMelMod$mod3)
+smTerms <- pmelRes$s.table %>% as.data.frame() %>% 
+  rownames_to_column('Smoother') %>% 
+  rename(p='p-value') %>% mutate(p=roundLess(p,3)) %>% mutate_at(vars(2:4),roundLess,dig=2) %>% 
+  mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
+  mutate(p=ifelse(sig,boldRMD(p),p)) %>% select(-sig) #Make text bold
+kable(smTerms[c(1,2,4,5)],caption='\\label{tab:PteMelCoefs-smoothTerms} Smooth terms for _Pterostichus melanarius_, with effective degrees of freedom, Chi-squared coefficient, and p-value.
+_s_ indicates a thin-plate spline, _ti_ indicates a tensor-product interaction.
+All terms except for day and (E,N) are functional regression fits.',col.names=c('Smoothing term','Eff.
+_df_','$\\chi^2$','_p_'),
+        digits=c(1,2,2,2),align='rrll')
+```
+
+```{r PteMelCoefs-fixeff, echo=FALSE, fig.cap='\\label{fig:PteMelCoefs-fixeff} Landscape influence on _Pterostichus melanarius_ activity density.
+Lines/dots represent means, and bars/shaded regions represent 95% confidence intervals (1.96 x SE).
+Dashed line on panels b-f represents zero effect.
+Coloured regions represent early-, mid-, and late-season effects (red, green, blue)'}
+  include_graphics('../figures/Pterostichus_melanarius_fixeff.png')
+```
+
+*  _P.
+melanarius_ had a very strong random temporal and spatial component (both p<0.001), indicating that phenology and local geographic factors were strong drivers of ground beetle abundance (Figure \@ref(fig:PteMelCoefs-raneff))
+  + This could be related to climatic drivers (rainfall, growing degree days), or could simply represent a single yearly realization of a spatio-temporal random field
+
+```{r PteMelCoefs-raneff, echo=FALSE, fig.cap='\\label{fig:PteMelCoefs-raneff} Temporal and spatial components of _Pterostichus melanarius_ activity density'}
+  include_graphics('../figures/Pterostichus_melanarius_raneff.png')
+```
 
@@
 
-![Landscape influence on _P. distincta_ activity density](../figures/Pardosa_distincta_fixeff.png)
+```{r ParDisCoefs-linTerms, echo=FALSE, warning=FALSE}
+pmelRes <- summary(ParDisMod$mod3)
+linTerms <- pmelRes$p.table %>% as.data.frame() %>% 
+  rownames_to_column('loc') %>% 
+  mutate(loc=firstUpper(gsub('trapLoc','',loc))) %>% 
+  rename(p='Pr(>|z|)') %>% mutate(p=roundLess(p,3)) %>% 
+  mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
+  mutate(p=ifelse(sig,boldRMD(p),p)) %>% select(-sig) #Make text bold
+kable(linTerms,caption='\\label{tab:ParDisCoefs-linTerms} Linear terms for _Pardosa distincta_. Line',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
+        digits=c(1,2,2,2,2),align='rrrrl')
+```
+
+```{r ParDisCoefs-smoothTerms, echo=FALSE, warning=FALSE}
+pmelRes <- summary(ParDisMod$mod3)
+smTerms <- pmelRes$s.table %>% as.data.frame() %>% 
+  rownames_to_column('Smoother') %>% 
+  rename(p='p-value') %>% mutate(p=roundLess(p,3)) %>% mutate_at(vars(2:4),roundLess,dig=2) %>% 
+  mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
+  mutate(p=ifelse(sig,boldRMD(p),p)) %>% select(-sig) #Make text bold
+kable(smTerms[c(1,2,4,5)],caption='\\label{tab:ParDisCoefs-smoothTerms} Smooth terms for _Pardosa distincta_, with effective degrees of freedom, Chi-squared coefficient, and p-value.
+_s_ indicates a thin-plate spline, _ti_ indicates a tensor-product interaction.
+All terms except for day and (E,N) are functional regression fits.',col.names=c('Smoothing term','Eff.
+_df_','$\\chi^2$','_p_'),
+        digits=c(1,2,2,2),align='rrll')
+```
+
+```{r ParDisCoefs-fixeff, echo=FALSE, fig.cap='\\label{fig:ParDisCoefs-fixeff} Landscape influence on _Pardosa distincta_ activity density.
+Lines/dots represent means, and bars/shaded regions represent 95% confidence intervals (1.96 x SE).
+Dashed line on panels b-f represents zero effect.
+Coloured regions represent early-, mid-, and late-season effects (red, green, blue)'}
+  include_graphics('../figures/Pardosa_distincta_fixeff.png')
+```
+
+```{r ParDisCoefs-raneff, echo=FALSE, fig.cap='\\label{fig:ParDisCoefs-raneff} Temporal and spatial components of _Pardosa distincta_ activity density'}
+  include_graphics('../figures/Pardosa_distincta_raneff.png')
+```
 
@@
 
-![Landscape influence on _P. opilio_ activity density](../figures/Opiliones_fixeff.png)
+```{r OpilioCoefs-linTerms, echo=FALSE, warning=FALSE}
+pmelRes <- summary(OpilioMod$mod3)
+linTerms <- pmelRes$p.table %>% as.data.frame() %>% 
+  rownames_to_column('loc') %>% 
+  mutate(loc=firstUpper(gsub('trapLoc','',loc))) %>% 
+  rename(p='Pr(>|z|)') %>% mutate(p=roundLess(p,3)) %>% 
+  mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
+  mutate(p=ifelse(sig,boldRMD(p),p)) %>% select(-sig) #Make text bold
+kable(linTerms,caption='\\label{tab:OpilioCoefs-linTerms} Linear terms for _Phalangium opilio_. Line',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
+        digits=c(1,2,2,2,2),align='rrrrl')
+```
+
+```{r OpilioCoefs-smoothTerms, echo=FALSE, warning=FALSE}
+pmelRes <- summary(OpilioMod$mod3)
+smTerms <- pmelRes$s.table %>% as.data.frame() %>% 
+  rownames_to_column('Smoother') %>% 
+  rename(p='p-value') %>% mutate(p=roundLess(p,3)) %>% mutate_at(vars(2:4),roundLess,dig=2) %>% 
+  mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
+  mutate(p=ifelse(sig,boldRMD(p),p)) %>% select(-sig) #Make text bold
+kable(smTerms[c(1,2,4,5)],caption='\\label{tab:OpilioCoefs-smoothTerms} Smooth terms for _Phalangium opilio_, with effective degrees of freedom, Chi-squared coefficient, and p-value.
+_s_ indicates a thin-plate spline, _ti_ indicates a tensor-product interaction.
+All terms except for day and (E,N) are functional regression fits.',col.names=c('Smoothing term','Eff.
+_df_','$\\chi^2$','_p_'),
+        digits=c(1,2,2,2),align='rrll')
+```
+
+```{r OpilioCoefs-fixeff, echo=FALSE, fig.cap='\\label{fig:OpilioCoefs-fixeff} Landscape influence on _Phalangium opilio_ activity density.
+Lines/dots represent means, and bars/shaded regions represent 95% confidence regions.
+Dashed line on panels b-f represents zero effect.
+Coloured regions represent early-, mid-, and late-season effects (red, green, blue)'}
+  include_graphics('../figures/Opiliones_fixeff.png')
+```
+
+```{r OpilioCoefs-raneff, echo=FALSE, fig.cap='\\label{fig:OpilioCoefs-raneff} Temporal and spatial components of _Phalangium opilio_ activity density'}
+  include_graphics('../figures/Opiliones_raneff.png')
 

### 2020-05-15 manuscript/manuscript_outline.Rmd
Worked on Methods/Results

@@
 boldRMD <- function(x) paste0('**',x,'**')
+#Inverse of above
+unboldRMD <- function(x) gsub('\\**','',x)
 
@@
 load('../data/OpilioMod.Rdata')
+
+#Extract Pterostichus melanarius results
+pmelRes <- summary(PteMelMod$mod3)
+pmelLinTerms <- pmelRes$p.table %>% as.data.frame() %>% 
+  rownames_to_column('loc') %>% 
+  mutate(loc=firstUpper(gsub('trapLoc','',loc))) %>% 
+  rename(p='Pr(>|z|)') %>% mutate(p=roundLess(p,3)) %>% 
+  mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
+  mutate(p=ifelse(sig,boldRMD(p),p)) %>% select(-sig) #Make text bold
+pmelSmTerms <- pmelRes$s.table %>% as.data.frame() %>% 
+  rownames_to_column('Smoother') %>% 
+  rename(p='p-value') %>% mutate(p=roundLess(p,3)) %>% mutate_at(vars(2:4),roundLess,dig=2) %>% 
+  mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
+  mutate(p=ifelse(sig,boldRMD(p),p)) %>% select(-sig) #Make text bold
+
+#Extract Pardosa distincta results
+pdisRes <- summary(ParDisMod$mod3)
+pdisLinTerms <- pdisRes$p.table %>% as.data.frame() %>% 
+  rownames_to_column('loc') %>% 
+  mutate(loc=firstUpper(gsub('trapLoc','',loc))) %>% 
+  rename(p='Pr(>|z|)') %>% mutate(p=roundLess(p,3)) %>% 
+  mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
+  mutate(p=ifelse(sig,boldRMD(p),p)) %>% select(-sig) #Make text bold
+pdisSmTerms <- pdisRes$s.table %>% as.data.frame() %>% 
+  rownames_to_column('Smoother') %>% 
+  rename(p='p-value') %>% mutate(p=roundLess(p,3)) %>% mutate_at(vars(2:4),roundLess,dig=2) %>% 
+  mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
+  mutate(p=ifelse(sig,boldRMD(p),p)) %>% select(-sig) #Make text bold
+
+#Extract Phalangium opilio results
+opilRes <- summary(OpilioMod$mod3)
+opilLinTerms <- opilRes$p.table %>% as.data.frame() %>% 
+  rownames_to_column('loc') %>% 
+  mutate(loc=firstUpper(gsub('trapLoc','',loc))) %>% 
+  rename(p='Pr(>|z|)') %>% mutate(p=roundLess(p,3)) %>% 
+  mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
+  mutate(p=ifelse(sig,boldRMD(p),p)) %>% select(-sig) #Make text bold
+opilSmTerms <- opilRes$s.table %>% as.data.frame() %>% 
+  rownames_to_column('Smoother') %>% 
+  rename(p='p-value') %>% mutate(p=roundLess(p,3)) %>% mutate_at(vars(2:4),roundLess,dig=2) %>% 
+  mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
+  mutate(p=ifelse(sig,boldRMD(p),p)) %>% select(-sig) #Make text bold
 
@@
   + Landscape studies often use the landscape composition within a circle of a fixed radius surrounding each point
-  + However, the radius of the circle depends on the grain of the landscape that is relevant to the abundance of a given organism.
+  + However, the radius of the circle depends on the grain of the landscape that is relevant to the abundance of a given organism (@addicott1987)
   + Instead, we divided the landscape into annuli (rings) surrounding each trap location.
@@
 
-* Function-on-scalar (FOS) regression is a special type of linear model ($\hat{y}=X\beta$), where the values of the coefficients ($\beta$) are defined by a smooth function
-  + In our case, the coefficients represent the effect of a given type of landscape cover, and are a smooth function of distance from the trap (i.e. $\beta_i = f(distance_i)$)
-  + This technique has been used by other authors; @galpern2020 called this ``onion-skin regression"
+* Scalar-on-function (SoF) regression is a special type of linear model ($\hat{y}=X\beta$), where the columns of the model matrix $X$ contain some continuous predictor of the scalar $y$ (e.g.
+biomass as a function of monthly average temperatures), and the values of the coefficients ($\beta$) are modeled as a smooth function $f(x)$ of the continuous predictors
+  + In our case, each column represents the landscape composition within each annulus, with increasing radii away from the location of the trap, and the coefficients are a smooth function of distance ($\beta_i = f(distance_i)$), meaning that the coefficients represent the (additive) effect of a given type of landscape cover and  from the trap
+  + This avoids the fundamental problem of choosing an optimal radius of landscape composition, and allows the possibility that the size of the landscape ``grain" relevant to a given organism may change over the course of its life stages (@addicott1987, @lima1996)
+  + This technique has been used by other authors (``onion-skin regression" in @galpern2020)
   + We fit our functional regression models using _mgcv_ version 1.8-31.
+
+<!-- This part could be pared down. Probably not necessary to discuss several models if the full one is the only important one. -->
+* We used 4 nested models to gauge the relative importance of landscape composition for arthropod activity density
+  + Model 1 consisted of a temporal and spatial smoothers (``random effects"), necessary to account for the underlying spatiotemporal structure of the data 
+  <!-- Smoothers can be thought of as random effects, where the coefficients follow a probability distribution defined by a fixed smoothing coefficient $\lambda$ - see @wood2017 for the Bayesian/Frequentist details of this -->
+  + Model 2 added a local cover term, to account for the specific effect of local cover on activity density
+  + Model 3 added a smoother term for the landscape rings, modeling the effect of non-crop cover at varying distances on activity density
+  + Model 4, similar to model 3, modeled the effect of all underlying cover classes (crop and non-crop) at varying distances
+  + To account for different lengths of trap exposure, log-days since trap placement was used as a fixed effect with its slope held at 1 (``offset" variable)
+  + All models were fit using a negative binomial distribution, and model fits were compared using conditional Akaike's Information Criteria @wood2017
+
+Model    | Independent variables                                     | $r$ Formula
+-------- | --------------------------------------------------------- | -----------------------------------------------
+1        | Phenology + Geography                                     | Activity Density ~ s(Day) + s(E,N)
+2        | Phenology + Geography + Local cover                       | Activity Density ~ s(Day) + s(E,N) + Trap Location
+3        | Phenology + Geography + Local cover + Landscape (general) | Activity Density ~ s(Day) + s(E,N) + Trap Location + s(Non-crop Cover)                         
+4        | Phenology + Geography + Local cover + Landscape (specific)| Activity Density ~ s(Day) + s(E,N) + Trap Location + s(Cover 1) + s(Cover 2) + ... + s(Cover n)
 
@@
   + In landscape composition, proportion of urban land cover (roadside right-of-way) was the strongest predictor of activity density, and this varied across the season, with urban land acting as a sink during June, but becoming a source during July (Figure \@ref(fig:PteMelCoefs-fixeff)f); trees and shrubs followed a similar pattern (Figure \@ref(fig:PteMelCoefs-fixeff)d)
-  + Wetland cover had a negative influence on _P. melanarius_ abundance, but only after mid-July, indicating that wetlands may act as a sink for _P. melanarius_ populations later in the season
+  + Wetland cover had a negative influence on _P. melanarius_ activity density, but only after mid-July, indicating that wetlands may act as a sink for _P. melanarius_ populations later in the season
 
 ```{r PteMelCoefs-linTerms, echo=FALSE, warning=FALSE}
-pmelRes <- summary(PteMelMod$mod3)
-linTerms <- pmelRes$p.table %>% as.data.frame() %>% 
-  rownames_to_column('loc') %>% 
-  mutate(loc=firstUpper(gsub('trapLoc','',loc))) %>% 
-  rename(p='Pr(>|z|)') %>% mutate(p=roundLess(p,3)) %>% 
-  mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
-  mutate(p=ifelse(sig,boldRMD(p),p)) %>% select(-sig) #Make text bold
-kable(linTerms,caption='\\label{tab:PteMelCoefs-linTerms} Linear terms for _Pterostichus melanarius_. Line',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
+kable(pmelLinTerms,caption='\\label{tab:PteMelCoefs-linTerms} Linear terms for _Pterostichus melanarius_.',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
         digits=c(1,2,2,2,2),align='rrrrl')
@@
 ```{r PteMelCoefs-smoothTerms, echo=FALSE, warning=FALSE}
-pmelRes <- summary(PteMelMod$mod3)
-smTerms <- pmelRes$s.table %>% as.data.frame() %>% 
-  rownames_to_column('Smoother') %>% 
-  rename(p='p-value') %>% mutate(p=roundLess(p,3)) %>% mutate_at(vars(2:4),roundLess,dig=2) %>% 
-  mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
-  mutate(p=ifelse(sig,boldRMD(p),p)) %>% select(-sig) #Make text bold
-kable(smTerms[c(1,2,4,5)],caption='\\label{tab:PteMelCoefs-smoothTerms} Smooth terms for _Pterostichus melanarius_, with effective degrees of freedom, Chi-squared coefficient, and p-value.
+kable(pmelSmTerms[c(1,2,4,5)],caption='\\label{tab:PteMelCoefs-smoothTerms} Smooth terms for _Pterostichus melanarius_, with effective degrees of freedom, Chi-squared coefficient, and p-value.
 _s_ indicates a thin-plate spline, _ti_ indicates a tensor-product interaction.
-All terms except for day and (E,N) are functional regression fits.',col.names=c('Smoothing term','Eff.
+All terms except for day and (E,N) are functional regression fits.
+**NAMES OF SMOOTHING TERMS ARE CONFUSING - SHOULD BE SIMPLIFIED**',col.names=c('Smoothing term','Eff.
 _df_','$\\chi^2$','_p_'),
@@
 *  _P.
-melanarius_ had a very strong random temporal and spatial component (both p<0.001), indicating that phenology and local geographic factors were strong drivers of ground beetle abundance (Figure \@ref(fig:PteMelCoefs-raneff))
+melanarius_ had a very strong random temporal and spatial component (both p<0.001), indicating that phenology and local geographic factors were strong drivers of ground beetle activity density (Figure \@ref(fig:PteMelCoefs-raneff))
   + This could be related to climatic drivers (rainfall, growing degree days), or could simply represent a single yearly realization of a spatio-temporal random field
@@
 
+* _Pardosa distincta_ activity density was also strongly influenced by trap location and landscape composition (Tables \@ref(tab:ParDisCoefs-linTerms), \@ref(tab:ParDisCoefs-smoothTerms)), similar to _P.
+melanarius_.
+  + However, _P. distincta_ had far lower activity density in canola than any other cover type (Figure \@ref(fig:ParDisCoefs-fixeff)a).
+  + Interestingly, nearby canola appeared to act as a source of _P.
+distincta_ for surrounding landscape features, as activity density was positively related to the nearby proportion of canola (p = `r with(pdisSmTerms,unboldRMD(p[Smoother=='s(distMat):Canola']))`), at least early in the season (p = `r with(pdisSmTerms,unboldRMD(p[Smoother=='s(endDayMat):Canola']))`)
+  + Pulse crops had a similar effect, acting as a source of _P.
+distincta_ early in the season, and acting as a mild sink later in the season (p = `r with(pdisSmTerms,unboldRMD(p[Smoother=='ti(distMat,endDayMat):Pulses']))`, Figure \@ref(fig:ParDisCoefs-fixeff)d)
+  + Grassland acted as a weak source, at least earlier on in the season (p = `r with(pdisSmTerms,unboldRMD(p[Smoother=='s(endDayMat):Grassland']))`), and urban cover acted as a weak sink at intermediate distances (~600m)
+  + Similar to _P.
+melanarius_, _P.
+distincta_ activity density had a very strong temporal and spatial component (both p = `r with(pdisSmTerms,unboldRMD(p[grepl('E,N',Smoother)]))`, Figure \@ref(fig:ParDisCoefs-raneff))
+
 ```{r ParDisCoefs-linTerms, echo=FALSE, warning=FALSE}
-pmelRes <- summary(ParDisMod$mod3)
-linTerms <- pmelRes$p.table %>% as.data.frame() %>% 
-  rownames_to_column('loc') %>% 
-  mutate(loc=firstUpper(gsub('trapLoc','',loc))) %>% 
-  rename(p='Pr(>|z|)') %>% mutate(p=roundLess(p,3)) %>% 
-  mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
-  mutate(p=ifelse(sig,boldRMD(p),p)) %>% select(-sig) #Make text bold
-kable(linTerms,caption='\\label{tab:ParDisCoefs-linTerms} Linear terms for _Pardosa distincta_. Line',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
+kable(pdisLinTerms,caption='\\label{tab:ParDisCoefs-linTerms} Linear terms for _Pardosa distincta_. Line',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
         digits=c(1,2,2,2,2),align='rrrrl')
@@
 ```{r ParDisCoefs-smoothTerms, echo=FALSE, warning=FALSE}
-pmelRes <- summary(ParDisMod$mod3)
-smTerms <- pmelRes$s.table %>% as.data.frame() %>% 
-  rownames_to_column('Smoother') %>% 
-  rename(p='p-value') %>% mutate(p=roundLess(p,3)) %>% mutate_at(vars(2:4),roundLess,dig=2) %>% 
-  mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
-  mutate(p=ifelse(sig,boldRMD(p),p)) %>% select(-sig) #Make text bold
-kable(smTerms[c(1,2,4,5)],caption='\\label{tab:ParDisCoefs-smoothTerms} Smooth terms for _Pardosa distincta_, with effective degrees of freedom, Chi-squared coefficient, and p-value.
+kable(pdisSmTerms[c(1,2,4,5)],caption='\\label{tab:ParDisCoefs-smoothTerms} Smooth terms for _Pardosa distincta_, with effective degrees of freedom, Chi-squared coefficient, and p-value.
 _s_ indicates a thin-plate spline, _ti_ indicates a tensor-product interaction.
@@
 
+* _Phalangium opilio_ activity density was strongly influenced by trap location, with pivot corners and wetlands having the highest activity density (p = `r with(opilLinTerms, unboldRMD(p[loc=='Pivot']))`, `r with(opilLinTerms, unboldRMD(p[loc=='Wetland']))`)
+  + However, unlike _P.
+melanarius_ or _P.
+pardosa_, _P.
+opilio_ was not strongly influenced by any land cover type, except for Pasture (p = `r with(opilSmTerms,unboldRMD(p[Smoother=='ti(distMat,endDayMat):Pasture']))`)
+  + This specific effect of pasture was not large, as the model using non-crop cover performed similarly ($\Delta AIC$= `r with(OpilioMod, sprintf("%.2f",AIC(mod3)-AIC(mod4)))`)
+  + In fact, both models that used landscape composition performed worse than the model with only trap location ($\Delta AIC$= `r with(OpilioMod, sprintf("%.2f",AIC(mod2)-AIC(mod3)))`,`r with(OpilioMod, sprintf("%.2f",AIC(mod2)-AIC(mod4)))`)
+
 ```{r OpilioCoefs-linTerms, echo=FALSE, warning=FALSE}
-pmelRes <- summary(OpilioMod$mod3)
-linTerms <- pmelRes$p.table %>% as.data.frame() %>% 
-  rownames_to_column('loc') %>% 
-  mutate(loc=firstUpper(gsub('trapLoc','',loc))) %>% 
-  rename(p='Pr(>|z|)') %>% mutate(p=roundLess(p,3)) %>% 
-  mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
-  mutate(p=ifelse(sig,boldRMD(p),p)) %>% select(-sig) #Make text bold
-kable(linTerms,caption='\\label{tab:OpilioCoefs-linTerms} Linear terms for _Phalangium opilio_. Line',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
+kable(opilLinTerms,caption='\\label{tab:OpilioCoefs-linTerms} Linear terms for _Phalangium opilio_. Line',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
         digits=c(1,2,2,2,2),align='rrrrl')
@@
 ```{r OpilioCoefs-smoothTerms, echo=FALSE, warning=FALSE}
-pmelRes <- summary(OpilioMod$mod3)
-smTerms <- pmelRes$s.table %>% as.data.frame() %>% 
-  rownames_to_column('Smoother') %>% 
-  rename(p='p-value') %>% mutate(p=roundLess(p,3)) %>% mutate_at(vars(2:4),roundLess,dig=2) %>% 
-  mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
-  mutate(p=ifelse(sig,boldRMD(p),p)) %>% select(-sig) #Make text bold
-kable(smTerms[c(1,2,4,5)],caption='\\label{tab:OpilioCoefs-smoothTerms} Smooth terms for _Phalangium opilio_, with effective degrees of freedom, Chi-squared coefficient, and p-value.
+
+kable(opilSmTerms[c(1,2,4,5)],caption='\\label{tab:OpilioCoefs-smoothTerms} Smooth terms for _Phalangium opilio_, with effective degrees of freedom, Chi-squared coefficient, and p-value.
 _s_ indicates a thin-plate spline, _ti_ indicates a tensor-product interaction.
@@
   include_graphics('../figures/Opiliones_raneff.png')
+```
 
@@
 
+* Lemme tell ya 
+  + We found all kinds of stuff
+  + Boy oh boy is it cool
+
 # References

### 2020-05-15 manuscript/manuscript_outline.Rmd
Added concurve terms back into model
- Need to figure out what to do about this. Is regularization enough?

@@
 library(tidyverse)
+library(mgcv)
 
@@
   mutate(p=ifelse(sig,boldRMD(p),p)) %>% select(-sig) #Make text bold
+
+#Get variance components
+varComp <- rownames_to_column(data.frame(gam.vcomp(PteMelMod$mod3),spp='Pterostichus melanarius'),'term') %>% 
+  bind_rows(rownames_to_column(data.frame(gam.vcomp(ParDisMod$mod3),spp='Pardosa distincta'),'term')) %>% 
+  bind_rows(rownames_to_column(data.frame(gam.vcomp(OpilioMod$mod3),spp='Phalangium opilio'),'term')) %>%
+  mutate(term=factor(term,levels=names(PteMelMod$mod3$sp)))
 
@@
 opilio_ was not strongly influenced by any land cover type, except for Pasture (p = `r with(opilSmTerms,unboldRMD(p[Smoother=='ti(distMat,endDayMat):Pasture']))`)
-  + This specific effect of pasture was not large, as the model using non-crop cover performed similarly ($\Delta AIC$= `r with(OpilioMod, sprintf("%.2f",AIC(mod3)-AIC(mod4)))`)
-  + In fact, both models that used landscape composition performed worse than the model with only trap location ($\Delta AIC$= `r with(OpilioMod, sprintf("%.2f",AIC(mod2)-AIC(mod3)))`,`r with(OpilioMod, sprintf("%.2f",AIC(mod2)-AIC(mod4)))`)
+  + This effect of this specific land cover type was not very large, as the model using non-crop cover performed similarly ($\Delta AIC$= `r with(OpilioMod, sprintf("%.2f",AIC(mod3)-AIC(mod4)))`)
+  + In fact, the models that used landscape composition performed worse than the model with only trap location ($\Delta AIC$= `r with(OpilioMod, sprintf("%.2f",AIC(mod2)-AIC(mod3)))`,`r with(OpilioMod, sprintf("%.2f",AIC(mod2)-AIC(mod4)))`), indicating a weak effect of landscape composition
+  + The temporal and spatial components, as in the other two species, were very strong (both p = `r with(opilSmTerms,unboldRMD(p[grepl('E,N',Smoother)]))`, and Easting
 
@@
 
+```{r varComp, echo=FALSE, fig.cap='\\label{fig:varComp} Variance components of all models'}
+ggplot(varComp,aes(x=term,y=std.dev))+geom_col()+theme_classic()+facet_wrap(~spp,ncol=1,scales='free_y')+
+  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
+```
+
 # Discussion

### 2020-05-15 frAnalysis.R

@@ -31,7 +31,7 @@ oRingMat2Prop$NonCrop <- Reduce('+',oRingMat2Prop[names(oRingMat2Prop) %in% nonC
 
 #Trees + Shrubs
 oRingMat2Prop$TreeShrub <- oRingMat2Prop$Shrubland + oRingMat2Prop$Forest
-oRingMat2Prop$Shrubland <- NULL; oRingMat2Prop$Forest <- NULL
+# oRingMat2Prop$Shrubland <- NULL; oRingMat2Prop$Forest <- NULL
 # #Water + Wetland
 # oRingMat2Prop$WetlandWater <- oRingMat2Prop$Wetland + oRingMat2Prop$Water
 # oRingMat2Prop$Wetland <- NULL; oRingMat2Prop$Water <- NULL
@@ -40,7 +40,8 @@ oRingMat2Prop$Shrubland <- NULL; oRingMat2Prop$Forest <- NULL
 modFormulas <- 'count~offset(log(trapdays))+s(day,k=10,bs=basisFun)+s(E,N,k=50,bs=basisFun)' #Temporal + spatial
 # modFormulas <- paste0(modFormulas,'+ti(N,E,day,k=5,bs=basisFun)') # Add spatiotemporal interaction
 modFormulas[c(2,3,4)] <- paste0(modFormulas[1],'+trapLoc-1')
-mod3Vars <- c('Grassland','Canola','Pasture','Wetland','TreeShrub','Pulses','Urban') #Variables for mod3
+# mod3Vars <- c('Grassland','Canola','Pasture','Wetland','TreeShrub','Pulses','Urban') #Variables for mod3
+mod3Vars <- c('Grassland','Cereal','Canola','Pasture','Wetland','Forest','Shrubland','Pulses','Urban') #Variables for mod3
 #Cereal may be causing problems in estimation - collinear with canola
 for(i in 1:length(mod3Vars)){ #Add in specified terms (s and ti)
   #Main effects + interaction (s + ti)
@@ -66,7 +67,7 @@ arth %>% filter(grepl('PF',BTID),arthOrder=='Coleoptera') %>%
 #Select only P. melanarius
 tempArth <- arth %>% filter(genus=='Pterostichus',species=='melanarius') %>% group_by(BTID) %>% summarize(n=n())
 
-# PteMelMod <- runMods(tempArth,trap,nnDistMat,oRingMat2Prop,formulas=modFormulas,basisFun='ts'); beep(1)
[…]

### 2020-05-15 helperFunctions.R

@@ -14,7 +14,8 @@ matrixplot <- function(m,nam=NULL,mar=NULL,numSize=1,numCol='red'){
   if(is.null(mar)) mar <- c(1,5,5,1)
   par(mfrow=c(1,1),mar=mar)
   #Dark colours indicate high multicollinearity
-  image(m[1:n,n:1],axes=F,col=gray.colors(12,start=0.2,end=1,rev=T))
+  image(t(apply(m,2,rev)),axes=F,col=gray.colors(12,start=0.2,end=1,rev=T))
+  
   mtext(text=nam[n:1], side=2, line=0.3, at=seq(0,1,length.out=nrow(m)), las=1, cex=0.8)
   mtext(text=nam, side=3, line=0.3, at=seq(0,1,length.out=nrow(m)), las=2, cex=0.8)
   

### 2020-05-19 frAnalysis.R
Added concurvity plots

@@ -29,8 +29,8 @@ oRingMat2Prop$NonCrop <- Reduce('+',oRingMat2Prop[names(oRingMat2Prop) %in% nonC
 
 #Combine classes that are collinear/represent similar things
 
-#Trees + Shrubs
-oRingMat2Prop$TreeShrub <- oRingMat2Prop$Shrubland + oRingMat2Prop$Forest
+##Trees + Shrubs - try without this for now
+# oRingMat2Prop$TreeShrub <- oRingMat2Prop$Shrubland + oRingMat2Prop$Forest
 # oRingMat2Prop$Shrubland <- NULL; oRingMat2Prop$Forest <- NULL
 # #Water + Wetland
 # oRingMat2Prop$WetlandWater <- oRingMat2Prop$Wetland + oRingMat2Prop$Water
@@ -43,6 +43,8 @@ modFormulas[c(2,3,4)] <- paste0(modFormulas[1],'+trapLoc-1')
 # mod3Vars <- c('Grassland','Canola','Pasture','Wetland','TreeShrub','Pulses','Urban') #Variables for mod3
 mod3Vars <- c('Grassland','Cereal','Canola','Pasture','Wetland','Forest','Shrubland','Pulses','Urban') #Variables for mod3
 #Cereal may be causing problems in estimation - collinear with canola
+
+#Assemble formulas:
 for(i in 1:length(mod3Vars)){ #Add in specified terms (s and ti)
   #Main effects + interaction (s + ti)
   modFormulas[3] <- paste0(modFormulas[3],"+ s(distMat,by=",mod3Vars[i],",bs=basisFun)")
@@ -98,10 +100,13 @@ termNames <- rownames(checkMC)
 # termNames <- gsub('ti\\(distMat(,endDayMat)?\\)','ti',termNames)
 # termNames <- gsub('s\\(endjulian\\)','s:time',gsub('s\\(easting,northing\\)','s:space',termNames))
 # termNames <- gsub('ti\\(northing,easting,endjulian\\)','ti:spacetime',termNames)
-matrixplot(checkMC,mar=c(1, 10, 10, 1),termNames)
-matrixplot(checkMC[4:nrow(checkMC),4:nrow(checkMC)],mar=c(1, 10, 10, 1),termNames[4:nrow(checkMC)]) #Only landscape terms
[…]

### 2020-05-22 manuscript/manuscript_outline.Rmd
Added refs as sub-reference-database
- Tried using Water as a cover class, and it was highly "significant", but it gave some very strange results - not sure if model properly converged

@@
 output: bookdown::html_document2 
-bibliography: "/home/samuel/Documents/bibtexRefs/references.bib"
+bibliography: refs.bib
 csl: ecology-letters.csl
@@
   + Each annulus was 30 m thick, and had inner radii ranging from 30 to 1470m, in increments of 30m.
-  + Using functional regression (see below), we were able to incorporate landscape information at different distance, allowing us to assess the impact of both local and regional landscape composition
+  + Using functional regression [@ramsay2004], we were able to incorporate landscape information at different distance, allowing us to assess the impact of both local and regional landscape composition
 
@@
 
-* Scalar-on-function (SoF) regression is a special type of linear model ($\hat{y}=X\beta$), where the columns of the model matrix $X$ contain some continuous predictor of the scalar $y$ (e.g.
-biomass as a function of monthly average temperatures), and the values of the coefficients ($\beta$) are modeled as a smooth function $f(x)$ of the continuous predictors
-  + In our case, each column represents the landscape composition within each annulus, with increasing radii away from the location of the trap, and the coefficients are a smooth function of distance ($\beta_i = f(distance_i)$), meaning that the coefficients represent the (additive) effect of a given type of landscape cover and  from the trap
-  + This avoids the fundamental problem of choosing an optimal radius of landscape composition, and allows the possibility that the size of the landscape ``grain" relevant to a given organism may change over the course of its life stages (@addicott1987, @lima1996)
-  + This technique has been used by other authors (``onion-skin regression" in @galpern2020)
+* We used functional regression to model the effect of landscape composition on activity density 
+  +  Scalar-on-function (SoF) regression is a special type of functional linear regression model ($\hat{y}=X\beta$), where the columns of the model matrix $X$ contain some continuous predictor of the scalar $y$ (e.g.
+biomass in a plot (scalar) as a function of monthly average temperatures (vector)), and the values of the coefficients ($\beta$) are modeled as a smooth function $f(x)$ of the predictors
+  + In our case, each column represents the proportion of a given landscape cover class within each annulus, with increasing radii away from the location of the trap, and the coefficients are a smooth function of distance ($\beta_i = f(distance_i)$), meaning that the coefficients represent the (additive) effect of a given type of landscape cover and  from the trap
+  + This avoids the fundamental problem of choosing an optimal radius of landscape composition, and allows the possibility that the size of the landscape ``grain" relevant to a given organism may change over the course of its life stages [@addicott1987, @lima1996]
+  + This technique has been used by other authors [@yen2014, @galpern2020]
   + We fit our functional regression models using _mgcv_ version 1.8-31.
+
+* Some of the landscape terms in our model were strongly concurved, so we removed them from the model, or combined them into a single term
+  + Concurvity is an non-linear analogue of multicollinearity that can bias estimates of standard errors [@buja1989, @ramsay2003]
+  + There is no agreed-upon threshold of unacceptable concurvity, but 0.5 is commonly used [@dominici2002, @ramsay2003] 
+  + We found that some landscape terms were strongly concurved (Figure \@ref(fig:concurvity)), namely shrubland and forest (max: 0.71), canola and cereal (max: 0.74), and wetland and grassland (max: 0.63)
+  +
+
+```{r concurvity, echo=FALSE, fig.cap='\\label{fig:concurvity} Concurvity estimates for top land cover classes'}  
+  include_graphics('../figures/coverCorPlots/concurvityEstimate.png')
+```
 
@@
   + Model 1 consisted of a temporal and spatial smoothers (``random effects"), necessary to account for the underlying spatiotemporal structure of the data 
-  <!-- Smoothers can be thought of as random effects, where the coefficients follow a probability distribution defined by a fixed smoothing coefficient $\lambda$ - see @wood2017 for the Bayesian/Frequentist details of this -->
+  + Smoothers can be thought of as random effects, where the coefficients follow a probability distribution defined by a fixed smoothing coefficient $\lambda$ [@wood2017] 
   + Model 2 added a local cover term, to account for the specific effect of local cover on activity density

### 2020-05-22 extractGeoData.R

@@ -222,6 +222,8 @@ sapply(oRingMat2,sum)/sum(sapply(oRingMat2,sum))
 # Convert to proportions
 oRingMat2Prop <- lapply(oRingMat2,function(x) x/Reduce('+',oRingMat2))
 
+#Make figure of land cover distributions
+png('./figures/oRingPlot2_AAFC.png',800,1200,pointsize=20)
 par(mfrow=c(5,2))
 for(i in 1:10){
   covClass <- sapply(oRingMat2,sum)[order(sapply(oRingMat2,sum),decreasing=T)][i]
@@ -234,6 +236,7 @@ for(i in 1:10){
   }
 }
 par(mfrow=c(1,1))
+dev.off()
 
 #Save list of matrices
 save(oRingMat2,file='./data/geoDataAAFC.Rdata')

### 2020-05-22 frAnalysis.R

@@ -27,21 +27,21 @@ oRingMat2Prop <-  lapply(oRingMat2,function(x) x/Reduce('+',oRingMat2))
 nonCropClasses <- c('Grassland','Pasture','Wetland','Urban','Shrubland','Forest','Water','Barren','Fallow')
 oRingMat2Prop$NonCrop <- Reduce('+',oRingMat2Prop[names(oRingMat2Prop) %in% nonCropClasses])
 
-#Combine classes that are collinear/represent similar things
+#Combine classes that are concurved/represent similar things
+#Trees + Shrubs
+oRingMat2Prop$TreeShrub <- oRingMat2Prop$Shrubland + oRingMat2Prop$Forest
+oRingMat2Prop$Shrubland <- NULL; oRingMat2Prop$Forest <- NULL
 
-##Trees + Shrubs - try without this for now
-# oRingMat2Prop$TreeShrub <- oRingMat2Prop$Shrubland + oRingMat2Prop$Forest
-# oRingMat2Prop$Shrubland <- NULL; oRingMat2Prop$Forest <- NULL
-# #Water + Wetland
-# oRingMat2Prop$WetlandWater <- oRingMat2Prop$Wetland + oRingMat2Prop$Water
-# oRingMat2Prop$Wetland <- NULL; oRingMat2Prop$Water <- NULL
+#Grassland + Wetland
+oRingMat2Prop$GrassWetland <- oRingMat2Prop$Wetland + oRingMat2Prop$Grassland
+oRingMat2Prop$Wetland <- NULL; oRingMat2Prop$Grassland <- NULL
 
 #Create model formulas
 modFormulas <- 'count~offset(log(trapdays))+s(day,k=10,bs=basisFun)+s(E,N,k=50,bs=basisFun)' #Temporal + spatial
 # modFormulas <- paste0(modFormulas,'+ti(N,E,day,k=5,bs=basisFun)') # Add spatiotemporal interaction
 modFormulas[c(2,3,4)] <- paste0(modFormulas[1],'+trapLoc-1')
-# mod3Vars <- c('Grassland','Canola','Pasture','Wetland','TreeShrub','Pulses','Urban') #Variables for mod3
-mod3Vars <- c('Grassland','Cereal','Canola','Pasture','Wetland','Forest','Shrubland','Pulses','Urban') #Variables for mod3
[…]

### 2020-05-22 prelimAnalysis.R

@@ -41,10 +41,9 @@ siteSf <- st_as_sf(site,coords=c('lon','lat'),crs=4326) %>%
 
 #Add coordinate system to trap df
 trapSf <- trap %>% left_join(select(site,BLID:lon),by='BLID') %>% 
-  rename('latSite'='lat','lonSite'='lon') %>% 
   #Replace trap lat/lon with site lat/lon if not recorded
   mutate(latTrap=ifelse(latTrap==0,latSite,latTrap),lonTrap=ifelse(lonTrap==0,lonSite,lonTrap)) %>% 
-  st_as_sf(coords=c('lonTrap','latTrap'),crs=4326) %>% 
+  st_as_sf(coords=c('lon','lat'),crs=4326) %>% 
   st_transform(3403)
 
 #Bounding box for 2016:2018 sites (excludes Grande Prairie)
@@ -105,5 +104,36 @@ yearNumbers <- arthNumbers %>%
   theme(axis.text=element_text(size=5),axis.text.x=element_text(angle=90,vjust=0.3,hjust=1)))
   # ggsave('./figures/maps/arthDistMap.png',p1,scale=1.5)
 
-rm(p1)
+#Pterostichus sampling (2017-2018)
+arth %>% select(BTID:BLID,year,genus,species) %>% filter(genus=='Pterostichus',species=='melanarius') %>% 
+  group_by(BTID) %>% summarize(count=n()) %>%
+  right_join(filter(trapSf,startYear==2017|startYear==2018),by='BTID') %>% 
+  mutate(count=ifelse(is.na(count),0,count),deployedWeeks=deployedhours/(24*7)) %>%
+  filter(!is.na(deployedWeeks)) %>% 
+  # ggplot()+geom_histogram(aes(x=deployedWeeks))
+  ggplot()+geom_sf(aes(geometry=geometry,size=count/deployedWeeks),alpha=0.1)+
+  facet_grid(trapType~startYear)
+
+#Opiliones sampling
+arth %>% select(BTID:BLID,year,genus,species) %>% filter(genus=='Phalangium',species=='opilio') %>% 
+  group_by(BTID) %>% summarize(count=n()) %>%
+  right_join(filter(trapSf,startYear==2017|startYear==2018),by='BTID') %>% 
+  mutate(count=ifelse(is.na(count),0,count),deployedWeeks=deployedhours/(24*7)) %>%
+  filter(!is.na(deployedWeeks)) %>% 
[…]

### 2020-05-25 manuscript/manuscript_outline.Rmd
Redid figures. Started to add P. opilio refs

@@
 
-* We used a system of pitfall traps installed in ditches, field margins, wetlands, and in-field sites across southern Alberta in 2017 (_need a map here_)
-  + Traps at in-field sites were installed 20, 100, 200m (?) along a transect from the nearest non-crop feature (wetland, grassland, pivot)
-  + Specimens were collected from the traps every 14 days, on average (SD: 2.9), and were identified to species
+* We used a system of pitfall traps installed at roadsides, field margins, wetlands, and in-field sites across southern Alberta in 2017 (_need a map here_)
+  + Pitfall traps consisted of 582 mL Solo® cups buried up to the rim, partially filled with ethylene glycol
+  + All traps had 2cm (?) chicken wire mounted over the rim to prevent small vertebrates from falling into the traps
+  + Traps at roadsides were located 5m (?) from the roads, while traps at in-field sites were installed 20, 100, 200m (?) along a transect from the nearest non-crop feature (wetland, grassland, pivot)
+  + Specimens were collected from the traps every 14 days (SD: 2.9), and were identified to species
 
-* To characterize landscape composition surrounding the traps, we used classified landscape data from AAFC
-  + Classifications are very accurate for fields (~90%), but less accurate for non-crop areas (~70%, [@AAFC_data])
-  + Landscape studies often use the landscape composition within a circle of a fixed radius surrounding each point
-  + However, the radius of the circle depends on the grain of the landscape that is relevant to the abundance of a given organism (@addicott1987)
-  + Instead, we divided the landscape into annuli (rings) surrounding each trap location.
+* We used three species of predatory arthropods that were present at very high abundances in the traps
+  + _Pterostichus melanarius_ is predatory introduced ground beetle that is a wide-ranging generalist [@carcamo1994, @larsen2003, @busch_Msc]
+  + It is commonly found in untilled grasslands [@purtauf2005] and grassy field margins may act as larval habitat [@desender1988]
+  + _Pardosa distincta_ is a species of wolf spider that is common across the Canadian prairies, and is commonly found in ungrazed pastures [@carcamo2014]
+  + Finally, _Phallangium opilio_ is a widely-distributed harvestment from the order Opilio
+  +
+
+* We modeled arthropod activity density as a function of landscape composition using generalized additive models @wood2017
+    + To account for different lengths of trap exposure, log-days since trap placement was used as a fixed effect with its slope held at 1 (``offset" variable)
+    + All models were fit using a negative binomial distribution
+    + We fit our functional regression models using _mgcv_ version 1.8-31
+
+* To characterize landscape composition surrounding the traps, we used classified landscape data from @AAFC_data
+  + AAFC cropland landscape classifications are very accurate for cultivated fields (~90%), but are less accurate for non-crop areas (~70%)
+  + We extracted the landscape composition within a circle of a fixed radius surrounding each trap location 
+  + However, the radius of the circle necessary to characterize the landscape depends on the ``grain" of the landscape that is relevant to the abundance of a given organism (@addicott1987)
+  + Therefore, we divided the landscape into annuli (rings) surrounding each trap location.
   + Each annulus was 30 m thick, and had inner radii ranging from 30 to 1470m, in increments of 30m.
+
   + Using functional regression [@ramsay2004], we were able to incorporate landscape information at different distance, allowing us to assess the impact of both local and regional landscape composition
@@
   + This technique has been used by other authors [@yen2014, @galpern2020]
-  + We fit our functional regression models using _mgcv_ version 1.8-31.
 
@@
   + We found that some landscape terms were strongly concurved (Figure \@ref(fig:concurvity)), namely shrubland and forest (max: 0.71), canola and cereal (max: 0.74), and wetland and grassland (max: 0.63)
-  +
 
@@
 
-<!-- This part could be pared down. Probably not necessary to discuss several models if the full one is the only important one. -->
-* We used 4 nested models to gauge the relative importance of landscape composition for arthropod activity density
-  + Model 1 consisted of a temporal and spatial smoothers (``random effects"), necessary to account for the underlying spatiotemporal structure of the data 
-  + Smoothers can be thought of as random effects, where the coefficients follow a probability distribution defined by a fixed smoothing coefficient $\lambda$ [@wood2017] 
-  + Model 2 added a local cover term, to account for the specific effect of local cover on activity density
-  + Model 3 added a smoother term for the landscape rings, modeling the effect of non-crop cover at varying distances on activity density
-  + Model 4, similar to model 3, modeled the effect of all underlying cover classes (crop and non-crop) at varying distances
-  + To account for different lengths of trap exposure, log-days since trap placement was used as a fixed effect with its slope held at 1 (``offset" variable)
-  + All models were fit using a negative binomial distribution, and model fits were compared using conditional Akaike's Information Criteria @wood2017
+<!-- * We used 4 nested models to gauge the relative importance of landscape composition for arthropod activity density -->
+<!--   + Model 1 consisted of a temporal and spatial smoothers (``random effects"), necessary to account for the underlying spatiotemporal structure of the data  -->
+<!--   + Smoothers can be thought of as random effects, where the coefficients follow a probability distribution defined by a fixed smoothing coefficient $\lambda$ [@wood2017]  -->
+<!--   + Model 2 added a local cover term, to account for the specific effect of local cover on activity density -->
+<!--   + Model 3 added a smoother term for the landscape rings, modeling the effect of non-crop cover at varying distances on activity density -->
+<!--   + Model 4, similar to model 3, modeled the effect of all underlying cover classes (crop and non-crop) at varying distances -->
 
-Model    | Independent variables                                     | $r$ Formula
--------- | --------------------------------------------------------- | -----------------------------------------------
-1        | Phenology + Geography                                     | Activity Density ~ s(Day) + s(E,N)
-2        | Phenology + Geography + Local cover                       | Activity Density ~ s(Day) + s(E,N) + Trap Location
-3        | Phenology + Geography + Local cover + Landscape (general) | Activity Density ~ s(Day) + s(E,N) + Trap Location + s(Non-crop Cover)                         
-4        | Phenology + Geography + Local cover + Landscape (specific)| Activity Density ~ s(Day) + s(E,N) + Trap Location + s(Cover 1) + s(Cover 2) + ... + s(Cover n)
+<!-- Model    | Independent variables                                     | $r$ Formula -->
+<!-- -------- | --------------------------------------------------------- | ----------------------------------------------- -->
+<!-- 1        | Phenology + Geography                                     | Activity Density ~ s(Day) + s(E,N) -->
+<!-- 2        | Phenology + Geography + Local cover                       | Activity Density ~ s(Day) + s(E,N) + Trap Location -->
+<!-- 3        | Phenology + Geography + Local cover + Landscape (general) | Activity Density ~ s(Day) + s(E,N) + Trap Location + s(Non-crop Cover)                          -->
+<!-- 4        | Phenology + Geography + Local cover + Landscape (specific)| Activity Density ~ s(Day) + s(E,N) + Trap Location + s(Cover 1) + s(Cover 2) + ... + s(Cover n) -->
 

### 2020-05-25 frAnalysis.R

@@ -55,16 +55,8 @@ for(i in 1:length(mod3Vars)){ #Add in specified terms (s and ti)
 }
 modFormulas[4] <- paste0(modFormulas[2],'+s(distMat,by=NonCrop,bs=basisFun)+s(endDayMat,by=NonCrop,bs=basisFun)+ti(distMat,endDayMat,by=NonCrop,bs=basisFun)')
 
+
 # Pterostichus melanarius ----------------------------------
-
-#What spp of beetles are present?
-arth %>% filter(grepl('PF',BTID),arthOrder=='Coleoptera') %>%
-  mutate(genSpp=paste(genus,species,sep=' ')) %>% group_by(family,genus,species) %>% 
-  summarize(n=n()) %>% arrange(genus,desc(n)) %>% data.frame()
-
-arth %>% filter(grepl('PF',BTID),arthOrder=='Coleoptera') %>%
-  group_by(genus) %>% summarize(n=n()) %>% data.frame() %>% 
-  arrange(desc(n))
 
 #Select only P. melanarius
 tempArth <- arth %>% filter(genus=='Pterostichus',species=='melanarius') %>% group_by(BTID) %>% summarize(n=n())
@@ -230,19 +222,13 @@ detach(PteMelMod)
 
 # Pardosa distincta (wolf spider) -----------------------------------------------------------------
 
-#What spp of spiders are present?
-arth %>% filter(grepl('PF',BTID),arthOrder=='Araneae') %>%
-  mutate(genSpp=paste(genus,species,sep=' ')) %>% group_by(family,genus,species) %>% 
-  summarize(n=n()) %>% arrange(family,genus,desc(n)) %>% data.frame()
-#Lots of Pardosa distincta and P. moesta. Could try all lycosids at once, but this might be a stretch
-
 # #Select only wolf spiders
 # tempArth <- arth %>% filter(family=='Lycosidae') %>% group_by(BTID) %>% summarize(n=n())
 
 #Select only Pardosa distincta
 tempArth <- arth %>% filter(genus=='Pardosa',species=='distincta') %>% group_by(BTID) %>% summarize(n=n())
 
-# #Takes way longer to run. 5-10 mins +
+#Takes way longer to run. 5-10 mins +
[…]

### 2020-05-25 prelimAnalysis.R

@@ -9,6 +9,35 @@ theme_set(theme_classic())
 theme_update(panel.border=element_rect(size=1,fill=NA),axis.line=element_blank()) #Better for maps
 library(sf)
 
+# Abundance tables --------------------------------------------------------
+
+#What spp of beetles are present in pitfall traps?
+arth %>% filter(grepl('PF',BTID),arthOrder=='Coleoptera') %>%
+  mutate(genSpp=paste(genus,species,sep=' ')) %>% group_by(family,genus,species) %>% 
+  summarize(count=n()) %>% arrange(desc(count)) %>% 
+  unite(genSpp,genus,species,sep=' ') %>% 
+  mutate(genSpp=factor(genSpp,levels=genSpp)) %>% 
+  ggplot(aes(x=genSpp,y=count))+geom_col()+scale_y_sqrt()+
+  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
+
+#Tons of Pterostichus melanarius
+
+#Genera
+arth %>% filter(grepl('PF',BTID),arthOrder=='Coleoptera') %>%
+  group_by(genus) %>% summarize(count=n()) %>% data.frame() %>% 
+  arrange(desc(count)) %>% mutate(genus=factor(genus,levels=genus)) %>% 
+  ggplot(aes(x=genus,y=count))+geom_col()+
+  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
+
+
+
+#What spp of spiders are present in pitfall traps?
+arth %>% filter(grepl('PF',BTID),arthOrder=='Araneae') %>%
+  mutate(genSpp=paste(genus,species,sep=' ')) %>% group_by(family,genus,species) %>% 
+  summarize(n=n()) %>% arrange(family,genus,desc(n)) %>% data.frame()
+#Lots of Pardosa distincta and P. moesta. Could try all lycosids at once, but this might be a stretch
+
+
 # Basic maps of sites/trap distribution -----------------------------------
 
 #Calgary-centred projection from Paul - seems to be problems when using this

### 2020-05-27 manuscript/manuscript_outline.Rmd
Added refs. Tried out appendix section (somewhat successful)

@@
 date: "Spring 2020"
-output: bookdown::html_document2 
 bibliography: refs.bib
 csl: ecology-letters.csl
+output:
+  bookdown::html_document2:
+    pandoc_args: ["--include-after-body=manuscript_appendix.md"]
 ---
@@
 
-```{r varComp, echo=FALSE, fig.cap='\\label{fig:varComp} Variance components of all models'}
-ggplot(varComp,aes(x=term,y=std.dev))+geom_col()+theme_classic()+facet_wrap(~spp,ncol=1,scales='free_y')+
-  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
-```
-
 # Discussion
 
-* Lemme tell ya 
-  + We found all kinds of stuff
-  + Boy oh boy is it cool
+* Pterostichus responded to landscape composition
 

### 2020-05-27 prelimAnalysis.R

@@ -17,19 +17,17 @@ arth %>% filter(grepl('PF',BTID),arthOrder=='Coleoptera') %>%
   summarize(count=n()) %>% arrange(desc(count)) %>% 
   unite(genSpp,genus,species,sep=' ') %>% 
   mutate(genSpp=factor(genSpp,levels=genSpp)) %>% 
+  filter(genSpp!='Pterostichus melanarius') %>% #Strip out P. melanarius
   ggplot(aes(x=genSpp,y=count))+geom_col()+scale_y_sqrt()+
   theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
-
 #Tons of Pterostichus melanarius
 
 #Genera
-arth %>% filter(grepl('PF',BTID),arthOrder=='Coleoptera') %>%
+arth %>% filter(grepl('PF',BTID),arthOrder=='Coleoptera') %>% filter(species!='melanarius') %>% 
   group_by(genus) %>% summarize(count=n()) %>% data.frame() %>% 
   arrange(desc(count)) %>% mutate(genus=factor(genus,levels=genus)) %>% 
   ggplot(aes(x=genus,y=count))+geom_col()+
   theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
-
-
 
 #What spp of spiders are present in pitfall traps?
 arth %>% filter(grepl('PF',BTID),arthOrder=='Araneae') %>%

### 2020-05-27 manuscript/manuscript_outline.Rmd
Converted to PDF.
- Need to update refs and tables

@@
 ---
-title: "Landscape composition and beneficial insects"
-author: "Sam Robinson, Paul Galpern, et al."
+title: Landscape composition and beneficial insects
+subtitle: I like carabids
+author:
+  - name: Samuel Robinson
+    email: samuel.robinson@ucalgary.ca
+    affiliation: University of Calgary
+    footnote: 1
+  - name: Paul Galpern
+    email: paul.galpern@ucalgary.ca
+    affiliation: University of Calgary
+address:
+  - code: University of Calgary
+    address: 2500 University Drive NW, Calgary, AB, Canada
+footnote:
+  - code: 1
+    text: "Corresponding Author"
 date: "Spring 2020"
+abstract: Ground-dwelling arthropods are important generalist predators in prairie agro-ecosystems.
+However, we don't know what types of landscape features they live in.
+Some may act as sources of arthropods during some parts of the year, and sinks during others.
+We examined 3 widely-distributed species of arthropods, and used functional regression to examine their habitat preferences.
+We found that trees/shrubs, and roadside grasses acted as sources of arthropods.
+Other features did not function as significant sources or sinks.
+Farmers should keep these landscape intact in order to preserve populations of generalist predators to defend their crops.
+
 bibliography: refs.bib
@@
 output: 
-  bookdown::html_document2:
-    pandoc_args: ["--include-after-body=manuscript_appendix.md"]
+  bookdown::pdf_book:
+    base_format: rticles::elsevier_article
+    toc: false
+    fig_caption: false
+header-includes: 
+  \usepackage{float} \floatplacement{figure}{H} 
+  \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
+
 ---
+
+<!-- This argument in YAML header adds "manuscript_appendix.md" after document -->
+<!-- output: -->
+<!--   bookdown::html_document2: -->
+<!--     pandoc_args: ["--include-after-body=manuscript_appendix.md"] -->
 
@@
 
-#Adds ** around text (makes it bold in RMarkdown)
-boldRMD <- function(x) paste0('**',x,'**')
-#Inverse of above
-unboldRMD <- function(x) gsub('\\**','',x)
+boldRMD <- function(x) paste0('**',x,'**') #Makes text bold in rMarkdown
+boldLaTeX <- function(x) paste0('\\textbf{',x,'}') #Makes text bold in LaTeX
 
@@
   mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
-  mutate(p=ifelse(sig,boldRMD(p),p)) %>% select(-sig) #Make text bold
+  mutate(pTable=ifelse(sig,boldLaTeX(p),p)) %>% select(-sig) #Make text bold
 pmelSmTerms <- pmelRes$s.table %>% as.data.frame() %>% 
@@
   mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
-  mutate(p=ifelse(sig,boldRMD(p),p)) %>% select(-sig) #Make text bold
+  mutate(pTable=ifelse(sig,boldLaTeX(p),p)) %>% select(-sig) #Make text bold
 
@@
   mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
-  mutate(p=ifelse(sig,boldRMD(p),p)) %>% select(-sig) #Make text bold
+  mutate(pTable=ifelse(sig,boldLaTeX(p),p)) %>% select(-sig) #Make text bold
 pdisSmTerms <- pdisRes$s.table %>% as.data.frame() %>% 
@@
   mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
-  mutate(p=ifelse(sig,boldRMD(p),p)) %>% select(-sig) #Make text bold
+  mutate(pTable=ifelse(sig,boldLaTeX(p),p)) %>% select(-sig) #Make text bold
 opilSmTerms <- opilRes$s.table %>% as.data.frame() %>% 
@@
   + Pitfall traps consisted of 582 mL Solo® cups buried up to the rim, partially filled with ethylene glycol
-  + All traps had 2cm (?) chicken wire mounted over the rim to prevent small vertebrates from falling into the traps
-  + Traps at roadsides were located 5m (?) from the roads, while traps at in-field sites were installed 20, 100, 200m (?) along a transect from the nearest non-crop feature (wetland, grassland, pivot)
+  + All traps had 2cm chicken wire mounted over the rim to prevent small vertebrates from falling into the traps
+  + Traps at roadsides were located 5m from the roads, while traps at in-field sites were installed 20, 100, 200m (?) along a transect from the nearest non-crop feature (wetland, grassland, pivot)
   + Specimens were collected from the traps every 14 days (SD: 2.9), and were identified to species
@@
   + _Pardosa distincta_ is a species of wolf spider that is common across the Canadian prairies, and is commonly found in ungrazed pastures [@carcamo2014]
-  + Finally, _Phallangium opilio_ is a widely-distributed harvestment from the order Opilio
-  +
+  + Finally, _Phallangium opilio_ is a widely-distributed harvestmen from the order Opilio
 
@@
     + All models were fit using a negative binomial distribution
-    + We fit our functional regression models using _mgcv_ version 1.8-31
+    + We fit our functional regression models using _mgcv_ version `r packageVersion('mgcv')`
 
@@
   + We extracted the landscape composition within a circle of a fixed radius surrounding each trap location 
-  + However, the radius of the circle necessary to characterize the landscape depends on the ``grain" of the landscape that is relevant to the abundance of a given organism (@addicott1987)
+  + However, the radius of the circle necessary to characterize the landscape depends on the ``grain" of the landscape that is relevant to the abundance of a given organism [@addicott1987]
   + Therefore, we divided the landscape into annuli (rings) surrounding each trap location.
   + Each annulus was 30 m thick, and had inner radii ranging from 30 to 1470m, in increments of 30m.
-
   + Using functional regression [@ramsay2004], we were able to incorporate landscape information at different distance, allowing us to assess the impact of both local and regional landscape composition
@@
   + In our case, each column represents the proportion of a given landscape cover class within each annulus, with increasing radii away from the location of the trap, and the coefficients are a smooth function of distance ($\beta_i = f(distance_i)$), meaning that the coefficients represent the (additive) effect of a given type of landscape cover and  from the trap
-  + This avoids the fundamental problem of choosing an optimal radius of landscape composition, and allows the possibility that the size of the landscape ``grain" relevant to a given organism may change over the course of its life stages [@addicott1987, @lima1996]
+  + This avoids the fundamental problem of choosing an optimal radius of landscape composition, and allows the possibility that the size of the landscape ``grain" relevant to a given organism may change over the course of its life stages [@addicott1987 @lima1996]
   + This technique has been used by other authors [@yen2014, @galpern2020]
@@
   + We found that some landscape terms were strongly concurved (Figure \@ref(fig:concurvity)), namely shrubland and forest (max: 0.71), canola and cereal (max: 0.74), and wetland and grassland (max: 0.63)
-
-```{r concurvity, echo=FALSE, fig.cap='\\label{fig:concurvity} Concurvity estimates for top land cover classes'}  
-  include_graphics('../figures/coverCorPlots/concurvityEstimate.png')
-```
 
@@
 ```{r PteMelCoefs-linTerms, echo=FALSE, warning=FALSE}
-kable(pmelLinTerms,caption='\\label{tab:PteMelCoefs-linTerms} Linear terms for _Pterostichus melanarius_.',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
-        digits=c(1,2,2,2,2),align='rrrrl')
+pmelLinTerms %>% select(-p) %>% 
+  kable(.,caption='Linear terms for \\emph{Pterostichus melanarius}',
+      col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
+      digits=c(1,2,2,2,2),align='rrrrl',escape=FALSE)
 ```
@@
 ```{r PteMelCoefs-smoothTerms, echo=FALSE, warning=FALSE}
-kable(pmelSmTerms[c(1,2,4,5)],caption='\\label{tab:PteMelCoefs-smoothTerms} Smooth terms for _Pterostichus melanarius_, with effective degrees of freedom, Chi-squared coefficient, and p-value.
-_s_ indicates a thin-plate spline, _ti_ indicates a tensor-product interaction.
-All terms except for day and (E,N) are functional regression fits.
-**NAMES OF SMOOTHING TERMS ARE CONFUSING - SHOULD BE SIMPLIFIED**',col.names=c('Smoothing term','Eff.
-_df_','$\\chi^2$','_p_'),
-        digits=c(1,2,2,2),align='rrll')
+
+pmelSmTerms %>% select(-Ref.df,-p) %>% 
+  kable(.,caption='Smooth terms for \\emph{Pterostichus melanarius}.
+\\emph{s} indicates a thin-plate spline, \\emph{ti} indicates a tensor-product interaction.
+All terms except for day and (E,N) are functional regression fits.',
+      col.names=c('Smoothing term','Eff. _df_','$\\chi^2$','_p_'),
+      digits=c(1,2,2,2),align='rrll',escape=TRUE)
 ```
@@
   + Interestingly, nearby canola appeared to act as a source of _P.
-distincta_ for surrounding landscape features, as activity density was positively related to the nearby proportion of canola (p = `r with(pdisSmTerms,unboldRMD(p[Smoother=='s(distMat):Canola']))`), at least early in the season (p = `r with(pdisSmTerms,unboldRMD(p[Smoother=='s(endDayMat):Canola']))`)
+distincta_ for surrounding landscape features, as activity density was positively related to the nearby proportion of canola (p = `r with(pdisSmTerms,pTable[Smoother=='s(distMat):Canola'])`), at least early in the season (p = `r with(pdisSmTerms,pTable[Smoother=='s(endDayMat):Canola'])`)
   + Pulse crops had a similar effect, acting as a source of _P.
-distincta_ early in the season, and acting as a mild sink later in the season (p = `r with(pdisSmTerms,unboldRMD(p[Smoother=='ti(distMat,endDayMat):Pulses']))`, Figure \@ref(fig:ParDisCoefs-fixeff)d)
-  + Grassland acted as a weak source, at least earlier on in the season (p = `r with(pdisSmTerms,unboldRMD(p[Smoother=='s(endDayMat):Grassland']))`), and urban cover acted as a weak sink at intermediate distances (~600m)
+distincta_ early in the season, and acting as a mild sink later in the season (p = `r with(pdisSmTerms,pTable[Smoother=='ti(distMat,endDayMat):Pulses'])`, Figure \@ref(fig:ParDisCoefs-fixeff)d)
+  + Grassland acted as a weak source, at least earlier on in the season (p = `r with(pdisSmTerms,pTable[Smoother=='s(endDayMat):Grassland'])`), and urban cover acted as a weak sink at intermediate distances (~600m)
   + Similar to _P.
 melanarius_, _P.
-distincta_ activity density had a very strong temporal and spatial component (both p = `r with(pdisSmTerms,unboldRMD(p[grepl('E,N',Smoother)]))`, Figure \@ref(fig:ParDisCoefs-raneff))
+distincta_ activity density had a very strong temporal and spatial component (both p = `r with(pdisSmTerms,pTable[grepl('E,N',Smoother)])`, Figure \@ref(fig:ParDisCoefs-raneff))
 
 ```{r ParDisCoefs-linTerms, echo=FALSE, warning=FALSE}
-kable(pdisLinTerms,caption='\\label{tab:ParDisCoefs-linTerms} Linear terms for _Pardosa distincta_. Line',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
+pdisLinTerms %>% select(-p) %>% 
+  kable(.,caption='\\label{tab:ParDisCoefs-linTerms} Linear terms for _Pardosa distincta_. Line',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
         digits=c(1,2,2,2,2),align='rrrrl')
@@
 ```{r ParDisCoefs-smoothTerms, echo=FALSE, warning=FALSE}
-kable(pdisSmTerms[c(1,2,4,5)],caption='\\label{tab:ParDisCoefs-smoothTerms} Smooth terms for _Pardosa distincta_, with effective degrees of freedom, Chi-squared coefficient, and p-value.
-_s_ indicates a thin-plate spline, _ti_ indicates a tensor-product interaction.
-All terms except for day and (E,N) are functional regression fits.',col.names=c('Smoothing term','Eff.
-_df_','$\\chi^2$','_p_'),
-        digits=c(1,2,2,2),align='rrll')
+pdisSmTerms %>% select(-Ref.df,-p) %>% 
+  kable(.,caption='Smooth terms for \\emph{Pardosa distincta}.
+\\emph{s} indicates a thin-plate spline, \\emph{ti} indicates a tensor-product interaction.
+All terms except for day and (E,N) are functional regression fits.',
+        col.names=c('Smoothing term','Eff. _df_','$\\chi^2$','_p_'),
+        digits=c(1,2,2,2),align='rrll',escape=TRUE)
 ```
@@
 
+## _Pardosa moesta_
+
+```{r ParMoeCoefs-linTerms, echo=FALSE, warning=FALSE}
+pdisLinTerms %>% select(-p) %>% 
+  kable(.,caption='\\label{tab:ParMoeCoefs-linTerms} Linear terms for _Pardosa moesta_. Line',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
+        digits=c(1,2,2,2,2),align='rrrrl')
+```
+
+```{r ParMoeCoefs-smoothTerms, echo=FALSE, warning=FALSE}
+pdisSmTerms %>% select(-Ref.df,-p) %>% 
+  kable(.,caption='\\label{tab:ParMoeCoefs-smoothTerms} Smooth terms for _Pardosa moesta_.
+\\emph{s} indicates a thin-plate spline, \\emph{ti} indicates a tensor-product interaction.
+All terms except for day and (E,N) are functional regression fits.',
+        col.names=c('Smoothing term','Eff. _df_','$\\chi^2$','_p_'),
+        digits=c(1,2,2,2),align='rrll')
+```
+
+```{r ParMoeCoefs-fixeff, echo=FALSE, fig.cap='\\label{fig:ParMoeCoefs-fixeff} Landscape influence on _Pardosa moesta_ activity density.
+Lines/dots represent means, and bars/shaded regions represent 95% confidence intervals (1.96 x SE).
+Dashed line on panels b-f represents zero effect.
+Coloured regions represent early-, mid-, and late-season effects (red, green, blue)'}
+  include_graphics('../figures/Pardosa_moesta_fixeff.png')
+```
+
+```{r ParMoeCoefs-raneff, echo=FALSE, fig.cap='\\label{fig:ParMoeCoefs-raneff} Temporal and spatial components of _Pardosa moesta_ activity density'}
+  include_graphics('../figures/Pardosa_moesta_raneff.png')
+```
+
 ## _Phalangium opilio_
 
-* _Phalangium opilio_ activity density was strongly influenced by trap location, with pivot corners and wetlands having the highest activity density (p = `r with(opilLinTerms, unboldRMD(p[loc=='Pivot']))`, `r with(opilLinTerms, unboldRMD(p[loc=='Wetland']))`)
+* _Phalangium opilio_ activity density was strongly influenced by trap location, with pivot corners and wetlands having the highest activity density (p = `r with(opilLinTerms, pTable[loc=='Pivot'])`, `r with(opilLinTerms, pTable[loc=='Wetland'])`)
   + However, unlike _P.
@@
 pardosa_, _P.
-opilio_ was not strongly influenced by any land cover type, except for Pasture (p = `r with(opilSmTerms,unboldRMD(p[Smoother=='ti(distMat,endDayMat):Pasture']))`)
+opilio_ was not strongly influenced by any land cover type, except for Pasture (p = `r with(opilSmTerms,pTable[Smoother=='ti(distMat,endDayMat):Pasture'])`)
   + This effect of this specific land cover type was not very large, as the model using non-crop cover performed similarly ($\Delta AIC$= `r with(OpilioMod, sprintf("%.2f",AIC(mod3)-AIC(mod4)))`)
   + In fact, the models that used landscape composition performed worse than the model with only trap location ($\Delta AIC$= `r with(OpilioMod, sprintf("%.2f",AIC(mod2)-AIC(mod3)))`,`r with(OpilioMod, sprintf("%.2f",AIC(mod2)-AIC(mod4)))`), indicating a weak effect of landscape composition
-  + The temporal and spatial components, as in the other two species, were very strong (both p = `r with(opilSmTerms,unboldRMD(p[grepl('E,N',Smoother)]))`, and Easting
+  + The temporal and spatial components, as in the other two species, were very strong (both p = `r with(opilSmTerms,pTable[grepl('E,N',Smoother)])`, and Easting
 
 ```{r OpilioCoefs-linTerms, echo=FALSE, warning=FALSE}
-kable(opilLinTerms,caption='\\label{tab:OpilioCoefs-linTerms} Linear terms for _Phalangium opilio_. Line',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
+opilLinTerms %>% select(-p) %>% 
+  kable(.,caption='Linear terms for \\emph{Phalangium opilio}',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
         digits=c(1,2,2,2,2),align='rrrrl')
@@
 ```{r OpilioCoefs-smoothTerms, echo=FALSE, warning=FALSE}
-
-kable(opilSmTerms[c(1,2,4,5)],caption='\\label{tab:OpilioCoefs-smoothTerms} Smooth terms for _Phalangium opilio_, with effective degrees of freedom, Chi-squared coefficient, and p-value.
-_s_ indicates a thin-plate spline, _ti_ indicates a tensor-product interaction.
-All terms except for day and (E,N) are functional regression fits.',col.names=c('Smoothing term','Eff.
-_df_','$\\chi^2$','_p_'),
+opilSmTerms %>% select(-Ref.df,-p) %>% 
+  kable(.,caption='\\label{tab:OpilioCoefs-smoothTerms} Smooth terms for \\emph{Phalangium opilio}.
+\\emph{s} indicates a thin-plate spline, \\emph{ti} indicates a tensor-product interaction.
+All terms except for day and (E,N) are functional regression fits.',
+        col.names=c('Smoothing term','Eff. df_','$\\chi^2$','p'),
         digits=c(1,2,2,2),align='rrll')
@@
 
+\newpage
+
+# Supplementary Material {-}
+
+\beginsupplement
+
+```{r concurvity, echo=FALSE, fig.cap='\\label{fig:concurvity} Concurvity estimates for top land cover classes'}  
+  include_graphics('../figures/coverCorPlots/concurvityEstimate.png')
+```
+
 # References

### 2020-05-27 frAnalysis.R

@@ -225,13 +225,13 @@ detach(PteMelMod)
 # #Select only wolf spiders
 # tempArth <- arth %>% filter(family=='Lycosidae') %>% group_by(BTID) %>% summarize(n=n())
 
-#Select only Pardosa distincta
-tempArth <- arth %>% filter(genus=='Pardosa',species=='distincta') %>% group_by(BTID) %>% summarize(n=n())
+# #Select only Pardosa distincta
+# tempArth <- arth %>% filter(genus=='Pardosa',species=='distincta') %>% group_by(BTID) %>% summarize(n=n())
 
-#Takes way longer to run. 5-10 mins +
+# # Takes way longer to run. 5-10 mins +
 # ParDisMod <- runMods(tempArth,trap,nnDistMat,oRingMat2Prop,formulas=modFormulas,basisFun='ts'); beep(1)
 # save(ParDisMod,file='./data/ParDisMod.Rdata')
-load('./data/ParDisMod.Rdata')
+# load('./data/ParDisMod.Rdata')
 
 #Check models
 attach(ParDisMod)
@@ -245,7 +245,7 @@ plot(mod3,pages=1,scheme=2,rug=F,shade=T,all.terms=T)
 #Check for multicollinearity (same as above)
 
 #Smoothing term estimates
-matrixplot(abs(cov2cor(sp.vcov(mod3))),c(names(mod3$sp),'scale'),numSize=1,mar=c(1,8,8,1))
+matrixplot(abs(cov2cor(sp.vcov(mod3))),c('scale',names(mod3$sp)),numSize=1,mar=c(1,8,8,1))
 
 #Variance component
 varcomp <- gam.vcomp(mod3) #Large amount of variation explained by easting
@@ -320,6 +320,105 @@ fixeffPlot <- ggarrange(p1,p2,p3,p4,p5,
 ggsave('./figures/Pardosa_distincta_fixeff.png',fixeffPlot,width=8,height=4,scale=2)
 rm(p1,p2,p3,p4,p5,raneffPlot,fixeffPlot) #Cleanup
 detach(ParDisMod)
+
+
+# Pardosa moesta (wolf spider) --------------------------------------------
+
+#Select only Pardosa moesta
+tempArth <- arth %>% filter(genus=='Pardosa',species=='moesta') %>% group_by(BTID) %>% summarize(n=n())
+
+# Takes way longer to run. 5-10 mins +
[…]

### 2020-05-27 prelimAnalysis.R

@@ -18,9 +18,10 @@ arth %>% filter(grepl('PF',BTID),arthOrder=='Coleoptera') %>%
   unite(genSpp,genus,species,sep=' ') %>% 
   mutate(genSpp=factor(genSpp,levels=genSpp)) %>% 
   filter(genSpp!='Pterostichus melanarius') %>% #Strip out P. melanarius
-  ggplot(aes(x=genSpp,y=count))+geom_col()+scale_y_sqrt()+
+  ggplot(aes(x=genSpp,y=count))+geom_col()+
+  # scale_y_sqrt()+
   theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
-#Tons of Pterostichus melanarius
+#Tons of Pterostichus melanarius. 
 
 #Genera
 arth %>% filter(grepl('PF',BTID),arthOrder=='Coleoptera') %>% filter(species!='melanarius') %>% 
@@ -32,9 +33,13 @@ arth %>% filter(grepl('PF',BTID),arthOrder=='Coleoptera') %>% filter(species!='m
 #What spp of spiders are present in pitfall traps?
 arth %>% filter(grepl('PF',BTID),arthOrder=='Araneae') %>%
   mutate(genSpp=paste(genus,species,sep=' ')) %>% group_by(family,genus,species) %>% 
-  summarize(n=n()) %>% arrange(family,genus,desc(n)) %>% data.frame()
-#Lots of Pardosa distincta and P. moesta. Could try all lycosids at once, but this might be a stretch
-
+  summarize(count=n()) %>% ungroup() %>% arrange(desc(count)) %>%
+  unite(genSpp,genus,species,sep=' ') %>% 
+  mutate(genSpp=factor(genSpp,levels=genSpp)) %>% 
+  ggplot(aes(x=genSpp,y=count))+geom_col()+ 
+  # scale_y_sqrt()+
+  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
+#Lots of Pardosa distincta and moesta. Could try all lycosids or Pardosa at once, but this might be a stretch
 
 # Basic maps of sites/trap distribution -----------------------------------
 

### 2020-05-29 manuscript/manuscript_outline.Rmd
Fixed bibtex refs

@@
 title: Landscape composition and beneficial insects
-subtitle: I like carabids
+# subtitle: 
 author:
@@
 bibliography: refs.bib
-csl: ecology-letters.csl
+# csl: ecology-letters.csl
 output: 
@@
 * We used three species of predatory arthropods that were present at very high abundances in the traps
-  + _Pterostichus melanarius_ is predatory introduced ground beetle that is a wide-ranging generalist [@carcamo1994, @larsen2003, @busch_Msc]
+  + _Pterostichus melanarius_ is predatory introduced ground beetle that is a wide-ranging generalist [@carcamo1994; @larsen2003; @busch_Msc]
   + It is commonly found in untilled grasslands [@purtauf2005] and grassy field margins may act as larval habitat [@desender1988]
   + _Pardosa distincta_ is a species of wolf spider that is common across the Canadian prairies, and is commonly found in ungrazed pastures [@carcamo2014]
-  + Finally, _Phallangium opilio_ is a widely-distributed harvestmen from the order Opilio
+  + Finally, _Phallangium opilio_ is a widely-distributed harvestman that lives in
 
@@
   + In our case, each column represents the proportion of a given landscape cover class within each annulus, with increasing radii away from the location of the trap, and the coefficients are a smooth function of distance ($\beta_i = f(distance_i)$), meaning that the coefficients represent the (additive) effect of a given type of landscape cover and  from the trap
-  + This avoids the fundamental problem of choosing an optimal radius of landscape composition, and allows the possibility that the size of the landscape ``grain" relevant to a given organism may change over the course of its life stages [@addicott1987 @lima1996]
-  + This technique has been used by other authors [@yen2014, @galpern2020]
+  + This avoids the fundamental problem of choosing an optimal radius of landscape composition, and allows the possibility that the size of the landscape ``grain" relevant to a given organism may change over the course of its life stages [@addicott1987; @lima1996]
+  + This technique has been used by other authors [@yen2014; @galpern2020]
 
 * Some of the landscape terms in our model were strongly concurved, so we removed them from the model, or combined them into a single term
-  + Concurvity is an non-linear analogue of multicollinearity that can bias estimates of standard errors [@buja1989, @ramsay2003]
-  + There is no agreed-upon threshold of unacceptable concurvity, but 0.5 is commonly used [@dominici2002, @ramsay2003] 
+  + Concurvity is an non-linear analogue of multicollinearity that can bias estimates of standard errors [@buja1989; @ramsay2003]
+  + There is no agreed-upon threshold of unacceptable concurvity, but 0.5 is commonly used [@dominici2002; @ramsay2003] 
   + We found that some landscape terms were strongly concurved (Figure \@ref(fig:concurvity)), namely shrubland and forest (max: 0.71), canola and cereal (max: 0.74), and wetland and grassland (max: 0.63)

### 2020-05-29 manuscript/manuscript_outline.Rmd
Updated figures and wrote some more in the Intro

@@
     toc: false
-    fig_caption: false
+    fig_caption: true
 header-includes: 
   \usepackage{float} \floatplacement{figure}{H} 
-  \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
+  \newcommand{\beginsupplement}{\setcounter{table}{0} \newpage \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
 
@@
 load('../data/ParDisMod.Rdata')
+load('../data/ParMoeMod.Rdata')
 load('../data/OpilioMod.Rdata')
@@
 
+#Extract Pardosa moesta results
+pmoeRes <- summary(ParMoeMod$mod3)
+pmoeLinTerms <- pmoeRes$p.table %>% as.data.frame() %>% 
+  rownames_to_column('loc') %>% 
+  mutate(loc=firstUpper(gsub('trapLoc','',loc))) %>% 
+  rename(p='Pr(>|z|)') %>% mutate(p=roundLess(p,3)) %>% 
+  mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
+  mutate(pTable=ifelse(sig,boldLaTeX(p),p)) %>% select(-sig) #Make text bold
+pmoeSmTerms <- pmoeRes$s.table %>% as.data.frame() %>% 
+  rownames_to_column('Smoother') %>% 
+  rename(p='p-value') %>% mutate(p=roundLess(p,3)) %>% mutate_at(vars(2:4),roundLess,dig=2) %>% 
+  mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
+  mutate(pTable=ifelse(sig,boldLaTeX(p),p)) %>% select(-sig) #Make text bold
+
 #Extract Phalangium opilio results
@@
   mutate(pTable=ifelse(sig,boldLaTeX(p),p)) %>% select(-sig) #Make text bold
+
+# #Extract concurvity from PteMel model
+# mod3concurv <- concurvity(PteMelMod$mod3,FALSE)$estimate
 
@@
 
-* We don't have a good understanding of what drives beneficial arthropod abundance
+* Understanding of how landscape structure drives beneficial arthropod abundance is incomplete
   + Bees are generally driven by flower/nest substrate availability [@roulston2011]
-  + Limited understanding of other arthropods
+  + Limited understanding of other arthropods (but see ``beetle hedges" from UK?)
   + Beetles are limited by water, food, and oviposition sites [@lovei1996]
+  + No-till agriculture is better for some ground beetles [@busch_Msc]
   + Arachnids are similarly limited by food, shelter
@@
 * Landscape structure can influence abundance of beneficial arthropods in agricultural areas [@albrecht2010]
-  + No-till agriculture is better for some ground beetles [@busch_Msc]
-  + How can we design landscapes to benefit both farmers and insects?
+  + Spillover occurs when organisms migrate from suitable habitat patches
+  + Can occur with pests or beneficial organisms [@woodcock2016]
+  + Management goal: be able to design landscapes that benefit both farmers and insect diversity/abundance
 
@@
   + e.g. Carabid beetles are thought to reproduce in field margins, but adults feed in fields [@desender1988]
+  + This means that spillover depends not only on habitat type, but on time of the year
+  + Certain habitat types may be sources of arthropods during some times of the year, but sinks during other times
   + Counts in pitfall traps are a proxy of activity density (not actual density), but this is probably an OK measure, at least within fields [@lang2000]
+
 * In this study, we used pitfall trap counts of three species of beneficial arthropod to determine how landscape composition affects activity density of arthropods
   + We hypothesized that:
-  1. Abundance of semi-natural land (SNL) would result in increased arthropod abundance
-  2. Nearby SNL acts as a source of arthropods earlier in the season, and act as a sink later on, as arthropods migrate into margins to reproduce
+  1. Untilled semi-natural land (SNL) provides oviposition and feeding areas for beneficial arthropods, meaning that nearby SNL should act as a source of arthropods, depending on habitat preferences
+  2.
+Crops in agricultural land attract pest insects during the growing season, and these insects are preyed upon by beneficial arthropods.
+However, pest phenology/crop senescence at the end of the season causes a decrease in the number of pests.
+This means that crop cover may act as a sink for beneficial insects early in the season as they migrate into the crop, and a source later on as they migrate out of the crop
 
@@
 
+* Functional regression plots of landscape composition may seem cryptic, but are fairly straightforward to interpret:
+  + Positive responses to nearby landscape cover classes indicate that the cover class acts as a source (i.e. organisms spill over *from* it)
+  + Neutral responses indicate that the cover class does not act as a significant source or sink
+  + However, negative responses to nearby landscape cover classes indicate one of two things
+  + 1) It indicates that the cover class acts as a sink (i.e. organisms spill over *into* it)
+  + 2) It indicates that the cover class acts as a source, but is unoccupied (i.e. no organisms available to spill over)
+  +
+
 * Some of the landscape terms in our model were strongly concurved, so we removed them from the model, or combined them into a single term
@@
   + There is no agreed-upon threshold of unacceptable concurvity, but 0.5 is commonly used [@dominici2002; @ramsay2003] 
-  + We found that some landscape terms were strongly concurved (Figure \@ref(fig:concurvity)), namely shrubland and forest (max: 0.71), canola and cereal (max: 0.74), and wetland and grassland (max: 0.63)
+  + Some landscape terms were strongly concurved (Figure \@ref(fig:concurvity)), namely forest and shrubland (max: 0.71), canola and cereal (max: 0.74), and grassland and wetland (max: 0.63)
+  + Forest and shrubland were combined into the ``TreeShrub" category, grassland and wetland were combined into the "GrassWetland" category, as they were strongly positively correlated at all distances, indicating similar feature classes
+  + Cereal was removed from the model, as it was negatively correlated with canola at distances less than 200m and positively correlated at distances over 500m, likely reflecting the most common crop rotations and landscape structure present across our study region
 
@@
 
-## _Pterostichus melanarius_
+## Pterostichus melanarius
 
-* _P. melanarius_ activity density was strongly influenced by trap location and landscape composition (Tables \@ref(tab:PteMelCoefs-linTerms), \@ref(tab:PteMelCoefs-smoothTerms))
-  + Canola crops had a higher activity density of _P. melanarius_ than any other trap location, while roadside ditches had the lowest (Figure \@ref(fig:PteMelCoefs-fixeff)a)
+* _P. melanarius_ activity density was strongly influenced by trap location and landscape composition (Tables \@ref(tab:PteMelLinear), \@ref(tab:PteMelSmooth))
+  + Canola crops had a higher activity density of _P. melanarius_ than any other trap location, while roadside ditches had the lowest (Figure \@ref(fig:PteMelLandscape)a) 
   + This indicates that low-density stands of canola may allow faster movement of ground beetles.
-  + In landscape composition, proportion of urban land cover (roadside right-of-way) was the strongest predictor of activity density, and this varied across the season, with urban land acting as a sink during June, but becoming a source during July (Figure \@ref(fig:PteMelCoefs-fixeff)f); trees and shrubs followed a similar pattern (Figure \@ref(fig:PteMelCoefs-fixeff)d)
+  + In landscape composition, proportion of urban land cover (roadside right-of-way) was the strongest predictor of activity density, and this varied across the season, with urban land acting as a sink during June, but becoming a source during July (Figure \@ref(fig:PteMelLandscape)f); trees and shrubs followed a similar pattern (Figure \@ref(fig:PteMelLandscape)d)
   + Wetland cover had a negative influence on _P. melanarius_ activity density, but only after mid-July, indicating that wetlands may act as a sink for _P. melanarius_ populations later in the season
 
-```{r PteMelCoefs-linTerms, echo=FALSE, warning=FALSE}
-pmelLinTerms %>% select(-p) %>% 
-  kable(.,caption='Linear terms for \\emph{Pterostichus melanarius}',
-      col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
-      digits=c(1,2,2,2,2),align='rrrrl',escape=FALSE)
-```
-
-```{r PteMelCoefs-smoothTerms, echo=FALSE, warning=FALSE}
-
-pmelSmTerms %>% select(-Ref.df,-p) %>% 
-  kable(.,caption='Smooth terms for \\emph{Pterostichus melanarius}.
-\\emph{s} indicates a thin-plate spline, \\emph{ti} indicates a tensor-product interaction.
-All terms except for day and (E,N) are functional regression fits.',
-      col.names=c('Smoothing term','Eff. _df_','$\\chi^2$','_p_'),
-      digits=c(1,2,2,2),align='rrll',escape=TRUE)
-```
-
-```{r PteMelCoefs-fixeff, echo=FALSE, fig.cap='\\label{fig:PteMelCoefs-fixeff} Landscape influence on _Pterostichus melanarius_ activity density.
+```{r PteMelLandscape, echo=FALSE, fig.cap='Landscape influence on _Pterostichus melanarius_ activity density.
 Lines/dots represent means, and bars/shaded regions represent 95% confidence intervals (1.96 x SE).
-Dashed line on panels b-f represents zero effect.
 Coloured regions represent early-, mid-, and late-season effects (red, green, blue)'}
@@
 *  _P.
-melanarius_ had a very strong random temporal and spatial component (both p<0.001), indicating that phenology and local geographic factors were strong drivers of ground beetle activity density (Figure \@ref(fig:PteMelCoefs-raneff))
+melanarius_ had a very strong random temporal and spatial component (both p<0.001), indicating that phenology and local geographic factors were strong drivers of ground beetle activity density (Figure \@ref(fig:PteMelSpatiotemporal))
   + This could be related to climatic drivers (rainfall, growing degree days), or could simply represent a single yearly realization of a spatio-temporal random field
 
-```{r PteMelCoefs-raneff, echo=FALSE, fig.cap='\\label{fig:PteMelCoefs-raneff} Temporal and spatial components of _Pterostichus melanarius_ activity density'}
+```{r PteMelSpatiotemporal, echo=FALSE, fig.cap='Temporal and spatial components of _Pterostichus melanarius_ activity density'}
   include_graphics('../figures/Pterostichus_melanarius_raneff.png')
@@
 
-## _Pardosa distincta_
+## Pardosa distincta
 
-* _Pardosa distincta_ activity density was also strongly influenced by trap location and landscape composition (Tables \@ref(tab:ParDisCoefs-linTerms), \@ref(tab:ParDisCoefs-smoothTerms)), similar to _P.
-melanarius_.
-  + However, _P. distincta_ had far lower activity density in canola than any other cover type (Figure \@ref(fig:ParDisCoefs-fixeff)a).
+* _Pardosa distincta_ activity density was also strongly influenced by trap location and landscape composition (Tables \@ref(tab:ParDisLinear), \@ref(tab:ParDisSmooth)), similar to _P. melanarius_.
+  + However, _P. distincta_ had far lower activity density in canola than any other cover type (Figure \@ref(fig:ParDisLandscape)a).
   + Interestingly, nearby canola appeared to act as a source of _P.
-distincta_ for surrounding landscape features, as activity density was positively related to the nearby proportion of canola (p = `r with(pdisSmTerms,pTable[Smoother=='s(distMat):Canola'])`), at least early in the season (p = `r with(pdisSmTerms,pTable[Smoother=='s(endDayMat):Canola'])`)
+distincta_ for surrounding landscape features, as activity density was positively related to the nearby proportion of canola (p = `r with(pdisSmTerms,p[Smoother=='s(distMat):Canola'])`), at least early in the season (p = `r with(pdisSmTerms,p[Smoother=='s(endDayMat):Canola'])`)
   + Pulse crops had a similar effect, acting as a source of _P.
-distincta_ early in the season, and acting as a mild sink later in the season (p = `r with(pdisSmTerms,pTable[Smoother=='ti(distMat,endDayMat):Pulses'])`, Figure \@ref(fig:ParDisCoefs-fixeff)d)
-  + Grassland acted as a weak source, at least earlier on in the season (p = `r with(pdisSmTerms,pTable[Smoother=='s(endDayMat):Grassland'])`), and urban cover acted as a weak sink at intermediate distances (~600m)
+distincta_ early in the season, and acting as a mild sink later in the season (p = `r with(pdisSmTerms,p[Smoother=='ti(distMat,endDayMat):Pulses'])`, Figure \@ref(fig:ParDisLandscape)d)
+  + Grassland acted as a weak source, at least earlier on in the season (p = `r with(pdisSmTerms,p[Smoother=='s(endDayMat):Grassland'])`), and urban cover acted as a weak sink at intermediate distances (~600m)
   + Similar to _P.
 melanarius_, _P.
-distincta_ activity density had a very strong temporal and spatial component (both p = `r with(pdisSmTerms,pTable[grepl('E,N',Smoother)])`, Figure \@ref(fig:ParDisCoefs-raneff))
+distincta_ activity density had a very strong temporal and spatial component (both p = `r with(pdisSmTerms,p[grepl('E,N',Smoother)])`, Figure \@ref(fig:ParDisCoefs-raneff))
 
-```{r ParDisCoefs-linTerms, echo=FALSE, warning=FALSE}
-pdisLinTerms %>% select(-p) %>% 
-  kable(.,caption='\\label{tab:ParDisCoefs-linTerms} Linear terms for _Pardosa distincta_. Line',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
-        digits=c(1,2,2,2,2),align='rrrrl')
-```
-
-```{r ParDisCoefs-smoothTerms, echo=FALSE, warning=FALSE}
-pdisSmTerms %>% select(-Ref.df,-p) %>% 
-  kable(.,caption='Smooth terms for \\emph{Pardosa distincta}.
-\\emph{s} indicates a thin-plate spline, \\emph{ti} indicates a tensor-product interaction.
-All terms except for day and (E,N) are functional regression fits.',
-        col.names=c('Smoothing term','Eff. _df_','$\\chi^2$','_p_'),
-        digits=c(1,2,2,2),align='rrll',escape=TRUE)
-```
-
-```{r ParDisCoefs-fixeff, echo=FALSE, fig.cap='\\label{fig:ParDisCoefs-fixeff} Landscape influence on _Pardosa distincta_ activity density.
+```{r ParDisLandscape, echo=FALSE, fig.cap='Landscape influence on _Pardosa distincta_ activity density.
 Lines/dots represent means, and bars/shaded regions represent 95% confidence intervals (1.96 x SE).
-Dashed line on panels b-f represents zero effect.
 Coloured regions represent early-, mid-, and late-season effects (red, green, blue)'}
@@
 
-```{r ParDisCoefs-raneff, echo=FALSE, fig.cap='\\label{fig:ParDisCoefs-raneff} Temporal and spatial components of _Pardosa distincta_ activity density'}
+```{r ParDisCoefs-raneff, echo=FALSE, fig.cap='Temporal and spatial components of _Pardosa distincta_ activity density'}
   include_graphics('../figures/Pardosa_distincta_raneff.png')
@@
 
-## _Pardosa moesta_
+## Pardosa moesta
 
-```{r ParMoeCoefs-linTerms, echo=FALSE, warning=FALSE}
-pdisLinTerms %>% select(-p) %>% 
-  kable(.,caption='\\label{tab:ParMoeCoefs-linTerms} Linear terms for _Pardosa moesta_. Line',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
-        digits=c(1,2,2,2,2),align='rrrrl')
-```
+* _P. moesta_ was also heavily influenced by trap location and landscape composition (Tables \@ref(tab:ParMoeLinear), \@ref(tab:ParMoeSmooth))
+  + Similar to the other Lycosid spider _P. distincta_, _P. moesta_ had much lower activity density in canola than any other trap location (Figure \@ref(fig:ParMoeLandscape)a)
+  + Nearby canola also acted as a source of _P.
+moesta_ (Figure \@ref(fig:ParMoeLandscape)b, p = `r with(pmoeSmTerms,p[Smoother=='s(distMat):Canola'])`), although the effect was only strong at the end of the season (p = `r with(pmoeSmTerms,p[Smoother=='ti(distMat,endDayMat):Canola'])`)
+  + This indicates that both _P. distincta_ and _P. moesta_ migrate out of canola into adjacent habitat in order to overwinter or oviposit
+  + _P. moesta_ also had similar responses to pulses (Figures \@ref(fig:ParMoeLandscape)d)
+  + _P. moesta_ responded negatively to nearby tree and shrub cover, indicating that they are possible sinks of 
+  + Urban land cover was a sink, but only at certain times of the year
 
-```{r ParMoeCoefs-smoothTerms, echo=FALSE, warning=FALSE}
-pdisSmTerms %>% select(-Ref.df,-p) %>% 
-  kable(.,caption='\\label{tab:ParMoeCoefs-smoothTerms} Smooth terms for _Pardosa moesta_.
-\\emph{s} indicates a thin-plate spline, \\emph{ti} indicates a tensor-product interaction.
-All terms except for day and (E,N) are functional regression fits.',
-        col.names=c('Smoothing term','Eff. _df_','$\\chi^2$','_p_'),
-        digits=c(1,2,2,2),align='rrll')
-```
-
-```{r ParMoeCoefs-fixeff, echo=FALSE, fig.cap='\\label{fig:ParMoeCoefs-fixeff} Landscape influence on _Pardosa moesta_ activity density.
+```{r ParMoeLandscape, echo=FALSE, fig.cap='Landscape influence on \\emph{Pardosa moesta} activity density.
 Lines/dots represent means, and bars/shaded regions represent 95% confidence intervals (1.96 x SE).
-Dashed line on panels b-f represents zero effect.
 Coloured regions represent early-, mid-, and late-season effects (red, green, blue)'}
@@
 
-```{r ParMoeCoefs-raneff, echo=FALSE, fig.cap='\\label{fig:ParMoeCoefs-raneff} Temporal and spatial components of _Pardosa moesta_ activity density'}
+```{r ParMoeSpatiotemporal, echo=FALSE, fig.cap='Temporal and spatial components of \\emph{Pardosa moesta} activity density'}
   include_graphics('../figures/Pardosa_moesta_raneff.png')
@@
 
-## _Phalangium opilio_
+## Phalangium opilio
 
-* _Phalangium opilio_ activity density was strongly influenced by trap location, with pivot corners and wetlands having the highest activity density (p = `r with(opilLinTerms, pTable[loc=='Pivot'])`, `r with(opilLinTerms, pTable[loc=='Wetland'])`)
+* _Phalangium opilio_ activity density was strongly influenced by trap location, with pivot corners and wetlands having the highest activity density (p = `r with(opilLinTerms, p[loc=='Pivot'])`, `r with(opilLinTerms, p[loc=='Wetland'])`)
   + However, unlike _P.
@@
 pardosa_, _P.
-opilio_ was not strongly influenced by any land cover type, except for Pasture (p = `r with(opilSmTerms,pTable[Smoother=='ti(distMat,endDayMat):Pasture'])`)
+opilio_ was not strongly influenced by any land cover type, except for Pasture (p = `r with(opilSmTerms,p[Smoother=='ti(distMat,endDayMat):Pasture'])`)
   + This effect of this specific land cover type was not very large, as the model using non-crop cover performed similarly ($\Delta AIC$= `r with(OpilioMod, sprintf("%.2f",AIC(mod3)-AIC(mod4)))`)
   + In fact, the models that used landscape composition performed worse than the model with only trap location ($\Delta AIC$= `r with(OpilioMod, sprintf("%.2f",AIC(mod2)-AIC(mod3)))`,`r with(OpilioMod, sprintf("%.2f",AIC(mod2)-AIC(mod4)))`), indicating a weak effect of landscape composition
-  + The temporal and spatial components, as in the other two species, were very strong (both p = `r with(opilSmTerms,pTable[grepl('E,N',Smoother)])`, and Easting
+  + The temporal and spatial components, as in the other two species, were both very strong (both p = `r with(opilSmTerms,p[grepl('E,N',Smoother)])`)
+  + This indicates that _P. opilio_ activity density is shaped mostly by large-scale geographic patterns, rather than landscape composition
 
-```{r OpilioCoefs-linTerms, echo=FALSE, warning=FALSE}
-opilLinTerms %>% select(-p) %>% 
-  kable(.,caption='Linear terms for \\emph{Phalangium opilio}',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
-        digits=c(1,2,2,2,2),align='rrrrl')
-```
-
-```{r OpilioCoefs-smoothTerms, echo=FALSE, warning=FALSE}
-opilSmTerms %>% select(-Ref.df,-p) %>% 
-  kable(.,caption='\\label{tab:OpilioCoefs-smoothTerms} Smooth terms for \\emph{Phalangium opilio}.
-\\emph{s} indicates a thin-plate spline, \\emph{ti} indicates a tensor-product interaction.
-All terms except for day and (E,N) are functional regression fits.',
-        col.names=c('Smoothing term','Eff. df_','$\\chi^2$','p'),
-        digits=c(1,2,2,2),align='rrll')
-```
-
-```{r OpilioCoefs-fixeff, echo=FALSE, fig.cap='\\label{fig:OpilioCoefs-fixeff} Landscape influence on _Phalangium opilio_ activity density.
+```{r OpilioLandscape, echo=FALSE, fig.cap='Landscape influence on _Phalangium opilio_ activity density.
 Lines/dots represent means, and bars/shaded regions represent 95% confidence regions.
@@
 
-```{r OpilioCoefs-raneff, echo=FALSE, fig.cap='\\label{fig:OpilioCoefs-raneff} Temporal and spatial components of _Phalangium opilio_ activity density'}
+```{r OpilioSpatiotemporal, echo=FALSE, fig.cap='Temporal and spatial components of _Phalangium opilio_ activity density'}
   include_graphics('../figures/Opiliones_raneff.png')
@@
 
-* Pterostichus responded to landscape composition
+* The predatory ground beetle _Pterostichus melanarius_ responded to landscape composition
 
+* The Lycosid spiders _Pardosa distincta_ and _Pardosa moesta_ responded to landscape composition
+
+* The harvestman _Phalangium opilio_ did not respond to landscape composition
+
+* 
 \newpage
@@
 
-```{r concurvity, echo=FALSE, fig.cap='\\label{fig:concurvity} Concurvity estimates for top land cover classes'}  
+```{r concurvity, echo=FALSE, fig.cap='Concurvity estimates for top land cover classes'}  
   include_graphics('../figures/coverCorPlots/concurvityEstimate.png')
@@
 
+```{r PteMelLinear, echo=FALSE, warning=FALSE}
+pmelLinTerms %>% select(-p) %>% 
+  kable(.,caption='Linear terms for \\emph{Pterostichus melanarius}',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
+      digits=c(1,2,2,2,2),align='rrrrl',escape=FALSE)
+```
+
+```{r PteMelSmooth, echo=FALSE, warning=FALSE}
+pmelSmTerms %>% select(-Ref.df,-p) %>% 
+  kable(.,caption='Smooth terms for \\emph{Pterostichus melanarius}.
+\\emph{s} indicates a thin-plate spline, \\emph{ti} indicates a tensor-product interaction.
+All terms except for day and (E,N) are functional regression fits.',
+      col.names=c('Smoothing term','E.d.f.','$\\chi^2$','p'),
+      digits=c(1,2,2,2),align='rrll',escape=FALSE)
+```
+
+```{r ParDisLinear, echo=FALSE, warning=FALSE}
+pdisLinTerms %>% select(-p) %>% 
+  kable(.,caption='Linear terms for \\emph{Pardosa distincta}. Line',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
+        digits=c(1,2,2,2,2),align='rrrrl',escape=FALSE)
+```
+
+```{r ParDisSmooth, echo=FALSE, warning=FALSE}
+pdisSmTerms %>% select(-Ref.df,-p) %>% 
+  kable(.,caption='Smooth terms for \\emph{Pardosa distincta}.
+\\emph{s} indicates a thin-plate spline, \\emph{ti} indicates a tensor-product interaction.
+All terms except for day and (E,N) are functional regression fits.',
+        col.names=c('Smoothing term','E.d.f.','$\\chi^2$','p'),
+        digits=c(1,2,2,2),align='rrll',escape=FALSE)
+```
+
+```{r ParMoeLinear, echo=FALSE, warning=FALSE}
+pdisLinTerms %>% select(-p) %>% 
+  kable(.,caption='Linear terms for \\emph{Pardosa moesta}. Line',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
+        digits=c(1,2,2,2,2),align='rrrrl',escape=FALSE)
+```
+
+```{r ParMoeSmooth, echo=FALSE, warning=FALSE}
+pdisSmTerms %>% select(-Ref.df,-p) %>% 
+  kable(.,caption='Smooth terms for \\emph{Pardosa moesta}.
+\\emph{s} indicates a thin-plate spline, \\emph{ti} indicates a tensor-product interaction.
+All terms except for day and (E,N) are functional regression fits.',
+        col.names=c('Smoothing term','E.d.f.','$\\chi^2$','p'),
+        digits=c(1,2,2,2),align='rrll',escape=FALSE)
+```
+
+```{r OpilioLinear, echo=FALSE, warning=FALSE}
+opilLinTerms %>% select(-p) %>% 
+  kable(.,caption='Linear terms for \\emph{Phalangium opilio}',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
+        digits=c(1,2,2,2,2),align='rrrrl',escape=FALSE)
+```
+
+```{r OpilioSmooth, echo=FALSE, warning=FALSE}
+opilSmTerms %>% select(-Ref.df,-p) %>% 
+  kable(.,caption='Smooth terms for \\emph{Phalangium opilio}.
+\\emph{s} indicates a thin-plate spline, \\emph{ti} indicates a tensor-product interaction.
+All terms except for day and (E,N) are functional regression fits.',
+        col.names=c('Smoothing term','E.d.f.','$\\chi^2$','p'),
+        digits=c(1,2,2,2),align='rrll',escape=FALSE)
+```
+
 # References

### 2020-05-29 frAnalysis.R

@@ -3,8 +3,6 @@
 
 library(tidyverse)
 library(ggpubr)
-theme_set(theme_classic())
-maptheme <- theme(panel.border=element_rect(size=1,fill=NA),axis.line=element_blank()) #Better for maps
 library(mgcv)
 library(sf)
 library(gstat)
@@ -55,13 +53,20 @@ for(i in 1:length(mod3Vars)){ #Add in specified terms (s and ti)
 }
 modFormulas[4] <- paste0(modFormulas[2],'+s(distMat,by=NonCrop,bs=basisFun)+s(endDayMat,by=NonCrop,bs=basisFun)+ti(distMat,endDayMat,by=NonCrop,bs=basisFun)')
 
+#Parameters for multiplot figures
+landscapeFigX <- 8 #width
+landscapeFigY <- 6 #height
+landscapeLabel <- 20 #label size (letters a-f) 
+theme_set(theme_classic()) #Classic theme
+maptheme <- theme(panel.border=element_rect(size=1,fill=NA),axis.line=element_blank()) #Better theme for maps
+
 
 # Pterostichus melanarius ----------------------------------
 
 #Select only P. melanarius
 tempArth <- arth %>% filter(genus=='Pterostichus',species=='melanarius') %>% group_by(BTID) %>% summarize(n=n())
 
-PteMelMod <- runMods(tempArth,trap,nnDistMat,oRingMat2Prop,formulas=modFormulas,basisFun='ts'); beep(1)
+# PteMelMod <- runMods(tempArth,trap,nnDistMat,oRingMat2Prop,formulas=modFormulas,basisFun='ts'); beep(1)
 # save(PteMelMod,file='./data/PteMelMod.Rdata')
 load('./data/PteMelMod.Rdata')
 
@@ -148,8 +153,8 @@ p2 <- with(datList,expand.grid(E=seq(from=min(E)-5,to=max(E)+5,length.out=100),N
   theme(legend.position = c(0.85, 0.2),legend.background = element_rect(size=0.5,linetype="solid",colour="black"))+
   maptheme
 
-raneffPlot <- ggarrange(p1,p2,labels=letters[1:2]) #Plot spatial/temporal effects
-ggsave('./figures/Pterostichus_melanarius_raneff.png',raneffPlot,width=8,height=4,scale=2)
[…]

### 2020-06-05 manuscript/manuscript_outline.Rmd
Added to methods. Added to discussion

@@
 Some may act as sources of arthropods during some parts of the year, and sinks during others.
-We examined 3 widely-distributed species of arthropods, and used functional regression to examine their habitat preferences.
+We examined four widely-distributed species of arthropods, and used functional regression to examine their habitat preferences.
 We found that trees/shrubs, and roadside grasses acted as sources of arthropods.
@@
   + Pitfall traps consisted of 582 mL Solo® cups buried up to the rim, partially filled with ethylene glycol
-  + All traps had 2cm chicken wire mounted over the rim to prevent small vertebrates from falling into the traps
+  + All traps had 2cm wire mounted over the rim to prevent small vertebrates from falling into the traps
   + Traps at roadsides were located 5m from the roads, while traps at in-field sites were installed 20, 100, 200m (?) along a transect from the nearest non-crop feature (wetland, grassland, pivot)
@@
   + _Pardosa distincta_ is a species of wolf spider that is common across the Canadian prairies, and is commonly found in ungrazed pastures [@carcamo2014]
-  + Finally, _Phallangium opilio_ is a widely-distributed harvestman that lives in
-
-* We modeled arthropod activity density as a function of landscape composition using generalized additive models @wood2017
-    + To account for different lengths of trap exposure, log-days since trap placement was used as a fixed effect with its slope held at 1 (``offset" variable)
-    + All models were fit using a negative binomial distribution
-    + We fit our functional regression models using _mgcv_ version `r packageVersion('mgcv')`
+  + Finally, _Phallangium opilio_ is a widely-distributed generalist harvestman, whose habitat preferences are poorly understood
 
@@
 * We used functional regression to model the effect of landscape composition on activity density 
-  +  Scalar-on-function (SoF) regression is a special type of functional linear regression model ($\hat{y}=X\beta$), where the columns of the model matrix $X$ contain some continuous predictor of the scalar $y$ (e.g.
+  +  Scalar-on-function (SoF) regression is a special type of functional regression model ($\hat{y}=X\beta$), where the columns of the model matrix $X$ contain some continuous predictor of the scalar $y$ (e.g.
 biomass in a plot (scalar) as a function of monthly average temperatures (vector)), and the values of the coefficients ($\beta$) are modeled as a smooth function $f(x)$ of the predictors
@@
 
-* Functional regression plots of landscape composition may seem cryptic, but are fairly straightforward to interpret:
-  + Positive responses to nearby landscape cover classes indicate that the cover class acts as a source (i.e. organisms spill over *from* it)
-  + Neutral responses indicate that the cover class does not act as a significant source or sink
-  + However, negative responses to nearby landscape cover classes indicate one of two things
-  + 1) It indicates that the cover class acts as a sink (i.e. organisms spill over *into* it)
-  + 2) It indicates that the cover class acts as a source, but is unoccupied (i.e. no organisms available to spill over)
-  +
+* Activity density of each arthropod was  fit as generalized additive models @wood2017, using _mgcv_ version `r packageVersion('mgcv')` 
+    + Count data of arthropods were fit using a negative binomial distribution
+    + To account for different lengths of trap exposure, log-days since trap placement was used as a fixed effect with its slope held at 1 (``offset" variable)
+    + To account for overall spatial and temporal autocorrelation in the data, we included day of year as a 1-dimensional smooth and easting and northing as a 2-dimensional smooth
+    + For each landscape term, we used three SoF regression terms:
+    + First, we used the proportion cover of all landscape cover classes in the annuli surrounding each trap location (spatial effect of cover class)
+    + Second, we used day of the year multiplied by the proportion of cover classes in each annuli (temporal effect of cover class) 
+    + Finally, we used a tensor-product interaction of landscape cover and day of year (spatio-temporal interaction of cover class)
+    + We used 10 basis dimensions for the spatial and temporal landscape smoothers, and 16 basis dimensions for the spatio-temporal interaction
+    + This was deemed adequate, as the effective degrees of freedom for all smoothing terms were far below the number of basis dimensions, indicating that no additional basis dimensions were needed (see Tables \@ref(tab:PteMelSmooth), \@ref(tab:ParDisSmooth), \@ref(tab:ParMoeSmooth), \@ref(tab:OpilioSmooth))
+    + To remove unimportant terms from the model, we used thin-plate regression splines with shrinkage ("bs=`ts'" in _mgcv_)
+    + This is a continuous analog to stepwise model selection, whereby weaker terms can be completely removed from the model, rather than just reduced to a line [@marra2011]
+    <!-- + Double-penalization gave qualitatively similar results, but required twice the number of penalty terms, and some of the penalty terms were unstable  -->
 
-* Some of the landscape terms in our model were strongly concurved, so we removed them from the model, or combined them into a single term
-  + Concurvity is an non-linear analogue of multicollinearity that can bias estimates of standard errors [@buja1989; @ramsay2003]
+* Functional regression plots of landscape composition reveal which cover classes are acting as sources or sinks of organisms
+  + Positive responses to nearby landscape cover classes indicate that the cover class acts as a source (i.e. arthropods spill over *from* it)
+  + However, negative responses to nearby landscape cover classes can indicate one of two things:
+  + 1) It may indicate that the cover class acts as a sink (i.e. organisms spill over *into* it)
+  + 2) It may indicate that the cover class acts as a source, but it is unoccupied (i.e. no organisms available to spill over)
+  + We consider 1) to be the more likely scenario, as it is unlikely that any one cover class is *completely* unoccupied
+  + This model does not consider the next-generation fitness consequences of spillover
+  + For example, a cover class with low-quality habitat could act as an ecological trap [@galpern2017] if it acts as a sink but never as a source
+  + Alternatively, a cover class could act as a sink by providing high-quality habitat at certain times of the year (e.g.
+egg laying/feeding), but act as a source at other times (e.g.
+during emergence)
+
+* Some of the landscape terms in our model were strongly concurved, so we removed them from the model or combined them into a single term
+  + Concurvity is an non-linear analogue of multicollinearity that can bias estimates of standard errors [@buja1989]
   + There is no agreed-upon threshold of unacceptable concurvity, but 0.5 is commonly used [@dominici2002; @ramsay2003] 
@@
 
-## Pterostichus melanarius
+## *Ground beetle:* Pterostichus melanarius
 
@@
   + Wetland cover had a negative influence on _P. melanarius_ activity density, but only after mid-July, indicating that wetlands may act as a sink for _P. melanarius_ populations later in the season
+  + Finally, _P.
+melanarius_ activity density had a very strong temporal and spatial component (both p<0.001), indicating that phenology and local geographic factors were strong drivers of ground beetle activity density (Figure \@ref(fig:PteMelSpatiotemporal))
+  + Together, the landscape composition and the spatio-temporal component explained `r round(with(PteMelMod,summary(mod3)$dev.expl),3)*100`% of deviance
+  <!-- + This could be related to climatic drivers (rainfall, growing degree days), or could simply represent a single yearly realization of a spatio-temporal random field  -->
 
@@
 
-*  _P.
-melanarius_ had a very strong random temporal and spatial component (both p<0.001), indicating that phenology and local geographic factors were strong drivers of ground beetle activity density (Figure \@ref(fig:PteMelSpatiotemporal))
-  + This could be related to climatic drivers (rainfall, growing degree days), or could simply represent a single yearly realization of a spatio-temporal random field
-
 ```{r PteMelSpatiotemporal, echo=FALSE, fig.cap='Temporal and spatial components of _Pterostichus melanarius_ activity density'}
@@
 
-## Pardosa distincta
+## *Wolf spiders:* Pardosa distincta *and* Pardosa moesta
 
 * _Pardosa distincta_ activity density was also strongly influenced by trap location and landscape composition (Tables \@ref(tab:ParDisLinear), \@ref(tab:ParDisSmooth)), similar to _P. melanarius_.
-  + However, _P. distincta_ had far lower activity density in canola than any other cover type (Figure \@ref(fig:ParDisLandscape)a).
+  + Unlike _P. melanarius_, _P. distincta_ had far lower activity density in canola than any other cover type (Figure \@ref(fig:ParDisLandscape)a).
   + Interestingly, nearby canola appeared to act as a source of _P.
-distincta_ for surrounding landscape features, as activity density was positively related to the nearby proportion of canola (p = `r with(pdisSmTerms,p[Smoother=='s(distMat):Canola'])`), at least early in the season (p = `r with(pdisSmTerms,p[Smoother=='s(endDayMat):Canola'])`)
+distincta_ for surrounding landscape features, as activity density was positively related to the nearby proportion of canola (p = `r with(pdisSmTerms,p[Smoother=='s(distMat):Canola'])`), and that this effect was slightly stronger early in the season (p = `r with(pdisSmTerms,p[Smoother=='s(endDayMat):Canola'])`)
   + Pulse crops had a similar effect, acting as a source of _P.
 distincta_ early in the season, and acting as a mild sink later in the season (p = `r with(pdisSmTerms,p[Smoother=='ti(distMat,endDayMat):Pulses'])`, Figure \@ref(fig:ParDisLandscape)d)
-  + Grassland acted as a weak source, at least earlier on in the season (p = `r with(pdisSmTerms,p[Smoother=='s(endDayMat):Grassland'])`), and urban cover acted as a weak sink at intermediate distances (~600m)
+  + Grassland acted as a weak sink in the middle of the season (p = `r with(pdisSmTerms,p[Smoother=='s(endDayMat):Grassland'])`), and urban cover acted as a weak sink at intermediate distances (~600m)
+  <!-- How should this be interpreted? -->
   + Similar to _P.
@@
 distincta_ activity density had a very strong temporal and spatial component (both p = `r with(pdisSmTerms,p[grepl('E,N',Smoother)])`, Figure \@ref(fig:ParDisCoefs-raneff))
+  + The landscape composition and the spatio-temporal component explained `r round(with(ParDisMod,summary(mod3)$dev.expl),3)*100`% of deviance
 
@@
 
-## Pardosa moesta
-
 * _P. moesta_ was also heavily influenced by trap location and landscape composition (Tables \@ref(tab:ParMoeLinear), \@ref(tab:ParMoeSmooth))
-  + Similar to the other Lycosid spider _P. distincta_, _P. moesta_ had much lower activity density in canola than any other trap location (Figure \@ref(fig:ParMoeLandscape)a)
+  + Like its sister species _P. distincta_, _P. moesta_ had much lower activity density in canola than any other trap location (Figure \@ref(fig:ParMoeLandscape)a)
   + Nearby canola also acted as a source of _P.
 moesta_ (Figure \@ref(fig:ParMoeLandscape)b, p = `r with(pmoeSmTerms,p[Smoother=='s(distMat):Canola'])`), although the effect was only strong at the end of the season (p = `r with(pmoeSmTerms,p[Smoother=='ti(distMat,endDayMat):Canola'])`)
-  + This indicates that both _P. distincta_ and _P. moesta_ migrate out of canola into adjacent habitat in order to overwinter or oviposit
+  + This indicates that both _P. distincta_ and _P. moesta_ may migrate out of canola into adjacent habitat in order to overwinter or oviposit
   + _P. moesta_ also had similar responses to pulses (Figures \@ref(fig:ParMoeLandscape)d)
   + _P. moesta_ responded negatively to nearby tree and shrub cover, indicating that they are possible sinks of 
-  + Urban land cover was a sink, but only at certain times of the year
+  + Urban land cover acted as a sink, but only at certain times of the year
+  + The landscape composition and the spatio-temporal component explained `r round(with(ParMoeMod,summary(mod3)$dev.expl),3)*100`% of deviance
 
@@
 
-## Phalangium opilio
+## *Harvestman:* Phalangium opilio
 
@@
   + This effect of this specific land cover type was not very large, as the model using non-crop cover performed similarly ($\Delta AIC$= `r with(OpilioMod, sprintf("%.2f",AIC(mod3)-AIC(mod4)))`)
-  + In fact, the models that used landscape composition performed worse than the model with only trap location ($\Delta AIC$= `r with(OpilioMod, sprintf("%.2f",AIC(mod2)-AIC(mod3)))`,`r with(OpilioMod, sprintf("%.2f",AIC(mod2)-AIC(mod4)))`), indicating a weak effect of landscape composition
+  + In fact, the models that used landscape composition performed worse than the model with only trap location ($\Delta AIC$= `r with(OpilioMod, sprintf("%.2f",AIC(mod2)-AIC(mod3)))`, `r with(OpilioMod, sprintf("%.2f",AIC(mod2)-AIC(mod4)))`), indicating a weak effect of landscape composition
   + The temporal and spatial components, as in the other two species, were both very strong (both p = `r with(opilSmTerms,p[grepl('E,N',Smoother)])`)
-  + This indicates that _P. opilio_ activity density is shaped mostly by large-scale geographic patterns, rather than landscape composition
+  + Together, these results indicate that _P. opilio_ activity density is influenced by large-scale geographic patterns rather than landscape composition
+  + The landscape composition and the spatio-temporal component explained `r round(with(OpilioMod,summary(mod3)$dev.expl),3)*100`% of deviance
 
@@
 
-* The predatory ground beetle _Pterostichus melanarius_ responded to landscape composition
+* We found that while _Pterostichus melanarius_, _Pardosa distincta_, and _Pardosa moesta_ responded to landscape composition, _Phalangium opilio_ did not
+  + _P. melanarius_ was influenced by grassland/wetland, pasture, trees/shrubs, pulses, and urban land cover
+  + _P. distincta_ was influenced by grassland/wetland, canola, pulses, and urban land cover
+  + _P. moesta_ was influenced by the same landscape components: grassland/wetland, canola, pulses, and urban land cover
+  + Finally, _P. opilio_ was weakly influenced by pasture, and trees/shrubs
+  + These results highlight the important of non-crop marginal lands for predatory arthropod abundance
+
+Cover class     | _Pterostichus_          | _Pardosa_               | _Phalangium_
+--------------- | ----------------------- | ----------------------- | ------------
+Grass/Wetland   | Late sink               | Early source (weak)     |
+Canola          |                         | Early, mid source       |
+Pasture         | Early source            |                         | Early sink, late source
+Trees/Shrubland | Early sink, Late source | Variable                | Early sink, mid source (weak)
+Pulses          | Source                  | Variable                |
+Flax            |                         |                         |
+Urban           | Early sink, Mid source  | Variable                |
+
+* The predatory ground beetle _Pterostichus melanarius_ responded to landscape composition, and responded most strongly to urban and tree/shrub land cover
 
@@
 
-* 
+* The influence of landscape composition tended to be limited to a radius of about 500m, indicating that large-scale land cover may have a stronger effect on arthropod abundance than small-scale land cover
+
+* There was a strong temporal component to the landscape effects, meaning that it is important to consider how sinks and sources may change over the year
+
+* These patterns indicate movement between landscape features, but since we did not directly observe arthropod movement between features, future studies should examine this
+  + Mark-recapture studies or two-sided traps would be a good start
+  + Should also be linked to ecosystem services (e.g. predation on bait insects - imagine the scene from Jurassic Park where the T-rex eats the goat)
+
 \newpage

### 2020-06-05 frAnalysis.R

@@ -66,9 +66,11 @@ maptheme <- theme(panel.border=element_rect(size=1,fill=NA),axis.line=element_bl
 #Select only P. melanarius
 tempArth <- arth %>% filter(genus=='Pterostichus',species=='melanarius') %>% group_by(BTID) %>% summarize(n=n())
 
-# PteMelMod <- runMods(tempArth,trap,nnDistMat,oRingMat2Prop,formulas=modFormulas,basisFun='ts'); beep(1)
+# PteMelMod <- runMods(tempArth,trap,nnDistMat,oRingMat2Prop,formulas=modFormulas,basisFun='ts',doublePenalize=FALSE); beep(1)
 # save(PteMelMod,file='./data/PteMelMod.Rdata')
 load('./data/PteMelMod.Rdata')
+
+#Tried running this with double-penalization instead of shrinkage. Results were similar, but some of the shrinkage 
 
 #Check models
 attach(PteMelMod)
@@ -114,10 +116,10 @@ dev.off(); rm(N,lN)
 #Urban ~ Grassland,Wetland,Canola (not as bad)
 
 #Check for correlation in smoothers - seems to be OK for reduced set, but starts acting strangely if Water included
-matrixplot(abs(cov2cor(sp.vcov(mod3))),c('scale',names(mod3$sp)),mar=c(1,10,10,1))
+matrixplot(abs(cov2cor(sp.vcov(mod3))),c('scale',names(mod3$sp)),mar=c(1,10,10,1),numSize=0.75)
 
 #Hessian
-matrixplot(mod3$outer.info$hess,c('scale',names(mod3$sp)),mar=c(1,10,10,1))
+matrixplot(mod3$outer.info$hess,c('scale',names(mod3$sp)),mar=c(1,10,10,1),numSize=0.75)
 
 varcomp <- gam.vcomp(mod3) #Large amount of variation explained by easting
 
@@ -300,8 +302,9 @@ p2 <- expand.grid(endDayMat=c(173,203,232),distMat=seq(30,1500,30),GrassWetland=
   effectPlot()+labs(x='Distance (m)',y='Grass/Wetland effect')
 
 #Canola
-p3 <- expand.grid(distMat=seq(30,1500,30),Canola=1,y=NA) %>% 
-  smoothPred(mod3,whichSmooth=6) %>% rename(x=distMat) %>% 
[…]

### 2020-06-09 manuscript/manuscript_outline.Rmd
Worked on Discussion

@@
   + Finally, _P. opilio_ was weakly influenced by pasture, and trees/shrubs
-  + These results highlight the important of non-crop marginal lands for predatory arthropod abundance
+  + These results highlight the seasonal importance of non-crop marginal lands for predatory arthropod abundance (Table \@ref(tab:sumTab))
 
-Cover class     | _Pterostichus_          | _Pardosa_               | _Phalangium_
---------------- | ----------------------- | ----------------------- | ------------
-Grass/Wetland   | Late sink               | Early source (weak)     |
-Canola          |                         | Early, mid source       |
-Pasture         | Early source            |                         | Early sink, late source
-Trees/Shrubland | Early sink, Late source | Variable                | Early sink, mid source (weak)
-Pulses          | Source                  | Variable                |
-Flax            |                         |                         |
-Urban           | Early sink, Mid source  | Variable                |
+Table: (\#tab:sumTab) Summary table of results. Early, mid, and late indicate the time of the season when cover classes had strong effects on abundance.
 
-* The predatory ground beetle _Pterostichus melanarius_ responded to landscape composition, and responded most strongly to urban and tree/shrub land cover
+Cover class      | _Pterostichus melanarius_| _Pardosa distincta_      | _Pardosa moesta_     | _Phalangium opilio_
+---------------- | -----------------------  | ------------------------ | -------------------  | ------------
+Grass/ Wetland   | Late sink                | Late sink (weak)         |                      |
+Canola           |                          | Source                   | Source               |
+Pasture          | Early source             |                          |                      | Early sink, Late source
+Trees/ Shrubland | Early sink, Late source  |                          | Source               | Early sink, Mid source (weak)
+Pulses           | Source                   | Early source, Late sink  | Sink                 |
+Urban            | Early sink, Mid source   | Sink                     | Mid sink (weak)      |
 
-* The Lycosid spiders _Pardosa distincta_ and _Pardosa moesta_ responded to landscape composition
+* The predatory ground beetle _Pterostichus melanarius_ responded to landscape composition, and responded most strongly to urban and tree/shrub cover
+  + _P. melanarius_ is found in a wide variety of habitats, but tends to prefer agricultural fields [@larsen2003]
+  + Other studies have found similar results, suggesting that untilled land is important off-field habitat for carabids [@desender1988, @fournier2002, but see @hatten2007]
+ + In particular, @purtauf2005 found that carabid density increased with proportion of nearby grasslands; our finding of grassland/wetland as late-season sink may represent _P.
+melanarius_ moving to overwintering habitat at the end of the season
+ + We also identified several other candidate land cover types as early- and mid-season sources of _P. melanarius_, namely urban, pasture, and pulse crops (primarily lentils in Alberta)
+ + The roles that carabids play in pulse crops is not well-studied, but carabids are known predators of pea-leaf weevils (_Sitona lineatus_) on other Fabacea [@hamon1990], so it is possible that pulses represent a source of spill-over
+ + Alternatively, _P. melanarius_ is known to predate upon other carabid predators of _S. lineatus_ (_Bembidion quadrimaculatum_, @vankosky2011)
+ <!-- + Carabid diversity is higher in no-till agriculture [@bourassa2008, @puech2014] -->
+
+* The Lycosid spiders _Pardosa distincta_ and _Pardosa moesta_ responded to landscape composition, in particular, pulses, canola, urban, and trees/shrubs 
+  + Surprisingly, canola acted as a source for both species, indicating that _Pardosa_ may use canola as foraging grounds
+  + Similar to our findings, @drapela2011 also found that _Pardosa agresti_ had higher activity density in areas with more woody trees and shrubs, as well as in areas close to roadside strips, suggesting similar habitat preferences in Canadian and European contexts
 
@@
 
-* There was a strong temporal component to the landscape effects, meaning that it is important to consider how sinks and sources may change over the year
+* There was a strong temporal component to the landscape effects, meaning that it is important to consider how sinks and sources may change over the season
+  + We did not consider the influence of previous years' crops, although carabids tend to be more abundant in areas of high crop rotation [@busch_Msc, @bertrand2015]
 
 * These patterns indicate movement between landscape features, but since we did not directly observe arthropod movement between features, future studies should examine this
-  + Mark-recapture studies or two-sided traps would be a good start
-  + Should also be linked to ecosystem services (e.g. predation on bait insects - imagine the scene from Jurassic Park where the T-rex eats the goat)
+  + Mark-recapture studies, monitoring movement patterns (e.g. radio tags), or two-sided traps could be useful
+  + Should also be linked to ecosystem services (e.g. predation on bait insects or weed seeds)
 
@@
 ```{r ParMoeLinear, echo=FALSE, warning=FALSE}
-pdisLinTerms %>% select(-p) %>% 
+pmoeLinTerms %>% select(-p) %>% 
   kable(.,caption='Linear terms for \\emph{Pardosa moesta}. Line',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
@@
 ```{r ParMoeSmooth, echo=FALSE, warning=FALSE}
-pdisSmTerms %>% select(-Ref.df,-p) %>% 
+pmoeSmTerms %>% select(-Ref.df,-p) %>% 
   kable(.,caption='Smooth terms for \\emph{Pardosa moesta}.

### 2020-06-10 manuscript/manuscript_outline.Rmd
Added reference

@@
   + Together, these results indicate that _P. opilio_ activity density is influenced by large-scale geographic patterns rather than landscape composition
-  + The landscape composition and the spatio-temporal component explained `r round(with(OpilioMod,summary(mod3)$dev.expl),3)*100`% of deviance
+  + The landscape composition and the spatio-temporal component explained `r round(with(OpilioMod,summary(mod3)$dev.expl),3)*100`% of model deviance
 

### 2020-06-10 manuscript/manuscript_outline.Rmd
Worked on Discussion

@@
 pardosa_, _P.
-opilio_ was not strongly influenced by any land cover type, except for Pasture (p = `r with(opilSmTerms,p[Smoother=='ti(distMat,endDayMat):Pasture'])`)
+opilio_ was not strongly influenced by any land cover type, except for Pasture (p = `r with(opilSmTerms,p[Smoother=='ti(distMat,endDayMat):Pasture'])`) and trees/shrubs (p = `r with(opilSmTerms,p[Smoother=='ti(distMat,endDayMat):TreeShrub'])`)
   + This effect of this specific land cover type was not very large, as the model using non-crop cover performed similarly ($\Delta AIC$= `r with(OpilioMod, sprintf("%.2f",AIC(mod3)-AIC(mod4)))`)
@@
   + _P. melanarius_ is found in a wide variety of habitats, but tends to prefer agricultural fields [@larsen2003]
-  + Other studies have found similar results, suggesting that untilled land is important off-field habitat for carabids [@desender1988, @fournier2002, but see @hatten2007]
+  + Other studies have found similar results, suggesting that untilled land is important off-field habitat for carabids [@desender1988; @fournier2002; but see @hatten2007]
  + In particular, @purtauf2005 found that carabid density increased with proportion of nearby grasslands; our finding of grassland/wetland as late-season sink may represent _P.
@@
  + The roles that carabids play in pulse crops is not well-studied, but carabids are known predators of pea-leaf weevils (_Sitona lineatus_) on other Fabacea [@hamon1990], so it is possible that pulses represent a source of spill-over
- + Alternatively, _P. melanarius_ is known to predate upon other carabid predators of _S. lineatus_ (_Bembidion quadrimaculatum_, @vankosky2011)
+ + Alternatively, _P. melanarius_ is known to predate upon other carabid predators of _S. lineatus_, such as _Bembidion quadrimaculatum_ [@vankosky2011]
  <!-- + Carabid diversity is higher in no-till agriculture [@bourassa2008, @puech2014] -->
@@
 
-* The harvestman _Phalangium opilio_ did not respond to landscape composition
+* _Phalangium opilio_ activity density did not respond to landscape composition, aside from pasture (p = `r with(opilSmTerms,p[Smoother=='ti(distMat,endDayMat):Pasture'])`) and a weaker response to trees/shrubland (p = `r with(opilSmTerms,p[Smoother=='ti(distMat,endDayMat):TreeShrub'])`)
+  + _P. opilio_ avoids heavily grazed areas, possibly due to low humidity, but is active in most other habitat types [@sajna2011]
+  + In particular, it is largely found in human-altered landscapes with a large proportion of farming [@muster2014; @vandepoel2015Msc]
+  + Our results show that _P. opilio_ migrated into pastures
+  + It is also found in large numbers at the edges of forests, and may migrate from forests into farmlands [@vandepoel2015Msc]
+  + We found the opposite pattern (albeit weakly): _P. opilio_ appears to migrate into forests
 
@@
 * There was a strong temporal component to the landscape effects, meaning that it is important to consider how sinks and sources may change over the season
-  + We did not consider the influence of previous years' crops, although carabids tend to be more abundant in areas of high crop rotation [@busch_Msc, @bertrand2015]
+  + We did not consider the influence of previous years' crops, although carabids tend to be more abundant in areas of high crop rotation [@busch_Msc; @bertrand2016]
 

### 2020-06-12 manuscript/manuscript_outline.Rmd
Found potential problem in matrix allignment within runMods

@@
 
-* The influence of landscape composition tended to be limited to a radius of about 500m, indicating that large-scale land cover may have a stronger effect on arthropod abundance than small-scale land cover
+* Overall, we found that trees/shrubs, 
+  + The influence of landscape composition tended to be limited to a radius of about 500m, indicating that large-scale land cover may have a stronger effect on arthropod abundance than small-scale land cover
 

### 2020-06-12 frAnalysis.R

@@ -66,7 +66,11 @@ maptheme <- theme(panel.border=element_rect(size=1,fill=NA),axis.line=element_bl
 #Select only P. melanarius
 tempArth <- arth %>% filter(genus=='Pterostichus',species=='melanarius') %>% group_by(BTID) %>% summarize(n=n())
 
-# PteMelMod <- runMods(tempArth,trap,nnDistMat,oRingMat2Prop,formulas=modFormulas,basisFun='ts',doublePenalize=FALSE); beep(1)
+# PteMelMod <-
+
+#Something is going wrong here. Check allignment b/w landscape comp matrix and ID column within runMods
+debugonce(runMods)
+runMods(tempArth,trap,nnDistMat,oRingMat2Prop,formulas=modFormulas,basisFun='ts',doublePenalize=FALSE); beep(1)
 # save(PteMelMod,file='./data/PteMelMod.Rdata')
 load('./data/PteMelMod.Rdata')
 
@@ -227,7 +231,26 @@ rm(p1,p2,p3,p4,p5,p6,raneffPlot,fixeffPlot) #Cleanup
 
 #Looks like the ring model of landscape does better. Important landscape features seem to be:
 # Urban (spatial + temporal), Pasture, Pulses (weak), Tree/Shrubs (weak)
+
+#Trying out some distance plots.
+#Need to identify sites at differing distances into fields
+
+#Figure out which sites have the higest amount of pasture
+PteMelMod$datList$Pasture %>% apply(.,1,sum) %>%
+  data.frame(pasture=.,ID=PteMelMod$tempTrap$ID)
+
+#Choose only 26133 at pass 4
+chooseMe <- which(with(PteMelMod$tempTrap,BLID=='26133'&pass==4))
+
+dat <- lapply(PteMelMod$datList,function(x) if(is.matrix(x)) x[chooseMe,] else x[chooseMe])
+
+PteMelMod$tempTrap$BTID
+
 detach(PteMelMod)
+
+
+
+
 
 # Pardosa distincta (wolf spider) -----------------------------------------------------------------
 

### 2020-06-12 manuscript/manuscript_outline.Rmd
Fixed mismatch in matrices, but results have changed
- Update Results and Discussion section accordingly

@@
   rownames_to_column('Smoother') %>% 
+  mutate(Smoother=gsub('distMat','Distance',Smoother),Smoother=gsub('endDayMat','Day',Smoother),Smoother=gsub('day','Day',Smoother)) %>% 
   rename(p='p-value') %>% mutate(p=roundLess(p,3)) %>% mutate_at(vars(2:4),roundLess,dig=2) %>% 
@@
 <!-- 2        | Phenology + Geography + Local cover                       | Activity Density ~ s(Day) + s(E,N) + Trap Location -->
-<!-- 3        | Phenology + Geography + Local cover + Landscape (general) | Activity Density ~ s(Day) + s(E,N) + Trap Location + s(Non-crop Cover)                          -->
+<!-- 3        | Phenology + Geography + Local cover + Landscape (general) | Activity Density ~ s(Day) + s(E,N) + Trap Location + s(Non-crop Cover)-->
 <!-- 4        | Phenology + Geography + Local cover + Landscape (specific)| Activity Density ~ s(Day) + s(E,N) + Trap Location + s(Cover 1) + s(Cover 2) + ... + s(Cover n) -->
@@
 * _P. melanarius_ activity density was strongly influenced by trap location and landscape composition (Tables \@ref(tab:PteMelLinear), \@ref(tab:PteMelSmooth))
-  + Canola crops had a higher activity density of _P. melanarius_ than any other trap location, while roadside ditches had the lowest (Figure \@ref(fig:PteMelLandscape)a) 
-  + This indicates that low-density stands of canola may allow faster movement of ground beetles.
-  + In landscape composition, proportion of urban land cover (roadside right-of-way) was the strongest predictor of activity density, and this varied across the season, with urban land acting as a sink during June, but becoming a source during July (Figure \@ref(fig:PteMelLandscape)f); trees and shrubs followed a similar pattern (Figure \@ref(fig:PteMelLandscape)d)
-  + Wetland cover had a negative influence on _P. melanarius_ activity density, but only after mid-July, indicating that wetlands may act as a sink for _P. melanarius_ populations later in the season
+  + Canola crops had a marginally higher activity density of _P.
+melanarius_ than other trap locations (Figure \@ref(fig:PteMelLandscape)a), possibly indicating that (comparitively) low-density stands of canola may allow faster movement of ground beetles.
+  + In landscape composition, nearby grassland/wetland cover had a neutral effect early in the summer, but a negative effect later in the summer (Figure \@ref(fig:PteMelLandscape)b), indicating that _P.
+melanarius_ may move into grasslands later in the year
+  + Nearby canola had a positive effect in the early summer, but conversely, far-away canola (>800 m) had a negative effect, indicating that areas with widespread amounts of canola coverage had lower _P.
+melanarius_ activity density than those with simply local canola cover
+  + Two other crop types had unexpected effects on _P. melanarius_ activity density: pulses and flax
+  + Pulses acted as a late-season source, possibly indicating that _P. melanarius_ migrate out of the crop after (or during) harvest
+  + Flax acted as both a local and far-away sink, suggesting that the crop is not suitable for _P. melanarius_ foraging
   + Finally, _P.
 melanarius_ activity density had a very strong temporal and spatial component (both p<0.001), indicating that phenology and local geographic factors were strong drivers of ground beetle activity density (Figure \@ref(fig:PteMelSpatiotemporal))
-  + Together, the landscape composition and the spatio-temporal component explained `r round(with(PteMelMod,summary(mod3)$dev.expl),3)*100`% of deviance
+  + Together, the landscape composition and the spatio-temporal component explained `r round(with(PteMelMod,summary(mod3)$dev.expl),3)*100`% of deviance ($R^2_{adj}$ = `r round(with(PteMelMod,summary(mod3)$r.sq),3)`)
   <!-- + This could be related to climatic drivers (rainfall, growing degree days), or could simply represent a single yearly realization of a spatio-temporal random field  -->
@@
 
-```{r PteMelSpatiotemporal, echo=FALSE, fig.cap='Temporal and spatial components of _Pterostichus melanarius_ activity density'}
-  include_graphics('../figures/Pterostichus_melanarius_raneff.png')
-```
-
 ## *Wolf spiders:* Pardosa distincta *and* Pardosa moesta
 
-* _Pardosa distincta_ activity density was also strongly influenced by trap location and landscape composition (Tables \@ref(tab:ParDisLinear), \@ref(tab:ParDisSmooth)), similar to _P. melanarius_.
-  + Unlike _P. melanarius_, _P. distincta_ had far lower activity density in canola than any other cover type (Figure \@ref(fig:ParDisLandscape)a).
+* _Pardosa distincta_ activity density was strongly influenced by trap location and landscape composition (Tables \@ref(tab:ParDisLinear), \@ref(tab:ParDisSmooth))
+  + Unlike _P. melanarius_, _P. distincta_ had far lower activity density in canola than any other cover type (Figure \@ref(fig:ParDisLandscape)a)
+  +
+
   + Interestingly, nearby canola appeared to act as a source of _P.
@@
 distincta_ activity density had a very strong temporal and spatial component (both p = `r with(pdisSmTerms,p[grepl('E,N',Smoother)])`, Figure \@ref(fig:ParDisCoefs-raneff))
-  + The landscape composition and the spatio-temporal component explained `r round(with(ParDisMod,summary(mod3)$dev.expl),3)*100`% of deviance
+  + The landscape composition and the spatio-temporal component explained `r round(with(ParDisMod,summary(mod3)$dev.expl),3)*100`% of deviance ($R^2_{adj}$ = `r round(with(ParDisMod,summary(mod3)$r.sq),3)`)
 
@@
   include_graphics('../figures/Pardosa_distincta_fixeff.png')
-```
-
-```{r ParDisCoefs-raneff, echo=FALSE, fig.cap='Temporal and spatial components of _Pardosa distincta_ activity density'}
-  include_graphics('../figures/Pardosa_distincta_raneff.png')
 ```
@@
   + Urban land cover acted as a sink, but only at certain times of the year
-  + The landscape composition and the spatio-temporal component explained `r round(with(ParMoeMod,summary(mod3)$dev.expl),3)*100`% of deviance
+  + The landscape composition and the spatio-temporal component explained `r round(with(ParMoeMod,summary(mod3)$dev.expl),3)*100`% of deviance ($R^2_{adj}$ = `r round(with(ParMoeMod,summary(mod3)$r.sq),3)`)
 
@@
   include_graphics('../figures/Pardosa_moesta_fixeff.png')
-```
-
-```{r ParMoeSpatiotemporal, echo=FALSE, fig.cap='Temporal and spatial components of \\emph{Pardosa moesta} activity density'}
-  include_graphics('../figures/Pardosa_moesta_raneff.png')
 ```
@@
   + Together, these results indicate that _P. opilio_ activity density is influenced by large-scale geographic patterns rather than landscape composition
-  + The landscape composition and the spatio-temporal component explained `r round(with(OpilioMod,summary(mod3)$dev.expl),3)*100`% of model deviance
+  + The landscape composition and the spatio-temporal component explained `r round(with(OpilioMod,summary(mod3)$dev.expl),3)*100`% of model deviance ($R^2_{adj}$ = `r round(with(OpilioMod,summary(mod3)$r.sq),3)`)
 
@@
   include_graphics('../figures/Opiliones_fixeff.png')
-```
-
-```{r OpilioSpatiotemporal, echo=FALSE, fig.cap='Temporal and spatial components of _Phalangium opilio_ activity density'}
-  include_graphics('../figures/Opiliones_raneff.png')
 ```
@@
 Cover class      | _Pterostichus melanarius_| _Pardosa distincta_      | _Pardosa moesta_               | _Phalangium opilio_
----------------- | -----------------------  | ------------------------ | -------------------  | ------------
-Grass/ Wetland   | Late sink                | Late sink (weak)         |                      |
-Canola           |                          | Source                   | Source               |
-Pasture          | Early source             |                          |                      | Early sink, Late source
-Trees/ Shrubland | Early sink, Late source  |                          | Source               | Early sink, Mid source (weak)
-Pulses           | Source                   | Early source, Late sink  | Sink                 |
-Urban            | Early sink, Mid source   | Sink                     | Mid sink (weak)      |
+---------------- | -----------------------  | ------------------------ | -----------------------------  | -----------------------
+Grass/ Wetland   | Late sink                | Late sink (weak)         | Sink                           | Early sink, late source
+Canola           | Early source             | Early source             | Early source, late sink        | 
+Pasture          |                          | Landscape-level sink     |                                | 
+Trees/ Shrubland |                          | Late sink                | Early source, late sink (weak) | Early sink
+Pulses           | Late source              |                          | Landscape-level source         |
+Flax             | Sink                     |                          |                                | Mid & late sink
+Urban            |                          |                          | Early source, late sink        |
 
@@
   include_graphics('../figures/coverCorPlots/concurvityEstimate.png')
+```
+
+```{r PteMelSpatiotemporal, echo=FALSE, fig.cap='Temporal and spatial components of _Pterostichus melanarius_ activity density'}
+  include_graphics('../figures/Pterostichus_melanarius_raneff.png')
+```
+
+```{r ParDisCoefs-raneff, echo=FALSE, fig.cap='Temporal and spatial components of _Pardosa distincta_ activity density'}
+  include_graphics('../figures/Pardosa_distincta_raneff.png')
+```
+
+```{r ParMoeSpatiotemporal, echo=FALSE, fig.cap='Temporal and spatial components of \\emph{Pardosa moesta} activity density'}
+  include_graphics('../figures/Pardosa_moesta_raneff.png')
+```
+
+```{r OpilioSpatiotemporal, echo=FALSE, fig.cap='Temporal and spatial components of _Phalangium opilio_ activity density'}
+  include_graphics('../figures/Opiliones_raneff.png')
 ```

### 2020-06-12 frAnalysis.R

@@ -54,23 +54,24 @@ for(i in 1:length(mod3Vars)){ #Add in specified terms (s and ti)
 modFormulas[4] <- paste0(modFormulas[2],'+s(distMat,by=NonCrop,bs=basisFun)+s(endDayMat,by=NonCrop,bs=basisFun)+ti(distMat,endDayMat,by=NonCrop,bs=basisFun)')
 
 #Parameters for multiplot figures
+#Landscape-level parameters
 landscapeFigX <- 8 #width
 landscapeFigY <- 6 #height
 landscapeLabel <- 20 #label size (letters a-f) 
+#Spatiotemporal smoother
+stFigX <- 6 #width
+stFigY <- 3 #height
+stLegPosX <- 0.85 #Legend position X
+stLegPosY <- 0.3 #Legend position Y
 theme_set(theme_classic()) #Classic theme
 maptheme <- theme(panel.border=element_rect(size=1,fill=NA),axis.line=element_blank()) #Better theme for maps
-
 
 # Pterostichus melanarius ----------------------------------
 
 #Select only P. melanarius
 tempArth <- arth %>% filter(genus=='Pterostichus',species=='melanarius') %>% group_by(BTID) %>% summarize(n=n())
 
-# PteMelMod <-
-
-#Something is going wrong here. Check allignment b/w landscape comp matrix and ID column within runMods
-debugonce(runMods)
-runMods(tempArth,trap,nnDistMat,oRingMat2Prop,formulas=modFormulas,basisFun='ts',doublePenalize=FALSE); beep(1)
+# PteMelMod <- runMods(tempArth,trap,nnDistMat,oRingMat2Prop,formulas=modFormulas,basisFun='ts',doublePenalize=FALSE); beep(1)
 # save(PteMelMod,file='./data/PteMelMod.Rdata')
 load('./data/PteMelMod.Rdata')
 
@@ -156,17 +157,20 @@ p2 <- with(datList,expand.grid(E=seq(from=min(E)-5,to=max(E)+5,length.out=100),N
   geom_point(data=tempTrap,aes(x=easting,y=northing))+
   scale_fill_gradient(low='blue',high='red')+
   labs(x='Easting (km)',y='Northing (km)',fill='Activity')+
[…]

### 2020-06-12 helperFunctions.R

@@ -73,7 +73,7 @@ runMods <- function(tempArth,trap,nnDistMat,oRingMat2,formulas=NULL,
   #Arrange matrices from oRingMat2 to correspond with rows of tempTrap
   oRingMat2 <- lapply(oRingMat2,function(x){
     x %>% as.data.frame() %>% rownames_to_column('ID') %>% 
-      left_join(st_drop_geometry(select(tempTrap,ID)),by='ID') %>% 
+      right_join(st_drop_geometry(select(tempTrap,ID)),by='ID') %>% 
       select(-ID) %>% as.matrix() })
   
   #Distance matrix to use in functional regression

### 2020-06-15 manuscript/manuscript_outline.Rmd
Worked on Results

@@
   + Canola crops had a marginally higher activity density of _P.
-melanarius_ than other trap locations (Figure \@ref(fig:PteMelLandscape)a), possibly indicating that (comparitively) low-density stands of canola may allow faster movement of ground beetles.
+melanarius_ than other trap locations (Figure \@ref(fig:PteMelLandscape)a), possibly indicating that canola may allow faster movement of ground beetles
   + In landscape composition, nearby grassland/wetland cover had a neutral effect early in the summer, but a negative effect later in the summer (Figure \@ref(fig:PteMelLandscape)b), indicating that _P.
@@
   + Pulses acted as a late-season source, possibly indicating that _P. melanarius_ migrate out of the crop after (or during) harvest
-  + Flax acted as both a local and far-away sink, suggesting that the crop is not suitable for _P. melanarius_ foraging
+  + Flax had both a local and landscape-level negative effect, suggesting that the crop is not suitable for _P. melanarius_ foraging
   + Finally, _P.
@@
 
-* _Pardosa distincta_ activity density was strongly influenced by trap location and landscape composition (Tables \@ref(tab:ParDisLinear), \@ref(tab:ParDisSmooth))
-  + Unlike _P. melanarius_, _P. distincta_ had far lower activity density in canola than any other cover type (Figure \@ref(fig:ParDisLandscape)a)
-  +
-
-  + Interestingly, nearby canola appeared to act as a source of _P.
-distincta_ for surrounding landscape features, as activity density was positively related to the nearby proportion of canola (p = `r with(pdisSmTerms,p[Smoother=='s(distMat):Canola'])`), and that this effect was slightly stronger early in the season (p = `r with(pdisSmTerms,p[Smoother=='s(endDayMat):Canola'])`)
-  + Pulse crops had a similar effect, acting as a source of _P.
-distincta_ early in the season, and acting as a mild sink later in the season (p = `r with(pdisSmTerms,p[Smoother=='ti(distMat,endDayMat):Pulses'])`, Figure \@ref(fig:ParDisLandscape)d)
-  + Grassland acted as a weak sink in the middle of the season (p = `r with(pdisSmTerms,p[Smoother=='s(endDayMat):Grassland'])`), and urban cover acted as a weak sink at intermediate distances (~600m)
-  <!-- How should this be interpreted? -->
-  + Similar to _P.
-melanarius_, _P.
-distincta_ activity density had a very strong temporal and spatial component (both p = `r with(pdisSmTerms,p[grepl('E,N',Smoother)])`, Figure \@ref(fig:ParDisCoefs-raneff))
-  + The landscape composition and the spatio-temporal component explained `r round(with(ParDisMod,summary(mod3)$dev.expl),3)*100`% of deviance ($R^2_{adj}$ = `r round(with(ParDisMod,summary(mod3)$r.sq),3)`)
+* Activity density of _Pardosa_ was strongly influenced by trap location and landscape composition (Tables \@ref(tab:ParDisLinear), \@ref(tab:ParDisSmooth))
+  + Unlike _P. melanarius_, both _Pardosa_ species had far lower activity density in canola than any other cover type (Figures \@ref(fig:ParDisLandscape)a, \@ref(fig:ParMoeLandscape)a)
+  + Interestingly, nearby canola appeared to act as a source of both _Pardosa_, as activity density was positively related to the local proportion of canola early in the season, but negatively related later in the season (Figures \@ref(fig:ParDisLandscape)b, \@ref(fig:ParMoeLandscape)c, p = `r with(pdisSmTerms,p[Smoother=='s(distMat):Canola'])`, `r with(pmoeSmTerms,p[Smoother=='s(distMat):Canola'])`)
+  <!-- + This may indicate?? -->
+  + Urban land cover had a similar effect on _P. moesta_, acting as an early source and a late sink (Figure \@ref(fig:ParMoeLandscape)f)
+  + Trees and shrubs acted as a sink for _P.
+distincta_ later in the season, and as a weak source early on in the season for _P.
+moesta_ (Figures \@ref(fig:ParDisLandscape)d, \@ref(fig:ParMoeLandscape)d)
+  + Grass and wetlands had strong local negative effect on _P.
+moesta_, but a positive landscape-level effect, indicating that while these cover types act as a sink, the general amount of grasslands and wetlands in the area have a positive effect on _P.
+moesta_ abundance
+  + Pulses had a similar effect on _P. distincta_ activity density, where landscape-level abundance of pulses increased _P. distincta_ density, but local abundance had a neutral effect
+  + Finally, activity density of both _Pardosa_ species had a very strong temporal and spatial component, although the temporal component was dominant for _P.
+distincta_ (Figure \@ref(fig:ParDisSpatiotemporal)a, p = `r with(pdisSmTerms,p[Smoother=='s(Day)'])`) whereas the spatial component was dominant for _P.
+moesta_ (Figure \@ref(fig:ParMoeSpatiotemporal)b, p = `r with(pdisSmTerms,p[Smoother=='s(E,N)'])`)
+  + The landscape composition and the spatio-temporal component explained `r round(with(ParDisMod,summary(mod3)$dev.expl),3)*100`% of deviance ($R^2_{adj}$ = `r round(with(ParDisMod,summary(mod3)$r.sq),3)`) and `r round(with(ParMoeMod,summary(mod3)$dev.expl),3)*100`% of deviance ($R^2_{adj}$ = `r round(with(ParMoeMod,summary(mod3)$r.sq),3)`) for _P.
+distincta_ and _P.
+moesta_, respectively
 
@@
 ```
-
-* _P. moesta_ was also heavily influenced by trap location and landscape composition (Tables \@ref(tab:ParMoeLinear), \@ref(tab:ParMoeSmooth))
-  + Like its sister species _P. distincta_, _P. moesta_ had much lower activity density in canola than any other trap location (Figure \@ref(fig:ParMoeLandscape)a)
-  + Nearby canola also acted as a source of _P.
-moesta_ (Figure \@ref(fig:ParMoeLandscape)b, p = `r with(pmoeSmTerms,p[Smoother=='s(distMat):Canola'])`), although the effect was only strong at the end of the season (p = `r with(pmoeSmTerms,p[Smoother=='ti(distMat,endDayMat):Canola'])`)
-  + This indicates that both _P. distincta_ and _P. moesta_ may migrate out of canola into adjacent habitat in order to overwinter or oviposit
-  + _P. moesta_ also had similar responses to pulses (Figures \@ref(fig:ParMoeLandscape)d)
-  + _P. moesta_ responded negatively to nearby tree and shrub cover, indicating that they are possible sinks of 
-  + Urban land cover acted as a sink, but only at certain times of the year
-  + The landscape composition and the spatio-temporal component explained `r round(with(ParMoeMod,summary(mod3)$dev.expl),3)*100`% of deviance ($R^2_{adj}$ = `r round(with(ParMoeMod,summary(mod3)$r.sq),3)`)
 
@@
 
-```{r ParDisCoefs-raneff, echo=FALSE, fig.cap='Temporal and spatial components of _Pardosa distincta_ activity density'}
+```{r ParDisSpatiotemporal, echo=FALSE, fig.cap='Temporal and spatial components of _Pardosa distincta_ activity density'}
   include_graphics('../figures/Pardosa_distincta_raneff.png')

### 2020-06-20 manuscript/manuscript_outline.Rmd
Worked on updating Results

@@
   + Unlike _P. melanarius_, both _Pardosa_ species had far lower activity density in canola than any other cover type (Figures \@ref(fig:ParDisLandscape)a, \@ref(fig:ParMoeLandscape)a)
-  + Interestingly, nearby canola appeared to act as a source of both _Pardosa_, as activity density was positively related to the local proportion of canola early in the season, but negatively related later in the season (Figures \@ref(fig:ParDisLandscape)b, \@ref(fig:ParMoeLandscape)c, p = `r with(pdisSmTerms,p[Smoother=='s(distMat):Canola'])`, `r with(pmoeSmTerms,p[Smoother=='s(distMat):Canola'])`)
-  <!-- + This may indicate?? -->
+  + Interestingly, nearby canola appeared to act as a source of both _Pardosa_, as activity density was positively related to the local proportion of canola early in the season, but negatively related later in the season (Figures \@ref(fig:ParDisLandscape)b, \@ref(fig:ParMoeLandscape)c, p=`r with(pdisSmTerms,p[Smoother=='ti(Distance,Day):Canola'])`, `r with(pmoeSmTerms,p[Smoother==ti(Distance,Day):Canola'])`)
   + Urban land cover had a similar effect on _P. moesta_, acting as an early source and a late sink (Figure \@ref(fig:ParMoeLandscape)f)
@@
   + Finally, activity density of both _Pardosa_ species had a very strong temporal and spatial component, although the temporal component was dominant for _P.
-distincta_ (Figure \@ref(fig:ParDisSpatiotemporal)a, p = `r with(pdisSmTerms,p[Smoother=='s(Day)'])`) whereas the spatial component was dominant for _P.
-moesta_ (Figure \@ref(fig:ParMoeSpatiotemporal)b, p = `r with(pdisSmTerms,p[Smoother=='s(E,N)'])`)
+distincta_ (Figure \@ref(fig:ParDisSpatiotemporal)a, p=`r with(pdisSmTerms,p[Smoother=='s(Day)'])`) whereas the spatial component was dominant for _P.
+moesta_ (Figure \@ref(fig:ParMoeSpatiotemporal)b, p=`r with(pdisSmTerms,p[Smoother=='s(E,N)'])`)
   + The landscape composition and the spatio-temporal component explained `r round(with(ParDisMod,summary(mod3)$dev.expl),3)*100`% of deviance ($R^2_{adj}$ = `r round(with(ParDisMod,summary(mod3)$r.sq),3)`) and `r round(with(ParMoeMod,summary(mod3)$dev.expl),3)*100`% of deviance ($R^2_{adj}$ = `r round(with(ParMoeMod,summary(mod3)$r.sq),3)`) for _P.
@@
 
-* _Phalangium opilio_ activity density was strongly influenced by trap location, with pivot corners and wetlands having the highest activity density (p = `r with(opilLinTerms, p[loc=='Pivot'])`, `r with(opilLinTerms, p[loc=='Wetland'])`)
-  + However, unlike _P.
-melanarius_ or _P.
-pardosa_, _P.
-opilio_ was not strongly influenced by any land cover type, except for Pasture (p = `r with(opilSmTerms,p[Smoother=='ti(distMat,endDayMat):Pasture'])`) and trees/shrubs (p = `r with(opilSmTerms,p[Smoother=='ti(distMat,endDayMat):TreeShrub'])`)
-  + This effect of this specific land cover type was not very large, as the model using non-crop cover performed similarly ($\Delta AIC$= `r with(OpilioMod, sprintf("%.2f",AIC(mod3)-AIC(mod4)))`)
-  + In fact, the models that used landscape composition performed worse than the model with only trap location ($\Delta AIC$= `r with(OpilioMod, sprintf("%.2f",AIC(mod2)-AIC(mod3)))`, `r with(OpilioMod, sprintf("%.2f",AIC(mod2)-AIC(mod4)))`), indicating a weak effect of landscape composition
-  + The temporal and spatial components, as in the other two species, were both very strong (both p = `r with(opilSmTerms,p[grepl('E,N',Smoother)])`)
-  + Together, these results indicate that _P. opilio_ activity density is influenced by large-scale geographic patterns rather than landscape composition
+* _Phalangium opilio_ activity density was strongly influenced by trap location, with pivot corners and wetlands having the highest activity density (Figure \@ref(fig:OpilioLandscape)a)
+  + _P.
+opilio_ was affected by grassland/wetlands (p=`r with(opilSmTerms,p[Smoother=='ti(Distance,Day):GrassWetland'])`), trees/shrubs (p`r with(opilSmTerms,p[Smoother=='s(Distance):TreeShrub'])`), and flax (p <`r with(opilSmTerms,p[Smoother=='s(Day):Flax'])`)
+  + Nearby grassland/wetland and trees/shrubs both had a negative effect on _P. opilio_ activity density, but only early in the season (Figures \@ref(fig:OpilioLandscape)b,c)
+  + Flax had a negative influence, but this effect was only strong during the middle of the season (Figure \@ref(fig:OpilioLandscape)d)
+  + However, the specific effect of these land cover types was not very large, as a competing model using only non-crop cover performed slightly better (Full model AIC = `r with(OpilioMod, sprintf("%.1f",AIC(mod3)))`, Non-crop model AIC = `r with(OpilioMod, sprintf("%.1f",AIC(mod4)))`)
+  + The temporal and spatial components, as in the other two species, were both very strong (both p`r with(opilSmTerms,p[grepl('E,N',Smoother)])`)
+  + Together, these results indicate that _P. opilio_ activity density is more strongly influenced by large-scale geographic patterns, and less so by landscape composition
   + The landscape composition and the spatio-temporal component explained `r round(with(OpilioMod,summary(mod3)$dev.expl),3)*100`% of model deviance ($R^2_{adj}$ = `r round(with(OpilioMod,summary(mod3)$r.sq),3)`)
@@
 
-Cover class      | _Pterostichus melanarius_| _Pardosa distincta_      | _Pardosa moesta_               | _Phalangium opilio_
----------------- | -----------------------  | ------------------------ | -----------------------------  | -----------------------
-Grass/ Wetland   | Late sink                | Late sink (weak)         | Sink                           | Early sink, late source
-Canola           | Early source             | Early source             | Early source, late sink        | 
-Pasture          |                          | Landscape-level sink     |                                | 
-Trees/ Shrubland |                          | Late sink                | Early source, late sink (weak) | Early sink
-Pulses           | Late source              |                          | Landscape-level source         |
-Flax             | Sink                     |                          |                                | Mid & late sink
-Urban            |                          |                          | Early source, late sink        |
+Cover class      | _P. melanarius_                        | _P. distincta_      | _P. moesta_        | _P. opilio_
+---------------- | -------------------------------        | ------------------  | -----------------  | ------------------
+Grass/ Wetland   | Late sink                              |                     | *                  | *                   
+Canola           | Local source, landscape sink (early)   | Local source (weak) | *                  | 
+Pasture          |                                        | Landscape sink      |                    | 
+Trees/ Shrubland |                                        | Sink (late)         |                    | *         
+Pulses           | Late source                            |                     | *                  |
+Flax             | Local and landscape sink               |                     |                    | *              
+Urban            |                                        |                     | *                  |
 
@@
 
-* _Phalangium opilio_ activity density did not respond to landscape composition, aside from pasture (p = `r with(opilSmTerms,p[Smoother=='ti(distMat,endDayMat):Pasture'])`) and a weaker response to trees/shrubland (p = `r with(opilSmTerms,p[Smoother=='ti(distMat,endDayMat):TreeShrub'])`)
+* _Phalangium opilio_ activity density did not respond to landscape composition, aside from pasture (p=`r with(opilSmTerms,p[Smoother=='ti(distMat,endDayMat):Pasture'])`) and a weaker response to trees/shrubland (p=`r with(opilSmTerms,p[Smoother=='ti(distMat,endDayMat):TreeShrub'])`)
   + _P. opilio_ avoids heavily grazed areas, possibly due to low humidity, but is active in most other habitat types [@sajna2011]

### 2020-06-20 frAnalysis.R

@@ -524,4 +524,41 @@ fixeffPlot <- ggarrange(p1,p2,p3,p4,
 ggsave('./figures/Opiliones_fixeff.png',fixeffPlot,width=landscapeFigX,height=landscapeFigY,scale=1)
 rm(p1,p2,p3,p4,raneffPlot,fixeffPlot) #Cleanup
 
+
+#Make plots for mod4 (non-crop only)
+
+#Temporal smoother
+p1 <- data.frame(day=min(datList$day):max(datList$day)) %>% 
+  smoothPred(mod4,whichSmooth=1) %>% 
+  ggplot(aes(x=day,y=pred))+geom_ribbon(aes(ymax=upr,ymin=lwr),alpha=0.3)+
+  geom_line()+
+  labs(x='Day of Year',y='Activity')
+
+#Spatial smoother
+p2 <- with(datList,expand.grid(E=seq(from=min(E),to=max(E),length.out=100),N=seq(from=min(N),to=max(N),length.out=100))) %>% 
+  smoothPred(mod4,whichSmooth=2) %>% 
+  filter(!exclude.too.far(E,N,datList$E,datList$N,0.1)) %>% 
+  ggplot(aes(x=E,y=N))+geom_raster(aes(fill=pred))+
+  geom_point(data=tempTrap,aes(x=easting,y=northing))+
+  scale_fill_gradient(low='blue',high='red')+
+  labs(x='Easting (km)',y='Northing (km)',fill='Activity')+
+  theme(legend.position = c(stLegPosX, stLegPosY), legend.background = element_rect(size=0.5,linetype="solid",colour="black"))+
+  maptheme
+
+#Trap location - less in canola, more in wetland/pivot
+p3 <- data.frame(trapLoc=tempTrap$trapLoc,pred=predict(mod4,type='terms',terms='trapLoc',se.fit=T)) %>% 
+  rename('pred'='pred.trapLoc','se'='pred.trapLoc.1') %>% distinct() %>% 
+  mutate(upr=pred+se*1.96,lwr=pred-se*1.96) %>% 
+  mutate(trapLoc=factor(trapLoc,labels=firstUpper(levels(trapLoc)))) %>% 
+  ggplot(aes(x=trapLoc,y=pred))+geom_pointrange(aes(ymax=upr,ymin=lwr))+
+  labs(x='Trap location',y='Activity')
+
+#Noncrop
[…]

### 2020-06-23 manuscript/manuscript_outline.Rmd
Worked on Discussion

@@
 Some may act as sources of arthropods during some parts of the year, and sinks during others.
-We examined four widely-distributed species of arthropods, and used functional regression to examine their habitat preferences.
+We examined four widely-distributed species of arthropods, using functional regression to examine their habitat preferences.
 We found that trees/shrubs, and roadside grasses acted as sources of arthropods.
@@
 * To characterize landscape composition surrounding the traps, we used classified landscape data from @AAFC_data
-  + AAFC cropland landscape classifications are very accurate for cultivated fields (~90%), but are less accurate for non-crop areas (~70%)
+  <!-- + AAFC cropland landscape classifications are very accurate for cultivated fields (~90%), but are less accurate for non-crop areas (~70%) -->
+  + We combined functionally similar landscape categories (cereals: _Triticum aestivum_ and _Hordeum vulgare_, pulses: _Pisum sativum_ and _Lens culinaris_, forest: coniferous and broadleaf) 
   + We extracted the landscape composition within a circle of a fixed radius surrounding each trap location 
@@
 
-* Some of the landscape terms in our model were strongly concurved, so we removed them from the model or combined them into a single term
+* Some of the landscape terms in our model were strongly concurved, so we removed them from the model or combined them
   + Concurvity is an non-linear analogue of multicollinearity that can bias estimates of standard errors [@buja1989]
@@
   + Some landscape terms were strongly concurved (Figure \@ref(fig:concurvity)), namely forest and shrubland (max: 0.71), canola and cereal (max: 0.74), and grassland and wetland (max: 0.63)
-  + Forest and shrubland were combined into the ``TreeShrub" category, grassland and wetland were combined into the "GrassWetland" category, as they were strongly positively correlated at all distances, indicating similar feature classes
-  + Cereal was removed from the model, as it was negatively correlated with canola at distances less than 200m and positively correlated at distances over 500m, likely reflecting the most common crop rotations and landscape structure present across our study region
+  + Forest and shrubland were combined into the ``Tree\Shrub" category, grassland and wetland were combined into the "Grass\Wetland" category, as they were strongly positively correlated at all distances, indicating similar feature classes
+  + Cereal was removed from the model, as it was negatively correlated with canola cover at distances less than 200m and was positively correlated at distances over 500m, reflecting the most common crop rotations (canola -> wheat -> barley) and the landscape structure present across our study region
 
@@
 # Results
+
+## Landscape composition
+
+* Grassland, cereal, and canola were the three most-abundant landcover classes surrounding our traps, accounting for `r 27.44+25.76+22.65`% of land cover
+  + Several landscape ``fingerprints" were evident in the landscape annuli, with cereal cover increasing with distance away, along with a corresponding decrease in canola cover (leading to the strong concurvity)
+  + Grassland cover was largely constant with distance, although a cluster of sites had uniformly high or low cover of grassland with distance
+  + Figure \@ref(fig:landscapeComp) displays the proportions of the 10 most-dominant land cover over distance
 
@@
   + Unlike _P. melanarius_, both _Pardosa_ species had far lower activity density in canola than any other cover type (Figures \@ref(fig:ParDisLandscape)a, \@ref(fig:ParMoeLandscape)a)
-  + Interestingly, nearby canola appeared to act as a source of both _Pardosa_, as activity density was positively related to the local proportion of canola early in the season, but negatively related later in the season (Figures \@ref(fig:ParDisLandscape)b, \@ref(fig:ParMoeLandscape)c, p=`r with(pdisSmTerms,p[Smoother=='ti(Distance,Day):Canola'])`, `r with(pmoeSmTerms,p[Smoother==ti(Distance,Day):Canola'])`)
+  + Interestingly, nearby canola appeared to act as a source of both _Pardosa_, as activity density was positively related to the local proportion of canola early in the season, but negatively related later in the season (Figures \@ref(fig:ParDisLandscape)b, \@ref(fig:ParMoeLandscape)c, p=`r with(pdisSmTerms,p[Smoother=='ti(Distance,Day):Canola'])`, `r with(pmoeSmTerms,p[Smoother=='ti(Distance,Day):Canola'])`)
   + Urban land cover had a similar effect on _P. moesta_, acting as an early source and a late sink (Figure \@ref(fig:ParMoeLandscape)f)
@@
 
-Table: (\#tab:sumTab) Summary table of results. Early, mid, and late indicate the time of the season when cover classes had strong effects on abundance.
+Table: (\#tab:sumTab) Summary table of results.
+Early, mid, and late indicate the time of the season when cover classes had strong effects on abundance.
+Italics indicates that effects were weak (95% intervals overlapped zero)
 
-Cover class      | _P. melanarius_                        | _P. distincta_      | _P. moesta_        | _P. opilio_
----------------- | -------------------------------        | ------------------  | -----------------  | ------------------
-Grass/ Wetland   | Late sink                              |                     | *                  | *                   
-Canola           | Local source, landscape sink (early)   | Local source (weak) | *                  | 
-Pasture          |                                        | Landscape sink      |                    | 
-Trees/ Shrubland |                                        | Sink (late)         |                    | *         
-Pulses           | Late source                            |                     | *                  |
-Flax             | Local and landscape sink               |                     |                    | *              
-Urban            |                                        |                     | *                  |
++-----------------+----------------------------+----------------------------+-----------------------------+-----------------------+
+| Cover class     | _P. melanarius_            | _P. distincta_             | _P. moesta_                 | _P. opilio_           |
++=================+============================+============================+=============================+=======================+
+| Grass/ Wetland  | - Local sink (late)        |                            | - Local sink                | - Local sink (early)  |
+|                 |                            |                            | - Landscape source          |                       |
++-----------------+----------------------------+----------------------------+-----------------------------+-----------------------+
+| Canola          | - Local source (early)     | - _Local source (early)_   | - Local source (early)      |                       |
+|                 | - Landscape sink (early)   | - _Local sink (late)_      | - Local sink (late)         |                       |
++-----------------+----------------------------+----------------------------+-----------------------------+-----------------------+
+| Pasture         |                            | - Landscape sink           |                             |                       | 
++-----------------+----------------------------+----------------------------+-----------------------------+-----------------------+
+| Trees/Shrubland |                            | - Overall sink (late)      | - _Overall source (early)_  | - Local sink (early)  |
+|                 |                            |                            | - _Overall sink (late)_     |                       |
++-----------------+----------------------------+----------------------------+-----------------------------+-----------------------+
+| Pulses          | - Overall source (late)    |                            | - Landscape source          |                       |
++-----------------+----------------------------+----------------------------+-----------------------------+-----------------------+
+| Flax            | - Local sink               |                            |                             | - Overall sink        |
+|                 | - Landscape sink           |                            |                             |                       |
++-----------------+----------------------------+----------------------------+-----------------------------+-----------------------+
+| Urban           |                            |                            | - Local source (early)      |                       |
+|                 |                            |                            | - Local sink (early)        |                       |
+|                 |                            |                            | - Landscape sink (late)     |                       |
+|                 |                            |                            | - Landscape source (late)   |                       |
++-----------------+----------------------------+----------------------------+-----------------------------+-----------------------+
 
-* The predatory ground beetle _Pterostichus melanarius_ responded to landscape composition, and responded most strongly to urban and tree/shrub cover
-  + _P. melanarius_ is found in a wide variety of habitats, but tends to prefer agricultural fields [@larsen2003]
+* The predatory ground beetle _Pterostichus melanarius_ responded to landscape composition, primarily to different crop types (Table \@ref(tab:sumTab),\@ref(tab:PteMelSmooth))
+  + Of the non-crop land categories, grassland and wetland cover acted as a late-season sink, suggesting that _P. melanarius_ may migrate into it at the end of the summer
   + Other studies have found similar results, suggesting that untilled land is important off-field habitat for carabids [@desender1988; @fournier2002; but see @hatten2007]
@@
 melanarius_ moving to overwintering habitat at the end of the season
- + We also identified several other candidate land cover types as early- and mid-season sources of _P. melanarius_, namely urban, pasture, and pulse crops (primarily lentils in Alberta)
- + The roles that carabids play in pulse crops is not well-studied, but carabids are known predators of pea-leaf weevils (_Sitona lineatus_) on other Fabacea [@hamon1990], so it is possible that pulses represent a source of spill-over
+ + However, _P. melanarius_ is also found in a wide variety of habitats, and tends to prefer agricultural fields [@larsen2003], which our models also demonstrated
+ + We found that canola and pulse crops acted as early- and mid-season sources of _P. melanarius_ 
+ + The roles that carabids play in pulse crops is not well-studied, but carabids are known predators of pea-leaf weevils (_Sitona lineatus_) on other Fabacea [@hamon1990]
  + Alternatively, _P. melanarius_ is known to predate upon other carabid predators of _S. lineatus_, such as _Bembidion quadrimaculatum_ [@vankosky2011]
+ + Either way this suggests that pulses may represent a potential food resource for _P. melanarius_, at least earlier in the season
+
  <!-- + Carabid diversity is higher in no-till agriculture [@bourassa2008, @puech2014] -->
@@
   include_graphics('../figures/coverCorPlots/concurvityEstimate.png')
+```
+
+```{r landscapeComp, echo=FALSE, fig.cap='Landscape composition in annuli surrounding each trap location'}  
+  include_graphics('../figures/oRingPlot2_AAFC.png')
 ```

### 2020-06-23 manuscript/manuscript_outline.Rmd
Added to refs

@@
  + We found that canola and pulse crops acted as early- and mid-season sources of _P. melanarius_ 
- + The roles that carabids play in pulse crops is not well-studied, but carabids are known predators of pea-leaf weevils (_Sitona lineatus_) on other Fabacea [@hamon1990]
+ + The roles that carabids play in pulse crops is not well-studied, but carabids are predators of pea-leaf weevils (_Sitona lineatus_) on other Fabaceae [@hamon1990]
  + Alternatively, _P. melanarius_ is known to predate upon other carabid predators of _S. lineatus_, such as _Bembidion quadrimaculatum_ [@vankosky2011]
  + Either way this suggests that pulses may represent a potential food resource for _P. melanarius_, at least earlier in the season
+ + Surprisingly, flax acted as a local and landscape level sink, suggesting that it may
 
@@
 * These patterns indicate movement between landscape features, but since we did not directly observe arthropod movement between features, future studies should examine this
+  + Some land cover classes were strongly concurved (canola and cereal, wetland and grassland) with each other, we removed or combined them, meaning that we could not consider the influence of the categories independently
   + Mark-recapture studies, monitoring movement patterns (e.g. radio tags), or two-sided traps could be useful

### 2020-06-23 frAnalysis.R

@@ -71,7 +71,7 @@ maptheme <- theme(panel.border=element_rect(size=1,fill=NA),axis.line=element_bl
 #Select only P. melanarius
 tempArth <- arth %>% filter(genus=='Pterostichus',species=='melanarius') %>% group_by(BTID) %>% summarize(n=n())
 
-# PteMelMod <- runMods(tempArth,trap,nnDistMat,oRingMat2Prop,formulas=modFormulas,basisFun='ts',doublePenalize=FALSE); beep(1)
+PteMelMod <- runMods(tempArth,trap,nnDistMat,oRingMat2Prop,formulas=modFormulas,basisFun='ts',doublePenalize=FALSE); beep(1)
 # save(PteMelMod,file='./data/PteMelMod.Rdata')
 load('./data/PteMelMod.Rdata')
 

### 2020-06-24 manuscript/manuscript_outline.Rmd
Worked on discussion. Added refs

@@
  + Either way this suggests that pulses may represent a potential food resource for _P. melanarius_, at least earlier in the season
- + Surprisingly, flax acted as a local and landscape level sink, suggesting that it may
+ + Surprisingly, flax acted as a local and landscape level sink, suggesting that it may be inappropriate feeding or nesting cover for _P. melanarius_.
+ + To our knowledge, there is no published research demonstrating this
 

### 2020-06-25 manuscript/manuscript_outline.Rmd
Worked on Discussion.
- Checked data once again, and it appears to allign properly

--- 2020-06-23 manuscript/manuscript_outline.Rmd
@@
   + Some landscape terms were strongly concurved (Figure \@ref(fig:concurvity)), namely forest and shrubland (max: 0.71), canola and cereal (max: 0.74), and grassland and wetland (max: 0.63)
-  + Forest and shrubland were combined into the ``Tree\Shrub" category, grassland and wetland were combined into the "Grass\Wetland" category, as they were strongly positively correlated at all distances, indicating similar feature classes
+  + Forest and shrubland were combined into the ``Tree/Shrub" category, grassland and wetland were combined into the "Grass/Wetland" category, as they were strongly positively correlated at all distances, indicating similar feature classes
   + Cereal was removed from the model, as it was negatively correlated with canola cover at distances less than 200m and was positively correlated at distances over 500m, reflecting the most common crop rotations (canola -> wheat -> barley) and the landscape structure present across our study region
@@
 Early, mid, and late indicate the time of the season when cover classes had strong effects on abundance.
-Italics indicates that effects were weak (95% intervals overlapped zero)
+Italics indicates that effects were weak (p>=0.05)
 
@@
   + However, _P. melanarius_ is also found in a wide variety of habitats, and tends to prefer agricultural fields [@larsen2003], which our models also demonstrated
- + We found that canola and pulse crops acted as early- and mid-season sources of _P. melanarius_ 
+  + We also found that canola and pulse crops acted as early- and mid-season sources of _P. melanarius_ 
   + The roles that carabids play in pulse crops is not well-studied, but carabids are predators of pea-leaf weevils (_Sitona lineatus_) on other Fabaceae [@hamon1990]
- + Alternatively, _P. melanarius_ is known to predate upon other carabid predators of _S. lineatus_, such as _Bembidion quadrimaculatum_ [@vankosky2011]
+  + _P. melanarius_ is also known to prey upon other carabids that are predators of _S. lineatus_, such as _Bembidion quadrimaculatum_ [@vankosky2011]
   + Either way this suggests that pulses may represent a potential food resource for _P. melanarius_, at least earlier in the season
- + Surprisingly, flax acted as a local and landscape level sink, suggesting that it may
+  <!-- + Carabid diversity is higher in no-till agriculture [@bourassa2008, @puech2014] -->
 
- <!-- + Carabid diversity is higher in no-till agriculture [@bourassa2008, @puech2014] -->
+* Surprisingly, flax acted as a local and landscape level sink for _P.
+melanarius_, and as an overall sink for _P.
+opilio_, suggesting that it may be inappropriate feeding or nesting cover for these beneficial arthropods
+  + Flax is more sensitive to weed competition than other small grains [@friesen1986; @kandel2020], so weed control tends to be more intense
+  + Lower weed abundance may cause flax fields to have lower levels of weed seeds to feed on, causing seed-feeding carabids to move to other locations [@trichard2014] 
+  + Alternatively, it could be that plant structural diversity due to extensive weed control, meaning that carabids have lower amounts of attractive ground cover [@butts2003; @clark1993]
+  + Why this occurs in flax fields but not canola or pulse crops is unclear, but may have to do with decreased shading or ground cover being less attractive to carabids [@butts2003]
+  + To our knowledge, there is no published research investigating effects of flax cropping on beneficial arthropods, so the causes of this pattern are speculative
 
@@
   + Surprisingly, canola acted as a source for both species, indicating that _Pardosa_ may use canola as foraging grounds
-  + Similar to our findings, @drapela2011 also found that _Pardosa agresti_ had higher activity density in areas with more woody trees and shrubs, as well as in areas close to roadside strips, suggesting similar habitat preferences in Canadian and European contexts
+  + @drapela2011 also found that _Pardosa agresti_ had higher activity density in areas with more woody trees and shrubs, as well as in areas close to roadside strips, suggesting similar habitat preferences in both Canadian and European contexts
+  +
 

### 2020-06-25 frAnalysis.R

@@ -69,9 +69,9 @@ maptheme <- theme(panel.border=element_rect(size=1,fill=NA),axis.line=element_bl
 # Pterostichus melanarius ----------------------------------
 
 #Select only P. melanarius
-tempArth <- arth %>% filter(genus=='Pterostichus',species=='melanarius') %>% group_by(BTID) %>% summarize(n=n())
+tempArth <- arth %>% filter(genus=='Pterostichus',species=='melanarius',year==2017) %>% group_by(BTID) %>% summarize(n=n())
 
-PteMelMod <- runMods(tempArth,trap,nnDistMat,oRingMat2Prop,formulas=modFormulas,basisFun='ts',doublePenalize=FALSE); beep(1)
+# PteMelMod <- runMods(tempArth,trap,nnDistMat,oRingMat2Prop,formulas=modFormulas,basisFun='ts',doublePenalize=FALSE); beep(1)
 # save(PteMelMod,file='./data/PteMelMod.Rdata')
 load('./data/PteMelMod.Rdata')
 
@@ -79,6 +79,7 @@ load('./data/PteMelMod.Rdata')
 
 #Check models
 attach(PteMelMod)
+
 # detach(PteMelMod)
 AIC(mod1,mod2,mod3,mod4) #Best model has separate land cover types + SpatioTemporal effect
 
@@ -233,7 +234,7 @@ detach(PteMelMod)
 # Pardosa distincta (wolf spider) -----------------------------------------------------------------
 
 #Select only Pardosa distincta
-tempArth <- arth %>% filter(genus=='Pardosa',species=='distincta') %>% group_by(BTID) %>% summarize(n=n())
+tempArth <- arth %>% filter(genus=='Pardosa',species=='distincta',year==2017) %>% group_by(BTID) %>% summarize(n=n())
 
 # Takes way longer to run. 5-10 mins +
 # ParDisMod <- runMods(tempArth,trap,nnDistMat,oRingMat2Prop,formulas=modFormulas,basisFun='ts'); beep(1)
@@ -242,6 +243,8 @@ load('./data/ParDisMod.Rdata')
 
 #Check models
 attach(ParDisMod)
+
+#Check 10212-4-DPF-2017 and 10212-5-DPF-2017, looks like both have 127 count?
 
 AIC(mod1,mod2,mod3,mod4) 
 
@@ -325,7 +328,7 @@ detach(ParDisMod)
[…]

### 2020-06-26 manuscript/manuscript_outline.Rmd
Added a bit to Discussion.
- Need to check covergence of P. distincta model

@@
 * We found that while _Pterostichus melanarius_, _Pardosa distincta_, and _Pardosa moesta_ responded to landscape composition, _Phalangium opilio_ did not
-  + _P. melanarius_ was influenced by grassland/wetland, pasture, trees/shrubs, pulses, and urban land cover
-  + _P. distincta_ was influenced by grassland/wetland, canola, pulses, and urban land cover
+  + _P. melanarius_ was influenced by grass/wetland, pasture, trees/shrubs, pulses, and urban land cover
+  + _P. distincta_ was influenced by grass/wetland, canola, pulses, and urban land cover
   + _P. moesta_ was influenced by the same landscape components: grassland/wetland, canola, pulses, and urban land cover
@@
 +=================+============================+============================+=============================+=======================+
-| Grass/ Wetland  | - Local sink (late)        |                            | - Local sink                | - Local sink (early)  |
+| Grass & Wetland | - Local sink (late)        |                            | - Local sink                | - Local sink (early)  |
 |                 |                            |                            | - Landscape source          |                       |
@@
 +-----------------+----------------------------+----------------------------+-----------------------------+-----------------------+
-| Trees/Shrubland |                            | - Overall sink (late)      | - _Overall source (early)_  | - Local sink (early)  |
+| Forest & Shrubs |                            | - Overall sink (late)      | - _Overall source (early)_  | - Local sink (early)  |
 |                 |                            |                            | - _Overall sink (late)_     |                       |
@@
 
-* The Lycosid spiders _Pardosa distincta_ and _Pardosa moesta_ responded to landscape composition, in particular, pulses, canola, urban, and trees/shrubs 
-  + Surprisingly, canola acted as a source for both species, indicating that _Pardosa_ may use canola as foraging grounds
+* The wolf spiders _Pardosa distincta_ and _Pardosa moesta_ both responded to landscape composition, but in slightly different ways
+  + Canola acted as an early-season source for both species, indicating that _Pardosa_ may use canola as foraging grounds
+  +
+
   + @drapela2011 also found that _Pardosa agresti_ had higher activity density in areas with more woody trees and shrubs, as well as in areas close to roadside strips, suggesting similar habitat preferences in both Canadian and European contexts
-  +
 

### 2020-06-26 frAnalysis.R

@@ -243,9 +243,6 @@ load('./data/ParDisMod.Rdata')
 
 #Check models
 attach(ParDisMod)
-
-#Check 10212-4-DPF-2017 and 10212-5-DPF-2017, looks like both have 127 count?
-
 AIC(mod1,mod2,mod3,mod4) 
 
 #Model 3 
@@ -254,11 +251,22 @@ plot(mod3,pages=1,scheme=2,rug=F,shade=T,all.terms=T)
 
 #Check for multicollinearity (same as above)
 
+#Check residuals
+sumres <- with(datList,data.frame(trapLoc,day,E,N)) %>% 
+  mutate(EN=factor(paste(E,N,sep='_'))) %>% 
+  mutate(res=residuals(mod3)) %>% group_by(EN) %>% 
+  summarize(E=first(E),N=first(N),res=sum(res))
+
+ggplot(sumres,aes(x=E,y=N,size=res,col=res))+geom_point(alpha=0.5)+
+  scale_colour_gradient(low='red',high='blue')
+
+gam(res~s(E,N),data=sumres) %>% plot(.,scheme=2,rug=F)
+
 #Smoothing term estimates - problem here with distance term for TreeShrub
 matrixplot(abs(cov2cor(sp.vcov(mod3))),c('scale',names(mod3$sp)),numSize=1,mar=c(1,8,8,1))
 
 #Variance component
-varcomp <- gam.vcomp(mod3) #Large amount of variation explained by easting
+varcomp <- gam.vcomp(mod3) 
 round(varcomp,3)
 
 #Temporal smoother

### 2020-07-01 manuscript/manuscript_outline.Rmd
Tried out some other modeling tweaks, and added refs

@@
   <!-- + AAFC cropland landscape classifications are very accurate for cultivated fields (~90%), but are less accurate for non-crop areas (~70%) -->
-  + We combined functionally similar landscape categories (cereals: _Triticum aestivum_ and _Hordeum vulgare_, pulses: _Pisum sativum_ and _Lens culinaris_, forest: coniferous and broadleaf) 
-  + We extracted the landscape composition within a circle of a fixed radius surrounding each trap location 
+  + We combined functionally similar landscape categories (cereals: _Triticum aestivum_ and _Hordeum vulgare_, pulses: _Pisum sativum_ and _Lens culinaris_, forest: coniferous and broadleaf), then extracted the landscape composition within a circle of a fixed radius surrounding each trap location
   + However, the radius of the circle necessary to characterize the landscape depends on the ``grain" of the landscape that is relevant to the abundance of a given organism [@addicott1987]
@@
   + In our case, each column represents the proportion of a given landscape cover class within each annulus, with increasing radii away from the location of the trap, and the coefficients are a smooth function of distance ($\beta_i = f(distance_i)$), meaning that the coefficients represent the (additive) effect of a given type of landscape cover and  from the trap
-  + This avoids the fundamental problem of choosing an optimal radius of landscape composition, and allows the possibility that the size of the landscape ``grain" relevant to a given organism may change over the course of its life stages [@addicott1987; @lima1996]
+  + This avoids the fundamental problem of choosing an optimal radius of landscape composition, and allows the possibility that the size of the landscape ``grain" relevant to a given organism may change over the course of its life stages [@addicott1987; @lima1996; @gardiner2010]
+  + It also allows for the possibility that certain land cover types may be locally beneficial, but detremental at wider scales, indicating that the cover type may not constitute a completely useable habitat
   + This technique has been used by other authors [@yen2014; @galpern2020]
@@
 * Activity density of each arthropod was fit as generalized additive models @wood2017, using _mgcv_ version `r packageVersion('mgcv')` 
-    + Count data of arthropods were fit using a negative binomial distribution
+    + Count data of arthropods were fit using a negative binomial distribution with a log-link
     + To account for different lengths of trap exposure, log-days since trap placement was used as a fixed effect with its slope held at 1 (``offset" variable)
-    + To account for overall spatial and temporal autocorrelation in the data, we included day of year as a 1-dimensional smooth and easting and northing as a 2-dimensional smooth
+    + We included day of year as a 1-dimensional smooth and easting and northing as a 2-dimensional smooth, in order to account for underlying spatial and temporal autocorrelation in the data
     + For each landscape term, we used three SoF regression terms:
@@
   + Canola acted as an early-season source for both species, indicating that _Pardosa_ may use canola as foraging grounds
-  +
+  + Trees and shrubs acted as a late season sink in both species, suggesting that they migrate to off-field areas with woody shrubs and trees 
+  + @drapela2011 also found that _Pardosa agrestis_ had higher activity density in areas with woody trees and shrubs
+  + While _Pardosa_ are found in areas close to disturbed roadside strips [@drapela2011; @kowal2011], _P.
+distincta_ appears to be less sensitive to disturbances than _P.
+moesta_ [@collins1996; @wade2010]
+  + We found that roads clearly acted as an early source and a late sink of _P. moesta_
+  + Grassland and wetland, as well as pulses, also acted as a local sink, but a landscape-level source for _P. moesta_
+  + @oberg2007
 
-  + @drapela2011 also found that _Pardosa agresti_ had higher activity density in areas with more woody trees and shrubs, as well as in areas close to roadside strips, suggesting similar habitat preferences in both Canadian and European contexts
+  a wandering-active predation strategy [@young1990],
 

### 2020-07-01 frAnalysis.R

@@ -39,6 +39,7 @@ modFormulas <- 'count~offset(log(trapdays))+s(day,k=10,bs=basisFun)+s(E,N,k=50,b
 # modFormulas <- paste0(modFormulas,'+ti(N,E,day,k=5,bs=basisFun)') # Add spatiotemporal interaction
 modFormulas[c(2,3,4)] <- paste0(modFormulas[1],'+trapLoc-1')
 mod3Vars <- c('GrassWetland','Canola','Pasture','TreeShrub','Pulses','Flax','Urban') #Variables for mod3
+mod3Vars <- c('GrassWetland','Cereal','Canola','TreeShrub','Pulses','Flax','Urban') #Includes cereal, excludes pasture
 # mod3Vars <- c('Grassland','Cereal','Canola','Pasture','Pulses','Wetland','Urban','Shrubland','Flax','Forest','Water') #Expanded variables for mod3
 #Cereal may be causing problems in estimation - collinear with canola
 
@@ -66,16 +67,18 @@ stLegPosY <- 0.3 #Legend position Y
 theme_set(theme_classic()) #Classic theme
 maptheme <- theme(panel.border=element_rect(size=1,fill=NA),axis.line=element_blank()) #Better theme for maps
 
+
 # Pterostichus melanarius ----------------------------------
 
 #Select only P. melanarius
 tempArth <- arth %>% filter(genus=='Pterostichus',species=='melanarius',year==2017) %>% group_by(BTID) %>% summarize(n=n())
 
-# PteMelMod <- runMods(tempArth,trap,nnDistMat,oRingMat2Prop,formulas=modFormulas,basisFun='ts',doublePenalize=FALSE); beep(1)
+PteMelMod <- runMods(tempArth,trap,nnDistMat,oRingMat2Prop,formulas=modFormulas,basisFun='ts',doublePenalize=FALSE); beep(1)
 # save(PteMelMod,file='./data/PteMelMod.Rdata')
-load('./data/PteMelMod.Rdata')
+# load('./data/PteMelMod.Rdata')
 
 #Tried running this with double-penalization instead of shrinkage. Results were similar, but some of the shrinkage 
+#Also tried running this with Cereal included, despite concurvity. Fits, but causes a bunch of weird instability in other results.
 
 #Check models
 attach(PteMelMod)
@@ -237,9 +240,10 @@ detach(PteMelMod)
[…]

### 2020-07-02 manuscript/manuscript_outline.Rmd
Added some refs

@@
 * The wolf spiders _Pardosa distincta_ and _Pardosa moesta_ both responded to landscape composition, but in slightly different ways
+  + Lycosids employ a wandering-active predation strategy [@young1990], meaning that nearby landscape composition may be more influential than large-scale composition [@oberg2007; @oberg2008]
   + Canola acted as an early-season source for both species, indicating that _Pardosa_ may use canola as foraging grounds
-  + Trees and shrubs acted as a late season sink in both species, suggesting that they migrate to off-field areas with woody shrubs and trees 
+  + Trees and shrubs acted as a late season sink in both species, suggesting that they migrate to off-field areas with woody shrubs and trees for overwintering [but _P.
+distincta_ are known to be active during the winter; @aitchison1984]
   + @drapela2011 also found that _Pardosa agrestis_ had higher activity density in areas with woody trees and shrubs
-  + While _Pardosa_ are found in areas close to disturbed roadside strips [@drapela2011; @kowal2011], _P.
+  + @moring1994 showed that _P. distincta_ were more active in grassy substrates
+  + While _Pardosa_ are found in areas close to disturbed roadside strips [@drapela2008; @drapela2011; @kowal2011], _P.
 distincta_ appears to be less sensitive to disturbances than _P.
@@
   + Grassland and wetland, as well as pulses, also acted as a local sink, but a landscape-level source for _P. moesta_
-  + @oberg2007
-
-  a wandering-active predation strategy [@young1990],
 

### 2020-08-05 manuscript/manuscript_outline.Rmd
Got rid of point form

--- 2020-06-26 manuscript/manuscript_outline.Rmd
@@
 Other features did not function as significant sources or sinks.
-Farmers should keep these landscape intact in order to preserve populations of generalist predators to defend their crops.
+Farmers should consider retaining these landscape features in order to preserve populations of helpful generalist predators in their crops.
 
@@
 
-# Introduction
+# Introduction - needs flushing out
 
-* Arthropod diversity is important to understand in agricultural systems
-  + Pests can cause large amounts of damage
-  + Beneficial insects can offset this
-  + Important for global biodiversity - insects may be declining globally
-  + Agriculture is ~36% of land worldwide
-  + Potential for win-win scenarios
+Arthropod diversity is important to understand in agricultural systems
+Pests can cause large amounts of damage
+Beneficial insects can offset this
+Important for global biodiversity - insects may be declining globally
+Agriculture is ~36% of land worldwide
+Potential for win-win scenarios
 
-* Understanding of how landscape structure drives beneficial arthropod abundance is incomplete
-  + Bees are generally driven by flower/nest substrate availability [@roulston2011]
-  + Limited understanding of other arthropods (but see ``beetle hedges" from UK?)
-  + Beetles are limited by water, food, and oviposition sites [@lovei1996]
-  + No-till agriculture is better for some ground beetles [@busch_Msc]
-  + Arachnids are similarly limited by food, shelter
+Understanding of how landscape structure drives beneficial arthropod abundance is incomplete
+Bees are generally driven by flower/nest substrate availability [@roulston2011]
+Limited understanding of other arthropods (but see ``beetle hedges" from UK?)
+Beetles are limited by water, food, and oviposition sites [@lovei1996]
+No-till agriculture is better for some ground beetles [@busch_Msc]
+Arachnids are similarly limited by food, shelter
 
-* Landscape structure can influence abundance of beneficial arthropods in agricultural areas [@albrecht2010]
-  + Spillover occurs when organisms migrate from suitable habitat patches
-  + Can occur with pests or beneficial organisms [@woodcock2016]
-  + Management goal: be able to design landscapes that benefit both farmers and insect diversity/abundance
+Landscape structure can influence abundance of beneficial arthropods in agricultural areas [@albrecht2010]
+Spillover occurs when organisms migrate from suitable habitat patches
+Can occur with pests or beneficial organisms [@woodcock2016]
+Management goal: be able to design landscapes that benefit both farmers and insect diversity/abundance
 
-* Point estimates of abundance are influenced by spatio-temporal processes 
-  + Arthropods move between landscape components depending on their life history
-  + e.g. Carabid beetles are thought to reproduce in field margins, but adults feed in fields [@desender1988]
-  + This means that spillover depends not only on habitat type, but on time of the year
-  + Certain habitat types may be sources of arthropods during some times of the year, but sinks during other times
-  + Counts in pitfall traps are a proxy of activity density (not actual density), but this is probably an OK measure, at least within fields [@lang2000]
+Point estimates of abundance are influenced by spatio-temporal processes 
+Arthropods move between landscape components depending on their life history
+e.g. Carabid beetles are thought to reproduce in field margins, but adults feed in fields [@desender1988]
+This means that spillover depends not only on habitat type, but on time of the year
+Certain habitat types may be sources of arthropods during some times of the year, but sinks during other times
+Counts in pitfall traps are a proxy of activity density (not actual density), but this is probably an OK measure, at least within fields [@lang2000]
 
-* In this study, we used pitfall trap counts of three species of beneficial arthropod to determine how landscape composition affects activity density of arthropods
-  + We hypothesized that:
-  1. Untilled semi-natural land (SNL) provides oviposition and feeding areas for beneficial arthropods, meaning that nearby SNL should act as a source of arthropods, depending on habitat preferences
-  2.
-Crops in agricultural land attract pest insects during the growing season, and these insects are preyed upon by beneficial arthropods.
+In this study, we used pitfall trap counts of three species of beneficial arthropod to determine how landscape composition affects activity density of arthropods.
+We hypothesized that:
+1) Untilled semi-natural land (SNL) provides oviposition and feeding areas for beneficial arthropods, meaning that nearby SNL should act as a source of arthropods.
+2) Crops in agricultural land attract pest insects during the growing season, and these insects are preyed upon by beneficial arthropods. 
 However, pest phenology/crop senescence at the end of the season causes a decrease in the number of pests. 
-This means that crop cover may act as a sink for beneficial insects early in the season as they migrate into the crop, and a source later on as they migrate out of the crop
+This means that crop cover may act as a sink for beneficial insects early in the season as they migrate into the crop, and a source later on as they migrate out of the crop.
 
@@
 
-* We used a system of pitfall traps installed at roadsides, field margins, wetlands, and in-field sites across southern Alberta in 2017 (_need a map here_)
-  + Pitfall traps consisted of 582 mL Solo® cups buried up to the rim, partially filled with ethylene glycol
-  + All traps had 2cm wire mounted over the rim to prevent small vertebrates from falling into the traps
-  + Traps at roadsides were located 5m from the roads, while traps at in-field sites were installed 20, 100, 200m (?) along a transect from the nearest non-crop feature (wetland, grassland, pivot)
-  + Specimens were collected from the traps every 14 days (SD: 2.9), and were identified to species
+We used a system of pitfall traps installed at roadsides, field margins, wetlands, and in-field sites across southern Alberta in 2017 (_need a map here_).
+Pitfall traps consisted of 582 mL Solo® cups buried up to the rim, partially filled with ethylene glycol.
+All traps had 2 cm diameter wire mesh mounted over the rim to prevent vertebrates from falling into the traps.
+Traps at roadsides were located 5m from the roads, while traps at in-field sites were installed 20, 100, 200m (?) along a transect from the nearest non-crop feature (wetland, grassland, pivot).
+Specimens were collected from the traps every 14 days (SD: 2.9), and were identified to species.
 
-* We used three species of predatory arthropods that were present at very high abundances in the traps
-  + _Pterostichus melanarius_ is predatory introduced ground beetle that is a wide-ranging generalist [@carcamo1994; @larsen2003; @busch_Msc]
-  + It is commonly found in untilled grasslands [@purtauf2005] and grassy field margins may act as larval habitat [@desender1988]
-  + _Pardosa distincta_ is a species of wolf spider that is common across the Canadian prairies, and is commonly found in ungrazed pastures [@carcamo2014]
-  + Finally, _Phallangium opilio_ is a widely-distributed generalist harvestman, whose habitat preferences are poorly understood
+We used three species of predatory arthropods that were present at very high abundances in the traps.
+_Pterostichus melanarius_ is predatory introduced ground beetle that is a wide-ranging generalist [@carcamo1994; @larsen2003; @busch_Msc].
+It is commonly found in untilled grasslands [@purtauf2005] and grassy field margins may act as larval habitat [@desender1988].
+_Pardosa distincta_ is a species of wolf spider that is common across the Canadian prairies, and is commonly found in ungrazed pastures [@carcamo2014].
+Finally, _Phallangium opilio_ is a widely-distributed generalist harvestman, whose habitat preferences are poorly understood.
 
-* To characterize landscape composition surrounding the traps, we used classified landscape data from @AAFC_data
+To characterize landscape composition surrounding the traps, we used classified landscape data from @AAFC_data.
 <!-- + AAFC cropland landscape classifications are very accurate for cultivated fields (~90%), but are less accurate for non-crop areas (~70%) -->
-  + We combined functionally similar landscape categories (cereals: _Triticum aestivum_ and _Hordeum vulgare_, pulses: _Pisum sativum_ and _Lens culinaris_, forest: coniferous and broadleaf) 
-  + We extracted the landscape composition within a circle of a fixed radius surrounding each trap location 
-  + However, the radius of the circle necessary to characterize the landscape depends on the ``grain" of the landscape that is relevant to the abundance of a given organism [@addicott1987]
-  + Therefore, we divided the landscape into annuli (rings) surrounding each trap location.
-  + Each annulus was 30 m thick, and had inner radii ranging from 30 to 1470m, in increments of 30m.
-  + Using functional regression [@ramsay2004], we were able to incorporate landscape information at different distance, allowing us to assess the impact of both local and regional landscape composition
+We combined functionally similar landscape categories (cereals: _Triticum aestivum_ and _Hordeum vulgare_, pulses: _Pisum sativum_ and _Lens culinaris_, forest: coniferous and broadleaf), then extracted the landscape composition within a circle of a fixed radius surrounding each trap location.
+However, the radius of the circle necessary to characterize the landscape depends on the ``grain" of the landscape that is relevant to the abundance of a given organism [@addicott1987].
+Therefore, we divided the landscape into annuli (rings) surrounding each trap location.
+Each annulus was 30 m thick, and had inner radii ranging from 30 to 1470m, in increments of 30m.
+Using functional regression [@ramsay2004], we were able to incorporate landscape information at different distance, allowing us to assess the impact of both local and regional landscape composition.
 
@@
 
-* We used functional regression to model the effect of landscape composition on activity density 
-  +  Scalar-on-function (SoF) regression is a special type of functional regression model ($\hat{y}=X\beta$), where the columns of the model matrix $X$ contain some continuous predictor of the scalar $y$ (e.g.
-biomass in a plot (scalar) as a function of monthly average temperatures (vector)), and the values of the coefficients ($\beta$) are modeled as a smooth function $f(x)$ of the predictors
-  + In our case, each column represents the proportion of a given landscape cover class within each annulus, with increasing radii away from the location of the trap, and the coefficients are a smooth function of distance ($\beta_i = f(distance_i)$), meaning that the coefficients represent the (additive) effect of a given type of landscape cover and  from the trap
-  + This avoids the fundamental problem of choosing an optimal radius of landscape composition, and allows the possibility that the size of the landscape ``grain" relevant to a given organism may change over the course of its life stages [@addicott1987; @lima1996]
-  + This technique has been used by other authors [@yen2014; @galpern2020]
+We used functional regression to model the effect of landscape composition on activity density.
+Scalar-on-function (SoF) regression is a special type of functional regression model ($\hat{y}=X\beta$), where the columns of the model matrix $X$ contain some continuous predictor of the scalar $y$ (e.g.
+biomass in a plot (scalar) as a function of monthly average temperatures (vector)), and the values of the coefficients ($\beta$) are modeled as a smooth function $f(x)$ of the predictors.
+In our case, each column represents the proportion of a given landscape cover class within each annulus, with increasing radii away from the location of the trap, and the coefficients are a smooth function of distance ($\beta_i = f(distance_i)$), meaning that the coefficients represent the (additive) effect of a given type of landscape cover at distances away from the trap.
+This avoids the fundamental problem of choosing an optimal radius of landscape composition, and allows the possibility that the size of the landscape ``grain" relevant to a given organism may change over the course of its life stages [@addicott1987; @lima1996; @gardiner2010].
+It also allows for the possibility that certain land cover types may be locally beneficial, but detremental at wider scales, indicating that the cover type may not constitute a completely useable habitat.
+This technique has been used by other authors [@yen2014; @galpern2020].
 
-* Activity density of each arthropod was  fit as generalized additive models @wood2017, using _mgcv_ version `r packageVersion('mgcv')` 
-    + Count data of arthropods were fit using a negative binomial distribution
-    + To account for different lengths of trap exposure, log-days since trap placement was used as a fixed effect with its slope held at 1 (``offset" variable)
-    + To account for overall spatial and temporal autocorrelation in the data, we included day of year as a 1-dimensional smooth and easting and northing as a 2-dimensional smooth
-    + For each landscape term, we used three SoF regression terms:
-    + First, we used the proportion cover of all landscape cover classes in the annuli surrounding each trap location (spatial effect of cover class)
-    + Second, we used day of the year multiplied by the proportion of cover classes in each annuli (temporal effect of cover class) 
-    + Finally, we used a tensor-product interaction of landscape cover and day of year (spatio-temporal interaction of cover class)
-    + We used 10 basis dimensions for the spatial and temporal landscape smoothers, and 16 basis dimensions for the spatio-temporal interaction
-    + This was deemed adequate, as the effective degrees of freedom for all smoothing terms were far below the number of basis dimensions, indicating that no additional basis dimensions were needed (see Tables \@ref(tab:PteMelSmooth), \@ref(tab:ParDisSmooth), \@ref(tab:ParMoeSmooth), \@ref(tab:OpilioSmooth))
-    + To remove unimportant terms from the model, we used thin-plate regression splines with shrinkage ("bs=`ts'" in _mgcv_)
-    + This is a continuous analog to stepwise model selection, whereby weaker terms can be completely removed from the model, rather than just reduced to a line [@marra2011]
+Activity density of each arthropod was fit as generalized additive models @wood2017, using _mgcv_ version `r packageVersion('mgcv')`. 
+Count data of arthropods were fit using a negative binomial distribution with a log-link.
+To account for different lengths of trap exposure, log-days since trap placement was used as a fixed effect with its slope held at 1 ("offset" variable).
+We included day of year as a 1-dimensional smooth and easting and northing as a 2-dimensional smooth, in order to account for underlying spatial and temporal autocorrelation in the data.
+For each landscape term, we used three SoF regression terms:
+First, we used the proportion cover of all landscape cover classes in the annuli surrounding each trap location (spatial effect of cover class).
+Second, we used day of the year multiplied by the proportion of cover classes in each annuli (temporal effect of cover class). 
+Finally, we used a tensor-product interaction of landscape cover and day of year (spatio-temporal interaction of cover class).
+We used 10 basis dimensions for the spatial and temporal landscape smoothers, and 16 basis dimensions for the spatio-temporal interaction.
+This was deemed adequate, as the effective degrees of freedom for all smoothing terms were far below the number of basis dimensions, indicating that no additional basis dimensions were needed (see Tables \@ref(tab:PteMelSmooth), \@ref(tab:ParDisSmooth), \@ref(tab:ParMoeSmooth), \@ref(tab:OpilioSmooth)).
+To remove unimportant terms from the model, we used thin-plate regression splines with shrinkage ("bs=`ts'" in _mgcv_).
+This is a continuous analog to stepwise model selection, whereby weaker terms can be completely removed from the model, rather than just reduced to a line [@marra2011].
 <!-- + Double-penalization gave qualitatively similar results, but required twice the number of penalty terms, and some of the penalty terms were unstable  -->
 
-* Functional regression plots of landscape composition reveal which cover classes are acting as sources or sinks of organisms
-  + Positive responses to nearby landscape cover classes indicate that the cover class acts as a source (i.e. arthropods spill over *from* it)
-  + However, negative responses to nearby landscape cover classes can indicate one of two things:
-  + 1) It may indicate that the cover class acts as a sink (i.e. organisms spill over *into* it)
-  + 2) It may indicate that the cover class acts as a source, but it is unoccupied (i.e. no organisms available to spill over)
-  + We consider 1) to be the more likely scenario, as it is unlikely that any one cover class is *completely* unoccupied
-  + This model does not consider the next-generation fitness consequences of spillover
-  + For example, a cover class with low-quality habitat could act as an ecological trap [@galpern2017] if it acts as a sink but never as a source
-  + Alternatively, a cover class could act as a sink by providing high-quality habitat at certain times of the year (e.g.
-egg laying/feeding), but act as a source at other times (e.g.
-during emergence)
+Functional regression plots of landscape composition reveal which cover classes are acting as sources or sinks of organisms.
+Positive responses to nearby landscape cover classes indicate that the cover class acts as a source (i.e. arthropods spill over *from* it).
+However, negative responses to nearby landscape cover classes can indicate one of two things:
+1) It may indicate that the cover class acts as a sink (i.e.
+organisms spill over *into* it) or 2) it may indicate that the cover class acts as a source, but it is unoccupied (i.e.
+no organisms available to spill over).
+We consider 1) to be the more likely scenario, as it is unlikely that any one cover class is *completely* unoccupied.
+This model does not consider the next-generation fitness consequences of spillover.
+For example, a cover class with low-quality habitat could act as an ecological trap [@galpern2017] if it acts as a sink but never as a source.
+Alternatively, a cover class could act as a sink by providing high-quality habitat at certain times of the year (e.g. egg laying/feeding), but act as a source at other times (e.g. during emergence).
 
-* Some of the landscape terms in our model were strongly concurved, so we removed them from the model or combined them
-  + Concurvity is an non-linear analogue of multicollinearity that can bias estimates of standard errors [@buja1989]
-  + There is no agreed-upon threshold of unacceptable concurvity, but 0.5 is commonly used [@dominici2002; @ramsay2003] 
-  + Some landscape terms were strongly concurved (Figure \@ref(fig:concurvity)), namely forest and shrubland (max: 0.71), canola and cereal (max: 0.74), and grassland and wetland (max: 0.63)
-  + Forest and shrubland were combined into the ``Tree/Shrub" category, grassland and wetland were combined into the "Grass/Wetland" category, as they were strongly positively correlated at all distances, indicating similar feature classes
-  + Cereal was removed from the model, as it was negatively correlated with canola cover at distances less than 200m and was positively correlated at distances over 500m, reflecting the most common crop rotations (canola -> wheat -> barley) and the landscape structure present across our study region
+Some of the landscape terms in our model were strongly concurved, so we removed them from the model or combined them.
+Concurvity is a nonlinear analogue of multicollinearity, and can bias estimates of standard errors [@buja1989].
+There is no agreed-upon threshold of "unacceptable" concurvity, but 0.5 is commonly used [@dominici2002; @ramsay2003]. 
+Some landscape terms were strongly concurved (Figure \@ref(fig:concurvity)), namely forest and shrubland (max: 0.71), canola and cereal (max: 0.74), and grassland and wetland (max: 0.63).
+Forest and shrubland were combined into the ``Tree/Shrub" category, grassland and wetland were combined into the "Grass/Wetland" category, as they were strongly positively correlated at all distances, indicating similar feature classes.
+Cereal was removed from the model, as it was negatively correlated with canola cover at distances less than 200m and was positively correlated at distances over 500m, reflecting the most common crop rotations (canola -> wheat -> barley) and the landscape structure present across our study region.
 
@@
 
-* Grassland, cereal, and canola were the three most-abundant landcover classes surrounding our traps, accounting for `r 27.44+25.76+22.65`% of land cover
-  + Several landscape ``fingerprints" were evident in the landscape annuli, with cereal cover increasing with distance away, along with a corresponding decrease in canola cover (leading to the strong concurvity)
-  + Grassland cover was largely constant with distance, although a cluster of sites had uniformly high or low cover of grassland with distance
-  + Figure \@ref(fig:landscapeComp) displays the proportions of the 10 most-dominant land cover over distance
+Grassland, cereal, and canola were the three most-abundant landcover classes surrounding our traps, accounting for `r 27.44+25.76+22.65`% of land cover.
+Several landscape ``fingerprints" were evident in the landscape annuli, with cereal cover increasing with distance away, along with a corresponding decrease in canola cover (leading to the strong concurvity).
+Grassland cover was largely constant with distance, although a cluster of sites had uniformly high or low cover of grassland with distance.
+Figure \@ref(fig:landscapeComp) displays the proportions of the 10 most-dominant land cover over distance.
 
@@
 
-* _P. melanarius_ activity density was strongly influenced by trap location and landscape composition (Tables \@ref(tab:PteMelLinear), \@ref(tab:PteMelSmooth))
-  + Canola crops had a marginally higher activity density of _P.
-melanarius_ than other trap locations (Figure \@ref(fig:PteMelLandscape)a), possibly indicating that canola may allow faster movement of ground beetles
-  + In landscape composition, nearby grassland/wetland cover had a neutral effect early in the summer, but a negative effect later in the summer (Figure \@ref(fig:PteMelLandscape)b), indicating that _P.
-melanarius_ may move into grasslands later in the year
-  + Nearby canola had a positive effect in the early summer, but conversely, far-away canola (>800 m) had a negative effect, indicating that areas with widespread amounts of canola coverage had lower _P.
-melanarius_ activity density than those with simply local canola cover
-  + Two other crop types had unexpected effects on _P. melanarius_ activity density: pulses and flax
-  + Pulses acted as a late-season source, possibly indicating that _P. melanarius_ migrate out of the crop after (or during) harvest
-  + Flax had both a local and landscape-level negative effect, suggesting that the crop is not suitable for _P. melanarius_ foraging
-  + Finally, _P.
-melanarius_ activity density had a very strong temporal and spatial component (both p<0.001), indicating that phenology and local geographic factors were strong drivers of ground beetle activity density (Figure \@ref(fig:PteMelSpatiotemporal))
-  + Together, the landscape composition and the spatio-temporal component explained `r round(with(PteMelMod,summary(mod3)$dev.expl),3)*100`% of deviance ($R^2_{adj}$ = `r round(with(PteMelMod,summary(mod3)$r.sq),3)`)
+_P. melanarius_ activity density was strongly influenced by trap location and landscape composition (Tables \@ref(tab:PteMelLinear), \@ref(tab:PteMelSmooth)).
+Canola crops had a marginally higher activity density of _P.
+melanarius_ than other trap locations (Figure \@ref(fig:PteMelLandscape)a), possibly indicating that canola may allow faster movement of ground beetles.
+In landscape composition, nearby grassland/wetland cover had a neutral effect early in the summer, but a negative effect later in the summer (Figure \@ref(fig:PteMelLandscape)b), indicating that _P.
+melanarius_ may move into grasslands later in the year.
+Nearby canola had a positive effect in the early summer, but conversely, far-away canola (>800 m) had a negative effect, indicating that areas with widespread amounts of canola coverage had lower _P.
+melanarius_ activity density than those with simply local canola cover.
+Two other crop types had unexpected effects on _P. melanarius_ activity density: pulses and flax.
+Pulses acted as a late-season source, possibly indicating that _P. melanarius_ migrate out of the crop after (or during) harvest.
+Flax had both a local and landscape-level negative effect, suggesting that the crop is not suitable for _P. melanarius_ foraging.
+Finally, _P.
+melanarius_ activity density had a very strong temporal and spatial component (both p<0.001), indicating that phenology and local geographic factors were strong drivers of ground beetle activity density (Figure \@ref(fig:PteMelSpatiotemporal)).
+Together, the landscape composition and the spatio-temporal component explained `r round(with(PteMelMod,summary(mod3)$dev.expl),3)*100`% of deviance ($R^2_{adj}$ = `r round(with(PteMelMod,summary(mod3)$r.sq),3)`).
 <!-- + This could be related to climatic drivers (rainfall, growing degree days), or could simply represent a single yearly realization of a spatio-temporal random field  -->
@@
 
-* Activity density of _Pardosa_ was strongly influenced by trap location and landscape composition (Tables \@ref(tab:ParDisLinear), \@ref(tab:ParDisSmooth))
-  + Unlike _P. melanarius_, both _Pardosa_ species had far lower activity density in canola than any other cover type (Figures \@ref(fig:ParDisLandscape)a, \@ref(fig:ParMoeLandscape)a)
-  + Interestingly, nearby canola appeared to act as a source of both _Pardosa_, as activity density was positively related to the local proportion of canola early in the season, but negatively related later in the season (Figures \@ref(fig:ParDisLandscape)b, \@ref(fig:ParMoeLandscape)c, p=`r with(pdisSmTerms,p[Smoother=='ti(Distance,Day):Canola'])`, `r with(pmoeSmTerms,p[Smoother=='ti(Distance,Day):Canola'])`)
-  + Urban land cover had a similar effect on _P. moesta_, acting as an early source and a late sink (Figure \@ref(fig:ParMoeLandscape)f)
-  + Trees and shrubs acted as a sink for _P.
-distincta_ later in the season, and as a weak source early on in the season for _P.
-moesta_ (Figures \@ref(fig:ParDisLandscape)d, \@ref(fig:ParMoeLandscape)d)
-  + Grass and wetlands had strong local negative effect on _P.
+Activity density of _Pardosa_ was strongly influenced by trap location and landscape composition (Tables \@ref(tab:ParDisLinear), \@ref(tab:ParDisSmooth)).
+Unlike _P. melanarius_, both _Pardosa_ species had far lower activity density in canola than any other cover type (Figures \@ref(fig:ParDisLandscape)a, \@ref(fig:ParMoeLandscape)a).
+Interestingly, nearby canola appeared to act as a source of both _Pardosa_, as activity density was positively related to the local proportion of canola early in the season, but negatively related later in the season (Figures \@ref(fig:ParDisLandscape)b, \@ref(fig:ParMoeLandscape)c, p=`r with(pdisSmTerms,p[Smoother=='ti(Distance,Day):Canola'])`, `r with(pmoeSmTerms,p[Smoother=='ti(Distance,Day):Canola'])`).
+Urban land cover had a similar effect on _P. moesta_, acting as an early source and a late sink (Figure \@ref(fig:ParMoeLandscape)f).
+Trees and shrubs acted as a sink for _P. distincta_ later in the season, and as a weak source early on in the season for _P. moesta_ (Figures \@ref(fig:ParDisLandscape)d, \@ref(fig:ParMoeLandscape)d).
+Grass and wetlands had strong local negative effect on _P.
 moesta_, but a positive landscape-level effect, indicating that while these cover types act as a sink, the general amount of grasslands and wetlands in the area have a positive effect on _P.
-moesta_ abundance
-  + Pulses had a similar effect on _P. distincta_ activity density, where landscape-level abundance of pulses increased _P. distincta_ density, but local abundance had a neutral effect
-  + Finally, activity density of both _Pardosa_ species had a very strong temporal and spatial component, although the temporal component was dominant for _P.
+moesta_ abundance.
+Pulses had a similar effect on _P. distincta_ activity density, where landscape-level abundance of pulses increased _P. distincta_ density, but local abundance had a neutral effect.
+Finally, activity density of both _Pardosa_ species had a very strong temporal and spatial component, although the temporal component was dominant for _P.
 distincta_ (Figure \@ref(fig:ParDisSpatiotemporal)a, p=`r with(pdisSmTerms,p[Smoother=='s(Day)'])`) whereas the spatial component was dominant for _P.
-moesta_ (Figure \@ref(fig:ParMoeSpatiotemporal)b, p=`r with(pdisSmTerms,p[Smoother=='s(E,N)'])`)
-  + The landscape composition and the spatio-temporal component explained `r round(with(ParDisMod,summary(mod3)$dev.expl),3)*100`% of deviance ($R^2_{adj}$ = `r round(with(ParDisMod,summary(mod3)$r.sq),3)`) and `r round(with(ParMoeMod,summary(mod3)$dev.expl),3)*100`% of deviance ($R^2_{adj}$ = `r round(with(ParMoeMod,summary(mod3)$r.sq),3)`) for _P.
+moesta_ (Figure \@ref(fig:ParMoeSpatiotemporal)b, p=`r with(pdisSmTerms,p[Smoother=='s(E,N)'])`).
+The landscape composition and the spatio-temporal component explained `r round(with(ParDisMod,summary(mod3)$dev.expl),3)*100`% of deviance ($R^2_{adj}$ = `r round(with(ParDisMod,summary(mod3)$r.sq),3)`) and `r round(with(ParMoeMod,summary(mod3)$dev.expl),3)*100`% of deviance ($R^2_{adj}$ = `r round(with(ParMoeMod,summary(mod3)$r.sq),3)`) for _P.
 distincta_ and _P.
-moesta_, respectively
+moesta_, respectively.
 
@@
 
-* _Phalangium opilio_ activity density was strongly influenced by trap location, with pivot corners and wetlands having the highest activity density (Figure \@ref(fig:OpilioLandscape)a)
-  + _P.
-opilio_ was affected by grassland/wetlands (p=`r with(opilSmTerms,p[Smoother=='ti(Distance,Day):GrassWetland'])`), trees/shrubs (p`r with(opilSmTerms,p[Smoother=='s(Distance):TreeShrub'])`), and flax (p <`r with(opilSmTerms,p[Smoother=='s(Day):Flax'])`)
-  + Nearby grassland/wetland and trees/shrubs both had a negative effect on _P. opilio_ activity density, but only early in the season (Figures \@ref(fig:OpilioLandscape)b,c)
-  + Flax had a negative influence, but this effect was only strong during the middle of the season (Figure \@ref(fig:OpilioLandscape)d)
-  + However, the specific effect of these land cover types was not very large, as a competing model using only non-crop cover performed slightly better (Full model AIC = `r with(OpilioMod, sprintf("%.1f",AIC(mod3)))`, Non-crop model AIC = `r with(OpilioMod, sprintf("%.1f",AIC(mod4)))`)
-  + The temporal and spatial components, as in the other two species, were both very strong (both p`r with(opilSmTerms,p[grepl('E,N',Smoother)])`)
-  + Together, these results indicate that _P. opilio_ activity density is more strongly influenced by large-scale geographic patterns, and less so by landscape composition
-  + The landscape composition and the spatio-temporal component explained `r round(with(OpilioMod,summary(mod3)$dev.expl),3)*100`% of model deviance ($R^2_{adj}$ = `r round(with(OpilioMod,summary(mod3)$r.sq),3)`)
+_Phalangium opilio_ activity density was strongly influenced by trap location, with pivot corners and wetlands having the highest activity density (Figure \@ref(fig:OpilioLandscape)a).
+_P.
+opilio_ was affected by grassland/wetlands (p=`r with(opilSmTerms,p[Smoother=='ti(Distance,Day):GrassWetland'])`), trees/shrubs (p`r with(opilSmTerms,p[Smoother=='s(Distance):TreeShrub'])`), and flax (p <`r with(opilSmTerms,p[Smoother=='s(Day):Flax'])`).
+Nearby grassland/wetland and trees/shrubs both had a negative effect on _P. opilio_ activity density, but only early in the season (Figures \@ref(fig:OpilioLandscape)b,c).
+Flax had a negative influence, but this effect was only strong during the middle of the season (Figure \@ref(fig:OpilioLandscape)d).
+However, the specific effect of these land cover types was not very large, as a competing model using only non-crop cover performed slightly better (Full model AIC = `r with(OpilioMod, sprintf("%.1f",AIC(mod3)))`, Non-crop model AIC = `r with(OpilioMod, sprintf("%.1f",AIC(mod4)))`).
+The temporal and spatial components, as in the other two species, were both very strong (both p`r with(opilSmTerms,p[grepl('E,N',Smoother)])`).
+Together, these results indicate that _P. opilio_ activity density is more strongly influenced by large-scale geographic patterns, and less so by landscape composition.
+The landscape composition and the spatio-temporal component explained `r round(with(OpilioMod,summary(mod3)$dev.expl),3)*100`% of model deviance ($R^2_{adj}$ = `r round(with(OpilioMod,summary(mod3)$r.sq),3)`).
 
@@
 
-* We found that while _Pterostichus melanarius_, _Pardosa distincta_, and _Pardosa moesta_ responded to landscape composition, _Phalangium opilio_ did not
-  + _P. melanarius_ was influenced by grass/wetland, pasture, trees/shrubs, pulses, and urban land cover
-  + _P. distincta_ was influenced by grass/wetland, canola, pulses, and urban land cover
-  + _P. moesta_ was influenced by the same landscape components: grassland/wetland, canola, pulses, and urban land cover
-  + Finally, _P. opilio_ was weakly influenced by pasture, and trees/shrubs
-  + These results highlight the seasonal importance of non-crop marginal lands for predatory arthropod abundance (Table \@ref(tab:sumTab))
+We found that while _Pterostichus melanarius_, _Pardosa distincta_, and _Pardosa moesta_ responded to landscape composition, _Phalangium opilio_ did not.
+_P. melanarius_ was influenced by grass/wetland, pasture, trees/shrubs, pulses, and urban land cover.
+_P. distincta_ was influenced by grass/wetland, canola, pulses, and urban land cover.
+_P. moesta_ was influenced by the same landscape components: grassland/wetland, canola, pulses, and urban land cover.
+Finally, _P. opilio_ was weakly influenced by pasture, and trees/shrubs.
+These results highlight the seasonal importance of non-crop marginal lands for predatory arthropod abundance (Table \@ref(tab:sumTab)).
 
@@
 
-* The predatory ground beetle _Pterostichus melanarius_ responded to landscape composition, primarily to different crop types (Table \@ref(tab:sumTab),\@ref(tab:PteMelSmooth))
-  + Of the non-crop land categories, grassland and wetland cover acted as a late-season sink, suggesting that _P. melanarius_ may migrate into it at the end of the summer
-  + Other studies have found similar results, suggesting that untilled land is important off-field habitat for carabids [@desender1988; @fournier2002; but see @hatten2007]
-  + In particular, @purtauf2005 found that carabid density increased with proportion of nearby grasslands; our finding of grassland/wetland as late-season sink may represent _P.
-melanarius_ moving to overwintering habitat at the end of the season
-  + However, _P. melanarius_ is also found in a wide variety of habitats, and tends to prefer agricultural fields [@larsen2003], which our models also demonstrated
-  + We also found that canola and pulse crops acted as early- and mid-season sources of _P. melanarius_ 
-  + The roles that carabids play in pulse crops is not well-studied, but carabids are predators of pea-leaf weevils (_Sitona lineatus_) on other Fabaceae [@hamon1990]
-  + _P. melanarius_ is also known to prey upon other carabids that are predators of _S. lineatus_, such as _Bembidion quadrimaculatum_ [@vankosky2011]
-  + Either way this suggests that pulses may represent a potential food resource for _P. melanarius_, at least earlier in the season
+The predatory ground beetle _Pterostichus melanarius_ responded to landscape composition, primarily to different crop types (Table \@ref(tab:sumTab),\@ref(tab:PteMelSmooth)).
+Of the non-crop land categories, grassland and wetland cover acted as a late-season sink, suggesting that _P. melanarius_ may migrate into it at the end of the summer.
+Other studies have found similar results, suggesting that untilled land is important off-field habitat for carabids [@desender1988; @fournier2002; but see @hatten2007].
+In particular, @purtauf2005 found that carabid density increased with proportion of nearby grasslands; our finding of grassland/wetland as late-season sink may represent _P.
+melanarius_ moving to overwintering habitat at the end of the season.
+However, _P. melanarius_ is also found in a wide variety of habitats, and tends to prefer agricultural fields [@larsen2003], which our models also demonstrated.
+We also found that canola and pulse crops acted as early- and mid-season sources of _P. melanarius_. 
+The roles that carabids play in pulse crops is not well-studied, but carabids are predators of pea-leaf weevils (_Sitona lineatus_) on other Fabaceae [@hamon1990].
+_P. melanarius_ is also known to prey upon other carabids that are predators of _S. lineatus_, such as _Bembidion quadrimaculatum_ [@vankosky2011].
+Either way this suggests that pulses may represent a potential food resource for _P. melanarius_, at least earlier in the season.
   <!-- + Carabid diversity is higher in no-till agriculture [@bourassa2008, @puech2014] -->
 
-* Surprisingly, flax acted as a local and landscape level sink for _P.
+Surprisingly, flax acted as a local and landscape level sink for _P.
 melanarius_, and as an overall sink for _P.
-opilio_, suggesting that it may be inappropriate feeding or nesting cover for these beneficial arthropods
-  + Flax is more sensitive to weed competition than other small grains [@friesen1986; @kandel2020], so weed control tends to be more intense
-  + Lower weed abundance may cause flax fields to have lower levels of weed seeds to feed on, causing seed-feeding carabids to move to other locations [@trichard2014] 
-  + Alternatively, it could be that plant structural diversity due to extensive weed control, meaning that carabids have lower amounts of attractive ground cover [@butts2003; @clark1993]
-  + Why this occurs in flax fields but not canola or pulse crops is unclear, but may have to do with decreased shading or ground cover being less attractive to carabids [@butts2003]
-  + To our knowledge, there is no published research investigating effects of flax cropping on beneficial arthropods, so the causes of this pattern are speculative
+opilio_, suggesting that it may be inappropriate feeding or nesting cover for these beneficial arthropods.
+Flax is more sensitive to weed competition than other small grains [@friesen1986; @kandel2020], so weed control tends to be more intense.
+Lower weed abundance may cause flax fields to have lower levels of weed seeds to feed on, causing seed-feeding carabids to move to other locations [@trichard2014].
+Alternatively, it could be that plant structural diversity due to extensive weed control, meaning that carabids have lower amounts of attractive ground cover [@butts2003; @clark1993].
+Why this occurs in flax fields but not canola or pulse crops is unclear, but may have to do with decreased shading or ground cover being less attractive to carabids [@butts2003].
+To our knowledge, there is no published research investigating effects of flax cropping on beneficial arthropods, so the causes of this pattern are speculative.
 
-* The wolf spiders _Pardosa distincta_ and _Pardosa moesta_ both responded to landscape composition, but in slightly different ways
-  + Canola acted as an early-season source for both species, indicating that _Pardosa_ may use canola as foraging grounds
-  +
+The wolf spiders _Pardosa distincta_ and _Pardosa moesta_ both responded to landscape composition, but in slightly different ways.
+Lycosids employ a wandering-active predation strategy [@young1990], meaning that nearby landscape composition may be more influential than large-scale composition [@oberg2007; @oberg2008].
+Canola acted as an early-season source for both species, indicating that _Pardosa_ may use canola as foraging grounds.
+Trees and shrubs acted as a late season sink in both species, suggesting that they migrate to off-field areas with woody shrubs and trees for overwintering [but _P.
+distincta_ are known to be active during the winter; @aitchison1984].
+@drapela2011 also found that _Pardosa agrestis_ had higher activity density in areas with woody trees and shrubs.
+@moring1994 showed that _P. distincta_ were more active in grassy substrates.
+While _Pardosa_ are found in areas close to disturbed roadside strips [@drapela2008; @drapela2011; @kowal2011], _P.
+distincta_ appears to be less sensitive to disturbances than _P.
+moesta_ [@collins1996; @wade2010].
+We found that roads clearly acted as an early source and a late sink of _P. moesta_.
+Grassland and wetland, as well as pulses, also acted as a local sink, but a landscape-level source for _P. moesta_.
 
-  + @drapela2011 also found that _Pardosa agresti_ had higher activity density in areas with more woody trees and shrubs, as well as in areas close to roadside strips, suggesting similar habitat preferences in both Canadian and European contexts
+_Phalangium opilio_ activity density did not respond to landscape composition, aside from pasture (p=`r with(opilSmTerms,p[Smoother=='ti(distMat,endDayMat):Pasture'])`) and a weaker response to trees/shrubland (p=`r with(opilSmTerms,p[Smoother=='ti(distMat,endDayMat):TreeShrub'])`).
+_P. opilio_ avoids heavily grazed areas, possibly due to low humidity, but is active in most other habitat types [@sajna2011].
+In particular, it is largely found in human-altered landscapes with a large proportion of farming [@muster2014; @vandepoel2015Msc].
+Our results show that _P. opilio_ migrated into pastures.
+It is also found in large numbers at the edges of forests, and may migrate from forests into farmlands [@vandepoel2015Msc].
+We found the opposite pattern (albeit weakly): _P. opilio_ appears to migrate into forests.
 
-* _Phalangium opilio_ activity density did not respond to landscape composition, aside from pasture (p=`r with(opilSmTerms,p[Smoother=='ti(distMat,endDayMat):Pasture'])`) and a weaker response to trees/shrubland (p=`r with(opilSmTerms,p[Smoother=='ti(distMat,endDayMat):TreeShrub'])`)
-  + _P. opilio_ avoids heavily grazed areas, possibly due to low humidity, but is active in most other habitat types [@sajna2011]
-  + In particular, it is largely found in human-altered landscapes with a large proportion of farming [@muster2014; @vandepoel2015Msc]
-  + Our results show that _P. opilio_ migrated into pastures
-  + It is also found in large numbers at the edges of forests, and may migrate from forests into farmlands [@vandepoel2015Msc]
-  + We found the opposite pattern (albeit weakly): _P. opilio_ appears to migrate into forests
+Overall, we found that trees/shrubs, 
+The influence of landscape composition tended to be limited to a radius of about 500m, indicating that large-scale land cover may have a stronger effect on arthropod abundance than small-scale land cover
 
-* Overall, we found that trees/shrubs, 
-  + The influence of landscape composition tended to be limited to a radius of about 500m, indicating that large-scale land cover may have a stronger effect on arthropod abundance than small-scale land cover
+There was a strong temporal component to the landscape effects, meaning that it is important to consider how sinks and sources may change over the season.
+We did not consider the influence of previous years' crops, although carabids tend to be more abundant in areas of high crop rotation [@busch_Msc; @bertrand2016].
 
-* There was a strong temporal component to the landscape effects, meaning that it is important to consider how sinks and sources may change over the season
-  + We did not consider the influence of previous years' crops, although carabids tend to be more abundant in areas of high crop rotation [@busch_Msc; @bertrand2016]
-
-* These patterns indicate movement between landscape features, but since we did not directly observe arthropod movement between features, future studies should examine this
-  + Some land cover classes were strongly concurved (canola and cereal, wetland and grassland) with each other, we removed or combined them, meaning that we could not consider the influence of the categories independently
-  + Mark-recapture studies, monitoring movement patterns (e.g. radio tags), or two-sided traps could be useful
-  + Should also be linked to ecosystem services (e.g. predation on bait insects or weed seeds)
+These patterns indicate movement between landscape features, but since we did not directly observe arthropod movement between features, future studies should examine this
+Some land cover classes were strongly concurved (canola and cereal, wetland and grassland) with each other, we removed or combined them, meaning that we could not consider the influence of the categories independently.
+Mark-recapture studies, monitoring movement patterns (e.g. radio tags), or two-sided traps could be useful.
+Should also be linked to ecosystem services (e.g. predation on bait insects or weed seeds).
 

### 2020-08-05 frAnalysis.R
Reran models without cereal cover

@@ -38,8 +38,8 @@ oRingMat2Prop$GrassWetland <- oRingMat2Prop$Wetland + oRingMat2Prop$Grassland
 modFormulas <- 'count~offset(log(trapdays))+s(day,k=10,bs=basisFun)+s(E,N,k=50,bs=basisFun)' #Temporal + spatial
 # modFormulas <- paste0(modFormulas,'+ti(N,E,day,k=5,bs=basisFun)') # Add spatiotemporal interaction
 modFormulas[c(2,3,4)] <- paste0(modFormulas[1],'+trapLoc-1')
-# mod3Vars <- c('GrassWetland','Canola','Pasture','TreeShrub','Pulses','Flax','Urban') #Variables for mod3 (drops cereal)
-mod3Vars <- c('GrassWetland','Cereal','Canola','Pasture','TreeShrub','Pulses','Flax','Urban') #Includes cereal
+mod3Vars <- c('GrassWetland','Canola','Pasture','TreeShrub','Pulses','Flax','Urban') #Variables for mod3 (drops cereal)
+# mod3Vars <- c('GrassWetland','Cereal','Canola','Pasture','TreeShrub','Pulses','Flax','Urban') #Includes cereal
 # mod3Vars <- c('GrassWetland','Cereal','Canola','TreeShrub','Pulses','Flax','Urban') #Includes cereal, excludes pasture
 
 # mod3Vars <- c('Grassland','Cereal','Canola','Pasture','Pulses','Wetland','Urban','Shrubland','Flax','Forest') #Expanded variables for mod3 - adding Water causes problems
@@ -75,7 +75,7 @@ maptheme <- theme(panel.border=element_rect(size=1,fill=NA),axis.line=element_bl
 tempArth <- arth %>% filter(genus=='Pterostichus',species=='melanarius',year==2017) %>% group_by(BTID) %>% summarize(n=n())
 
 PteMelMod <- runMods(tempArth,trap,nnDistMat,oRingMat2Prop,formulas=modFormulas,basisFun='ts',doublePenalize=FALSE); beep(1)
-# save(PteMelMod,file='./data/PteMelMod.Rdata')
+save(PteMelMod,file='./data/PteMelMod.Rdata')
 # load('./data/PteMelMod.Rdata')
 
 #Tried running this with double-penalization instead of shrinkage. Results were similar, but some of the shrinkage 
[…]

### 2020-08-05 manuscript/manuscript_outline.Rmd
Got rid of old figure

@@
 
-Understanding of how landscape structure drives beneficial arthropod abundance is incomplete
+Landscape structure drives beneficial arthropod abundance, and is key for understanding how to manage benefical insects
 Bees are generally driven by flower/nest substrate availability [@roulston2011]
@@
 Can occur with pests or beneficial organisms [@woodcock2016]
+Contrast between landscape and local SNL is important [@boetzl2020; @vanSchalkwyk2020]; small patches can have a large effect if overall landscape lacks SNL
 Management goal: be able to design landscapes that benefit both farmers and insect diversity/abundance
 
-Point estimates of abundance are influenced by spatio-temporal processes 
+Abundance is also influenced by spatio-temporal processes, such as phenology and migration
 Arthropods move between landscape components depending on their life history
@@
 Certain habitat types may be sources of arthropods during some times of the year, but sinks during other times
-Counts in pitfall traps are a proxy of activity density (not actual density), but this is probably an OK measure, at least within fields [@lang2000]
+<!-- Counts in pitfall traps are a proxy of activity density (not actual density), but this is probably an OK measure, at least within fields [@lang2000] -->
 

### 2020-08-05 manuscript/manuscript_outline.Rmd
Added brief comment from PG

@@
 ---
-title: Landscape composition and beneficial insects
+title: Landscape composition and beneficial insects - time is important
+# PG: time is important in this paper - conservation efforts should consider temporal availability of resources
+# Find the angle and write for this
 # subtitle: 

### 2020-08-05 manuscript/manuscript_outline.Rmd
Removed flax from models. Updated figures.

@@
 load('../data/OpilioMod.Rdata')
+
+#Get landscape % cover for each cover class
+coverList <- PteMelMod$datList[9:25]
+siteID <- as.numeric(rownames(unique(cbind(PteMelMod$datList$E,PteMelMod$datList$N))))
+coverList <- lapply(coverList,function(x){
+  data.frame(site=as.character(siteID),x[siteID,]) %>%  #Get unique sites only, convert to DF
+  pivot_longer(cols=d30:d1500,names_to='dist',values_to='prop') %>% 
+  mutate(dist=as.numeric(gsub('d','',dist)))
+})
+coverList <- data.frame(cover=rep(names(coverList),each=nrow(coverList[[1]])),do.call('rbind',coverList))
 
@@
 We combined functionally similar landscape categories (cereals: _Triticum aestivum_ and _Hordeum vulgare_, pulses: _Pisum sativum_ and _Lens culinaris_, forest: coniferous and broadleaf), then extracted the landscape composition within a circle of a fixed radius surrounding each trap location.
-However, the radius of the circle necessary to characterize the landscape depends on the ``grain" of the landscape that is relevant to the abundance of a given organism [@addicott1987].
+The ten most-common cover classes represented 98% of the total land cover in our study region: grassland, cereal, canola, pasture, pulses, wetland, urban, shrubland, flax, and forest (Figure \@ref(fig:landscapeComp)); flax was removed, as only a single site had nearby flax cover.
+The radius of the circle necessary to characterize the landscape depends on the scale of the landscape that matters to a given organism [@addicott1987].
 Therefore, we divided the landscape into annuli (rings) surrounding each trap location.
@@
 We included day of year as a 1-dimensional smooth and easting and northing as a 2-dimensional smooth, in order to account for underlying spatial and temporal autocorrelation in the data.
+The deviance residuals from each model were visually inspected for normality and equal variance.
+
 For each landscape term, we used three SoF regression terms:
@@
 To remove unimportant terms from the model, we used thin-plate regression splines with shrinkage ("bs=`ts'" in _mgcv_).
-This is a continuous analog to stepwise model selection, whereby weaker terms can be completely removed from the model, rather than just reduced to a line [@marra2011].
+This is a continuous analog to stepwise model selection, whereby weaker terms can be completely removed from the model rather than reduced to a line [@marra2011].
 <!-- + Double-penalization gave qualitatively similar results, but required twice the number of penalty terms, and some of the penalty terms were unstable  -->
@@
 There is no agreed-upon threshold of "unacceptable" concurvity, but 0.5 is commonly used [@dominici2002; @ramsay2003]. 
-Some landscape terms were strongly concurved (Figure \@ref(fig:concurvity)), namely forest and shrubland (max: 0.71), canola and cereal (max: 0.74), and grassland and wetland (max: 0.63).
+Some landscape terms were strongly concurved (Figure \@ref(fig:concurvityFull)), namely forest and shrubland (max: 0.71), canola and cereal (max: 0.74), and grassland and wetland (max: 0.63).
 Forest and shrubland were combined into the ``Tree/Shrub" category, grassland and wetland were combined into the "Grass/Wetland" category, as they were strongly positively correlated at all distances, indicating similar feature classes.
 Cereal was removed from the model, as it was negatively correlated with canola cover at distances less than 200m and was positively correlated at distances over 500m, reflecting the most common crop rotations (canola -> wheat -> barley) and the landscape structure present across our study region.
+This resulted in a much-reduced set of landscape terms, none of which were strongly concurved with each other (Figure \@ref(fig:concurvity))
 
@@
 +-----------------+----------------------------+----------------------------+-----------------------------+-----------------------+
-| Flax            | - Local sink               |                            |                             | - Overall sink        |
-|                 | - Landscape sink           |                            |                             |                       |
-+-----------------+----------------------------+----------------------------+-----------------------------+-----------------------+
 | Urban           |                            |                            | - Local source (early)      |                       |
@@
 
-```{r concurvity, echo=FALSE, fig.cap='Concurvity estimates for top land cover classes'}  
-  include_graphics('../figures/coverCorPlots/concurvityEstimate.png')
+```{r landscapeComp, echo=FALSE, fig.cap='Landscape composition in annuli surrounding each trap location.
+Sites are represented by individual lines.
+Overall percent cover for each cover class is listed in each sub-figure heading.'}
+coverList %>% group_by(cover) %>% mutate(p=sum(prop)) %>% ungroup() %>% mutate(p=100*round(p/sum(unique(p)),4)) %>% 
+  mutate(cover=paste0(as.character(cover),' (',p,'%)'),prop=prop*100) %>% 
+  mutate(cover=factor(cover,levels=unique(cover))) %>% 
+  ggplot(aes(dist,prop,group=site))+geom_line(alpha=0.2)+
+  facet_wrap(~cover)+theme_classic()+labs(y='Percent cover',x='Distance (m)')
+
 ```
 
-```{r landscapeComp, echo=FALSE, fig.cap='Landscape composition in annuli surrounding each trap location'}  
-  include_graphics('../figures/oRingPlot2_AAFC.png')
+```{r concurvityFull, echo=FALSE, fig.cap='Concurvity estimates for ten most-abundant land cover classes'}  
+  include_graphics('../figures/coverCorPlots/concurvityEstimate_full.png')
+```
+
+```{r concurvity, echo=FALSE, fig.cap='Concurvity estimates for reduced cover classes used in models'}  
+  include_graphics('../figures/coverCorPlots/concurvityEstimate_reduced.png')
 ```

### 2020-08-05 frAnalysis.R

@@ -38,10 +38,8 @@ oRingMat2Prop$GrassWetland <- oRingMat2Prop$Wetland + oRingMat2Prop$Grassland
 modFormulas <- 'count~offset(log(trapdays))+s(day,k=10,bs=basisFun)+s(E,N,k=50,bs=basisFun)' #Temporal + spatial
 # modFormulas <- paste0(modFormulas,'+ti(N,E,day,k=5,bs=basisFun)') # Add spatiotemporal interaction
 modFormulas[c(2,3,4)] <- paste0(modFormulas[1],'+trapLoc-1')
-mod3Vars <- c('GrassWetland','Canola','Pasture','TreeShrub','Pulses','Flax','Urban') #Variables for mod3 (drops cereal)
-# mod3Vars <- c('GrassWetland','Cereal','Canola','Pasture','TreeShrub','Pulses','Flax','Urban') #Includes cereal
-# mod3Vars <- c('GrassWetland','Cereal','Canola','TreeShrub','Pulses','Flax','Urban') #Includes cereal, excludes pasture
-
+mod3Vars <- c('GrassWetland','Canola','Pasture','TreeShrub','Pulses','Urban') #Variables for mod3
+# mod3Vars <- c('GrassWetland','Cereal','Canola','Pasture','TreeShrub','Pulses','Flax','Urban') #As above, but includes cereal, flax
 # mod3Vars <- c('Grassland','Cereal','Canola','Pasture','Pulses','Wetland','Urban','Shrubland','Flax','Forest') #Expanded variables for mod3 - adding Water causes problems
 #Cereal may be causing problems in estimation - collinear with canola
 
@@ -90,15 +88,20 @@ AIC(mod1,mod2,mod3,mod4) #Best model has separate land cover types + SpatioTempo
 #Model 3 - landscape effects matter quite a bit
 summary(mod3); AIC(mod3)
 
+# #Checking whether flax adds anything
+# fitMethod <- 'REML'; fitFam <- 'nb'; basisFun <- 'ts'; doublePenalize <- F
+# mod3a <- update(mod3,.~. - s(distMat, by = Flax, bs = basisFun) - s(endDayMat, by = Flax, bs = basisFun) - ti(distMat, endDayMat, by = Flax, bs = basisFun))
+# summary(mod3a)
[…]

### 2020-08-07 manuscript/manuscript_outline.Rmd
Updated refs

@@
 bibliography: refs.bib
-# csl: ecology-letters.csl
+csl: ecology-letters.csl
 output: 
@@
 library(mgcv)
+library(pander)
 
@@
 The ten most-common cover classes represented 98% of the total land cover in our study region: grassland, cereal, canola, pasture, pulses, wetland, urban, shrubland, flax, and forest (Figure \@ref(fig:landscapeComp)); flax was removed, as only a single site had nearby flax cover.
-The radius of the circle necessary to characterize the landscape depends on the scale of the landscape that matters to a given organism [@addicott1987].
-Therefore, we divided the landscape into annuli (rings) surrounding each trap location.
-Each annulus was 30 m thick, and had inner radii ranging from 30 to 1470m, in increments of 30m.
+<!-- The radius of the circle necessary to characterize the landscape depends on the scale of the landscape that matters to a given organism [@addicott1987]. -->
+At each site, we extracted the proportion of each landscape cover class within 30m annuli (rings), with inner radii ranging from 30 to 1470m, in increments of 30m.
 Using functional regression [@ramsay2004], we were able to incorporate landscape information at different distance, allowing us to assess the impact of both local and regional landscape composition.
@@
 
-Functional regression plots of landscape composition reveal which cover classes are acting as sources or sinks of organisms.
-Positive responses to nearby landscape cover classes indicate that the cover class acts as a source (i.e. arthropods spill over *from* it).
+Some of the landscape terms in our model were strongly concurved, so we removed them from the model or combined them.
+Concurvity is a nonlinear analogue of multicollinearity, and can bias estimates of standard errors [@buja1989].
+There is no agreed-upon threshold of "unacceptable" concurvity, but 0.5 is commonly used [@dominici2002; @ramsay2003]. 
+Some landscape terms were strongly concurved (Figure \@ref(fig:concurvityFull)), namely forest and shrubland (max: 0.71), canola and cereal (max: 0.74), and grassland and wetland (max: 0.63).
+Forest and shrubland were combined into the ``Tree/Shrub" category, grassland and wetland were combined into the "Grass/Wetland" category, as they were strongly positively correlated at all distances, indicating similar feature classes.
+Cereal was removed from the model, as it was negatively correlated with canola cover at distances less than 200m and was positively correlated at distances over 500m, reflecting the most common crop rotations (canola $\rightarrow$ wheat $\rightarrow$ barley) and the commonly-used block structure (quarter-sections) present across our study region.
+This resulted in a reduced set of landscape terms, none of which were strongly concurved with each other (Figure \@ref(fig:concurvity))
+
+Functional regression plots of landscape composition reveal which cover classes are acting as sources or sinks of organisms, and at what spatial scale.
+Positive responses to nearby landscape cover classes indicate that the cover class acts as a net source (i.e. arthropods spill over *from* it).
 However, negative responses to nearby landscape cover classes can indicate one of two things:
@@
 We consider 1) to be the more likely scenario, as it is unlikely that any one cover class is *completely* unoccupied.
-This model does not consider the next-generation fitness consequences of spillover.
+As these data were collected from a single year, this model does not consider the next-generation fitness consequences of spillover.
 For example, a cover class with low-quality habitat could act as an ecological trap [@galpern2017] if it acts as a sink but never as a source.
 Alternatively, a cover class could act as a sink by providing high-quality habitat at certain times of the year (e.g. egg laying/feeding), but act as a source at other times (e.g. during emergence).
-
-Some of the landscape terms in our model were strongly concurved, so we removed them from the model or combined them.
-Concurvity is a nonlinear analogue of multicollinearity, and can bias estimates of standard errors [@buja1989].
-There is no agreed-upon threshold of "unacceptable" concurvity, but 0.5 is commonly used [@dominici2002; @ramsay2003]. 
-Some landscape terms were strongly concurved (Figure \@ref(fig:concurvityFull)), namely forest and shrubland (max: 0.71), canola and cereal (max: 0.74), and grassland and wetland (max: 0.63).
-Forest and shrubland were combined into the ``Tree/Shrub" category, grassland and wetland were combined into the "Grass/Wetland" category, as they were strongly positively correlated at all distances, indicating similar feature classes.
-Cereal was removed from the model, as it was negatively correlated with canola cover at distances less than 200m and was positively correlated at distances over 500m, reflecting the most common crop rotations (canola -> wheat -> barley) and the landscape structure present across our study region.
-This resulted in a much-reduced set of landscape terms, none of which were strongly concurved with each other (Figure \@ref(fig:concurvity))
 
@@
 
-Grassland, cereal, and canola were the three most-abundant landcover classes surrounding our traps, accounting for `r 27.44+25.76+22.65`% of land cover.
-Several landscape ``fingerprints" were evident in the landscape annuli, with cereal cover increasing with distance away, along with a corresponding decrease in canola cover (leading to the strong concurvity).
+Grassland, cereal, and canola were the three most-abundant landcover classes surrounding our traps, accounting for `r coverList %>% group_by(cover) %>% summarize(p=sum(prop)) %>% ungroup() %>% arrange(desc(p)) %>% mutate(prop=round(100*p/sum(p),2)) %>% slice(1:3) %>% pull(prop) %>% sum `% of land cover.
+Several landscape ``fingerprints" were evident in the landscape annuli, with cereal cover increasing with distance away, along with a corresponding decrease in canola cover (resulting in strong concurvity).
 Grassland cover was largely constant with distance, although a cluster of sites had uniformly high or low cover of grassland with distance.
@@
 Canola crops had a marginally higher activity density of _P.
-melanarius_ than other trap locations (Figure \@ref(fig:PteMelLandscape)a), possibly indicating that canola may allow faster movement of ground beetles.
-In landscape composition, nearby grassland/wetland cover had a neutral effect early in the summer, but a negative effect later in the summer (Figure \@ref(fig:PteMelLandscape)b), indicating that _P.
+melanarius_ than other trap locations (Figure \@ref(fig:PteMelLandscape)a), indicating that canola may allow faster movement of ground beetles, has higher overall population levels, or both.
+Nearby grassland/wetland cover had a neutral effect early in the summer, but a negative effect later in the summer (Figure \@ref(fig:PteMelLandscape)b), indicating that _P.
 melanarius_ may move into grasslands later in the year.
 Nearby canola had a positive effect in the early summer, but conversely, far-away canola (>800 m) had a negative effect, indicating that areas with widespread amounts of canola coverage had lower _P.
-melanarius_ activity density than those with simply local canola cover.
-Two other crop types had unexpected effects on _P. melanarius_ activity density: pulses and flax.
-Pulses acted as a late-season source, possibly indicating that _P. melanarius_ migrate out of the crop after (or during) harvest.
-Flax had both a local and landscape-level negative effect, suggesting that the crop is not suitable for _P. melanarius_ foraging.
+melanarius_ activity density than those with only local canola cover.
+Pulses acted as a late-season source, indicating that _P. melanarius_ may migrate out of the crop after (or during) harvest.
 Finally, _P.
@@
 
-Activity density of _Pardosa_ was strongly influenced by trap location and landscape composition (Tables \@ref(tab:ParDisLinear), \@ref(tab:ParDisSmooth)).
+Activity density of _P. distincta_ and _P. moesta_ was strongly influenced by trap location and landscape composition (Tables \@ref(tab:ParDisLinear), \@ref(tab:ParDisSmooth)).
 Unlike _P. melanarius_, both _Pardosa_ species had far lower activity density in canola than any other cover type (Figures \@ref(fig:ParDisLandscape)a, \@ref(fig:ParMoeLandscape)a).
@@
 moesta_ abundance.
-Pulses had a similar effect on _P. distincta_ activity density, where landscape-level abundance of pulses increased _P. distincta_ density, but local abundance had a neutral effect.
+_P. distincta_ was similarly affected by pulses: landscape-level abundance of pulses had a positive effect, but the local effect was neutral.
 Finally, activity density of both _Pardosa_ species had a very strong temporal and spatial component, although the temporal component was dominant for _P.
@@
 _Phalangium opilio_ activity density was strongly influenced by trap location, with pivot corners and wetlands having the highest activity density (Figure \@ref(fig:OpilioLandscape)a).
-_P.
-opilio_ was affected by grassland/wetlands (p=`r with(opilSmTerms,p[Smoother=='ti(Distance,Day):GrassWetland'])`), trees/shrubs (p`r with(opilSmTerms,p[Smoother=='s(Distance):TreeShrub'])`), and flax (p <`r with(opilSmTerms,p[Smoother=='s(Day):Flax'])`).
+_P. opilio_ was affected by grassland/wetlands (p=`r with(opilSmTerms,p[Smoother=='ti(Distance,Day):GrassWetland'])`) and trees/shrubs (p`r with(opilSmTerms,p[Smoother=='s(Distance):TreeShrub'])`). 
 Nearby grassland/wetland and trees/shrubs both had a negative effect on _P. opilio_ activity density, but only early in the season (Figures \@ref(fig:OpilioLandscape)b,c).
-Flax had a negative influence, but this effect was only strong during the middle of the season (Figure \@ref(fig:OpilioLandscape)d).
 However, the specific effect of these land cover types was not very large, as a competing model using only non-crop cover performed slightly better (Full model AIC = `r with(OpilioMod, sprintf("%.1f",AIC(mod3)))`, Non-crop model AIC = `r with(OpilioMod, sprintf("%.1f",AIC(mod4)))`).
@@
 
-We found that while _Pterostichus melanarius_, _Pardosa distincta_, and _Pardosa moesta_ responded to landscape composition, _Phalangium opilio_ did not.
+We found that while _Pterostichus melanarius_, _Pardosa distincta_, and _Pardosa moesta_ responded strongly to landscape composition, _Phalangium opilio_ did not.
 _P. melanarius_ was influenced by grass/wetland, pasture, trees/shrubs, pulses, and urban land cover.
@@
 _P. moesta_ was influenced by the same landscape components: grassland/wetland, canola, pulses, and urban land cover.
-Finally, _P. opilio_ was weakly influenced by pasture, and trees/shrubs.
+Finally, _P. opilio_ was influenced by pasture, and trees/shrubs.
 These results highlight the seasonal importance of non-crop marginal lands for predatory arthropod abundance (Table \@ref(tab:sumTab)).
@@
 
-+-----------------+----------------------------+----------------------------+-----------------------------+-----------------------+
++-----------------+----------------------------+----------------------------+---------------------------+-------------------------+
 | Cover class     | _P. melanarius_            | _P. distincta_             | _P. moesta_               | _P. opilio_             |
-+=================+============================+============================+=============================+=======================+
++================:+:===========================+:===========================+:==========================+:========================+
 | Grass & Wetland | - Local sink (late)        |                            | - Local sink              | - Local sink (early)    |
 |                 |                            |                            | - Landscape source        |                         |
-+-----------------+----------------------------+----------------------------+-----------------------------+-----------------------+
++-----------------+----------------------------+----------------------------+---------------------------+-------------------------+
 | Canola          | - Local source (early)     | - _Local source (early)_   | - Local source (early)    |                         |
 |                 | - Landscape sink (early)   | - _Local sink (late)_      | - Local sink (late)       |                         |
-+-----------------+----------------------------+----------------------------+-----------------------------+-----------------------+
++-----------------+----------------------------+----------------------------+---------------------------+-------------------------+
 | Pasture         |                            | - Landscape sink           |                           |                         | 
-+-----------------+----------------------------+----------------------------+-----------------------------+-----------------------+
-| Forest & Shrubs |                            | - Overall sink (late)      | - _Overall source (early)_  | - Local sink (early)  |
-|                 |                            |                            | - _Overall sink (late)_     |                       |
-+-----------------+----------------------------+----------------------------+-----------------------------+-----------------------+
-| Pulses          | - Overall source (late)    |                            | - Landscape source          |                       |
-+-----------------+----------------------------+----------------------------+-----------------------------+-----------------------+
++-----------------+----------------------------+----------------------------+---------------------------+-------------------------+
+| Forest & Shrubs |                            | - Sink (late)              |                           | - Local sink (early)    |
+|                 |                            |                            |                           | - Landscape source (mid)|
++-----------------+----------------------------+----------------------------+---------------------------+-------------------------+
+| Pulses          | - Source (late)            |                            | - Landscape source        |                         |
++-----------------+----------------------------+----------------------------+---------------------------+-------------------------+
 | Urban           |                            |                            | - Local source (early)    |                         |
-|                 |                            |                            | - Local sink (early)        |                       |
-|                 |                            |                            | - Landscape sink (late)     |                       |
+|                 |                            |                            | - Landscape sink (early)  |                         |
+|                 |                            |                            | - Local sink (late)       |                         |
 |                 |                            |                            | - Landscape source (late) |                         |
-+-----------------+----------------------------+----------------------------+-----------------------------+-----------------------+
++-----------------+----------------------------+----------------------------+---------------------------+-------------------------+
+
+<!-- This table looks like garbage, but I don't think pander will make it any better -->
 
@@
 
-Surprisingly, flax acted as a local and landscape level sink for _P.
+<!-- Surprisingly, flax acted as a local and landscape level sink for _P.
 melanarius_, and as an overall sink for _P.
 opilio_, suggesting that it may be inappropriate feeding or nesting cover for these beneficial arthropods.
-Flax is more sensitive to weed competition than other small grains [@friesen1986; @kandel2020], so weed control tends to be more intense.
-Lower weed abundance may cause flax fields to have lower levels of weed seeds to feed on, causing seed-feeding carabids to move to other locations [@trichard2014].
-Alternatively, it could be that plant structural diversity due to extensive weed control, meaning that carabids have lower amounts of attractive ground cover [@butts2003; @clark1993].
-Why this occurs in flax fields but not canola or pulse crops is unclear, but may have to do with decreased shading or ground cover being less attractive to carabids [@butts2003].
-To our knowledge, there is no published research investigating effects of flax cropping on beneficial arthropods, so the causes of this pattern are speculative.
+-->
+<!-- Flax is more sensitive to weed competition than other small grains [@friesen1986; @kandel2020], so weed control tends to be more intense. -->
+<!-- Lower weed abundance may cause flax fields to have lower levels of weed seeds to feed on, causing seed-feeding carabids to move to other locations [@trichard2014]. -->
+<!-- Alternatively, it could be that plant structural diversity due to extensive weed control, meaning that carabids have lower amounts of attractive ground cover [@butts2003; @clark1993]. -->
+<!-- Why this occurs in flax fields but not canola or pulse crops is unclear, but may have to do with decreased shading or ground cover being less attractive to carabids [@butts2003]. -->
+<!-- To our knowledge, there is no published research investigating effects of flax cropping on beneficial arthropods, so the causes of this pattern are speculative. -->
 
@@
 
-_Phalangium opilio_ activity density did not respond to landscape composition, aside from pasture (p=`r with(opilSmTerms,p[Smoother=='ti(distMat,endDayMat):Pasture'])`) and a weaker response to trees/shrubland (p=`r with(opilSmTerms,p[Smoother=='ti(distMat,endDayMat):TreeShrub'])`).
+_Phalangium opilio_ activity density responded grasslands and wetlands (p=`r with(opilSmTerms,p[Smoother=='ti(distMat,endDayMat):GrassWetland'])`) and trees/shrubland (p=`r with(opilSmTerms,p[Smoother=='ti(distMat,endDayMat):TreeShrub'])`).
 _P. opilio_ avoids heavily grazed areas, possibly due to low humidity, but is active in most other habitat types [@sajna2011].
@@
 Sites are represented by individual lines.
-Overall percent cover for each cover class is listed in each sub-figure heading.'}
+Overall percent cover for each cover class is listed in each sub-figure heading.', fig.width=7, fig.height=7}
 coverList %>% group_by(cover) %>% mutate(p=sum(prop)) %>% ungroup() %>% mutate(p=100*round(p/sum(unique(p)),4)) %>% 
@@
   ggplot(aes(dist,prop,group=site))+geom_line(alpha=0.2)+
-  facet_wrap(~cover)+theme_classic()+labs(y='Percent cover',x='Distance (m)')
+  facet_wrap(~cover,ncol=4)+theme_classic()+labs(y='Percent cover',x='Radius of annulus (m)')
 

### 2020-08-10 manuscript/manuscript_outline.Rmd
Worked on intro

@@
 ---
-title: Landscape composition and beneficial insects - time is important
+title: Non-crop features influence the abundance and timing of beneficial arthropod abundance
 # PG: time is important in this paper - conservation efforts should consider temporal availability of resources
 # Find the angle and write for this
+#Potential titles:
+# Non-crop features influence the abundance and timing of beneficial arthropod abundance
+# Seasonal sinks and sources of beneficial arthropods in Canadian prairie agroecosystems
+#
+
 # subtitle: 
@@
 abstract: Ground-dwelling arthropods are important generalist predators in prairie agro-ecosystems. 
-However, we don't know what types of landscape features they live in.
-Some may act as sources of arthropods during some parts of the year, and sinks during others.
-We examined four widely-distributed species of arthropods, using functional regression to examine their habitat preferences.
+However, we don't know what types of landscape features are useful for which types of arthropods, and during which parts of the year.
+Habitat features may act as sources of arthropods during some times of the year, but act as sinks at other times.
+We modeled the activity density of four widely-distributed species of arthropods, and used functional regression to reveal their habitat preferences. 
 We found that trees/shrubs, and roadside grasses acted as sources of arthropods. 
@@
 
+<!-- "Throwaway paragraph" -->
 Arthropod diversity is important to understand in agricultural systems
@@
 
-Landscape structure drives beneficial arthropod abundance, and is key for understanding how to manage benefical insects
-Bees are generally driven by flower/nest substrate availability [@roulston2011]
-Limited understanding of other arthropods (but see ``beetle hedges" from UK?)
-Beetles are limited by water, food, and oviposition sites [@lovei1996]
-No-till agriculture is better for some ground beetles [@busch_Msc]
-Arachnids are similarly limited by food, shelter
+Landscape structure drives beneficial arthropod abundance [@albrecht2010], and is key for understanding how to manage benefical arthropods in agroecosystems
+Non-cultivated areas, such as natural or semi-natural land (SNL) can act as important habitat for some arthropods [@duelli2003].
+Ground-nesting bees are generally driven by flower/nest substrate availability [@roulston2011], and beetles can be limited by water, food, and oviposition sites [@lovei1996].
+However, while the effect of SNL on bees is generally positive, its effect on beetles and parasitoids is unclear [@shackelford2013] 
+Other organisms may use SNL as travel corridors or overwintering sites, but may not be directly dependent on them.
+Spillover from SNL occurs when organisms migrate from SNL into adjacent cropland [@woodcock2016; @scheiner2020]. 
+The degree to which spillover occurs depends on the life history of the organism in question, as well as their reliance on the specific type of SNL.
+Non-adjacent cropland can also influence arthropod abundance if the organisms are long-distance dispersers [@oberg2008].
 
-Landscape structure can influence abundance of beneficial arthropods in agricultural areas [@albrecht2010]
-Spillover occurs when organisms migrate from suitable habitat patches
-Can occur with pests or beneficial organisms [@woodcock2016]
-Contrast between landscape and local SNL is important [@boetzl2020; @vanSchalkwyk2020]; small patches can have a large effect if overall landscape lacks SNL
-Management goal: be able to design landscapes that benefit both farmers and insect diversity/abundance
+<!-- Small patches of SNL can have a large effect if overall landscape lacks SNL (landscape contrast [@boetzl2020; @vanSchalkwyk2020]) -->
+<!-- Limited understanding of other arthropods (but see ``beetle hedges" from UK?) -->
+<!-- No-till agriculture is better for some ground beetles [@busch_Msc] -->
+<!-- Arachnids are similarly limited by food, shelter -->
 
-Abundance is also influenced by spatio-temporal processes, such as phenology and migration
-Arthropods move between landscape components depending on their life history
-e.g. Carabid beetles are thought to reproduce in field margins, but adults feed in fields [@desender1988]
-This means that spillover depends not only on habitat type, but on time of the year
-Certain habitat types may be sources of arthropods during some times of the year, but sinks during other times
+Abundance of benefical arthropods is also influenced by spatio-temporal processes, such as phenology and migration.
+Arthropods move between landscape components depending on their life history.
+e.g. Carabid beetles are thought to reproduce in field margins, but adults feed in fields [@desender1988].
+This means that spillover depends not only on habitat type, but on time of the year.
+Certain habitat types may be sources of arthropods during some times of the year, but sinks during other times.
 <!-- Counts in pitfall traps are a proxy of activity density (not actual density), but this is probably an OK measure, at least within fields [@lang2000] -->
+
+Our understanding of how landscape features influence beneficial arthropod abundance is incomplete.
+The feeding and life-history characteristics of many predatory ground beetles and spiders is not well-documented, meaning that it is difficult to make generalizations of which types of habitat may increase their abundance.
+Choosing the spatial scale of analysis depends on the characteristics of the organisms [@ahrenfeldt2015]; for example, bumblebee abundance can be controlled by both local- and landscape-wide SNL abundance [@westphal2006]
+Finally, different SNL patches may act as sources or sinks of arthropods at different times of the year, but this is rarely considered [@desender1988]
 
@@
 1) Untilled semi-natural land (SNL) provides oviposition and feeding areas for beneficial arthropods, meaning that nearby SNL should act as a source of arthropods.
-2) Crops in agricultural land attract pest insects during the growing season, and these insects are preyed upon by beneficial arthropods. 
+2) Crops in agricultural land attract pest insects during the growing season, and these insects are preyed upon by beneficial arthropods, meaning that crops consitute  
 However, pest phenology/crop senescence at the end of the season causes a decrease in the number of pests. 

### 2020-08-11 manuscript/manuscript_outline.Rmd
Added to Intro

@@
 # 
-
 # subtitle: 
@@
 Important for global biodiversity - insects may be declining globally
-Agriculture is ~36% of land worldwide
+Agriculture constitutes ~36% of land worldwide [@ramankutty2018], meaning large conservation potential
 Potential for win-win scenarios
 
-Landscape structure drives beneficial arthropod abundance [@albrecht2010], and is key for understanding how to manage benefical arthropods in agroecosystems
+Landscape structure drives beneficial arthropod abundance [@albrecht2010], and is key for understanding how to manage benefical arthropods in agroecosystems [@martin2020]
 Non-cultivated areas, such as natural or semi-natural land (SNL) can act as important habitat for some arthropods [@duelli2003].
-Ground-nesting bees are generally driven by flower/nest substrate availability [@roulston2011], and beetles can be limited by water, food, and oviposition sites [@lovei1996].
-However, while the effect of SNL on bees is generally positive, its effect on beetles and parasitoids is unclear [@shackelford2013] 
-Other organisms may use SNL as travel corridors or overwintering sites, but may not be directly dependent on them.
+Ground-nesting bees are generally driven by flower/nest substrate availability [@roulston2011], and beetles can be limited by water, food, and oviposition sites [@lovei1996; @gardiner2010].
+However, while the effect of SNL on bees is generally positive, its effect on beetles and parasitoids less consistent [@macfadyen2013; @shackelford2013] 
+Other organisms may use SNL as travel corridors or overwintering sites, but may not be directly dependent on them for reproduction.
 Spillover from SNL occurs when organisms migrate from SNL into adjacent cropland [@woodcock2016; @scheiner2020]. 
@@
 
-Abundance of benefical arthropods is also influenced by spatio-temporal processes, such as phenology and migration.
+The effect of SNL on arthropod abundance also depends on the seasonal timing of emergence, feeding, and hibernation.
+For this reason, it is important to consider the effect as being inherently spatio-temporal.
 Arthropods move between landscape components depending on their life history.
@@
 The feeding and life-history characteristics of many predatory ground beetles and spiders is not well-documented, meaning that it is difficult to make generalizations of which types of habitat may increase their abundance.
-Choosing the spatial scale of analysis depends on the characteristics of the organisms [@ahrenfeldt2015]; for example, bumblebee abundance can be controlled by both local- and landscape-wide SNL abundance [@westphal2006]
-Finally, different SNL patches may act as sources or sinks of arthropods at different times of the year, but this is rarely considered [@desender1988]
+Choosing the spatial scale of analysis depends on the characteristics of the organisms [@ahrenfeldt2015]; for example, bumblebee abundance can be controlled by both local- and landscape-wide SNL abundance [@westphal2006].
+Finally, different SNL patches may act as sources or sinks of arthropods at different times of the year, but this is rarely considered [but see @desender1988].
 
-In this study, we used pitfall trap counts of three species of beneficial arthropod to determine how landscape composition affects activity density of arthropods.
+In this study, we used pitfall traps to determine how landscape composition affects the seasonal activity density of arthropods across a prairie agroecosystem.
 We hypothesized that:
-1) Untilled semi-natural land (SNL) provides oviposition and feeding areas for beneficial arthropods, meaning that nearby SNL should act as a source of arthropods.
-2) Crops in agricultural land attract pest insects during the growing season, and these insects are preyed upon by beneficial arthropods, meaning that crops consitute  
-However, pest phenology/crop senescence at the end of the season causes a decrease in the number of pests. 
-This means that crop cover may act as a sink for beneficial insects early in the season as they migrate into the crop, and a source later on as they migrate out of the crop.
+1.
+Untilled semi-natural land (SNL) provides oviposition and feeding areas for predatory arthropods, meaning that nearby SNL should act as a source of arthropods during the early part of the season, and a sink during the later part of the season.
+2.
+Crops in agricultural land act as sources of pest insects during the growing season, while crop senescence at the end of the season causes a crash in the number of pests.
+This should result in agricultural land becoming a sink for predators in the early part of the season as they migrate into the crop, and a source at the end of the season as they migrate out of the crop.
+Using a novel statistical technique, we were able to isolate seasonal signals of changes in arthropod abundance at multiple landscape scales.
 

### 2020-08-11 manuscript/manuscript_outline.Rmd
Added to Intro

@@
 <!-- "Throwaway paragraph" -->
-Arthropod diversity is important to understand in agricultural systems
-Pests can cause large amounts of damage
-Beneficial insects can offset this
-Important for global biodiversity - insects may be declining globally
-Agriculture constitutes ~36% of land worldwide [@ramankutty2018], meaning large conservation potential
-Potential for win-win scenarios
+Arthropods are one of the most influential groups of animals in agricultural systems.
+Pest arthropods can cause huge amounts of damage to crops, resulting in yield losses for farmers and negative downstream economic effects.
+On the other hand, beneficial arthropods can deliver increased crop yields from extra pollination or free pest control.
+The seasonal "pulses" of food resources from agricultural land act as a bottom-up driver of arthropod communities, which include both native and introduced species.
+Agricultural land also constitutes 15 million km^2 (~36%) of land worldwide [@ramankutty2018], meaning that conservation of insect biodiversity should consider agricultural practices, as small changes in agricultural practices can have large effects globally.
+In particular, land managers and conservationists are interested in finding "win-win" practices; that is, practices that result in better conservation outcomes while achieving the same (or higher) crop yields.
 
-Landscape structure drives beneficial arthropod abundance [@albrecht2010], and is key for understanding how to manage benefical arthropods in agroecosystems [@martin2020]
+One method of passively manipulating agricultural arthropods is through landscape management [@albrecht2010; @landis2000; @martin2020].
 Non-cultivated areas, such as natural or semi-natural land (SNL) can act as important habitat for some arthropods [@duelli2003].
-Ground-nesting bees are generally driven by flower/nest substrate availability [@roulston2011], and beetles can be limited by water, food, and oviposition sites [@lovei1996; @gardiner2010].
+Ground-nesting bees are generally driven by flower and nest availability [@roulston2011], and beetles can be limited by water, food, and egg-laying sites [@lovei1996; @gardiner2010].
 However, while the effect of SNL on bees is generally positive, its effect on beetles and parasitoids less consistent [@macfadyen2013; @shackelford2013] 
 Other organisms may use SNL as travel corridors or overwintering sites, but may not be directly dependent on them for reproduction.
-Spillover from SNL occurs when organisms migrate from SNL into adjacent cropland [@woodcock2016; @scheiner2020]. 
+Spillover from SNL occurs when organisms migrate from SNL into adjacent cropland, or from cropland into SNL [@tscharntke2005b]. 
 The degree to which spillover occurs depends on the life history of the organism in question, as well as their reliance on the specific type of SNL.
@@
 1.
-Untilled semi-natural land (SNL) provides oviposition and feeding areas for predatory arthropods, meaning that nearby SNL should act as a source of arthropods during the early part of the season, and a sink during the later part of the season.
+Untilled semi-natural land (SNL) provides egg-laying and feeding areas for predatory arthropods, meaning that nearby SNL should act as a source of arthropods during the early part of the season, and a sink during the later part of the season.
 2.
-Crops in agricultural land act as sources of pest insects during the growing season, while crop senescence at the end of the season causes a crash in the number of pests.
+Crops in agricultural land act as sources of food for predatory arthropods during the growing season, while crop senescence at the end of the season causes a crash as pest popuations decrease.
 This should result in agricultural land becoming a sink for predators in the early part of the season as they migrate into the crop, and a source at the end of the season as they migrate out of the crop.
+3.
+Crops may act as a temporary feeding site for predators, but do not act as permanent habitat.
+Therefore, crops may act as a local sink for arthropods, but will also be negatively associated at larger (landscape-level) scales.
 Using a novel statistical technique, we were able to isolate seasonal signals of changes in arthropod abundance at multiple landscape scales.

### 2020-08-12 manuscript/manuscript_outline.Rmd
Worked on Discussion

@@
 # Seasonal sinks and sources of beneficial arthropods in Canadian prairie agroecosystems
+# Non-crop features create seasonal sinks and sources of beneficial arthropods
 # 
@@
 
-<!-- "Throwaway paragraph" -->
+<!-- Ralph's "throwaway paragraph" -->
 Arthropods are one of the most influential groups of animals in agricultural systems.
@@
 The seasonal "pulses" of food resources from agricultural land act as a bottom-up driver of arthropod communities, which include both native and introduced species.
-Agricultural land also constitutes 15 million km^2 (~36%) of land worldwide [@ramankutty2018], meaning that conservation of insect biodiversity should consider agricultural practices, as small changes in agricultural practices can have large effects globally.
+Agricultural land also constitutes 15 million km$^2$ (~36%) of land worldwide [@ramankutty2018], meaning that conservation of insect biodiversity should consider agricultural practices, as small changes in agricultural practices can have large effects globally.
 In particular, land managers and conservationists are interested in finding "win-win" practices; that is, practices that result in better conservation outcomes while achieving the same (or higher) crop yields.
@@
 
-<!-- This table looks like garbage, but I don't think pander will make it any better -->
+<!-- This table looks terrible, but I don't think pander will make it any better -->
 
-The predatory ground beetle _Pterostichus melanarius_ responded to landscape composition, primarily to different crop types (Table \@ref(tab:sumTab),\@ref(tab:PteMelSmooth)).
-Of the non-crop land categories, grassland and wetland cover acted as a late-season sink, suggesting that _P. melanarius_ may migrate into it at the end of the summer.
+The predatory ground beetle _Pterostichus melanarius_ responded to landscape composition, primarily to canola, pulses, and grass and wetland cover.
+Grassland and wetland cover acted as a late-season sink, suggesting that _P. melanarius_ may migrate into it at the end of the summer.
 Other studies have found similar results, suggesting that untilled land is important off-field habitat for carabids [@desender1988; @fournier2002; but see @hatten2007].
@@
 We also found that canola and pulse crops acted as early- and mid-season sources of _P. melanarius_.
-The roles that carabids play in pulse crops is not well-studied, but carabids are predators of pea-leaf weevils (_Sitona lineatus_) on other Fabaceae [@hamon1990].
-_P. melanarius_ is also known to prey upon other carabids that are predators of _S. lineatus_, such as _Bembidion quadrimaculatum_ [@vankosky2011].
-Either way this suggests that pulses may represent a potential food resource for _P. melanarius_, at least earlier in the season.
+Early in the season, canola crops acted as local source but a landscape-level sink, which may indicate that they provide only temporary feeding habitat.
+The effect of pulse crops on carabid abundance is not well-studied, but our results suggest that pulses may represent a potential food resource for _P. melanarius_.
+Carabids are predators of pea-leaf weevils (_Sitona lineatus_) on other Fabaceae [@hamon1990], and _P.
+melanarius_ can prey upon other carabids that are predators of _S.
+lineatus_, such as _Bembidion quadrimaculatum_ [@vankosky2011], so this effect may be direct or indirect.
+
 <!-- + Carabid diversity is higher in no-till agriculture [@bourassa2008, @puech2014] -->
-
 <!-- Surprisingly, flax acted as a local and landscape level sink for _P.
@@
 The wolf spiders _Pardosa distincta_ and _Pardosa moesta_ both responded to landscape composition, but in slightly different ways.
-Lycosids employ a wandering-active predation strategy [@young1990], meaning that nearby landscape composition may be more influential than large-scale composition [@oberg2007; @oberg2008].
-Canola acted as an early-season source for both species, indicating that _Pardosa_ may use canola as foraging grounds.
-Trees and shrubs acted as a late season sink in both species, suggesting that they migrate to off-field areas with woody shrubs and trees for overwintering [but _P.
-distincta_ are known to be active during the winter; @aitchison1984].
-@drapela2011 also found that _Pardosa agrestis_ had higher activity density in areas with woody trees and shrubs.
-@moring1994 showed that _P. distincta_ were more active in grassy substrates.
-While _Pardosa_ are found in areas close to disturbed roadside strips [@drapela2008; @drapela2011; @kowal2011], _P.
+Canola acted as an early-season source for both species, indicating that _Pardosa_ may use canola as foraging grounds, similar to _P. melanarius_.
+The response to other landscape cover classes, however, was different between each species.
+Aside from the (weak) effect of canola, we found that the only other landscape classes that influenced _P. distincta_ were pasture, and trees and shrubs.
+Pasture had a negative effect at the landscape scale, and trees and shrubs acted as a late season sink, suggesting that they use woody shrubs and trees for overwintering or winter foraging [@aitchison1984].
+_Pardosa_ are found in areas close to disturbed roadside strips [@drapela2008; @drapela2011; @kowal2011], but _P.
 distincta_ appears to be less sensitive to disturbances than _P.
 moesta_ [@collins1996; @wade2010].
-We found that roads clearly acted as an early source and a late sink of _P. moesta_.
-Grassland and wetland, as well as pulses, also acted as a local sink, but a landscape-level source for _P. moesta_.
+@moring1994 showed that _P.
+distincta_ were more active in grassy habitats, but we did not find evidence of this, aside from generally higher activity density in trap locations with higher grass cover (Figure \@ref(fig:ParDisLandscape)a).
+For _P. moesta_, we found that roads clearly acted as an early source and a late sink [similar to @drapela2008 and @drapela2011]. 
+Grassland and wetland, as well as pulses, also acted as a local sink, but a landscape-level source, suggesting that they draw _P.
+moesta_ away from trapping locations but enhance their landscape-level abundance.
+Lycosids employ a wandering-active predation strategy [@young1990], meaning that nearby landscape composition may be more influential than large-scale composition [@oberg2007; @oberg2008].
+However, we showed that several landscape features were also important at large spatial scales, including grass and wetland, pasture, pulses, and urban, showing that their dispersal distance may be further than previously though.
 
-_Phalangium opilio_ activity density responded grasslands and wetlands (p=`r with(opilSmTerms,p[Smoother=='ti(distMat,endDayMat):GrassWetland'])`) and trees/shrubland (p=`r with(opilSmTerms,p[Smoother=='ti(distMat,endDayMat):TreeShrub'])`).
+_Phalangium opilio_ activity density responded to grasslands and wetlands.
 _P. opilio_ avoids heavily grazed areas, possibly due to low humidity, but is active in most other habitat types [@sajna2011].

### 2020-08-13 manuscript/manuscript_outline.Rmd
Added Nakagawa R2 estimates

@@
   mutate(term=factor(term,levels=names(PteMelMod$mod3$sp)))
+
+#Calculate marginal and conditional R2 (Nakagawa and Schielzeth 2013)
+r2Nakagawa <- sapply(list(PteMelMod=PteMelMod,ParDisMod=ParDisMod,ParMoeMod=ParMoeMod,OpilioMod=OpilioMod), function(modList){
+  with(modList,getR2Terms(mod3,intVal=exp(mod1$coefficients[[1]]),thetaVal=mod1$family$getTheta(TRUE)))
+})
 
@@
 
-_Phalangium opilio_ activity density responded to grasslands and wetlands.
+_Phalangium opilio_ activity density responded to grasslands and wetlands as well as trees and shrubs, but habitat
+Grasslands and wetlands acted
+
 _P. opilio_ avoids heavily grazed areas, possibly due to low humidity, but is active in most other habitat types [@sajna2011].
 In particular, it is largely found in human-altered landscapes with a large proportion of farming [@muster2014; @vandepoel2015Msc].
-Our results show that _P. opilio_ migrated into pastures.
 It is also found in large numbers at the edges of forests, and may migrate from forests into farmlands [@vandepoel2015Msc].

### 2020-08-13 helperFunctions.R

@@ -219,3 +219,51 @@ compareFM <- function(female,male,topTitle='',vlines=NA){
   
   ggarrange(p1,p2,ncol=1,common.legend=TRUE,legend='right') 
 }
+
+#Function to extract marginal variance from terms from a GAM (a la Nakagawa and Schielzeth 2013)
+getR2Terms <- function(mod,intVal,thetaVal){ #Model object, plus intercept value from null model.
+  #Note from Appendix: intVal (exp(beta0)) should be obtained either from a model with centred or scaled variables (sense Schielzeth 2010), or an intercept‐only model while including all random effects. Not clear whether this should be done with theta as well, but I assume so.
+  #Assumes models follow same structure as used in frAnalysis.R
+  
+  #Distribution-specific variance:
+  
+  #For a poisson distribution (see Appendix 1 in https://doi.org/10.1111/j.2041-210x.2012.00261.x):
+  # E(x) = lambda
+  # var(x) = lambda
+  # var(ln(x)) = ln(1 + var(x)/lambda^2)
+  #            = ln(1 + lambda/lambda^2)
+  #            = ln(1 + 1/lambda)
+  
+  #For a negative binomial distribution (see Appendix 1 in https://doi.org/10.1101/095851):
+  # E(x) = mu
+  # var(x) = mu(1+mu/theta)
+  # var(ln(x)) = ln(1 + var(x)/mu^2)
+  #            = ln(1 + mu(1+mu/theta)/mu^2)
+  #            = ln(1 + 1/mu + 1/theta)
+  #            = ln(1 + 1/exp(Intercept) + 1/theta)
+  
+  c1 <- mod$coefficients #Coefs
+  m1 <- model.matrix(mod) #Model matrix
+  
+  #Linear terms
+  lt <- attributes(mod$pterms)$term.labels
+  ltVar <- sapply(lt,function(x) var(m1[,grepl(x,colnames(m1))] %*% c1[grepl(x,names(c1))])) 
+  
+  #Smooth terms
+  st <- sapply(mod$smooth,function(x) x$label) #Get smoothing terms
+  st <- unique(gsub('(s|ti)\\((distMat|endDayMat|distMat,endDayMat)\\)\\:','',st)) #Reduce to unique terms
[…]

### 2020-08-15 manuscript/manuscript_outline.Rmd
Worked on Nakagawa R2

--- 2020-08-12 manuscript/manuscript_outline.Rmd
@@
 library(knitr)
+# library(kableExtra)
 library(tidyverse)
 library(mgcv)
-library(pander)
-
-#Helper functions
-
-#Capitalize
-firstUpper <- function(x){
-  paste0(toupper(substring(x,1,1)),substring(x,2,nchar(x)))
-}
-
-#Rounds to dig digits, converts to character, anything less than digits becomes "<0.xx1"
-# Useful for tables
-roundLess <- function(x,dig){
-  x <- as.character(round(x,dig))
-  x[x=='0'] <- paste0('<0.',strrep('0',dig-1),'1',collapse='')
-  return(x)
-}
-
-boldRMD <- function(x) paste0('**',x,'**') #Makes text bold in rMarkdown
-boldLaTeX <- function(x) paste0('\\textbf{',x,'}') #Makes text bold in LaTeX
 
@@
 load('../data/OpilioMod.Rdata')
+
+source('../helperFunctions.R') #Load helper functions
 
@@
 coverList <- data.frame(cover=rep(names(coverList),each=nrow(coverList[[1]])),do.call('rbind',coverList))
+
+#Calculate marginal and conditional R2 (Nakagawa and Schielzeth 2013)
+
+#Overall R2 (conditional/marginal)
+r2Nakagawa <- sapply(list(PteMelMod=PteMelMod,ParDisMod=ParDisMod,ParMoeMod=ParMoeMod,OpilioMod=OpilioMod), function(modList){
+  with(modList,getR2Terms(mod3,intVal=exp(mod1$coefficients[[1]]),thetaVal=mod1$family$getTheta(TRUE)))
+}) %>% round(.,3) %>% as.data.frame()
+
+#Piecewise R2
+r2Nakagawa2 <- lapply(list(PteMelMod=PteMelMod,ParDisMod=ParDisMod,ParMoeMod=ParMoeMod,OpilioMod=OpilioMod), function(modList){
+  with(modList,getR2Terms(mod3,intVal=exp(mod1$coefficients[[1]]),thetaVal=mod1$family$getTheta(TRUE),individual=TRUE)) %>%
+    mutate(fixed=!grepl('(day|E,N|sigmaD)',terms),random=grepl('(day|E,N)',terms)) %>% 
+    mutate(r2comp=round(var/sum(var),4))
+}) %>% do.call('rbind',.) %>% rownames_to_column('model') %>% mutate(model=gsub('.[0-9]{1,2}','',model))
 
@@
 This is a continuous analog to stepwise model selection, whereby weaker terms can be completely removed from the model rather than reduced to a line [@marra2011].
+Finally, we calculated the R$^2$ for each group of terms in each model [@nakagawa2013; @nakagawa2017].
 <!-- + Double-penalization gave qualitatively similar results, but required twice the number of penalty terms, and some of the penalty terms were unstable  -->
@@
 melanarius_ activity density had a very strong temporal and spatial component (both p<0.001), indicating that phenology and local geographic factors were strong drivers of ground beetle activity density (Figure \@ref(fig:PteMelSpatiotemporal)).
-Together, the landscape composition and the spatio-temporal component explained `r round(with(PteMelMod,summary(mod3)$dev.expl),3)*100`% of deviance ($R^2_{adj}$ = `r round(with(PteMelMod,summary(mod3)$r.sq),3)`).
-<!-- + This could be related to climatic drivers (rainfall, growing degree days), or could simply represent a single yearly realization of a spatio-temporal random field  -->
+The landscape composition and trap location explained `r r2Nakagawa$PteMelMod[1]*100`%  of variance in activity density, while the spatial and temporal smoothers accounted for `r with(r2Nakagawa,(PteMelMod[2]-PteMelMod[1])*100)`% (Table \@ref(tab:rSquared)).
 
 ```{r PteMelLandscape, echo=FALSE, fig.cap='Landscape influence on _Pterostichus melanarius_ activity density.
-Lines/dots represent means, and bars/shaded regions represent 95% confidence intervals (1.96 x SE).
+Lines and dots represent means, and bars and shaded regions represent 95% confidence intervals (1.96 x SE).
 Coloured regions represent early-, mid-, and late-season effects (red, green, blue)'}
-  include_graphics('../figures/Pterostichus_melanarius_fixeff.png')
+  include_graphics('../figures/Pterostichus_melanarius_fixeff.png',dpi=NA)
 ```
@@
 moesta_ (Figure \@ref(fig:ParMoeSpatiotemporal)b, p=`r with(pdisSmTerms,p[Smoother=='s(E,N)'])`).
-The landscape composition and the spatio-temporal component explained `r round(with(ParDisMod,summary(mod3)$dev.expl),3)*100`% of deviance ($R^2_{adj}$ = `r round(with(ParDisMod,summary(mod3)$r.sq),3)`) and `r round(with(ParMoeMod,summary(mod3)$dev.expl),3)*100`% of deviance ($R^2_{adj}$ = `r round(with(ParMoeMod,summary(mod3)$r.sq),3)`) for _P.
+The landscape composition and trap location explained `r r2Nakagawa$ParDisMod[1]*100`%  and `r r2Nakagawa$ParMoeMod[1]*100`% of variance in activity density, while the spatial and temporal smoothers accounted for `r with(r2Nakagawa,(ParDisMod[2]-ParDisMod[1])*100)`%  and `r with(r2Nakagawa,(ParMoeMod[2]-ParMoeMod[1])*100)`%, for _P.
 distincta_ and _P.
-moesta_, respectively.
+moesta_ respectively.
 
 ```{r ParDisLandscape, echo=FALSE, fig.cap='Landscape influence on _Pardosa distincta_ activity density.
-Lines/dots represent means, and bars/shaded regions represent 95% confidence intervals (1.96 x SE).
+Lines and dots represent means, and bars and shaded regions represent 95% confidence intervals (1.96 x SE).
 Coloured regions represent early-, mid-, and late-season effects (red, green, blue)'}
-  include_graphics('../figures/Pardosa_distincta_fixeff.png')
+  include_graphics('../figures/Pardosa_distincta_fixeff.png',dpi=NA)
 ```
 
-```{r ParMoeLandscape, echo=FALSE, fig.cap='Landscape influence on \\emph{Pardosa moesta} activity density.
-Lines/dots represent means, and bars/shaded regions represent 95% confidence intervals (1.96 x SE).
+```{r ParMoeLandscape, echo=FALSE, fig.cap='Landscape influence on _Pardosa moesta_ activity density.
+Lines and dots represent means, and bars and shaded regions represent 95% confidence intervals (1.96 x SE).
 Coloured regions represent early-, mid-, and late-season effects (red, green, blue)'}
-  include_graphics('../figures/Pardosa_moesta_fixeff.png')
+  include_graphics('../figures/Pardosa_moesta_fixeff.png',dpi=NA)
 ```
@@
 Together, these results indicate that _P. opilio_ activity density is more strongly influenced by large-scale geographic patterns, and less so by landscape composition.
-The landscape composition and the spatio-temporal component explained `r round(with(OpilioMod,summary(mod3)$dev.expl),3)*100`% of model deviance ($R^2_{adj}$ = `r round(with(OpilioMod,summary(mod3)$r.sq),3)`).
+The landscape composition and trap location explained `r r2Nakagawa$OpilioMod[1]*100`%  of variance in activity density, while the spatial and temporal smoothers accounted for `r with(r2Nakagawa,(OpilioMod[2]-OpilioMod[1])*100)`%.
 
 ```{r OpilioLandscape, echo=FALSE, fig.cap='Landscape influence on _Phalangium opilio_ activity density.
-Lines/dots represent means, and bars/shaded regions represent 95% confidence regions.
+Lines and dots represent means, and bars and shaded regions represent 95% confidence regions.
 Dashed line on panels b-f represents zero effect.
 Coloured regions represent early-, mid-, and late-season effects (red, green, blue)'}
-  include_graphics('../figures/Opiliones_fixeff.png')
+  include_graphics('../figures/Opiliones_fixeff.png',dpi=NA)
+```
+
+```{r rSquared, echo=FALSE}  
+  r2Nakagawa2 %>% select(model,terms,r2comp) %>% mutate(terms=as.character(terms),r2comp=r2comp*1) %>% 
+  pivot_wider(names_from=model,values_from=r2comp) %>% 
+  mutate(terms=case_when(terms=='trapLoc' ~ 'Trap Location', terms=='s(day)' ~ 'Day of Year',
+                         terms=='s(E,N)' ~ 'Spatial Location', terms=='GrassWetland' ~ 'Grass/Wetland',
+                         terms=='TreeShrub' ~ 'Trees/Shrubs', terms=='sigmaD' ~ 'Residual',
+                         terms=='Urban' ~ 'Road margins', TRUE ~ terms)) %>% 
+  kable(.,caption='R$^2_{GLMM}$ for model components, representing the proportion of total variance attributable to each term.',
+        col.names=c('Term','$\\emph{Pterostichus melanarius}$','$\\emph{Pardosa distincta}$','$\\emph{Pardosa moesta}$','$\\emph{Phalangium opilio}$'),
+        digits=c(1,3,3,3,3),align='rllll',escape=FALSE) 
 ```
@@
 
-We found that while _Pterostichus melanarius_, _Pardosa distincta_, and _Pardosa moesta_ responded strongly to landscape composition, _Phalangium opilio_ did not.
+We found that _Pterostichus melanarius_, _Pardosa distincta_, _Pardosa moesta_, and _Phalangium opilio_ responded strongly to landscape composition.
 _P. melanarius_ was influenced by grass/wetland, pasture, trees/shrubs, pulses, and urban land cover.
@@
 _P. moesta_ was influenced by the same landscape components: grassland/wetland, canola, pulses, and urban land cover.
-Finally, _P. opilio_ was influenced by pasture, and trees/shrubs.
+Finally, _P. opilio_ was influenced by grass/wetland, and trees/shrubs.
 These results highlight the seasonal importance of non-crop marginal lands for predatory arthropod abundance (Table \@ref(tab:sumTab)).
@@
 ```{r concurvityFull, echo=FALSE, fig.cap='Concurvity estimates for ten most-abundant land cover classes'}  
-  include_graphics('../figures/coverCorPlots/concurvityEstimate_full.png')
+  include_graphics('../figures/coverCorPlots/concurvityEstimate_full.png',dpi=NA)
 ```
@@
 ```{r concurvity, echo=FALSE, fig.cap='Concurvity estimates for reduced cover classes used in models'}  
-  include_graphics('../figures/coverCorPlots/concurvityEstimate_reduced.png')
+  include_graphics('../figures/coverCorPlots/concurvityEstimate_reduced.png',dpi=NA)
 ```
@@
 ```{r PteMelSpatiotemporal, echo=FALSE, fig.cap='Temporal and spatial components of _Pterostichus melanarius_ activity density'}
-  include_graphics('../figures/Pterostichus_melanarius_raneff.png')
+  include_graphics('../figures/Pterostichus_melanarius_raneff.png',dpi=NA)
 ```
@@
 ```{r ParDisSpatiotemporal, echo=FALSE, fig.cap='Temporal and spatial components of _Pardosa distincta_ activity density'}
-  include_graphics('../figures/Pardosa_distincta_raneff.png')
+  include_graphics('../figures/Pardosa_distincta_raneff.png',dpi=NA)
 ```
@@
 ```{r ParMoeSpatiotemporal, echo=FALSE, fig.cap='Temporal and spatial components of \\emph{Pardosa moesta} activity density'}
-  include_graphics('../figures/Pardosa_moesta_raneff.png')
+  include_graphics('../figures/Pardosa_moesta_raneff.png',dpi=NA)
 ```
@@
 ```{r OpilioSpatiotemporal, echo=FALSE, fig.cap='Temporal and spatial components of _Phalangium opilio_ activity density'}
-  include_graphics('../figures/Opiliones_raneff.png')
+  include_graphics('../figures/Opiliones_raneff.png',dpi=NA)
 ```

### 2020-08-15 helperFunctions.R

@@ -221,7 +221,7 @@ compareFM <- function(female,male,topTitle='',vlines=NA){
 }
 
 #Function to extract marginal variance from terms from a GAM (a la Nakagawa and Schielzeth 2013)
-getR2Terms <- function(mod,intVal,thetaVal){ #Model object, plus intercept value from null model.
+getR2Terms <- function(mod,intVal,thetaVal,individual=FALSE){ #Model object, plus intercept value from null model.
   #Note from Appendix: intVal (exp(beta0)) should be obtained either from a model with centred or scaled variables (sense Schielzeth 2010), or an intercept‐only model while including all random effects. Not clear whether this should be done with theta as well, but I assume so.
   #Assumes models follow same structure as used in frAnalysis.R
   
@@ -242,8 +242,8 @@ getR2Terms <- function(mod,intVal,thetaVal){ #Model object, plus intercept value
   #            = ln(1 + 1/mu + 1/theta)
   #            = ln(1 + 1/exp(Intercept) + 1/theta)
   
-  c1 <- mod$coefficients #Coefs
-  m1 <- model.matrix(mod) #Model matrix
+  c1 <- mod$coefficients #Get coefs
+  m1 <- model.matrix(mod) #Get model matrix
   
   #Linear terms
   lt <- attributes(mod$pterms)$term.labels
@@ -260,10 +260,31 @@ getR2Terms <- function(mod,intVal,thetaVal){ #Model object, plus intercept value
   #Distribution-specific variance (sigma^2_d) - assumes intercept is 0
   sigmaD <- log(1+(1/intVal)+(1/thetaVal))
   
-  r2 <- c(sum(sigmaF$var[c(1,4:9)])/(sum(sigmaF$var)+sigmaD), #"Marginal" R2 (no spatial/temporal smoothers)
-          sum(sigmaF$var)/(sum(sigmaF$var)+sigmaD)) #Conditional R2
-  names(r2) <- c('Marginal','Conditional')
-  
-  return(r2)
+  if(individual){ #Return individual variance components, and let the user figure it out
+    return(rbind(sigmaF,data.frame(terms='sigmaD',var=sigmaD)))
+  } else {
+    r2 <- c(sum(sigmaF$var[!grepl('(day|E,N)',sigmaF$terms)])/(sum(sigmaF$var)+sigmaD), #"Marginal" R2 (no spatial/temporal smoothers)
[…]

### 2020-08-17 manuscript/manuscript_outline.Rmd
Finished first draft

@@
 The feeding and life-history characteristics of many predatory ground beetles and spiders is not well-documented, meaning that it is difficult to make generalizations of which types of habitat may increase their abundance.
-Choosing the spatial scale of analysis depends on the characteristics of the organisms [@ahrenfeldt2015]; for example, bumblebee abundance can be controlled by both local- and landscape-wide SNL abundance [@westphal2006].
+Choosing the spatial scale of analysis depends on the characteristics of the organisms [@ahrenfeldt2015]; for example, bumblebee abundance can be controlled by both local- and landscape-scale SNL abundance [@westphal2006].
 Finally, different SNL patches may act as sources or sinks of arthropods at different times of the year, but this is rarely considered [but see @desender1988].
@@
 3.
-Crops may act as a temporary feeding site for predators, but do not act as permanent habitat.
+Crops can act as a temporary feeding site for predators, but not as permanent habitat.
 Therefore, crops may act as a local sink for arthropods, but will also be negatively associated at larger (landscape-level) scales.
@@
 In our case, each column represents the proportion of a given landscape cover class within each annulus, with increasing radii away from the location of the trap, and the coefficients are a smooth function of distance ($\beta_i = f(distance_i)$), meaning that the coefficients represent the (additive) effect of a given type of landscape cover at distances away from the trap.
-This avoids the fundamental problem of choosing an optimal radius of landscape composition, and allows the possibility that the size of the landscape ``grain" relevant to a given organism may change over the course of its life stages [@addicott1987; @lima1996; @gardiner2010].
+This avoids the fundamental problem of choosing an optimal radius of landscape composition, and allows the possibility that the size of the landscape "grain" relevant to a given organism may change over the course of its life stages [@addicott1987; @lima1996; @gardiner2010].
 It also allows for the possibility that certain land cover types may be locally beneficial, but detremental at wider scales, indicating that the cover type may not constitute a completely useable habitat.
@@
 Finally, _P.
-melanarius_ activity density had a very strong temporal and spatial component (both p<0.001), indicating that phenology and local geographic factors were strong drivers of ground beetle activity density (Figure \@ref(fig:PteMelSpatiotemporal)).
+melanarius_ activity density had a strong temporal and spatial component (both p<0.001), indicating that phenology and local geographic factors were strong drivers of ground beetle activity density (Figure \@ref(fig:PteMelSpatiotemporal)).
 The landscape composition and trap location explained `r r2Nakagawa$PteMelMod[1]*100`%  of variance in activity density, while the spatial and temporal smoothers accounted for `r with(r2Nakagawa,(PteMelMod[2]-PteMelMod[1])*100)`% (Table \@ref(tab:rSquared)).
@@
 Unlike _P. melanarius_, both _Pardosa_ species had far lower activity density in canola than any other cover type (Figures \@ref(fig:ParDisLandscape)a, \@ref(fig:ParMoeLandscape)a).
-Interestingly, nearby canola appeared to act as a source of both _Pardosa_, as activity density was positively related to the local proportion of canola early in the season, but negatively related later in the season (Figures \@ref(fig:ParDisLandscape)b, \@ref(fig:ParMoeLandscape)c, p=`r with(pdisSmTerms,p[Smoother=='ti(Distance,Day):Canola'])`, `r with(pmoeSmTerms,p[Smoother=='ti(Distance,Day):Canola'])`).
+Nearby canola appeared to act as a source of _P.
+moesta_ and a weak source of _P.
+distincta_, as activity density was positively related to the local proportion of canola early in the season, but negatively related later in the season (Figures \@ref(fig:ParDisLandscape)b, \@ref(fig:ParMoeLandscape)c, p=`r with(pdisSmTerms,p[Smoother=='ti(Distance,Day):Canola'])`, `r with(pmoeSmTerms,p[Smoother=='ti(Distance,Day):Canola'])`).
 Urban land cover had a similar effect on _P. moesta_, acting as an early source and a late sink (Figure \@ref(fig:ParMoeLandscape)f).
@@
 Finally, activity density of both _Pardosa_ species had a very strong temporal and spatial component, although the temporal component was dominant for _P.
-distincta_ (Figure \@ref(fig:ParDisSpatiotemporal)a, p=`r with(pdisSmTerms,p[Smoother=='s(Day)'])`) whereas the spatial component was dominant for _P.
-moesta_ (Figure \@ref(fig:ParMoeSpatiotemporal)b, p=`r with(pdisSmTerms,p[Smoother=='s(E,N)'])`).
+distincta_, whereas the spatial component was dominant for _P.
+moesta_ (Figures \@ref(fig:ParDisSpatiotemporal) and \@ref(fig:ParMoeSpatiotemporal) ; both p`r with(pmoeSmTerms,p[Smoother=='s(E,N)'])`).
 The landscape composition and trap location explained `r r2Nakagawa$ParDisMod[1]*100`%  and `r r2Nakagawa$ParMoeMod[1]*100`% of variance in activity density, while the spatial and temporal smoothers accounted for `r with(r2Nakagawa,(ParDisMod[2]-ParDisMod[1])*100)`%  and `r with(r2Nakagawa,(ParMoeMod[2]-ParMoeMod[1])*100)`%, for _P.
@@
 The temporal and spatial components, as in the other two species, were both very strong (both p`r with(opilSmTerms,p[grepl('E,N',Smoother)])`).
-Together, these results indicate that _P. opilio_ activity density is more strongly influenced by large-scale geographic patterns, and less so by landscape composition.
+Together, these results indicate that _P. opilio_ activity density is less influenced by landscape composition than _P. melanarius_ or our two _Pardosa_ species.
 The landscape composition and trap location explained `r r2Nakagawa$OpilioMod[1]*100`%  of variance in activity density, while the spatial and temporal smoothers accounted for `r with(r2Nakagawa,(OpilioMod[2]-OpilioMod[1])*100)`%.
@@
 
-We found that _Pterostichus melanarius_, _Pardosa distincta_, _Pardosa moesta_, and _Phalangium opilio_ responded strongly to landscape composition.
-_P. melanarius_ was influenced by grass/wetland, pasture, trees/shrubs, pulses, and urban land cover.
-_P. distincta_ was influenced by grass/wetland, canola, pulses, and urban land cover.
-_P. moesta_ was influenced by the same landscape components: grassland/wetland, canola, pulses, and urban land cover.
-Finally, _P. opilio_ was influenced by grass/wetland, and trees/shrubs.
+The activity density of _Pterostichus melanarius_, _Pardosa distincta_, _Pardosa moesta_, and _Phalangium opilio_ responded strongly to landscape composition.
+There was also a strong temporal component to the landscape effects, meaning that it is important to consider how sinks and sources may change over the season.
+We found some support for our predictions of SNL (grass and wetland, forest and shrubs, and road margins) acting as a late-season sinks for beneficial arthropods.
+In particular, grass/wetland acted as a sink for _P. melanarius_, forest/shrubs acted as a sink for _P. distincta_, and road margins acted as a sink for _P. moesta_.
+While there was limited evidence of SNL acting as early-season sources, some acted as landscape-level sources (road margins on _P. moesta_), indicating either earlier or wider-scale dispersal.
+Canola and pasture acted as landscape-level sinks for _P. melanarius_ and _P. distincta_, respectively, meaning that these cover types likely represent insufficient habitat for these arthropods.
+The influence of landscape composition tended to be limited to a radius of about 500m, indicating that large-scale land cover may be more important than previously thought.
 These results highlight the seasonal importance of non-crop marginal lands for predatory arthropod abundance (Table \@ref(tab:sumTab)).
+
+<!-- 1. ... nearby SNL should act as a source of arthropods during the early part of the season, and a sink during the later part of the season.  -->
+<!-- 2.
+...
+should result in agricultural land becoming a sink for predators in the early part of the season as they migrate into the crop, and a source at the end of the season as they migrate out of the crop.
+-->
+<!-- 3. ... crops may act as a local sink for arthropods, but will also be negatively associated at larger (landscape-level) scales. -->
 
@@
 lineatus_, such as _Bembidion quadrimaculatum_ [@vankosky2011], so this effect may be direct or indirect.
+We did not consider the influence of previous years' crops, although carabids tend to be more abundant in areas of high crop rotation [@busch_Msc; @bertrand2016].
 
@@
 Lycosids employ a wandering-active predation strategy [@young1990], meaning that nearby landscape composition may be more influential than large-scale composition [@oberg2007; @oberg2008].
-However, we showed that several landscape features were also important at large spatial scales, including grass and wetland, pasture, pulses, and urban, showing that their dispersal distance may be further than previously though.
+While trapping location explained a large proportion of variance for both species (`r filter(r2Nakagawa2,model=='ParDisMod',grepl('trapLoc',terms))$r2comp` and `r filter(r2Nakagawa2,model=='ParMoeMod',grepl('trapLoc',terms))$r2comp`), several landscape features were also important at large spatial scales, including grass and wetland, pasture, pulses, and urban, showing that their dispersal distances may be further than previously though.
 
-_Phalangium opilio_ activity density responded to grasslands and wetlands as well as trees and shrubs, but habitat
-Grasslands and wetlands acted
+_Phalangium opilio_ activity density responded to grass and wetland cover, as well as trees and shrubs, but the trap location and landscape explained only `r r2Nakagawa$OpilioMod[1]*100`% of the variance.
+Other studies have found that _P.
+opilio_ is mostly found in human-altered landscapes with a large proportion of farming [@muster2014; @vandepoel2015Msc], and since most of our study area was in or near farmed land, this lack of variation is understandable.
+However, there were a few notable landscape-level patterns that emerged.
+_P. opilio_ activity density was higher in grassy pivot corners and wetlands, but grasslands and wetlands acted as a local sink of _P. opilio_ until late in the season.
+These indicate that while grass and wetlands could act as a reservoir, spillover into other land cover types may be limited, as _P.
+opilio_ avoids heavily grazed areas, possibly due to low humidity [@sajna2011].
+_P. opilio_ is also found in large numbers at the edges of forests, and may migrate from forests into farmlands [@vandepoel2015Msc].
+We found the opposite pattern: forests act as a weak sink for _P. opilio_, at least early in the year.
+Unlike the other arthropods, most of the variation in activity density for _P.
+opilio_ was explained by day of year (R$^2$ = `r filter(r2Nakagawa2,model=='OpilioMod',grepl('day',terms))$r2comp`), indicating strong seasonal emergence cues.
 
-_P. opilio_ avoids heavily grazed areas, possibly due to low humidity, but is active in most other habitat types [@sajna2011].
-In particular, it is largely found in human-altered landscapes with a large proportion of farming [@muster2014; @vandepoel2015Msc].
-It is also found in large numbers at the edges of forests, and may migrate from forests into farmlands [@vandepoel2015Msc].
-We found the opposite pattern (albeit weakly): _P. opilio_ appears to migrate into forests.
-
-Overall, we found that trees/shrubs, 
-The influence of landscape composition tended to be limited to a radius of about 500m, indicating that large-scale land cover may have a stronger effect on arthropod abundance than small-scale land cover
-
-There was a strong temporal component to the landscape effects, meaning that it is important to consider how sinks and sources may change over the season.
-We did not consider the influence of previous years' crops, although carabids tend to be more abundant in areas of high crop rotation [@busch_Msc; @bertrand2016].
-
-These patterns indicate movement between landscape features, but since we did not directly observe arthropod movement between features, future studies should examine this
-Some land cover classes were strongly concurved (canola and cereal, wetland and grassland) with each other, we removed or combined them, meaning that we could not consider the influence of the categories independently.
-Mark-recapture studies, monitoring movement patterns (e.g. radio tags), or two-sided traps could be useful.
-Should also be linked to ecosystem services (e.g. predation on bait insects or weed seeds).
+<!-- Why is this study special? Why do we care? Why do we need another landscape-level study of SNL and insect abundance? -->
+Many other studies have considered the overall effect of SNL on ecosystem service provision, but our study has highlighted the different spatial and temporal scales that ecosystem service provision is couched in.
+We have shown how a relatively new statistical technique can be used to consider multiple spatial scales of landscape composition, providing richer inference about the processes acting on beneficial arthropods.
+Other studies have considered how different SNL types act as sinks or sources at different times of year, but our results reveal the changes in sinks and sources within an agricultural landscape.
+These patterns imply movement of organisms between landscape features, but since we did not directly this, future studies could directly examine arthropod movement, with the goal of integrating landscape ecology and behavioural processes into a single model [@lima1996].
+Mark-recapture techniques, directly tracking movement patterns (e.g. radio tags), or two-sided traps could be useful for this.
+This would also allow direct inference about landscape categories that were combined in our dataset, allowing us to consider different landscape categories independently.
+Finally, future work should explicitly link landscape structure, arthropod abundance, and ecosystem services [@gagic2017].
 

### 2020-08-25 manuscript/manuscript_outline.Rmd
Worked on Intro

@@
 date: "Spring 2020"
-abstract: Ground-dwelling arthropods are important generalist predators in prairie agro-ecosystems.
-However, we don't know what types of landscape features are useful for which types of arthropods, and during which parts of the year.
-Habitat features may act as sources of arthropods during some times of the year, but act as sinks at other times.
-We modeled the activity density of four widely-distributed species of arthropods, and used functional regression to reveal their habitat preferences.
-We found that trees/shrubs, and roadside grasses acted as sources of arthropods.
-Other features did not function as significant sources or sinks.
-Farmers should consider retaining these landscape features in order to preserve populations of helpful generalist predators in their crops.
+abstract: Ground-dwelling arthropods are important generalist predators in prairie agro-ecosystems, and can use non-crop features as overwintering habitats.
+However, it is unclear which types of landscape features constitute useful non-crop habitat, and what spatial scale of habitat is required.
+Additionally, the same landscape feature may act as a sink or a source of arthropods at different times of the year, but this is rarely considered.
+We modeled the activity density of four highly-abundant species of Canadian prairie arthropods, and used functional regression to simultaneously consider both their habitat preferences and the timing of sources and sinks.
+We found that canola crops (_Brassica napus_ L.) acted as early-season sources, and that grasses and wetlands acted as late-season sinks of arthropods.
+Farmers should consider preserving existing grasslands and wetlands to act as reservoir habitats for the surrounding cropland.
 
@@
 
-# Introduction - needs flushing out
+# Introduction
 
@@
 Arthropods are one of the most influential groups of animals in agricultural systems.
-Pest arthropods can cause huge amounts of damage to crops, resulting in yield losses for farmers and negative downstream economic effects.
-On the other hand, beneficial arthropods can deliver increased crop yields from extra pollination or free pest control.
-The seasonal "pulses" of food resources from agricultural land act as a bottom-up driver of arthropod communities, which include both native and introduced species.
-Agricultural land also constitutes 15 million km$^2$ (~36%) of land worldwide [@ramankutty2018], meaning that conservation of insect biodiversity should consider agricultural practices, as small changes in agricultural practices can have large effects globally.
-In particular, land managers and conservationists are interested in finding "win-win" practices; that is, practices that result in better conservation outcomes while achieving the same (or higher) crop yields.
+Pest arthropods can cause large reductions in crop yield [@oerke2005], which can result in negative downstream economic effects and malnutrition.
+On the other hand, spillover of beneficial arthropods from adjacent non-crop patches can deliver increased crop yields by providing ecosystem services such as extra pollination or pest suppression [@losey2006; @klein2007; @garibaldi2013].
+Seasonal "pulses" of food resources from crop fields act as a bottom-up driver of their associated arthropod communities, meaning that agricultural land can act as a source of nutrients and individuals for adjacent non-crop land [@diekotter2010; @galpern2017].
+These important fluxes of mobile arthropods, both to crops and away from them, are key for managing both crop yield and biodiversity in agroecosystems.
+Finding "win-win" practices is of particular importance to land managers and conservationists; that is, practices that result in better conservation outcomes while achieving similar crop yields.
+Finally, agricultural land occupies 15 million km$^2$ (~36%) of land globally [@ramankutty2018], meaning that biodiversity conservation should pay particular attention to agricultural practices.
 
-One method of passively manipulating agricultural arthropods is through landscape management [@albrecht2010; @landis2000; @martin2020].
-Non-cultivated areas, such as natural or semi-natural land (SNL) can act as important habitat for some arthropods [@duelli2003].
-Ground-nesting bees are generally driven by flower and nest availability [@roulston2011], and beetles can be limited by water, food, and egg-laying sites [@lovei1996; @gardiner2010].
-However, while the effect of SNL on bees is generally positive, its effect on beetles and parasitoids less consistent [@macfadyen2013; @shackelford2013] 
-Other organisms may use SNL as travel corridors or overwintering sites, but may not be directly dependent on them for reproduction.
-Spillover from SNL occurs when organisms migrate from SNL into adjacent cropland, or from cropland into SNL [@tscharntke2005b]. 
-The degree to which spillover occurs depends on the life history of the organism in question, as well as their reliance on the specific type of SNL.
+Uncultivated semi-natural land (SNL) can act as important habitat for beneficial arthropods [@duelli2003], which may spill over into adjacent crops.
+Therefore, landscape management is a strategy to increase beneficial arthropod abundance in crops [@albrecht2010; @landis2000; @martin2020; but see @tscharntke2016; @karp2018].
+For example, bee abundance is largely driven by flower and nest availability [@roulston2011], and the effect of SNL on bee abundance and diversity is generally positive.
+Predatory arthopods such as beetles or spiders can be limited by water, food, and egg-laying sites [@lovei1996; @gardiner2010], but the effect of SNL on their abundance is less consistent [@macfadyen2013; @shackelford2013], as some taxa may use SNL as a travel corridor or overwintering site, not be obligately dependent on it for reproduction.
+Some taxa are not dependent on SNL at all, and thrive in cultivated landscapes, while others exclusively inhabit SNL and do not venture beyond the edge of cultivated fields.
+For example, carabid beetles are thought to reproduce in field margins, while the adults feed in fields [@desender1988].
+This depends on the life history of the organisms in question, such as the seasonal timing of emergence, feeding, and reproduction, as well as their traits such as dispersal capability.
 Non-adjacent cropland can also influence arthropod abundance if the organisms are long-distance dispersers [@oberg2008].
+This means that spillover of beneficial arthropods into crops depends not only on habitat type, but on time of the year, and the spatial scale of landscape that is relevant to the organism.
+
+<!-- Consider what this next paragraph should be about -->
+Spillover from SNL occurs when organisms migrate from SNL into adjacent cropland, but can also occur when arthropods migrate from cropland into SNL [@tscharntke2005b].
+That is certain habitat types may be sources of arthropods during some times of the year, but sinks during other times.
 
@@
 
-The effect of SNL on arthropod abundance also depends on the seasonal timing of emergence, feeding, and hibernation.
-For this reason, it is important to consider the effect as being inherently spatio-temporal.
-Arthropods move between landscape components depending on their life history.
-e.g. Carabid beetles are thought to reproduce in field margins, but adults feed in fields [@desender1988].
-This means that spillover depends not only on habitat type, but on time of the year.
-Certain habitat types may be sources of arthropods during some times of the year, but sinks during other times.
 <!-- Counts in pitfall traps are a proxy of activity density (not actual density), but this is probably an OK measure, at least within fields [@lang2000] -->

### 2020-09-02 manuscript/manuscript_outline.Rmd
Worked on Intro/Methods

@@
 Arthropods are one of the most influential groups of animals in agricultural systems.
-Pest arthropods can cause large reductions in crop yield [@oerke2005], which can result in negative downstream economic effects and malnutrition.
+Pest arthropods can cause large reductions in crop yield [@oerke2005], which can result in downstream economic effects, food insecurity, and malnutrition.
 On the other hand, spillover of beneficial arthropods from adjacent non-crop patches can deliver increased crop yields by providing ecosystem services such as extra pollination or pest suppression [@losey2006; @klein2007; @garibaldi2013].
@@
 Finding "win-win" practices is of particular importance to land managers and conservationists; that is, practices that result in better conservation outcomes while achieving similar crop yields.
-Finally, agricultural land occupies 15 million km$^2$ (~36%) of land globally [@ramankutty2018], meaning that biodiversity conservation should pay particular attention to agricultural practices.
+Finally, agricultural land occupies 15 million km$^2$ (~36%) of land globally [@ramankutty2018], meaning that conservation efforts should pay particular attention to agricultural practices.
 
@@
 Therefore, landscape management is a strategy to increase beneficial arthropod abundance in crops [@albrecht2010; @landis2000; @martin2020; but see @tscharntke2016; @karp2018].
-For example, bee abundance is largely driven by flower and nest availability [@roulston2011], and the effect of SNL on bee abundance and diversity is generally positive.
-Predatory arthopods such as beetles or spiders can be limited by water, food, and egg-laying sites [@lovei1996; @gardiner2010], but the effect of SNL on their abundance is less consistent [@macfadyen2013; @shackelford2013], as some taxa may use SNL as a travel corridor or overwintering site, not be obligately dependent on it for reproduction.
+For example, wild bee abundance in agricultural landscapes is largely driven by flower and nest availability [@roulston2011], and the effect of SNL on bee abundance and diversity is generally positive.
+Predatory arthopods such as beetles or spiders can be limited by water, food, and egg-laying sites [@lovei1996; @purtauf2005; @gardiner2010], but the effect of SNL on their abundance and diversity is less consistent [@macfadyen2013; @shackelford2013] as some taxa may use SNL as a travel corridor or overwintering site, but are not completely dependent on it for reproduction.
 Some taxa are not dependent on SNL at all, and thrive in cultivated landscapes, while others exclusively inhabit SNL and do not venture beyond the edge of cultivated fields.
@@
 This depends on the life history of the organisms in question, such as the seasonal timing of emergence, feeding, and reproduction, as well as their traits such as dispersal capability.
-Non-adjacent cropland can also influence arthropod abundance if the organisms are long-distance dispersers [@oberg2008].
-This means that spillover of beneficial arthropods into crops depends not only on habitat type, but on time of the year, and the spatial scale of landscape that is relevant to the organism.
+Non-adjacent cropland can also influence arthropod abundance if the organisms are long-distance dispersers[@oberg2008].
+<!-- Small patches of SNL can have a large effect if overall landscape lacks SNL (landscape contrast [@boetzl2020; @vanSchalkwyk2020]) -->
+In this way, the spillover of beneficial arthropods into crops depends not only on the amount of adjacent SNL, but the specific habitat type, the time of the year, and the spatial scale of landscape that is relevant to the organism.
 
 <!-- Consider what this next paragraph should be about -->
-Spillover from SNL occurs when organisms migrate from SNL into adjacent cropland, but can also occur when arthropods migrate from cropland into SNL [@tscharntke2005b].
-That is certain habitat types may be sources of arthropods during some times of the year, but sinks during other times.
 
-<!-- Small patches of SNL can have a large effect if overall landscape lacks SNL (landscape contrast [@boetzl2020; @vanSchalkwyk2020]) -->
 <!-- Limited understanding of other arthropods (but see ``beetle hedges" from UK?) -->
@@
 <!-- Arachnids are similarly limited by food, shelter -->
-
 <!-- Counts in pitfall traps are a proxy of activity density (not actual density), but this is probably an OK measure, at least within fields [@lang2000] -->
 
-Our understanding of how landscape features influence beneficial arthropod abundance is incomplete.
-The feeding and life-history characteristics of many predatory ground beetles and spiders is not well-documented, meaning that it is difficult to make generalizations of which types of habitat may increase their abundance.
-Choosing the spatial scale of analysis depends on the characteristics of the organisms [@ahrenfeldt2015]; for example, bumblebee abundance can be controlled by both local- and landscape-scale SNL abundance [@westphal2006].
-Finally, different SNL patches may act as sources or sinks of arthropods at different times of the year, but this is rarely considered [but see @desender1988].
+Despite what is known about the spatial and temporal aspects of beneficial arthropod spillover, these are rarely considered together.
+First, some habitat types may act as sources of arthropods during some times of the year, but as sinks during other times, meaning that the timing of spillover may not allign with key periods in crop development.
+Arthropods can migrate from managed crops back into adjacent SNL at the end of the season [@desender1988; @tscharntke2005b], but this is seldom considered.
+Second, the spatial "grain" of the landscape that is relevant to an organism depends on their traits and life history [@ahrenfeldt2015].
+For instance, bumblebee abundance can be controlled by both local- and landscape-scale SNL abundance [@westphal2006], but this is poorly studied for other groups of beneficial organisms [but see @sander2006].
+Finally, the feeding and life-history characteristics of many predatory ground beetles and spiders is often poorly-documented, especially in North America.
+This makes it difficult to make generalizations of which habitat types harbour beneficial arthropods, making it even more difficult to provide accurate information to farmers about land management practices.
 
-In this study, we used pitfall traps to determine how landscape composition affects the seasonal activity density of arthropods across a prairie agroecosystem.
-We hypothesized that:
+In this study, we used pitfall traps to determine how landscape composition affects the seasonal activity density of arthropods across a Canadian prairie agroecosystem.
+We considered the following hypotheses:
 1.
-Untilled semi-natural land (SNL) provides egg-laying and feeding areas for predatory arthropods, meaning that nearby SNL should act as a source of arthropods during the early part of the season, and a sink during the later part of the season.
+Untilled semi-natural land (SNL) provides egg-laying and feeding areas for predatory arthropods, meaning that SNL should act as a source of arthropods during the early part of the season, and a sink during the later part of the season.
 2.
-Crops in agricultural land act as sources of food for predatory arthropods during the growing season, while crop senescence at the end of the season causes a crash as pest popuations decrease.
+Crops act as sources of food (pest insects) for predatory arthropods during the growing season.
 This should result in agricultural land becoming a sink for predators in the early part of the season as they migrate into the crop, and a source at the end of the season as they migrate out of the crop.
-3.
-Crops can act as a temporary feeding site for predators, but not as permanent habitat.
-Therefore, crops may act as a local sink for arthropods, but will also be negatively associated at larger (landscape-level) scales.
-Using a novel statistical technique, we were able to isolate seasonal signals of changes in arthropod abundance at multiple landscape scales.
+3. Crops may act as a temporary feeding site for predators. Therefore, crops may act as a local sink for arthropods, but will also be negatively associated at larger (landscape-level) scales.
+Using a large pitfall trapping dataset, we were able to relate seasonal changes in arthropod abundance to landscape composition at multiple spatial scales, and found evidence of SNL acting as late-season sinks in abundance.
 
@@
 ## Data collection
+We used a set of 169 pitfall traps installed at roadsides, field margins, wetlands, and in-field sites across southern Alberta, Canada in 2017 (_need a map here_).
+Pitfall traps consisted of 582 mL Solo® cups buried up to the rim, partially filled with ethylene glycol.
+All traps had 2 cm wire mesh mounted over the rim to prevent vertebrates from falling into the traps.
+Traps at roadsides were located 5m from the roads, while traps at in-field sites were installed at 0, 25, 75, and 200 m along a transect heading away from the nearest non-crop feature (wetland, grassland, grassy field corners).
+Specimens were collected from the traps on average every 14 days (SD: 2.9), and were identified to species.
 
-We used a system of pitfall traps installed at roadsides, field margins, wetlands, and in-field sites across southern Alberta in 2017 (_need a map here_).
-Pitfall traps consisted of 582 mL Solo® cups buried up to the rim, partially filled with ethylene glycol.
-All traps had 2 cm diameter wire mesh mounted over the rim to prevent vertebrates from falling into the traps.
-Traps at roadsides were located 5m from the roads, while traps at in-field sites were installed 20, 100, 200m (?) along a transect from the nearest non-crop feature (wetland, grassland, pivot).
-Specimens were collected from the traps every 14 days (SD: 2.9), and were identified to species.
-
-We used three species of predatory arthropods that were present at very high abundances in the traps.
-_Pterostichus melanarius_ is predatory introduced ground beetle that is a wide-ranging generalist [@carcamo1994; @larsen2003; @busch_Msc].
-It is commonly found in untilled grasslands [@purtauf2005] and grassy field margins may act as larval habitat [@desender1988].
-_Pardosa distincta_ is a species of wolf spider that is common across the Canadian prairies, and is commonly found in ungrazed pastures [@carcamo2014].
-Finally, _Phallangium opilio_ is a widely-distributed generalist harvestman, whose habitat preferences are poorly understood.
+We used four highly-abundant species of predatory arthropods found in the pitfall traps, as common species drive ecosystem service provision more than rare species [@winfree2015].
+_Pterostichus melanarius_ is a introduced predatory ground beetle (Coleoptera: Carabidae) that is a wide-ranging generalist [@carcamo1994; @larsen2003; @busch_Msc].
+It is commonly found in untilled grasslands [@purtauf2005] and may use grassy field margins as larval habitat [@desender1988].
+_Pardosa distincta_ and _Pardosa moesta_ are wolf spiders (Araneae: Lycosidae) that are common across the Canadian prairies, and are often found in ungrazed pastures [@carcamo2014].
+Finally, _Phallangium opilio_ is a widely-distributed generalist harvestman (Opiliones: Phalangiidae), whose habitat preferences are poorly understood. 
+They are commonly found in human-altered landscapes [@muster2014; @vandepoel2015Msc] and are generally nocturnal hunters and scavengers [@halaj2000; @allard2005; @allard2005b].
 

### 2020-09-02 manuscript/manuscript_outline.Rmd
Added map, and worked on Methods

@@
 
+#Get number of traps in each location
+NtrapsPer <- select(PteMelMod$tempTrap,ID,trapLoc,distFrom) %>% data.frame() %>% distinct() %>% group_by(trapLoc) %>% summarize(n=n())
+
 ```
@@
 ## Data collection
-We used a set of 169 pitfall traps installed at roadsides, field margins, wetlands, and in-field sites across southern Alberta, Canada in 2017 (_need a map here_).
-Pitfall traps consisted of 582 mL Solo® cups buried up to the rim, partially filled with ethylene glycol.
-All traps had 2 cm wire mesh mounted over the rim to prevent vertebrates from falling into the traps.
-Traps at roadsides were located 5m from the roads, while traps at in-field sites were installed at 0, 25, 75, and 200 m along a transect heading away from the nearest non-crop feature (wetland, grassland, grassy field corners).
+We used a set of `r sum(NtrapsPer$n)` pitfall traps installed at roadsides (minimum of 5 m away from the road edge, `r with(NtrapsPer, sum(n[trapLoc=='ditch')` traps) and in-field locations (`r with(NtrapsPer, sum(n[trapLoc!='ditch')`) across southern Alberta, Canada in 2017 (Figure \@ref(fig:siteMap)).
+The sites spanned a west-to-east gradient of four natural subregions, including foothills parkland, foothills fescue, mixedgrass, and dry mixedgrass [@ABRegions2006].
+In-field traps were placed in canola crops (`r with(NtrapsPer, sum(n[trapLoc=='canola')`), wetlands (`r with(NtrapsPer, sum(n[trapLoc=='wetland')`), grassy field corners (`r with(NtrapsPer, sum(n[trapLoc=='pivot')`), and remnant prairie grassland (`r with(NtrapsPer, sum(n[trapLoc=='native')`).
+Traps in canola were installed at 25, 75, and 200 m along a transect heading away from the nearest non-crop feature, while the trap at 0 m was installed in the non-crop feature itself.
+We used 582 mL Solo® cups buried up to the rim and partially filled with ethylene glycol, with 2 cm wire mesh mounted over the rim to prevent vertebrates from falling into the traps.
 Specimens were collected from the traps on average every 14 days (SD: 2.9), and were identified to species.
 
-We used four highly-abundant species of predatory arthropods found in the pitfall traps, as common species drive ecosystem service provision more than rare species [@winfree2015].
+```{r siteMap, echo=FALSE, fig.cap='Location of pitfall traps during 2017, and classified cover f.
+Inset map shows study location within Alberta.
+Roadside traps were installed in road margins, while in-field traps were installed directly in canola fields or in adjacent wetland or grassy field corners.'}
+  include_graphics('../figures/maps/PF2017.png',dpi=NA)
+```
+
+We used four highly-abundant species of predatory arthropods found in the pitfall traps, as common species are often more important for ecosystem service provision than rare species [@winfree2015].
 _Pterostichus melanarius_ is a introduced predatory ground beetle (Coleoptera: Carabidae) that is a wide-ranging generalist [@carcamo1994; @larsen2003; @busch_Msc].
 It is commonly found in untilled grasslands [@purtauf2005] and may use grassy field margins as larval habitat [@desender1988].
-_Pardosa distincta_ and _Pardosa moesta_ are wolf spiders (Araneae: Lycosidae) that are common across the Canadian prairies, and are often found in ungrazed pastures [@carcamo2014].
+_Pardosa distincta_ and _Pardosa moesta_ are wolf spiders (Araneae: Lycosidae) that are common across the Canadian prairies and are often found in ungrazed pastures [@carcamo2014].
+_P. distincta_ is commonly found in disturbed environments [@collins1996; @wade2010], while _P. moesta_ appear to prefer less frequent disurbances [@kowal2011].
+_Pardosa_ use an active wandering predation strategy [@young1990], and may use road margins and wooded areas as habitat [@buddle2000; @drapela2011]. 
 Finally, _Phallangium opilio_ is a widely-distributed generalist harvestman (Opiliones: Phalangiidae), whose habitat preferences are poorly understood. 

### 2020-09-03 manuscript/manuscript_outline.Rmd
Redid figures and worked on Methods

@@
 ## Data collection
-We used a set of `r sum(NtrapsPer$n)` pitfall traps installed at roadsides (minimum of 5 m away from the road edge, `r with(NtrapsPer, sum(n[trapLoc=='ditch')` traps) and in-field locations (`r with(NtrapsPer, sum(n[trapLoc!='ditch')`) across southern Alberta, Canada in 2017 (Figure \@ref(fig:siteMap)).
+We used a set of `r sum(NtrapsPer$n)` pitfall traps installed in road margins (minimum of 5 m away from the road edge, `r with(NtrapsPer, sum(n[trapLoc=='ditch')` traps) and in-field locations (`r with(NtrapsPer, sum(n[trapLoc!='ditch')`) across southern Alberta, Canada in 2017 (Figure \@ref(fig:siteMap)).
 The sites spanned a west-to-east gradient of four natural subregions, including foothills parkland, foothills fescue, mixedgrass, and dry mixedgrass [@ABRegions2006].
-In-field traps were placed in canola crops (`r with(NtrapsPer, sum(n[trapLoc=='canola')`), wetlands (`r with(NtrapsPer, sum(n[trapLoc=='wetland')`), grassy field corners (`r with(NtrapsPer, sum(n[trapLoc=='pivot')`), and remnant prairie grassland (`r with(NtrapsPer, sum(n[trapLoc=='native')`).
+In-field traps were placed in canola crops (`r with(NtrapsPer, sum(n[trapLoc=='canola')`), wetlands (`r with(NtrapsPer, sum(n[trapLoc=='wetland')`), grassy field margins (`r with(NtrapsPer, sum(n[trapLoc=='pivot')`), and remnant prairie grasslands (`r with(NtrapsPer, sum(n[trapLoc=='native')`).
 Traps in canola were installed at 25, 75, and 200 m along a transect heading away from the nearest non-crop feature, while the trap at 0 m was installed in the non-crop feature itself.
@@
 Specimens were collected from the traps on average every 14 days (SD: 2.9), and were identified to species.
+Increased counts of organisms in pitfall traps can represent higher abundances or higher activity levels, meaning that it is impossible to disentangle arthropod activity from density using single traps ["activity density", @lang2000; @zhao2013].
+However, activity density is generally positively related to ecosystem services, at least in carabids [@trichard2014; @boetzl2018; @gonzalez2020], making it an acceptable metric for our study.
 
@@
 _P. distincta_ is commonly found in disturbed environments [@collins1996; @wade2010], while _P. moesta_ appear to prefer less frequent disurbances [@kowal2011].
-_Pardosa_ use an active wandering predation strategy [@young1990], and may use road margins and wooded areas as habitat [@buddle2000; @drapela2011]. 
+All _Pardosa_ use an active wandering predation strategy [@young1990], and may use road margins and wooded areas as habitat [@buddle2000; @drapela2011]. 
 Finally, _Phallangium opilio_ is a widely-distributed generalist harvestman (Opiliones: Phalangiidae), whose habitat preferences are poorly understood. 
@@
 
-To characterize landscape composition surrounding the traps, we used classified landscape data from @AAFC_data.
-<!-- + AAFC cropland landscape classifications are very accurate for cultivated fields (~90%), but are less accurate for non-crop areas (~70%) -->
-We combined functionally similar landscape categories (cereals: _Triticum aestivum_ and _Hordeum vulgare_, pulses: _Pisum sativum_ and _Lens culinaris_, forest: coniferous and broadleaf), then extracted the landscape composition within a circle of a fixed radius surrounding each trap location.
-The ten most-common cover classes represented 98% of the total land cover in our study region: grassland, cereal, canola, pasture, pulses, wetland, urban, shrubland, flax, and forest (Figure \@ref(fig:landscapeComp)); flax was removed, as only a single site had nearby flax cover.
+To characterize landscape composition surrounding the traps, we used publicly available classified landscape data [30 m resolution; @AAFC_data].
+AAFC cropland landscape classifications from 2017 were very accurate for cultivated fields (~90%), but were less accurate for non-crop areas (~70%).
+We combined functionally similar landscape categories (cereals: _Triticum aestivum_ and _Hordeum vulgare_, pulses: _Pisum sativum_ and _Lens culinaris_, forest: coniferous and broadleaf). 
 <!-- The radius of the circle necessary to characterize the landscape depends on the scale of the landscape that matters to a given organism [@addicott1987]. -->
-At each site, we extracted the proportion of each landscape cover class within 30m annuli (rings), with inner radii ranging from 30 to 1470m, in increments of 30m.
-Using functional regression [@ramsay2004], we were able to incorporate landscape information at different distance, allowing us to assess the impact of both local and regional landscape composition.
+At each site, we extracted the proportion of each cover class within 30m annuli (rings), with the inner radius of each annulus ranging from 30 to 1470m in increments of 30m (total of 49 annuli, 1.5 km maximum).
+The ten most-common cover classes surrounding our sites represented 98% of the total land cover in our study region: grassland, cereal, canola, pasture, pulses, wetland, urban, shrubland, flax, and forest (Figure \@ref(fig:landscapeComp)); flax was removed, as only a single site had nearby flax cover.
 
@@
 
-We used functional regression to model the effect of landscape composition on activity density.
-Scalar-on-function (SoF) regression is a special type of functional regression model ($\hat{y}=X\beta$), where the columns of the model matrix $X$ contain some continuous predictor of the scalar $y$ (e.g.
-biomass in a plot (scalar) as a function of monthly average temperatures (vector)), and the values of the coefficients ($\beta$) are modeled as a smooth function $f(x)$ of the predictors.
-In our case, each column represents the proportion of a given landscape cover class within each annulus, with increasing radii away from the location of the trap, and the coefficients are a smooth function of distance ($\beta_i = f(distance_i)$), meaning that the coefficients represent the (additive) effect of a given type of landscape cover at distances away from the trap.
-This avoids the fundamental problem of choosing an optimal radius of landscape composition, and allows the possibility that the size of the landscape "grain" relevant to a given organism may change over the course of its life stages [@addicott1987; @lima1996; @gardiner2010].
+Functional regression [@ramsay2004; @yen2014] was to incorporate landscape information at different distances, allowing assessment of both local and regional landscape composition [@galpern2020].
+Scalar-on-function regression is a special type of linear regression model ($y=X\beta + e$), where the columns of the model matrix $X$ contain some continuous predictor of the scalar $y$, and the values of the coefficients ($\beta$) are modeled as a smooth function $f(x)$ of the predictors.
+<!-- As an example of scalar-on-function regression, biomass in a plot (scalar) could be modeled as a smoothed function of monthly average temperatures at that plot (function), meaning that the effect of monthly temperatures would also be a function of time.
+-->
+In our case, the proportion of landscape cover ($X$) within each annulus surrounding the trap is a function of distance away from the trap, meaning that the coefficients are a smoothed function of distance ($\beta_i = f(distance_i)$), and represent the additive effect of a given type of landscape cover at distances away from the trap (i.e.
+$X\beta$).
+This allows the possibility that the size of the landscape "grain" relevant to a given organism may change over the course of its life stages [@addicott1987; @lima1996; @gardiner2010].
 It also allows for the possibility that certain land cover types may be locally beneficial, but detremental at wider scales, indicating that the cover type may not constitute a completely useable habitat.
-This technique has been used by other authors [@yen2014; @galpern2020].
 
-Activity density of each arthropod was fit as generalized additive models @wood2017, using _mgcv_ version `r packageVersion('mgcv')`. 
-Count data of arthropods were fit using a negative binomial distribution with a log-link.
-To account for different lengths of trap exposure, log-days since trap placement was used as a fixed effect with its slope held at 1 ("offset" variable).
-We included day of year as a 1-dimensional smooth and easting and northing as a 2-dimensional smooth, in order to account for underlying spatial and temporal autocorrelation in the data.
-The deviance residuals from each model were visually inspected for normality and equal variance.
+Scalar-on-function regression of activity density was fit using generalized additive models [_mgcv_ version `r packageVersion('mgcv')`; @wood2017]. 
+Count data of arthropods were modeled using a negative binomial distribution with a log-link function and a single dispersion parameter ($\theta$).
+To account for different lengths of trap exposure, log-days since trap placement were used as a fixed effect with their slope held at 1 ("offset" variable).
+We included day of year as a 1-dimensional smooth, and easting and northing (km east and north of the trap extent centre point) as a 2-dimensional smooth, in order to account for underlying spatial and temporal autocorrelation in the data.
+The deviance residuals from each model were visually inspected for normality and equal variance [@hilbe2011; @wood2017].
 
-For each landscape term, we used three SoF regression terms:
-First, we used the proportion cover of all landscape cover classes in the annuli surrounding each trap location (spatial effect of cover class).
-Second, we used day of the year multiplied by the proportion of cover classes in each annuli (temporal effect of cover class). 
+For each landscape cover class, we used three scalar-on-function terms.
+First, we used the proportion cover in the annuli surrounding each trap location (spatial effect of cover class).
+Second, we used the average landcover in all annuli across days of the year (temporal effect of cover class). 
 Finally, we used a tensor-product interaction of landscape cover and day of year (spatio-temporal interaction of cover class).
@@
 This was deemed adequate, as the effective degrees of freedom for all smoothing terms were far below the number of basis dimensions, indicating that no additional basis dimensions were needed (see Tables \@ref(tab:PteMelSmooth), \@ref(tab:ParDisSmooth), \@ref(tab:ParMoeSmooth), \@ref(tab:OpilioSmooth)).
-To remove unimportant terms from the model, we used thin-plate regression splines with shrinkage ("bs=`ts'" in _mgcv_).
-This is a continuous analog to stepwise model selection, whereby weaker terms can be completely removed from the model rather than reduced to a line [@marra2011].
-Finally, we calculated the R$^2$ for each group of terms in each model [@nakagawa2013; @nakagawa2017].
+To remove unimportant terms from the model, we used thin-plate regression splines with shrinkage, a continuous analog to stepwise model selection where weaker terms are completely removed from the model rather than reduced to a line [@marra2011].
+Finally, we calculated the R$^2$ for each group of terms [@nakagawa2013; @nakagawa2017].
 <!-- + Double-penalization gave qualitatively similar results, but required twice the number of penalty terms, and some of the penalty terms were unstable  -->
 
-Some of the landscape terms in our model were strongly concurved, so we removed them from the model or combined them.
+Preliminary model fits revealed that some of the landscape terms in our model were strongly concurved with each other (Figure \@ref(fig:concurvityFull)), so we removed them from the model or combined them.
 Concurvity is a nonlinear analogue of multicollinearity, and can bias estimates of standard errors [@buja1989].
 There is no agreed-upon threshold of "unacceptable" concurvity, but 0.5 is commonly used [@dominici2002; @ramsay2003]. 
-Some landscape terms were strongly concurved (Figure \@ref(fig:concurvityFull)), namely forest and shrubland (max: 0.71), canola and cereal (max: 0.74), and grassland and wetland (max: 0.63).
-Forest and shrubland were combined into the ``Tree/Shrub" category, grassland and wetland were combined into the "Grass/Wetland" category, as they were strongly positively correlated at all distances, indicating similar feature classes.
-Cereal was removed from the model, as it was negatively correlated with canola cover at distances less than 200m and was positively correlated at distances over 500m, reflecting the most common crop rotations (canola $\rightarrow$ wheat $\rightarrow$ barley) and the commonly-used block structure (quarter-sections) present across our study region.
+<!-- Some landscape terms were strongly concurved , namely forest and shrubland (max: 0.71), canola and cereal (max: 0.74), and grassland and wetland (max: 0.63). -->
+Forest and shrubland were combined into a single ``woodland" category, and grassland and wetland were combined into a single "grassland" category, as they were strongly positively correlated at all distances, indicating similar feature classes.
+Cereal was removed from the model, as it was negatively correlated with canola cover at distances less than 200m and was positively correlated at distances over 500m, reflecting the most common crop rotations (canola $\rightarrow$ wheat $\rightarrow$ barley) and the commonly-used 800 m block structure of farmland in our study region (quarter-sections).
 This resulted in a reduced set of landscape terms, none of which were strongly concurved with each other (Figure \@ref(fig:concurvity))
@@
 We consider 1) to be the more likely scenario, as it is unlikely that any one cover class is *completely* unoccupied.
-As these data were collected from a single year, this model does not consider the next-generation fitness consequences of spillover.
+<!-- As these data were collected from a single year, this model does not consider the next-generation fitness consequences of spillover. -->
 For example, a cover class with low-quality habitat could act as an ecological trap [@galpern2017] if it acts as a sink but never as a source.
@@
 melanarius_ than other trap locations (Figure \@ref(fig:PteMelLandscape)a), indicating that canola may allow faster movement of ground beetles, has higher overall population levels, or both.
-Nearby grassland/wetland cover had a neutral effect early in the summer, but a negative effect later in the summer (Figure \@ref(fig:PteMelLandscape)b), indicating that _P.
+Nearby grassland cover had a neutral effect early in the summer, but a negative effect later in the summer (Figure \@ref(fig:PteMelLandscape)b), indicating that _P.
 melanarius_ may move into grasslands later in the year.
@@
 Trees and shrubs acted as a sink for _P. distincta_ later in the season, and as a weak source early on in the season for _P. moesta_ (Figures \@ref(fig:ParDisLandscape)d, \@ref(fig:ParMoeLandscape)d).
-Grass and wetlands had strong local negative effect on _P.
-moesta_, but a positive landscape-level effect, indicating that while these cover types act as a sink, the general amount of grasslands and wetlands in the area have a positive effect on _P.
+Grasslands had strong local negative effect on _P.
+moesta_, but a positive landscape-level effect, indicating that while these cover types act as a sink, the general amount of grassland in the area had a positive effect on _P.
 moesta_ abundance.
@@
 _Phalangium opilio_ activity density was strongly influenced by trap location, with pivot corners and wetlands having the highest activity density (Figure \@ref(fig:OpilioLandscape)a).
-_P. opilio_ was affected by grassland/wetlands (p=`r with(opilSmTerms,p[Smoother=='ti(Distance,Day):GrassWetland'])`) and trees/shrubs (p`r with(opilSmTerms,p[Smoother=='s(Distance):TreeShrub'])`). 
-Nearby grassland/wetland and trees/shrubs both had a negative effect on _P. opilio_ activity density, but only early in the season (Figures \@ref(fig:OpilioLandscape)b,c).
+_P. opilio_ was affected by grasslands (p=`r with(opilSmTerms,p[Smoother=='ti(Distance,Day):GrassWetland'])`) and trees/shrubs (p`r with(opilSmTerms,p[Smoother=='s(Distance):TreeShrub'])`). 
+Nearby grassland and trees/shrubs both had a negative effect on _P. opilio_ activity density, but only early in the season (Figures \@ref(fig:OpilioLandscape)b,c).
 However, the specific effect of these land cover types was not very large, as a competing model using only non-crop cover performed slightly better (Full model AIC = `r with(OpilioMod, sprintf("%.1f",AIC(mod3)))`, Non-crop model AIC = `r with(OpilioMod, sprintf("%.1f",AIC(mod4)))`).
@@
 We found some support for our predictions of SNL (grass and wetland, forest and shrubs, and road margins) acting as a late-season sinks for beneficial arthropods.
-In particular, grass/wetland acted as a sink for _P. melanarius_, forest/shrubs acted as a sink for _P. distincta_, and road margins acted as a sink for _P. moesta_.
+In particular, grass/wetland acted as a sink for _P. melanarius_, woodlands acted as a sink for _P. distincta_, and road margins acted as a sink for _P. moesta_.
 While there was limited evidence of SNL acting as early-season sources, some acted as landscape-level sources (road margins on _P. moesta_), indicating either earlier or wider-scale dispersal.
@@
 Other studies have found similar results, suggesting that untilled land is important off-field habitat for carabids [@desender1988; @fournier2002; but see @hatten2007].
-In particular, @purtauf2005 found that carabid density increased with proportion of nearby grasslands; our finding of grassland/wetland as late-season sink may represent _P.
+In particular, @purtauf2005 found that carabid density increased with proportion of nearby grasslands; our finding of grassland as late-season sink may represent _P.
 melanarius_ moving to overwintering habitat at the end of the season.

### 2020-09-03 frAnalysis.R

@@ -66,15 +66,16 @@ stLegPosX <- 0.85 #Legend position X
 stLegPosY <- 0.3 #Legend position Y
 theme_set(theme_classic()) #Classic theme
 maptheme <- theme(panel.border=element_rect(size=1,fill=NA),axis.line=element_blank()) #Better theme for maps
+smoothCols <- c('blue','purple','red') #Colours for smoothing lines
 
 # Pterostichus melanarius ----------------------------------
 
 #Select only P. melanarius
 tempArth <- arth %>% filter(genus=='Pterostichus',species=='melanarius',year==2017) %>% group_by(BTID) %>% summarize(n=n())
 
-PteMelMod <- runMods(tempArth,trap,nnDistMat,oRingMat2Prop,formulas=modFormulas,basisFun='ts',doublePenalize=FALSE); beep(1)
-save(PteMelMod,file='./data/PteMelMod.Rdata')
-# load('./data/PteMelMod.Rdata')
+# PteMelMod <- runMods(tempArth,trap,nnDistMat,oRingMat2Prop,formulas=modFormulas,basisFun='ts',doublePenalize=FALSE); beep(1)
+# save(PteMelMod,file='./data/PteMelMod.Rdata')
+load('./data/PteMelMod.Rdata')
 
 #Tried running this with double-penalization instead of shrinkage. Results were similar, but some of the shrinkage 
 #Also tried running this with Cereal included, despite concurvity. Fits, but causes a bunch of weird instability in other results.
@@ -112,11 +113,15 @@ termNames[1] <- 'Linear terms'
 # termNames <- gsub('ti\\(distMat(,endDayMat)?\\)','ti',termNames)
 # termNames <- gsub('s\\(endjulian\\)','s:time',gsub('s\\(easting,northing\\)','s:space',termNames))
 # termNames <- gsub('ti\\(northing,easting,endjulian\\)','ti:spacetime',termNames)
+termNames <- gsub('endDayMat','Time',termNames)
+termNames <- gsub('distMat','Distance',termNames)
+termNames <- gsub('GrassWetland','Grassland',termNames)
[…]

### 2020-09-04 manuscript/manuscript_outline.Rmd
Finished revisions on draft, and added .docx version.

@@
 
+#Forces numbers displayed in inline hooks to be rounded
+inline_hook <- function(x) {
+  if (is.numeric(x)) {
+    format(x, digits = 2)
+  } else x
+}
+knitr::knit_hooks$set(inline = inline_hook)
+
 #Get landscape % cover for each cover class
@@
   rownames_to_column('loc') %>% 
-  mutate(loc=firstUpper(gsub('trapLoc','',loc))) %>% 
+  mutate(loc=gsub('trapLoc','',loc)) %>% 
+  mutate(loc=gsub('ditch','road margin',loc),loc=gsub('native','grassland',loc),loc=firstUpper(gsub('pivot','field edge',loc))) %>%
   rename(p='Pr(>|z|)') %>% mutate(p=roundLess(p,3)) %>% 
@@
   mutate(pTable=ifelse(sig,boldLaTeX(p),p)) %>% select(-sig) #Make text bold
+
 pmelSmTerms <- pmelRes$s.table %>% as.data.frame() %>% 
@@
   mutate(Smoother=gsub('distMat','Distance',Smoother),Smoother=gsub('endDayMat','Day',Smoother),Smoother=gsub('day','Day',Smoother)) %>%
+  mutate(Smoother=gsub('GrassWetland','Grassland',Smoother),Smoother=gsub('TreeShrub','Woodland',Smoother)) %>% 
   rename(p='p-value') %>% mutate(p=roundLess(p,3)) %>% mutate_at(vars(2:4),roundLess,dig=2) %>% 
@@
   mutate(Smoother=gsub('distMat','Distance',Smoother),Smoother=gsub('endDayMat','Day',Smoother),Smoother=gsub('day','Day',Smoother)) %>% 
+  mutate(Smoother=gsub('GrassWetland','Grassland',Smoother),Smoother=gsub('TreeShrub','Woodland',Smoother)) %>% 
   rename(p='p-value') %>% mutate(p=roundLess(p,3)) %>% mutate_at(vars(2:4),roundLess,dig=2) %>% 
@@
 
+#Get average catch rates per spp
+Ncatches <- lapply(list(PteMelMod,ParDisMod,ParMoeMod,OpilioMod),function(x){
+  with(data.frame(x$datList), data.frame(perDayMean=mean(count/trapdays),perDayMedian=median(count/trapdays),total=sum(count),perDaySD=sd(count/trapdays)))
+}) %>% do.call('rbind',.) %>% mutate(spp=c('PteMel','ParDis','ParMoe','Opilio'))
+
 ```
@@
 
-<!-- Ralph's "throwaway paragraph" -->
 Arthropods are one of the most influential groups of animals in agricultural systems.
@@
 For example, wild bee abundance in agricultural landscapes is largely driven by flower and nest availability [@roulston2011], and the effect of SNL on bee abundance and diversity is generally positive.
-Predatory arthopods such as beetles or spiders can be limited by water, food, and egg-laying sites [@lovei1996; @purtauf2005; @gardiner2010], but the effect of SNL on their abundance and diversity is less consistent [@macfadyen2013; @shackelford2013] as some taxa may use SNL as a travel corridor or overwintering site, but are not completely dependent on it for reproduction.
+Predatory arthropods such as beetles or spiders can be limited by water, food, and egg-laying sites [@lovei1996; @purtauf2005; @gardiner2010], but the effect of SNL on their abundance and diversity is less consistent [@macfadyen2013; @shackelford2013] as some taxa may use SNL as a travel corridor or overwintering site, but are not completely dependent on it for reproduction.
 Some taxa are not dependent on SNL at all, and thrive in cultivated landscapes, while others exclusively inhabit SNL and do not venture beyond the edge of cultivated fields.
@@
 
-<!-- Consider what this next paragraph should be about -->
-
-<!-- Limited understanding of other arthropods (but see ``beetle hedges" from UK?) -->
-<!-- No-till agriculture is better for some ground beetles [@busch_Msc] -->
-<!-- Arachnids are similarly limited by food, shelter -->
-<!-- Counts in pitfall traps are a proxy of activity density (not actual density), but this is probably an OK measure, at least within fields [@lang2000] -->
-
 Despite what is known about the spatial and temporal aspects of beneficial arthropod spillover, these are rarely considered together.
-First, some habitat types may act as sources of arthropods during some times of the year, but as sinks during other times, meaning that the timing of spillover may not allign with key periods in crop development.
+First, some habitat types may act as sources of arthropods during some times of the year, but as sinks during other times, meaning that the timing of spillover may not align with key periods in crop development.
 Arthropods can migrate from managed crops back into adjacent SNL at the end of the season [@desender1988; @tscharntke2005b], but this is seldom considered.
@@
 ## Data collection
-We used a set of `r sum(NtrapsPer$n)` pitfall traps installed in road margins (minimum of 5 m away from the road edge, `r with(NtrapsPer, sum(n[trapLoc=='ditch')` traps) and in-field locations (`r with(NtrapsPer, sum(n[trapLoc!='ditch')`) across southern Alberta, Canada in 2017 (Figure \@ref(fig:siteMap)).
+We used a set of `r sum(NtrapsPer$n)` pitfall traps installed in road margins (minimum of 5 m away from the road edge, `r with(NtrapsPer, sum(n[trapLoc=='ditch']))` traps) and in-field locations (`r with(NtrapsPer, sum(n[trapLoc!='ditch']))`) across southern Alberta, Canada in 2017 (Figure \@ref(fig:siteMap)).
+Traps were placed starting on `r format(as.Date(as.character(min(PteMelMod$tempTrap$startjulian)),format='%j'),format='%B %d')`, and collections ended on `r format(as.Date(as.character(max(PteMelMod$tempTrap$endjulian)),format='%j'),format='%B %d')` with collection occurring every `r round(mean(PteMelMod$tempTrap$trapdays),1)` days on average (SD: `r round(sd(PteMelMod$tempTrap$trapdays),1)`), for a total of `r round(sum(PteMelMod$tempTrap$trapdays),1)` trapping days.
 The sites spanned a west-to-east gradient of four natural subregions, including foothills parkland, foothills fescue, mixedgrass, and dry mixedgrass [@ABRegions2006].
-In-field traps were placed in canola crops (`r with(NtrapsPer, sum(n[trapLoc=='canola')`), wetlands (`r with(NtrapsPer, sum(n[trapLoc=='wetland')`), grassy field margins (`r with(NtrapsPer, sum(n[trapLoc=='pivot')`), and remnant prairie grasslands (`r with(NtrapsPer, sum(n[trapLoc=='native')`).
+In-field traps were placed in canola crops (`r with(NtrapsPer, sum(n[trapLoc=='canola']))`), wetlands (`r with(NtrapsPer, sum(n[trapLoc=='wetland']))`), grassy field margins (`r with(NtrapsPer, sum(n[trapLoc=='pivot']))`), and remnant prairie grasslands (`r with(NtrapsPer, sum(n[trapLoc=='native']))`).
 Traps in canola were installed at 25, 75, and 200 m along a transect heading away from the nearest non-crop feature, while the trap at 0 m was installed in the non-crop feature itself.
 We used 582 mL Solo® cups buried up to the rim and partially filled with ethylene glycol, with 2 cm wire mesh mounted over the rim to prevent vertebrates from falling into the traps.
-Specimens were collected from the traps on average every 14 days (SD: 2.9), and were identified to species.
-Increased counts of organisms in pitfall traps can represent higher abundances or higher activity levels, meaning that it is impossible to disentangle arthropod activity from density using single traps ["activity density", @lang2000; @zhao2013].
-However, activity density is generally positively related to ecosystem services, at least in carabids [@trichard2014; @boetzl2018; @gonzalez2020], making it an acceptable metric for our study.
+Specimens were identified to species using appropriate taxonomic literature.
 
@@
 Roadside traps were installed in road margins, while in-field traps were installed directly in canola fields or in adjacent wetland or grassy field corners.'}
-  include_graphics('../figures/maps/PF2017.png',dpi=NA)
+  include_graphics('../figures/maps/PF2017Map.png',dpi=NA)
 ```
@@
 _Pardosa distincta_ and _Pardosa moesta_ are wolf spiders (Araneae: Lycosidae) that are common across the Canadian prairies and are often found in ungrazed pastures [@carcamo2014].
-_P. distincta_ is commonly found in disturbed environments [@collins1996; @wade2010], while _P. moesta_ appear to prefer less frequent disurbances [@kowal2011].
+_P. distincta_ is commonly found in disturbed environments [@collins1996; @wade2010], while _P. moesta_ appear to prefer less frequent disturbances [@kowal2011].
 All _Pardosa_ use an active wandering predation strategy [@young1990], and may use road margins and wooded areas as habitat [@buddle2000; @drapela2011]. 
@@
 
+Increased counts of organisms in pitfall traps can represent higher activity levels (same number of organisms but moving more quickly) or higher abundances (more organisms present in the vicinity of the trap).
+This means that it is impossible to disentangle arthropod activity from density using single traps [@lang2000; @zhao2013], meaning that counts in the traps represent the "activity density" of a given organism.
+However, activity density is generally positively related to ecosystem services, at least in carabids [@trichard2014; @boetzl2018; @gonzalez2020], making it acceptable for our study. 
 To characterize landscape composition surrounding the traps, we used publicly available classified landscape data [30 m resolution; @AAFC_data].
@@
 This allows the possibility that the size of the landscape "grain" relevant to a given organism may change over the course of its life stages [@addicott1987; @lima1996; @gardiner2010].
-It also allows for the possibility that certain land cover types may be locally beneficial, but detremental at wider scales, indicating that the cover type may not constitute a completely useable habitat.
+It also allows for the possibility that certain land cover types may be locally beneficial, but detremental at wider scales, indicating that the cover type may not constitute a completely usable habitat.
 
@@
 
-Preliminary model fits revealed that some of the landscape terms in our model were strongly concurved with each other (Figure \@ref(fig:concurvityFull)), so we removed them from the model or combined them.
-Concurvity is a nonlinear analogue of multicollinearity, and can bias estimates of standard errors [@buja1989].
+Preliminary model fits revealed that some of the landscape terms in our model were strongly concurved with each other, so we removed them from the model or combined them.
+Concurvity is a nonlinear analogue of multicollinearity which can bias estimates of standard errors [@buja1989].
 There is no agreed-upon threshold of "unacceptable" concurvity, but 0.5 is commonly used [@dominici2002; @ramsay2003]. 
@@
 Positive responses to nearby landscape cover classes indicate that the cover class acts as a net source (i.e. arthropods spill over *from* it).
+__Paul, do we need a separate box/figure explaining how to interpret these plots, or should we just include references?__
 However, negative responses to nearby landscape cover classes can indicate one of two things:
@@
 
-## Landscape composition
+## Landscape composition and trap catches
 
-Grassland, cereal, and canola were the three most-abundant landcover classes surrounding our traps, accounting for `r coverList %>% group_by(cover) %>% summarize(p=sum(prop)) %>% ungroup() %>% arrange(desc(p)) %>% mutate(prop=round(100*p/sum(p),2)) %>% slice(1:3) %>% pull(prop) %>% sum `% of land cover.
+Grassland, cereal, and canola were the three most-abundant landcover classes surrounding our traps, accounting for `r coverList %>% group_by(cover) %>% summarize(p=sum(prop)) %>% ungroup() %>% arrange(desc(p)) %>% mutate(prop=round(100*p/sum(p),2)) %>% slice(1:3) %>% pull(prop) %>% sum `% of land cover (Figure \@ref(fig:landscapeComp)).
 Several landscape ``fingerprints" were evident in the landscape annuli, with cereal cover increasing with distance away, along with a corresponding decrease in canola cover (resulting in strong concurvity).
 Grassland cover was largely constant with distance, although a cluster of sites had uniformly high or low cover of grassland with distance.
-Figure \@ref(fig:landscapeComp) displays the proportions of the 10 most-dominant land cover over distance.
+The pitfall traps caught a total of `r with(Ncatches,total[spp=='PteMel'])` _Pterostichus melanarius_, `r with(Ncatches,total[spp=='ParDis'])` _Pardosa distincta_, `r with(Ncatches,total[spp=='ParMoe'])` _Pardosa moesta_, and `r with(Ncatches,total[spp=='Opilio'])` _Phalangium opilio_ (mean trapping rates per day: `r with(Ncatches,paste(round(perDayMean,2),collapse=', '))`, SDs: `r with(Ncatches,paste(round(perDaySD,2),collapse=', '))`).
+
+```{r landscapeComp, echo=FALSE, fig.cap='Landscape composition in annuli surrounding each trap location.
+Sites are represented by individual lines.
+Mean cover for each class is listed in each sub-figure heading.', fig.width=7, fig.height=7}
+coverList %>% group_by(cover) %>% mutate(p=sum(prop)) %>% ungroup() %>% mutate(p=100*round(p/sum(unique(p)),4)) %>% 
+  mutate(cover=paste0(as.character(cover),' (',p,'%)'),prop=prop*100) %>% 
+  mutate(cover=factor(cover,levels=unique(cover))) %>% 
+  ggplot(aes(dist,prop,group=site))+geom_line(alpha=0.2)+
+  facet_wrap(~cover,ncol=4)+theme_classic()+labs(y='Percent cover',x='Inner radius of annuli (m)')
+
+```
 
@@
 _P. melanarius_ activity density was strongly influenced by trap location and landscape composition (Tables \@ref(tab:PteMelLinear), \@ref(tab:PteMelSmooth)).
-Canola crops had a marginally higher activity density of _P.
-melanarius_ than other trap locations (Figure \@ref(fig:PteMelLandscape)a), indicating that canola may allow faster movement of ground beetles, has higher overall population levels, or both.
-Nearby grassland cover had a neutral effect early in the summer, but a negative effect later in the summer (Figure \@ref(fig:PteMelLandscape)b), indicating that _P.
+Canola crops had a marginally higher activity density of _P. melanarius_ than other trap locations (Figure \@ref(fig:PteMelLandscape)a).
+Grassland cover was the most important land cover type in explaining in activity density ($R^2$: 0.104, Table \@ref(tab:rSquared)), and nearby grassland had a neutral effect early in the summer but a negative effect later in the summer (Figure \@ref(fig:PteMelLandscape)b), suggesting that _P.
 melanarius_ may move into grasslands later in the year.
-Nearby canola had a positive effect in the early summer, but conversely, far-away canola (>800 m) had a negative effect, indicating that areas with widespread amounts of canola coverage had lower _P.
+Nearby canola had a positive effect in the early summer, but far-away canola (>800 m) had a negative effect, indicating that areas with widespread canola coverage had lower _P.
 melanarius_ activity density than those with only local canola cover.
@@
 melanarius_ activity density had a strong temporal and spatial component (both p<0.001), indicating that phenology and local geographic factors were strong drivers of ground beetle activity density (Figure \@ref(fig:PteMelSpatiotemporal)).
-The landscape composition and trap location explained `r r2Nakagawa$PteMelMod[1]*100`%  of variance in activity density, while the spatial and temporal smoothers accounted for `r with(r2Nakagawa,(PteMelMod[2]-PteMelMod[1])*100)`% (Table \@ref(tab:rSquared)).
+The landscape composition and trap location explained `r r2Nakagawa$PteMelMod[1]*100`% of the variance in activity density, while the spatial and temporal smoothers accounted for `r with(r2Nakagawa,(PteMelMod[2]-PteMelMod[1])*100)`% (Table \@ref(tab:rSquared)).
 
@@
 
-Activity density of _P. distincta_ and _P. moesta_ was strongly influenced by trap location and landscape composition (Tables \@ref(tab:ParDisLinear), \@ref(tab:ParDisSmooth)).
+Activity density of _P.
+distincta_ and _P.
+moesta_ was influenced by trap location and landscape composition (Tables \@ref(tab:ParDisLinear), \@ref(tab:ParDisSmooth)), but landscape composition had relatively weak effects on both species ($R^2$: `r filter(r2Nakagawa2,grepl('Par',model),!grepl('s\\(',terms),terms!='trapLoc',terms!='sigmaD') %>% group_by(model) %>% summarize(s=sum(r2comp)) %>% pull(s) %>% paste(.,collapse=', ')`).
 Unlike _P. melanarius_, both _Pardosa_ species had far lower activity density in canola than any other cover type (Figures \@ref(fig:ParDisLandscape)a, \@ref(fig:ParMoeLandscape)a).
@@
 Trees and shrubs acted as a sink for _P. distincta_ later in the season, and as a weak source early on in the season for _P. moesta_ (Figures \@ref(fig:ParDisLandscape)d, \@ref(fig:ParMoeLandscape)d).
-Grasslands had strong local negative effect on _P.
+Grasslands had a local negative effect on _P.
 moesta_, but a positive landscape-level effect, indicating that while these cover types act as a sink, the general amount of grassland in the area had a positive effect on _P.
@@
 _Phalangium opilio_ activity density was strongly influenced by trap location, with pivot corners and wetlands having the highest activity density (Figure \@ref(fig:OpilioLandscape)a).
-_P. opilio_ was affected by grasslands (p=`r with(opilSmTerms,p[Smoother=='ti(Distance,Day):GrassWetland'])`) and trees/shrubs (p`r with(opilSmTerms,p[Smoother=='s(Distance):TreeShrub'])`). 
-Nearby grassland and trees/shrubs both had a negative effect on _P. opilio_ activity density, but only early in the season (Figures \@ref(fig:OpilioLandscape)b,c).
-However, the specific effect of these land cover types was not very large, as a competing model using only non-crop cover performed slightly better (Full model AIC = `r with(OpilioMod, sprintf("%.1f",AIC(mod3)))`, Non-crop model AIC = `r with(OpilioMod, sprintf("%.1f",AIC(mod4)))`).
+Landscape composition explained `r filter(r2Nakagawa2,grepl('Opilio',model),!grepl('s\\(',terms),terms!='trapLoc',terms!='sigmaD') %>% summarize(s=sum(r2comp)) %>% pull(s) %>% paste(.,collapse=', ')`% of variance in _P.
+opilio_ activity density.
+Nearby grassland (p=`r with(opilSmTerms,p[Smoother=='ti(Distance,Day):GrassWetland'])`) and woodland (p=`r with(opilSmTerms,p[Smoother=='s(Distance):TreeShrub'])`) both had negative effects on _P.
+opilio_ activity density, but only early in the season (Figures \@ref(fig:OpilioLandscape)b,c).
+Compare this to _P. melanarius_, which is also influenced by grassland and woodland, but where the effect was negative _late_ in the season.
 The temporal and spatial components, as in the other two species, were both very strong (both p`r with(opilSmTerms,p[grepl('E,N',Smoother)])`).
-Together, these results indicate that _P. opilio_ activity density is less influenced by landscape composition than _P. melanarius_ or our two _Pardosa_ species.
 The landscape composition and trap location explained `r r2Nakagawa$OpilioMod[1]*100`%  of variance in activity density, while the spatial and temporal smoothers accounted for `r with(r2Nakagawa,(OpilioMod[2]-OpilioMod[1])*100)`%.
@@
 
-The activity density of _Pterostichus melanarius_, _Pardosa distincta_, _Pardosa moesta_, and _Phalangium opilio_ responded strongly to landscape composition.
-There was also a strong temporal component to the landscape effects, meaning that it is important to consider how sinks and sources may change over the season.
-We found some support for our predictions of SNL (grass and wetland, forest and shrubs, and road margins) acting as a late-season sinks for beneficial arthropods.
-In particular, grass/wetland acted as a sink for _P. melanarius_, woodlands acted as a sink for _P. distincta_, and road margins acted as a sink for _P. moesta_.
-While there was limited evidence of SNL acting as early-season sources, some acted as landscape-level sources (road margins on _P. moesta_), indicating either earlier or wider-scale dispersal.
-Canola and pasture acted as landscape-level sinks for _P. melanarius_ and _P. distincta_, respectively, meaning that these cover types likely represent insufficient habitat for these arthropods.
-The influence of landscape composition tended to be limited to a radius of about 500m, indicating that large-scale land cover may be more important than previously thought.
-These results highlight the seasonal importance of non-crop marginal lands for predatory arthropod abundance (Table \@ref(tab:sumTab)).
+The activity density of _Pterostichus melanarius_ and _Phalangium opilio_ responded to strongly landscape composition, but the response of _Pardosa distincta_ and _Pardosa moesta_ was weaker.
+We found some support for our predictions of SNL (grass and wetland, woodlands, and road margins) acting as a late-season sinks for beneficial arthropods.
+In particular, grass and wetland acted as a sink for _P. melanarius_, woodlands acted as a sink for _P. distincta_, and road margins acted as a sink for _P. moesta_.
+While there was limited evidence of SNL acting as early-season sources, some acted as landscape-level sources (grassland and road margins on _P. moesta_), indicating earlier or wider-scale dispersal.
+Canola and pasture acted as landscape-level sinks for _P. melanarius_ and _P. distincta_, respectively, meaning that these cover types likely represent only partial habitat for these arthropods.
+There was also a strong temporal component to most of the landscape effects, meaning that it is important to consider how sinks and sources may change over the season.
+Finally, the influence of landscape composition tended to be limited to a radius of about 500m, indicating that large-scale _and_ local land cover can be important to beneficial arthropod abundance.
+These results highlight the seasonal importance of non-crop marginal lands for predatory arthropod abundance.
 
@@
 
-Table: (\#tab:sumTab) Summary table of results.
-Early, mid, and late indicate the time of the season when cover classes had strong effects on abundance.
-Italics indicates that effects were weak (p>=0.05)
-
-+-----------------+----------------------------+----------------------------+---------------------------+-------------------------+
-| Cover class     | _P. melanarius_            | _P. distincta_             | _P. moesta_               | _P. opilio_             |
-+================:+:===========================+:===========================+:==========================+:========================+
-| Grass & Wetland | - Local sink (late)        |                            | - Local sink              | - Local sink (early)    |
-|                 |                            |                            | - Landscape source        |                         |
-+-----------------+----------------------------+----------------------------+---------------------------+-------------------------+
-| Canola          | - Local source (early)     | - _Local source (early)_   | - Local source (early)    |                         |
-|                 | - Landscape sink (early)   | - _Local sink (late)_      | - Local sink (late)       |                         |
-+-----------------+----------------------------+----------------------------+---------------------------+-------------------------+
-| Pasture         |                            | - Landscape sink           |                           |                         | 
-+-----------------+----------------------------+----------------------------+---------------------------+-------------------------+
-| Forest & Shrubs |                            | - Sink (late)              |                           | - Local sink (early)    |
-|                 |                            |                            |                           | - Landscape source (mid)|
-+-----------------+----------------------------+----------------------------+---------------------------+-------------------------+
-| Pulses          | - Source (late)            |                            | - Landscape source        |                         |
-+-----------------+----------------------------+----------------------------+---------------------------+-------------------------+
-| Urban           |                            |                            | - Local source (early)    |                         |
-|                 |                            |                            | - Landscape sink (early)  |                         |
-|                 |                            |                            | - Local sink (late)       |                         |
-|                 |                            |                            | - Landscape source (late) |                         |
-+-----------------+----------------------------+----------------------------+---------------------------+-------------------------+
-
-<!-- This table looks terrible, but I don't think pander will make it any better -->
-
 The predatory ground beetle _Pterostichus melanarius_ responded to landscape composition, primarily to canola, pulses, and grass and wetland cover.
@@
 Other studies have found similar results, suggesting that untilled land is important off-field habitat for carabids [@desender1988; @fournier2002; but see @hatten2007].
-In particular, @purtauf2005 found that carabid density increased with proportion of nearby grasslands; our finding of grassland as late-season sink may represent _P.
+In particular, @purtauf2005 found that carabid density increased with proportion of nearby grasslands, so our finding of grassland as late-season sink may represent _P.
 melanarius_ moving to overwintering habitat at the end of the season.
-However, _P. melanarius_ is also found in a wide variety of habitats, and tends to prefer agricultural fields [@larsen2003], which our models also demonstrated.
-We also found that canola and pulse crops acted as early- and mid-season sources of _P. melanarius_.
+However, _P. melanarius_ is also found in a wide variety of habitats, and tends to prefer agricultural fields [@larsen2003]. 
+Our models also suggest this, as they showed that canola and pulse crops acted as early- and mid-season sources of _P. melanarius_.
 Early in the season, canola crops acted as local source but a landscape-level sink, which may indicate that they provide only temporary feeding habitat.
-The effect of pulse crops on carabid abundance is not well-studied, but our results suggest that pulses may represent a potential food resource for _P. melanarius_.
+The effect of pulse crops on carabid abundance is not well-studied, but our results suggest that pulses may represent a potential food resource for _P.
+melanarius_, albeit a weak one (Table \@ref(tab:rSquared)).
 Carabids are predators of pea-leaf weevils (_Sitona lineatus_) on other Fabaceae [@hamon1990], and _P.
@@
 The wolf spiders _Pardosa distincta_ and _Pardosa moesta_ both responded to landscape composition, but in slightly different ways.
-Canola acted as an early-season source for both species, indicating that _Pardosa_ may use canola as foraging grounds, similar to _P. melanarius_.
-The response to other landscape cover classes, however, was different between each species.
-Aside from the (weak) effect of canola, we found that the only other landscape classes that influenced _P. distincta_ were pasture, and trees and shrubs.
-Pasture had a negative effect at the landscape scale, and trees and shrubs acted as a late season sink, suggesting that they use woody shrubs and trees for overwintering or winter foraging [@aitchison1984].
+Canola acted as an early-season source for both species, indicating that _Pardosa_ and _P. melanarius_ may both use canola as foraging grounds.
+The responses to other landscape cover classes, however, was different between each species of spider.
+The only other landscape classes that influenced _P. distincta_ were pasture and woodland.
+Pasture had a negative effect at the landscape scale, and woodland acted as a late season sink, suggesting that _Pardosa_ use woody shrubs and trees for overwintering or winter foraging [@aitchison1984].
 _Pardosa_ are found in areas close to disturbed roadside strips [@drapela2008; @drapela2011; @kowal2011], but _P.
@@
 @moring1994 showed that _P.
-distincta_ were more active in grassy habitats, but we did not find evidence of this, aside from generally higher activity density in trap locations with higher grass cover (Figure \@ref(fig:ParDisLandscape)a).
+distincta_ were more active in grassy habitats, which we found partial evidence of, as _P.
+distincta_ tended to have higher activity density in trap locations with higher grass cover (Figure \@ref(fig:ParDisLandscape)a).
 For _P. moesta_, we found that roads clearly acted as an early source and a late sink [similar to @drapela2008 and @drapela2011]. 
-Grassland and wetland, as well as pulses, also acted as a local sink, but a landscape-level source, suggesting that they draw _P.
+Grassland and wetland, as well as pulses, also acted as a local sink but a landscape-level source, suggesting that they draw _P.
 moesta_ away from trapping locations but enhance their landscape-level abundance.
-Lycosids employ a wandering-active predation strategy [@young1990], meaning that nearby landscape composition may be more influential than large-scale composition [@oberg2007; @oberg2008].
-While trapping location explained a large proportion of variance for both species (`r filter(r2Nakagawa2,model=='ParDisMod',grepl('trapLoc',terms))$r2comp` and `r filter(r2Nakagawa2,model=='ParMoeMod',grepl('trapLoc',terms))$r2comp`), several landscape features were also important at large spatial scales, including grass and wetland, pasture, pulses, and urban, showing that their dispersal distances may be further than previously though.
+Lycosids employ a wandering-active predation strategy [@young1990], meaning that nearby landscape composition may be more influential to _Pardosa_ than large-scale composition [@oberg2007; @oberg2008].
+While trapping location explained a large proportion of variance for both species (`r round(filter(r2Nakagawa2,model=='ParDisMod',grepl('trapLoc',terms))$r2comp,2)` and `r round(filter(r2Nakagawa2,model=='ParMoeMod',grepl('trapLoc',terms))$r2comp,2)`), several landscape features were also important at large spatial scales, including grass and wetland, pasture, pulses, and road margins.
+This suggests that _Pardosa_ dispersal distances may be further than previously though, either through ballooning as juveniles [@richter1970; @greenstone1982] or through other long-distance travel.
 
 _Phalangium opilio_ activity density responded to grass and wetland cover, as well as trees and shrubs, but the trap location and landscape explained only `r r2Nakagawa$OpilioMod[1]*100`% of the variance.
-Other studies have found that _P.
-opilio_ is mostly found in human-altered landscapes with a large proportion of farming [@muster2014; @vandepoel2015Msc], and since most of our study area was in or near farmed land, this lack of variation is understandable.
-However, there were a few notable landscape-level patterns that emerged.
+Other studies have found that _P. opilio_ is mostly found in human-altered landscapes with a large proportion of farming [@muster2014; @vandepoel2015Msc].
+Since most of our study area was in or near farmed land, the lack of variation is understandable, but there were a few notable landscape-level patterns that emerged.
 _P. opilio_ activity density was higher in grassy pivot corners and wetlands, but grasslands and wetlands acted as a local sink of _P. opilio_ until late in the season.
@@
 Unlike the other arthropods, most of the variation in activity density for _P.
-opilio_ was explained by day of year (R$^2$ = `r filter(r2Nakagawa2,model=='OpilioMod',grepl('day',terms))$r2comp`), indicating strong seasonal emergence cues.
+opilio_ was explained by day of year (R$^2$ = `r round(filter(r2Nakagawa2,model=='OpilioMod',grepl('day',terms))$r2comp,2)`), indicating strong seasonal emergence cues.
+<!-- Feels like this paragraph ends too soon. Why was there so little variation due to landscape? Link to biology of the critter. -->
 
-<!-- Why is this study special? Why do we care? Why do we need another landscape-level study of SNL and insect abundance? -->
-Many other studies have considered the overall effect of SNL on ecosystem service provision, but our study has highlighted the different spatial and temporal scales that ecosystem service provision is couched in.
-We have shown how a relatively new statistical technique can be used to consider multiple spatial scales of landscape composition, providing richer inference about the processes acting on beneficial arthropods.
-Other studies have considered how different SNL types act as sinks or sources at different times of year, but our results reveal the changes in sinks and sources within an agricultural landscape.
-These patterns imply movement of organisms between landscape features, but since we did not directly this, future studies could directly examine arthropod movement, with the goal of integrating landscape ecology and behavioural processes into a single model [@lima1996].
-Mark-recapture techniques, directly tracking movement patterns (e.g. radio tags), or two-sided traps could be useful for this.
+Many other studies have considered the overall effect of SNL on ecosystem service provision, but we have highlighted the different spatial and temporal aspects of ecosystem service provision.
+We have shown how a relatively straightforward statistical technique can be used to consider multiple spatial scales of landscape composition, providing richer inference about the processes acting on beneficial arthropods.
+Different types of SNL act as sinks or sources at different times of year, but our results reveal the changes in sinks and sources within an agricultural landscape.
+These patterns imply movement of organisms between landscape features, but since we did not directly measure this, future studies should directly examine arthropod movement, with the goal of integrating landscape ecology and behavioural processes into a single model [@lima1996].
 This would also allow direct inference about landscape categories that were combined in our dataset, allowing us to consider different landscape categories independently.
@@
 \beginsupplement
-
-```{r landscapeComp, echo=FALSE, fig.cap='Landscape composition in annuli surrounding each trap location.
-Sites are represented by individual lines.
-Overall percent cover for each cover class is listed in each sub-figure heading.', fig.width=7, fig.height=7}
-coverList %>% group_by(cover) %>% mutate(p=sum(prop)) %>% ungroup() %>% mutate(p=100*round(p/sum(unique(p)),4)) %>% 
-  mutate(cover=paste0(as.character(cover),' (',p,'%)'),prop=prop*100) %>% 
-  mutate(cover=factor(cover,levels=unique(cover))) %>% 
-  ggplot(aes(dist,prop,group=site))+geom_line(alpha=0.2)+
-  facet_wrap(~cover,ncol=4)+theme_classic()+labs(y='Percent cover',x='Radius of annulus (m)')
-
-```
-
-```{r concurvityFull, echo=FALSE, fig.cap='Concurvity estimates for ten most-abundant land cover classes'}  
-  include_graphics('../figures/coverCorPlots/concurvityEstimate_full.png',dpi=NA)
-```
 
@@
 pmelLinTerms %>% select(-p) %>% 
-  kable(.,caption='Linear terms for \\emph{Pterostichus melanarius}',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
+  kable(.,caption='Trap location effects for \\emph{Pterostichus melanarius}',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
       digits=c(1,2,2,2,2),align='rrrrl',escape=FALSE)
@@
 pdisLinTerms %>% select(-p) %>% 
-  kable(.,caption='Linear terms for \\emph{Pardosa distincta}. Line',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
+  kable(.,caption='Trap location effects for \\emph{Pardosa distincta}',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
         digits=c(1,2,2,2,2),align='rrrrl',escape=FALSE)
@@
 pmoeLinTerms %>% select(-p) %>% 
-  kable(.,caption='Linear terms for \\emph{Pardosa moesta}. Line',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
+  kable(.,caption='Trap location effects for \\emph{Pardosa moesta}.',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
         digits=c(1,2,2,2,2),align='rrrrl',escape=FALSE)
@@
 opilLinTerms %>% select(-p) %>% 
-  kable(.,caption='Linear terms for \\emph{Phalangium opilio}',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
+  kable(.,caption='Trap location effects for \\emph{Phalangium opilio}',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
         digits=c(1,2,2,2,2),align='rrrrl',escape=FALSE)

### 2020-09-04 frAnalysis.R

@@ -108,7 +108,7 @@ plot(mod3,scheme=2,shade=T,pages=1,all.terms=T,rug=F,seWithMean=T)
 concurvity(mod3) #High concurvity
 checkMC <- concurvity(mod3,full=F)$estimate
 termNames <- rownames(checkMC)
-termNames[1] <- 'Linear terms'
+termNames[1] <- 'Trap location'
 # termNames <- gsub('s\\(distMat(,endDayMat)?\\)','s',gsub('\\:oRingMat2Prop\\$',':',rownames(checkMC)))
 # termNames <- gsub('ti\\(distMat(,endDayMat)?\\)','ti',termNames)
 # termNames <- gsub('s\\(endjulian\\)','s:time',gsub('s\\(easting,northing\\)','s:space',termNames))

### 2020-09-30 manuscript/manuscript_outline.Rmd
Worked on revisions

@@
 ---
-title: Non-crop features influence the abundance and timing of beneficial arthropod abundance
-# PG: time is important in this paper - conservation efforts should consider temporal availability of resources
-# Find the angle and write for this
+title: "Beneficial arthropod habitat useage changes within-season: implications for pest control services in croplands"
 #Potential titles: 
 # Non-crop features influence the abundance and timing of beneficial arthropod abundance
-# Seasonal sinks and sources of beneficial arthropods in Canadian prairie agroecosystems
-# Non-crop features create seasonal sinks and sources of beneficial arthropods
+# 1) Cropland ecosystem services in space and time: Beneficial arthropod habitat use shifts within-season.
+# 2) Beneficial arthropod habitat use shifts within-season: implications for pest control services in croplands
 # 
-# subtitle: 
 author:
@@
     footnote: 1
+  - name: Diane Edwards
+    email: diane.edwards.ca@gmail.com
+    affiliation: University of Calgary
+  - name: Jess Vickruck
+    email: jessica.vickruck@canada.ca
+    affiliation: Agriculture and Agri-Food Canada
+  - name: Lincoln Best
+    email: lincoln.best@oregonstate.edu
+    affiliation: Oregon State University
   - name: Paul Galpern
@@
     address: 2500 University Drive NW, Calgary, AB, Canada
+  - code: Agriculture and Agri-Food Canada
+    address: 850 Lincoln Road, Fredericton, NB, Canada
+  - code: Oregon State University
+    address: 1500 SW Jefferson Way, Corvallis, OR, USA
 footnote:
@@
 date: "Spring 2020"
-abstract: Ground-dwelling arthropods are important generalist predators in prairie agro-ecosystems, and can use non-crop features as overwintering habitats.
-However, it is unclear which types of landscape features constitute useful non-crop habitat, and what spatial scale of habitat is required.
+abstract: Ground-dwelling arthropods are important generalist predators in agro-ecosystems, and can use non-crop features as overwintering habitats.
+However, it is unclear which types of landscape features constitute useful non-crop habitat, and at what spatial scale organisms gather resources at.
 Additionally, the same landscape feature may act as a sink or a source of arthropods at different times of the year, but this is rarely considered.
-We modeled the activity density of four highly-abundant species of Canadian prairie arthropods, and used functional regression to simultaneously consider both their habitat preferences and the timing of sources and sinks.
+We modeled the activity-density of four highly-abundant species of Canadian prairie arthropods, and used functional regression to simultaneously consider both their habitat preferences and the timing of sources and sinks.
 We found that canola crops (_Brassica napus_ L.) acted as early-season sources, and that grasses and wetlands acted as late-season sinks of arthropods.
@@
 header-includes: 
+  \usepackage{tcolorbox} 
   \usepackage{float} \floatplacement{figure}{H} 
   \newcommand{\beginsupplement}{\setcounter{table}{0} \newpage \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
-
 ---
@@
 These important fluxes of mobile arthropods, both to crops and away from them, are key for managing both crop yield and biodiversity in agroecosystems.
-Finding "win-win" practices is of particular importance to land managers and conservationists; that is, practices that result in better conservation outcomes while achieving similar crop yields.
-Finally, agricultural land occupies 15 million km$^2$ (~36%) of land globally [@ramankutty2018], meaning that conservation efforts should pay particular attention to agricultural practices.
+Finding "win-win" practices is of particular importance to land managers and conservationists; that is, practices that result in better conservation outcomes while maintaining or improving crop yields.
+Finally, agricultural land occupies 15 million km$^2$ (~36%) of land globally [@ramankutty2018], suggesting that there remains great potential to achieve conservation outcomes by adjusting agricultural practices.
 
-Uncultivated semi-natural land (SNL) can act as important habitat for beneficial arthropods [@duelli2003], which may spill over into adjacent crops.
+Uncultivated semi-natural land (SNL) can act as important habitat for beneficial arthropods [@duelli2003], which may spill over into adjacent cropland.
 Therefore, landscape management is a strategy to increase beneficial arthropod abundance in crops [@albrecht2010; @landis2000; @martin2020; but see @tscharntke2016; @karp2018].
@@
 This depends on the life history of the organisms in question, such as the seasonal timing of emergence, feeding, and reproduction, as well as their traits such as dispersal capability.
-Non-adjacent cropland can also influence arthropod abundance if the organisms are long-distance dispersers[@oberg2008].
+Non-adjacent cropland can also influence arthropod abundance if the organisms are long-distance dispersers [@oberg2008].
 <!-- Small patches of SNL can have a large effect if overall landscape lacks SNL (landscape contrast [@boetzl2020; @vanSchalkwyk2020]) -->
-In this way, the spillover of beneficial arthropods into crops depends not only on the amount of adjacent SNL, but the specific habitat type, the time of the year, and the spatial scale of landscape that is relevant to the organism.
+In this way, the spillover of beneficial arthropods into crops depends not only on the amount of adjacent SNL, but the specific habitat type, the time of the year, and the spatial scale at which an organism gathers resources.
 
@@
 
-In this study, we used pitfall traps to determine how landscape composition affects the seasonal activity density of arthropods across a Canadian prairie agroecosystem.
+In this study, we used pitfall traps to determine how landscape composition affects the seasonal activity-density of arthropods across a large Canadian prairie agroecosystem.
 We considered the following hypotheses:
@@
 3. Crops may act as a temporary feeding site for predators. Therefore, crops may act as a local sink for arthropods, but will also be negatively associated at larger (landscape-level) scales.
-Using a large pitfall trapping dataset, we were able to relate seasonal changes in arthropod abundance to landscape composition at multiple spatial scales, and found evidence of SNL acting as late-season sinks in abundance.
+Using a large pitfall trapping dataset, we related seasonal changes in arthropod abundance to landscape composition at multiple spatial scales.
 
@@
 We used a set of `r sum(NtrapsPer$n)` pitfall traps installed in road margins (minimum of 5 m away from the road edge, `r with(NtrapsPer, sum(n[trapLoc=='ditch']))` traps) and in-field locations (`r with(NtrapsPer, sum(n[trapLoc!='ditch']))`) across southern Alberta, Canada in 2017 (Figure \@ref(fig:siteMap)).
-Traps were placed starting on `r format(as.Date(as.character(min(PteMelMod$tempTrap$startjulian)),format='%j'),format='%B %d')`, and collections ended on `r format(as.Date(as.character(max(PteMelMod$tempTrap$endjulian)),format='%j'),format='%B %d')` with collection occurring every `r round(mean(PteMelMod$tempTrap$trapdays),1)` days on average (SD: `r round(sd(PteMelMod$tempTrap$trapdays),1)`), for a total of `r round(sum(PteMelMod$tempTrap$trapdays),1)` trapping days.
+Traps were placed starting on `r format(as.Date(as.character(min(PteMelMod$tempTrap$startjulian)),format='%j'),format='%B %d')`, and collections ended on `r format(as.Date(as.character(max(PteMelMod$tempTrap$endjulian)),format='%j'),format='%B %d')`, with collection occurring continuously and traps being emptied every `r round(mean(PteMelMod$tempTrap$trapdays),1)` days on average (SD: `r round(sd(PteMelMod$tempTrap$trapdays),1)`).
+This resulted in `r nrow(PteMelMod$tempTrap)` unique collection events, taking place across a total of `r round(sum(PteMelMod$tempTrap$trapdays),1)` trapping days.
 The sites spanned a west-to-east gradient of four natural subregions, including foothills parkland, foothills fescue, mixedgrass, and dry mixedgrass [@ABRegions2006].
@@
 We used 582 mL Solo® cups buried up to the rim and partially filled with ethylene glycol, with 2 cm wire mesh mounted over the rim to prevent vertebrates from falling into the traps.
-Specimens were identified to species using appropriate taxonomic literature.
+Specimens were identified to species using appropriate taxonomic literature [@dondale1990; @edgar1990; @vogel2004; @yigit2007].
+
+We used counts of organisms in our pitfall traps as proxies of ecosystem service provision.
+However, increased counts of organisms in pitfall traps can represent higher activity levels (same number of organisms but more mobile) or higher abundances in the vicinity of the trap.
+This makes it impossible to disentangle arthropod activity from density using single traps [@lang2000; @zhao2013], meaning that counts in the traps represent the "activity-density" of a given organism.
+Despite this disadvantage, activity-density is generally positively related to ecosystem services, at least in carabids [@trichard2014; @boetzl2018; @gonzalez2020], making it acceptable for our study.
 
@@
 
-We used four highly-abundant species of predatory arthropods found in the pitfall traps, as common species are often more important for ecosystem service provision than rare species [@winfree2015].
-_Pterostichus melanarius_ is a introduced predatory ground beetle (Coleoptera: Carabidae) that is a wide-ranging generalist [@carcamo1994; @larsen2003; @busch_Msc].
+We used four highly-abundant species of predatory arthropods found in the pitfall traps, as common species are often more important for ecosystem service provision than rare ones [@winfree2015].
+_Pterostichus melanarius_ is an introduced predatory ground beetle (Coleoptera: Carabidae) that is a wide-ranging generalist [@carcamo1994; @larsen2003; @busch_Msc].
 It is commonly found in untilled grasslands [@purtauf2005] and may use grassy field margins as larval habitat [@desender1988].
-_Pardosa distincta_ and _Pardosa moesta_ are wolf spiders (Araneae: Lycosidae) that are common across the Canadian prairies and are often found in ungrazed pastures [@carcamo2014].
-_P. distincta_ is commonly found in disturbed environments [@collins1996; @wade2010], while _P. moesta_ appear to prefer less frequent disturbances [@kowal2011].
-All _Pardosa_ use an active wandering predation strategy [@young1990], and may use road margins and wooded areas as habitat [@buddle2000; @drapela2011]. 
-Finally, _Phallangium opilio_ is a widely-distributed generalist harvestman (Opiliones: Phalangiidae), whose habitat preferences are poorly understood. 
-They are commonly found in human-altered landscapes [@muster2014; @vandepoel2015Msc] and are generally nocturnal hunters and scavengers [@halaj2000; @allard2005; @allard2005b].
+_Pardosa_ are wolf spiders (Araneae: Lycosidae) that use an active wandering predation strategy [@young1990], and are common across the Canadian prairies.
+Both _Pardosa distincta_ and _Pardosa moesta_ are found in a wide variety of habitats, but are common in ungrazed pastures [@dondale1990; @carcamo2014].
+_P. distincta_ is commonly found in disturbed environments [@collins1996; @wade2010], while _P. moesta_ appear to prefer less frequent disturbances [@graham2003; @kowal2011; but see @dondale1990].
+Other _Pardosa_ are known to use road margins and wooded areas as habitat [@buddle2000; @drapela2011].
+Finally, _Phallangium opilio_ is an introduced harvestman (Opiliones: Phalangiidae) that is found in drier disturbed areas [@bragg2009].
+Juveniles hatch from eggs during the spring, becoming adults during the summer, and eggs are laid during the fall [adults do not overwinter; @bragg2009].
+They are commonly found in human-altered landscapes [@muster2014; @vandepoel2015Msc] and are nocturnal generalist hunters and scavengers [@halaj2000; @allard2005; @allard2005b], mainly eating small soft-bodied invertebrates [@acosta2007].
 
-Increased counts of organisms in pitfall traps can represent higher activity levels (same number of organisms but moving more quickly) or higher abundances (more organisms present in the vicinity of the trap).
-This means that it is impossible to disentangle arthropod activity from density using single traps [@lang2000; @zhao2013], meaning that counts in the traps represent the "activity density" of a given organism.
-However, activity density is generally positively related to ecosystem services, at least in carabids [@trichard2014; @boetzl2018; @gonzalez2020], making it acceptable for our study. 
 To characterize landscape composition surrounding the traps, we used publicly available classified landscape data [30 m resolution; @AAFC_data].
@@
 
-Scalar-on-function regression of activity density was fit using generalized additive models [_mgcv_ version `r packageVersion('mgcv')`; @wood2017]. 
+Scalar-on-function regression of activity-density was fit using generalized additive models [_mgcv_ version `r packageVersion('mgcv')`; @wood2017]. 
 Count data of arthropods were modeled using a negative binomial distribution with a log-link function and a single dispersion parameter ($\theta$).
@@
 <!-- Some landscape terms were strongly concurved , namely forest and shrubland (max: 0.71), canola and cereal (max: 0.74), and grassland and wetland (max: 0.63). -->
-Forest and shrubland were combined into a single ``woodland" category, and grassland and wetland were combined into a single "grassland" category, as they were strongly positively correlated at all distances, indicating similar feature classes.
+Trees and shrubs were combined into a single ``woodland" category, and grassland and wetland were combined into a single "grassland" category, as they were strongly positively correlated at all distances, indicating similar feature classes.
 Cereal was removed from the model, as it was negatively correlated with canola cover at distances less than 200m and was positively correlated at distances over 500m, reflecting the most common crop rotations (canola $\rightarrow$ wheat $\rightarrow$ barley) and the commonly-used 800 m block structure of farmland in our study region (quarter-sections).
-This resulted in a reduced set of landscape terms, none of which were strongly concurved with each other (Figure \@ref(fig:concurvity))
+This resulted in a reduced set of landscape terms, none of which were strongly concurved with each other (grassland, canola, pasture, woodland, pulses, urban; see Figure \@ref(fig:concurvity))
 
@@
 
-<!-- * We used 4 nested models to gauge the relative importance of landscape composition for arthropod activity density -->
+<!-- * We used 4 nested models to gauge the relative importance of landscape composition for arthropod activity-density -->
 <!--   + Model 1 consisted of a temporal and spatial smoothers (``random effects"), necessary to account for the underlying spatiotemporal structure of the data  -->
 <!--   + Smoothers can be thought of as random effects, where the coefficients follow a probability distribution defined by a fixed smoothing coefficient $\lambda$ [@wood2017]  -->
-<!--   + Model 2 added a local cover term, to account for the specific effect of local cover on activity density -->
-<!--   + Model 3 added a smoother term for the landscape rings, modeling the effect of non-crop cover at varying distances on activity density -->
+<!--   + Model 2 added a local cover term, to account for the specific effect of local cover on activity-density -->
+<!--   + Model 3 added a smoother term for the landscape rings, modeling the effect of non-crop cover at varying distances on activity-density -->
 <!--   + Model 4, similar to model 3, modeled the effect of all underlying cover classes (crop and non-crop) at varying distances -->
@@
 <!-- -------- | --------------------------------------------------------- | ----------------------------------------------- -->
-<!-- 1        | Phenology + Geography                                     | Activity Density ~ s(Day) + s(E,N) -->
-<!-- 2        | Phenology + Geography + Local cover                       | Activity Density ~ s(Day) + s(E,N) + Trap Location -->
-<!-- 3        | Phenology + Geography + Local cover + Landscape (general) | Activity Density ~ s(Day) + s(E,N) + Trap Location + s(Non-crop Cover)-->
-<!-- 4        | Phenology + Geography + Local cover + Landscape (specific)| Activity Density ~ s(Day) + s(E,N) + Trap Location + s(Cover 1) + s(Cover 2) + ... + s(Cover n) -->
+<!-- 1        | Phenology + Geography                                     | activity-density ~ s(Day) + s(E,N) -->
+<!-- 2        | Phenology + Geography + Local cover                       | activity-density ~ s(Day) + s(E,N) + Trap Location -->
+<!-- 3        | Phenology + Geography + Local cover + Landscape (general) | activity-density ~ s(Day) + s(E,N) + Trap Location + s(Non-crop Cover)-->
+<!-- 4        | Phenology + Geography + Local cover + Landscape (specific)| activity-density ~ s(Day) + s(E,N) + Trap Location + s(Cover 1) + s(Cover 2) + ... + s(Cover n) -->
 
@@
 Grassland, cereal, and canola were the three most-abundant landcover classes surrounding our traps, accounting for `r coverList %>% group_by(cover) %>% summarize(p=sum(prop)) %>% ungroup() %>% arrange(desc(p)) %>% mutate(prop=round(100*p/sum(p),2)) %>% slice(1:3) %>% pull(prop) %>% sum `% of land cover (Figure \@ref(fig:landscapeComp)).
-Several landscape ``fingerprints" were evident in the landscape annuli, with cereal cover increasing with distance away, along with a corresponding decrease in canola cover (resulting in strong concurvity).
+Several landscape ``fingerprints" were evident in the landscape annuli, with cereal cover increasing with distance away, along with a corresponding decrease in canola cover.
 Grassland cover was largely constant with distance, although a cluster of sites had uniformly high or low cover of grassland with distance.
@@
 
-_P. melanarius_ activity density was strongly influenced by trap location and landscape composition (Tables \@ref(tab:PteMelLinear), \@ref(tab:PteMelSmooth)).
-Canola crops had a marginally higher activity density of _P. melanarius_ than other trap locations (Figure \@ref(fig:PteMelLandscape)a).
-Grassland cover was the most important land cover type in explaining in activity density ($R^2$: 0.104, Table \@ref(tab:rSquared)), and nearby grassland had a neutral effect early in the summer but a negative effect later in the summer (Figure \@ref(fig:PteMelLandscape)b), suggesting that _P.
+_P. melanarius_ activity-density was strongly influenced by trap location and landscape composition (Tables \@ref(tab:PteMelLinear), \@ref(tab:PteMelSmooth)).
+Canola crops had a marginally higher activity-density of _P. melanarius_ than other trap locations (Figure \@ref(fig:PteMelLandscape)a).
+Grassland cover was the most important land cover type in explaining in activity-density ($R^2$: 0.104, Table \@ref(tab:rSquared)), and nearby grassland had a neutral effect early in the summer but a negative effect later in the summer (Figure \@ref(fig:PteMelLandscape)b), suggesting that _P.
 melanarius_ may move into grasslands later in the year.
 Nearby canola had a positive effect in the early summer, but far-away canola (>800 m) had a negative effect, indicating that areas with widespread canola coverage had lower _P.
-melanarius_ activity density than those with only local canola cover.
+melanarius_ activity-density than those with only local canola cover.
 Pulses acted as a late-season source, indicating that _P. melanarius_ may migrate out of the crop after (or during) harvest.
 Finally, _P.
-melanarius_ activity density had a strong temporal and spatial component (both p<0.001), indicating that phenology and local geographic factors were strong drivers of ground beetle activity density (Figure \@ref(fig:PteMelSpatiotemporal)).
-The landscape composition and trap location explained `r r2Nakagawa$PteMelMod[1]*100`% of the variance in activity density, while the spatial and temporal smoothers accounted for `r with(r2Nakagawa,(PteMelMod[2]-PteMelMod[1])*100)`% (Table \@ref(tab:rSquared)).
+melanarius_ activity-density had a strong temporal and spatial component (both p<0.001), indicating that phenology and local geographic factors were strong drivers of ground beetle activity-density (Figure \@ref(fig:PteMelSpatiotemporal)).
+The landscape composition and trap location explained `r r2Nakagawa$PteMelMod[1]*100`% of the variance in activity-density, while the spatial and temporal smoothers accounted for `r with(r2Nakagawa,(PteMelMod[2]-PteMelMod[1])*100)`% (Table \@ref(tab:rSquared)).
 
-```{r PteMelLandscape, echo=FALSE, fig.cap='Landscape influence on _Pterostichus melanarius_ activity density.
+```{r PteMelLandscape, echo=FALSE, fig.cap='Landscape influence on _Pterostichus melanarius_ activity-density.
 Lines and dots represent means, and bars and shaded regions represent 95% confidence intervals (1.96 x SE).
@@
 moesta_ was influenced by trap location and landscape composition (Tables \@ref(tab:ParDisLinear), \@ref(tab:ParDisSmooth)), but landscape composition had relatively weak effects on both species ($R^2$: `r filter(r2Nakagawa2,grepl('Par',model),!grepl('s\\(',terms),terms!='trapLoc',terms!='sigmaD') %>% group_by(model) %>% summarize(s=sum(r2comp)) %>% pull(s) %>% paste(.,collapse=', ')`).
-Unlike _P. melanarius_, both _Pardosa_ species had far lower activity density in canola than any other cover type (Figures \@ref(fig:ParDisLandscape)a, \@ref(fig:ParMoeLandscape)a).
+Unlike _P. melanarius_, both _Pardosa_ species had far lower activity-density in canola than any other cover type (Figures \@ref(fig:ParDisLandscape)a, \@ref(fig:ParMoeLandscape)a).
 Nearby canola appeared to act as a source of _P.
 moesta_ and a weak source of _P.
-distincta_, as activity density was positively related to the local proportion of canola early in the season, but negatively related later in the season (Figures \@ref(fig:ParDisLandscape)b, \@ref(fig:ParMoeLandscape)c, p=`r with(pdisSmTerms,p[Smoother=='ti(Distance,Day):Canola'])`, `r with(pmoeSmTerms,p[Smoother=='ti(Distance,Day):Canola'])`).
+distincta_, as activity-density was positively related to the local proportion of canola early in the season, but negatively related later in the season (Figures \@ref(fig:ParDisLandscape)b, \@ref(fig:ParMoeLandscape)c, p=`r with(pdisSmTerms,p[Smoother=='ti(Distance,Day):Canola'])`, `r with(pmoeSmTerms,p[Smoother=='ti(Distance,Day):Canola'])`).
 Urban land cover had a similar effect on _P. moesta_, acting as an early source and a late sink (Figure \@ref(fig:ParMoeLandscape)f).
@@
 _P. distincta_ was similarly affected by pulses: landscape-level abundance of pulses had a positive effect, but the local effect was neutral.
-Finally, activity density of both _Pardosa_ species had a very strong temporal and spatial component, although the temporal component was dominant for _P.
+Finally, activity-density of both _Pardosa_ species had a very strong temporal and spatial component, although the temporal component was dominant for _P.
 distincta_, whereas the spatial component was dominant for _P.
 moesta_ (Figures \@ref(fig:ParDisSpatiotemporal) and \@ref(fig:ParMoeSpatiotemporal) ; both p`r with(pmoeSmTerms,p[Smoother=='s(E,N)'])`).
-The landscape composition and trap location explained `r r2Nakagawa$ParDisMod[1]*100`%  and `r r2Nakagawa$ParMoeMod[1]*100`% of variance in activity density, while the spatial and temporal smoothers accounted for `r with(r2Nakagawa,(ParDisMod[2]-ParDisMod[1])*100)`%  and `r with(r2Nakagawa,(ParMoeMod[2]-ParMoeMod[1])*100)`%, for _P.
+The landscape composition and trap location explained `r r2Nakagawa$ParDisMod[1]*100`%  and `r r2Nakagawa$ParMoeMod[1]*100`% of variance in activity-density, while the spatial and temporal smoothers accounted for `r with(r2Nakagawa,(ParDisMod[2]-ParDisMod[1])*100)`%  and `r with(r2Nakagawa,(ParMoeMod[2]-ParMoeMod[1])*100)`%, for _P.
 distincta_ and _P.
@@
 
-```{r ParDisLandscape, echo=FALSE, fig.cap='Landscape influence on _Pardosa distincta_ activity density.
+```{r ParDisLandscape, echo=FALSE, fig.cap='Landscape influence on _Pardosa distincta_ activity-density.
 Lines and dots represent means, and bars and shaded regions represent 95% confidence intervals (1.96 x SE).
@@
 
-```{r ParMoeLandscape, echo=FALSE, fig.cap='Landscape influence on _Pardosa moesta_ activity density.
+```{r ParMoeLandscape, echo=FALSE, fig.cap='Landscape influence on _Pardosa moesta_ activity-density.
 Lines and dots represent means, and bars and shaded regions represent 95% confidence intervals (1.96 x SE).
@@
 
-_Phalangium opilio_ activity density was strongly influenced by trap location, with pivot corners and wetlands having the highest activity density (Figure \@ref(fig:OpilioLandscape)a).
+_Phalangium opilio_ activity-density was strongly influenced by trap location, with pivot corners and wetlands having the highest activity-density (Figure \@ref(fig:OpilioLandscape)a).
 Landscape composition explained `r filter(r2Nakagawa2,grepl('Opilio',model),!grepl('s\\(',terms),terms!='trapLoc',terms!='sigmaD') %>% summarize(s=sum(r2comp)) %>% pull(s) %>% paste(.,collapse=', ')`% of variance in _P.
-opilio_ activity density.
+opilio_ activity-density.
 Nearby grassland (p=`r with(opilSmTerms,p[Smoother=='ti(Distance,Day):GrassWetland'])`) and woodland (p=`r with(opilSmTerms,p[Smoother=='s(Distance):TreeShrub'])`) both had negative effects on _P.
-opilio_ activity density, but only early in the season (Figures \@ref(fig:OpilioLandscape)b,c).
+opilio_ activity-density, but only early in the season (Figures \@ref(fig:OpilioLandscape)b,c).
 Compare this to _P. melanarius_, which is also influenced by grassland and woodland, but where the effect was negative _late_ in the season.
 The temporal and spatial components, as in the other two species, were both very strong (both p`r with(opilSmTerms,p[grepl('E,N',Smoother)])`).
-The landscape composition and trap location explained `r r2Nakagawa$OpilioMod[1]*100`%  of variance in activity density, while the spatial and temporal smoothers accounted for `r with(r2Nakagawa,(OpilioMod[2]-OpilioMod[1])*100)`%.
+The landscape composition and trap location explained `r r2Nakagawa$OpilioMod[1]*100`%  of variance in activity-density, while the spatial and temporal smoothers accounted for `r with(r2Nakagawa,(OpilioMod[2]-OpilioMod[1])*100)`%.
 
-```{r OpilioLandscape, echo=FALSE, fig.cap='Landscape influence on _Phalangium opilio_ activity density.
+```{r OpilioLandscape, echo=FALSE, fig.cap='Landscape influence on _Phalangium opilio_ activity-density.
 Lines and dots represent means, and bars and shaded regions represent 95% confidence regions.
@@
 
-The activity density of _Pterostichus melanarius_ and _Phalangium opilio_ responded to strongly landscape composition, but the response of _Pardosa distincta_ and _Pardosa moesta_ was weaker.
+The activity-density of _Pterostichus melanarius_ and _Phalangium opilio_ responded to strongly landscape composition, but the response of _Pardosa distincta_ and _Pardosa moesta_ was weaker.
 We found some support for our predictions of SNL (grass and wetland, woodlands, and road margins) acting as a late-season sinks for beneficial arthropods.
@@
 distincta_ were more active in grassy habitats, which we found partial evidence of, as _P.
-distincta_ tended to have higher activity density in trap locations with higher grass cover (Figure \@ref(fig:ParDisLandscape)a).
+distincta_ tended to have higher activity-density in trap locations with higher grass cover (Figure \@ref(fig:ParDisLandscape)a).
 For _P. moesta_, we found that roads clearly acted as an early source and a late sink [similar to @drapela2008 and @drapela2011]. 
@@
 
-_Phalangium opilio_ activity density responded to grass and wetland cover, as well as trees and shrubs, but the trap location and landscape explained only `r r2Nakagawa$OpilioMod[1]*100`% of the variance.
+_Phalangium opilio_ activity-density responded to grass and wetland cover, as well as trees and shrubs, but the trap location and landscape explained only `r r2Nakagawa$OpilioMod[1]*100`% of the variance.
 Other studies have found that _P. opilio_ is mostly found in human-altered landscapes with a large proportion of farming [@muster2014; @vandepoel2015Msc].
 Since most of our study area was in or near farmed land, the lack of variation is understandable, but there were a few notable landscape-level patterns that emerged.
-_P. opilio_ activity density was higher in grassy pivot corners and wetlands, but grasslands and wetlands acted as a local sink of _P. opilio_ until late in the season.
+_P. opilio_ activity-density was higher in grassy pivot corners and wetlands, but grasslands and wetlands acted as a local sink of _P. opilio_ until late in the season.
 These indicate that while grass and wetlands could act as a reservoir, spillover into other land cover types may be limited, as _P.
@@
 We found the opposite pattern: forests act as a weak sink for _P. opilio_, at least early in the year.
-Unlike the other arthropods, most of the variation in activity density for _P.
+Unlike the other arthropods, most of the variation in activity-density for _P.
 opilio_ was explained by day of year (R$^2$ = `r round(filter(r2Nakagawa2,model=='OpilioMod',grepl('day',terms))$r2comp,2)`), indicating strong seasonal emergence cues.
@@
 
-```{r PteMelSpatiotemporal, echo=FALSE, fig.cap='Temporal and spatial components of _Pterostichus melanarius_ activity density'}
+```{r PteMelSpatiotemporal, echo=FALSE, fig.cap='Temporal and spatial components of _Pterostichus melanarius_ activity-density'}
   include_graphics('../figures/Pterostichus_melanarius_raneff.png',dpi=NA)
@@
 
-```{r ParDisSpatiotemporal, echo=FALSE, fig.cap='Temporal and spatial components of _Pardosa distincta_ activity density'}
+```{r ParDisSpatiotemporal, echo=FALSE, fig.cap='Temporal and spatial components of _Pardosa distincta_ activity-density'}
   include_graphics('../figures/Pardosa_distincta_raneff.png',dpi=NA)
@@
 
-```{r ParMoeSpatiotemporal, echo=FALSE, fig.cap='Temporal and spatial components of \\emph{Pardosa moesta} activity density'}
+```{r ParMoeSpatiotemporal, echo=FALSE, fig.cap='Temporal and spatial components of \\emph{Pardosa moesta} activity-density'}
   include_graphics('../figures/Pardosa_moesta_raneff.png',dpi=NA)
@@
 
-```{r OpilioSpatiotemporal, echo=FALSE, fig.cap='Temporal and spatial components of _Phalangium opilio_ activity density'}
+```{r OpilioSpatiotemporal, echo=FALSE, fig.cap='Temporal and spatial components of _Phalangium opilio_ activity-density'}
   include_graphics('../figures/Opiliones_raneff.png',dpi=NA)

### 2020-10-01 manuscript/manuscript_outline.Rmd
Cleaned up figures

@@
 Inset map shows study location within Alberta.
-Roadside traps were installed in road margins, while in-field traps were installed directly in canola fields or in adjacent wetland or grassy field corners.'}
+Roadside traps were installed in road margins, while in-field traps were installed directly in canola fields or in adjacent wetland or grassy field corners.', out.width='100%'}
   include_graphics('../figures/maps/PF2017Map.png',dpi=NA)
@@
 Sites are represented by individual lines.
-Mean cover for each class is listed in each sub-figure heading.', fig.width=7, fig.height=7}
+Mean cover for each class is listed in each sub-figure heading.', out.width='100%'}
 coverList %>% group_by(cover) %>% mutate(p=sum(prop)) %>% ungroup() %>% mutate(p=100*round(p/sum(unique(p)),4)) %>% 
@@
 
-```{r PteMelLandscape, echo=FALSE, fig.cap='Landscape influence on _Pterostichus melanarius_ activity-density.
-Lines and dots represent means, and bars and shaded regions represent 95% confidence intervals (1.96 x SE).
-Coloured regions represent early-, mid-, and late-season effects (red, green, blue)'}
+<!-- Percent signs are escaped in LaTeX, but this causes havoc if used in fig.cap of chunk options (OK if used in internal captions, I think). Yihui uses "text references" instead. -->
+(ref:PteMelCap) Landscape influence on _Pterostichus melanarius_ activity-density.
+Lines and dots represent means, and bars and shaded regions represent 95 % confidence intervals (1.96 x SE).
+Coloured regions represent early-, mid-, and late-season effects (red, green, blue).
+
+```{r PteMelLandscape, echo=FALSE, fig.cap='(ref:PteMelCap)', out.width='100%'}  
   include_graphics('../figures/Pterostichus_melanarius_fixeff.png',dpi=NA)
@@
 
-```{r ParDisLandscape, echo=FALSE, fig.cap='Landscape influence on _Pardosa distincta_ activity-density.
-Lines and dots represent means, and bars and shaded regions represent 95% confidence intervals (1.96 x SE).
-Coloured regions represent early-, mid-, and late-season effects (red, green, blue)'}
+(ref:ParDisCap) Landscape influence on _Pardosa distincta_ activity-density.
+Lines and dots represent means, and bars and shaded regions represent 95 % confidence intervals (1.96 x SE).
+Coloured regions represent early-, mid-, and late-season effects (red, green, blue).
+
+```{r ParDisLandscape, echo=FALSE, fig.cap='(ref:ParDisCap)', out.width='100%'}  
   include_graphics('../figures/Pardosa_distincta_fixeff.png',dpi=NA)
@@
 
-```{r ParMoeLandscape, echo=FALSE, fig.cap='Landscape influence on _Pardosa moesta_ activity-density.
-Lines and dots represent means, and bars and shaded regions represent 95% confidence intervals (1.96 x SE).
-Coloured regions represent early-, mid-, and late-season effects (red, green, blue)'}
+(ref:ParMoeCap) Landscape influence on _Pardosa moesta_ activity-density.
+Lines and dots represent means, and bars and shaded regions represent 95 % confidence intervals (1.96 x SE).
+Coloured regions represent early-, mid-, and late-season effects (red, green, blue).
+
+```{r ParMoeLandscape, echo=FALSE, fig.cap='(ref:ParMoeCap)', out.width='100%'}  
   include_graphics('../figures/Pardosa_moesta_fixeff.png',dpi=NA)
@@
 
-```{r OpilioLandscape, echo=FALSE, fig.cap='Landscape influence on _Phalangium opilio_ activity-density.
-Lines and dots represent means, and bars and shaded regions represent 95% confidence regions.
-Dashed line on panels b-f represents zero effect.
-Coloured regions represent early-, mid-, and late-season effects (red, green, blue)'}
+(ref:OpilioCap) Landscape influence on _Phalangium opilio_ activity-density.
+Lines and dots represent means, and bars and shaded regions represent 95 % confidence intervals (1.96 x SE).
+Coloured regions represent early-, mid-, and late-season effects (red, green, blue).
+
+```{r OpilioLandscape, echo=FALSE, fig.cap='(ref:OpilioCap)', out.width='100%'}  
   include_graphics('../figures/Opiliones_fixeff.png',dpi=NA)
@@
 
-```{r rSquared, echo=FALSE}  
+```{r rSquared, echo=FALSE, out.width='100%'}  
   r2Nakagawa2 %>% select(model,terms,r2comp) %>% mutate(terms=as.character(terms),r2comp=r2comp*1) %>% 
@@
         col.names=c('Term','$\\emph{Pterostichus melanarius}$','$\\emph{Pardosa distincta}$','$\\emph{Pardosa moesta}$','$\\emph{Phalangium opilio}$'),
-        digits=c(1,3,3,3,3),align='rllll',escape=FALSE) 
+        digits=c(1,3,3,3,3),align='rllll',escape=FALSE, table.attr = "style='width:30%;'") 
 ```
@@
 
-```{r concurvity, echo=FALSE, fig.cap='Concurvity estimates for reduced cover classes used in models'}  
+```{r concurvity, echo=FALSE, fig.cap='Concurvity estimates for reduced cover classes used in models', out.width='100%'}  
   include_graphics('../figures/coverCorPlots/concurvityEstimate_reduced.png',dpi=NA)
@@
 
-```{r PteMelSpatiotemporal, echo=FALSE, fig.cap='Temporal and spatial components of _Pterostichus melanarius_ activity-density'}
+(ref:PteMelSTCap) Temporal and spatial components of _Pterostichus melanarius_ activity-density (after accounting for landscape composition and trap location).
+
+```{r PteMelSpatiotemporal, echo=FALSE, fig.cap='(ref:PteMelSTCap)', out.width='100%'}
   include_graphics('../figures/Pterostichus_melanarius_raneff.png',dpi=NA)
@@
 
-```{r ParDisSpatiotemporal, echo=FALSE, fig.cap='Temporal and spatial components of _Pardosa distincta_ activity-density'}
+(ref:ParDisSTCap) Temporal and spatial components of _Pardosa distincta_ activity-density (after accounting for landscape composition and trap location).
+
+```{r ParDisSpatiotemporal, echo=FALSE, fig.cap='(ref:ParDisSTCap)', out.width='100%'}
   include_graphics('../figures/Pardosa_distincta_raneff.png',dpi=NA)
@@
 
-```{r ParMoeSpatiotemporal, echo=FALSE, fig.cap='Temporal and spatial components of \\emph{Pardosa moesta} activity-density'}
+(ref:ParMoeSTCap) Temporal and spatial components of _Pardosa moesta_ activity-density (after accounting for landscape composition and trap location).
+
+```{r ParMoeSpatiotemporal, echo=FALSE, fig.cap='', out.width='100%'}
   include_graphics('../figures/Pardosa_moesta_raneff.png',dpi=NA)
@@
 
-```{r OpilioSpatiotemporal, echo=FALSE, fig.cap='Temporal and spatial components of _Phalangium opilio_ activity-density'}
+(ref:OpilioSTCap) Temporal and spatial components of _Phalangium opilio_ activity-density (after accounting for landscape composition and trap location).
+
+```{r OpilioSpatiotemporal, echo=FALSE, fig.cap='(ref:OpilioSTCap)', out.width='100%'}
   include_graphics('../figures/Opiliones_raneff.png',dpi=NA)

### 2020-10-02 manuscript/manuscript_outline.Rmd
Fixed table

@@
 library(knitr)
-# library(kableExtra)
+library(kableExtra)
 library(tidyverse)
@@
 ```{r rSquared, echo=FALSE, out.width='100%'}
+
 r2Nakagawa2 %>% select(model,terms,r2comp) %>% mutate(terms=as.character(terms),r2comp=r2comp*1) %>%
@@
                          terms=='Urban' ~ 'Road margins', TRUE ~ terms)) %>%
-  kable(.,caption='R$^2_{GLMM}$ for model components, representing the proportion of total variance attributable to each term.',
-        col.names=c('Term','$\\emph{Pterostichus melanarius}$','$\\emph{Pardosa distincta}$','$\\emph{Pardosa moesta}$','$\\emph{Phalangium opilio}$'),
-        digits=c(1,3,3,3,3),align='rllll',escape=FALSE, table.attr = "style='width:30%;'") 
+  kable(.,format='latex',caption='R$^2_{GLMM}$ for model components, representing the proportion of total variance attributable to each term.',
+        col.names=linebreak(x=c('Term','\\emph{Pterostichus}\n\\emph{melanarius}','\\emph{Pardosa}\n\\emph{distincta}',
+                              '\\emph{Pardosa}\n\\emph{moesta}','\\emph{Phalangium}\n\\emph{opilio}'),align='l'),
+        digits=c(1,3,3,3,3),align='rllll',escape=FALSE)
+# test_data <- data.frame(Mean = runif(5, 3.71, 7.72),
+#                         N = sample(57:59, 5, replace = TRUE),
+#                         sd = c(1, rep(0, 4)),
+#                         d = rep(1, 5),
+#                         naod = sample(1:4, 5, replace = TRUE),
+#                         a = sample(5:12, 5, replace = TRUE),
+#                         sa = sample(37:44, 5, replace = TRUE))
+# 
+# kable(test_data,"latex" ,booktabs=T, align="c",
+#       col.names=linebreak(c('Mean','\\textit{N}' ,'Strongly\n Disagree','Disagree','Neither Agree\n or Disagree','Agree','Strongly\n Agree')),
+#       row.names = T,escape=F) %>%
+#   row_spec(0,align = "c")
+
 ```
@@
 
-```{r ParMoeSpatiotemporal, echo=FALSE, fig.cap='', out.width='100%'}
+```{r ParMoeSpatiotemporal, echo=FALSE, fig.cap='(ref:ParMoeSTCap)', out.width='100%'}
   include_graphics('../figures/Pardosa_moesta_raneff.png',dpi=NA)

### 2020-10-02 manuscript/manuscript_outline.Rmd
Made plots for box in manuscript

@@
 The sites spanned a west-to-east gradient of four natural subregions, including foothills parkland, foothills fescue, mixedgrass, and dry mixedgrass [@ABRegions2006].
-In-field traps were placed in canola crops (`r with(NtrapsPer, sum(n[trapLoc=='canola']))`), wetlands (`r with(NtrapsPer, sum(n[trapLoc=='wetland']))`), grassy field margins (`r with(NtrapsPer, sum(n[trapLoc=='pivot']))`), and remnant prairie grasslands (`r with(NtrapsPer, sum(n[trapLoc=='native']))`).
-Traps in canola were installed at 25, 75, and 200 m along a transect heading away from the nearest non-crop feature, while the trap at 0 m was installed in the non-crop feature itself.
+In-field traps were placed in canola crops (`r with(NtrapsPer, sum(n[trapLoc=='canola']))`), wetlands (`r with(NtrapsPer, sum(n[trapLoc=='wetland']))`), grassy field edges (`r with(NtrapsPer, sum(n[trapLoc=='pivot']))`), and remnant prairie grasslands (`r with(NtrapsPer, sum(n[trapLoc=='native']))`).
+Traps in canola were installed at 25, 75, and 200 m along a transect heading away from the nearest non-crop feature (wetland, grassy field edges, or remnant prairie), while the trap at 0 m was installed in the non-crop feature itself.
 We used 582 mL Solo® cups buried up to the rim and partially filled with ethylene glycol, with 2 cm wire mesh mounted over the rim to prevent vertebrates from falling into the traps.
@@
 Inset map shows study location within Alberta.
-Roadside traps were installed in road margins, while in-field traps were installed directly in canola fields or in adjacent wetland or grassy field corners.', out.width='100%'}
+Roadside traps were installed in road margins, while in-field traps were installed directly in canola fields or in adjacent wetland or grassy field edges.', out.width='100%'}
   include_graphics('../figures/maps/PF2017Map.png',dpi=NA)
@@
 _Pterostichus melanarius_ is an introduced predatory ground beetle (Coleoptera: Carabidae) that is a wide-ranging generalist [@carcamo1994; @larsen2003; @busch_Msc].
-It is commonly found in untilled grasslands [@purtauf2005] and may use grassy field margins as larval habitat [@desender1988].
+It is commonly found in untilled grasslands [@purtauf2005] and may use grassy field edges as larval habitat [@desender1988].
 _Pardosa_ are wolf spiders (Araneae: Lycosidae) that use an active wandering predation strategy [@young1990], and are common across the Canadian prairies.
@@
 To account for different lengths of trap exposure, log-days since trap placement were used as a fixed effect with their slope held at 1 ("offset" variable).
-We included day of year as a 1-dimensional smooth, and easting and northing (km east and north of the trap extent centre point) as a 2-dimensional smooth, in order to account for underlying spatial and temporal autocorrelation in the data.
+Trapping location was included as a fixed effect with 5 levels (canola, field edge, grassland, road margin, and wetlands) to account for the effect of local cover independent of the surrounding landscape composition.
+Day of year was included as a 1-dimensional smooth, and easting and northing (km east and north of the trap extent centre point) were included as 2-dimensional smooths, in order to account for underlying spatial and temporal autocorrelation in the data.
 The deviance residuals from each model were visually inspected for normality and equal variance [@hilbe2011; @wood2017].
@@
 This resulted in a reduced set of landscape terms, none of which were strongly concurved with each other (grassland, canola, pasture, woodland, pulses, urban; see Figure \@ref(fig:concurvity))
+
+***
+**Box 1: Interpretation of Functional Regression Plots**
+
+This box explains how to interpret functional regression plots.
+
+***
 
@@
 Grassland cover was largely constant with distance, although a cluster of sites had uniformly high or low cover of grassland with distance.
-The pitfall traps caught a total of `r with(Ncatches,total[spp=='PteMel'])` _Pterostichus melanarius_, `r with(Ncatches,total[spp=='ParDis'])` _Pardosa distincta_, `r with(Ncatches,total[spp=='ParMoe'])` _Pardosa moesta_, and `r with(Ncatches,total[spp=='Opilio'])` _Phalangium opilio_ (mean trapping rates per day: `r with(Ncatches,paste(round(perDayMean,2),collapse=', '))`, SDs: `r with(Ncatches,paste(round(perDaySD,2),collapse=', '))`).
+The pitfall traps caught a total of `r with(Ncatches,total[spp=='PteMel'])` _Pterostichus melanarius_, `r with(Ncatches,total[spp=='ParDis'])` _Pardosa distincta_, `r with(Ncatches,total[spp=='ParMoe'])` _Pardosa moesta_, and `r with(Ncatches,total[spp=='Opilio'])` _Phalangium opilio_ (mean trapping rates per day: `r with(Ncatches,paste(round(perDayMean,2),collapse=', '))`, SD: `r with(Ncatches,paste(round(perDaySD,2),collapse=', '))`, respectively).
 
@@
 Lines and dots represent means, and bars and shaded regions represent 95 % confidence intervals (1.96 x SE).
-Coloured regions represent early-, mid-, and late-season effects (red, green, blue).
+Coloured regions represent early-, mid-, and late-season effects (red, purple, blue).
 
@@
 
-_Phalangium opilio_ activity-density was strongly influenced by trap location, with pivot corners and wetlands having the highest activity-density (Figure \@ref(fig:OpilioLandscape)a).
+_Phalangium opilio_ activity-density was strongly influenced by trap location, with grassy field edges and wetlands having the highest activity-density (Figure \@ref(fig:OpilioLandscape)a).
 Landscape composition explained `r filter(r2Nakagawa2,grepl('Opilio',model),!grepl('s\\(',terms),terms!='trapLoc',terms!='sigmaD') %>% summarize(s=sum(r2comp)) %>% pull(s) %>% paste(.,collapse=', ')`% of variance in _P.
@@
   mutate(terms=case_when(terms=='trapLoc' ~ 'Trap Location', terms=='s(day)' ~ 'Day of Year',
-                         terms=='s(E,N)' ~ 'Spatial Location', terms=='GrassWetland' ~ 'Grass/Wetland',
-                         terms=='TreeShrub' ~ 'Trees/Shrubs', terms=='sigmaD' ~ 'Residual',
+                         terms=='s(E,N)' ~ 'Spatial Location', terms=='GrassWetland' ~ 'Grassland',
+                         terms=='TreeShrub' ~ 'Woodland', terms=='sigmaD' ~ 'Residual',
                          terms=='Urban' ~ 'Road margins', TRUE ~ terms)) %>%
@@
         digits=c(1,3,3,3,3),align='rllll',escape=FALSE)
-# test_data <- data.frame(Mean = runif(5, 3.71, 7.72),
-#                         N = sample(57:59, 5, replace = TRUE),
-#                         sd = c(1, rep(0, 4)),
-#                         d = rep(1, 5),
-#                         naod = sample(1:4, 5, replace = TRUE),
-#                         a = sample(5:12, 5, replace = TRUE),
-#                         sa = sample(37:44, 5, replace = TRUE))
-# 
-# kable(test_data,"latex" ,booktabs=T, align="c",
-#       col.names=linebreak(c('Mean','\\textit{N}' ,'Strongly\n Disagree','Disagree','Neither Agree\n or Disagree','Agree','Strongly\n Agree')),
-#       row.names = T,escape=F) %>%
-#   row_spec(0,align = "c")
 
@@
 Since most of our study area was in or near farmed land, the lack of variation is understandable, but there were a few notable landscape-level patterns that emerged.
-_P. opilio_ activity-density was higher in grassy pivot corners and wetlands, but grasslands and wetlands acted as a local sink of _P. opilio_ until late in the season.
+_P. opilio_ activity-density was higher in grassy field edges and wetlands, but grasslands and wetlands acted as a local sink of _P. opilio_ until late in the season.
 These indicate that while grass and wetlands could act as a reservoir, spillover into other land cover types may be limited, as _P.

### 2020-10-02 frAnalysis.R

@@ -1,4 +1,4 @@
-#FUNCTIONAL REGRESSION ANALYSIS OF IN-FIELD INSECT ABUNDANCE USING ONION-RING LANDSCAPE DATA
+# FUNCTIONAL REGRESSION ANALYSIS OF IN-FIELD INSECT ABUNDANCE USING ONION-RING LANDSCAPE DATA
 # SR WINTER 2020
 
 library(tidyverse)

### 2020-10-02 frPlotDemo.R

@@ -1,0 +1,82 @@
+# EXAMPLES OF FUNCTIONAL REGRESSION PLOTS
+# USED FOR BOX 1 IN PAPER, EXPLAINING HOW TO INTERPRET FUNCTIONAL REGRESSION PLOTS
+# SR FALL 2020
+
+# Load everything ---------------------------------------------------------
+library(tidyverse)
+library(ggpubr)
+theme_set(theme_classic()) #Classic theme
+
+#Functions to simulate
+
+#Line
+lineFun <- function(int,slope,xRange=c(-1,1),n=100){
+  x <- seq(min(xRange),max(xRange),length.out=n)
+  y <- int + slope*x
+  return(y)
+}
+plot(lineFun(-1,0.001,xRange=c(0,1000))) #Works
+
+#Exponential
+expFun <- function(a,b,d,xRange=c(0,1),n=100){
+  x <- seq(min(xRange),max(xRange),length.out=n)
+  y <- a*(1-exp(-b/x))+d
+  return(y)
+}
+plot(expFun(1,0.05,-0.1)); abline(h=0)
+
+#Positively sloped line
+p1 <- apply(mapply(lineFun,int=rnorm(1000,0,0.1),slope=rnorm(1000,0.5,0.1),MoreArgs=list(n=1000)),
+      1,function(x) quantile(x,c(0.05,0.5,0.95))) %>% t(.) %>% 
+  data.frame(x=seq(0,1,length.out=length(.[,1])),.) %>% 
+  rename(lwr=`X5.`,med=`X50.`,upr=`X95.`) %>% 
+  ggplot(aes(x,med))+geom_ribbon(aes(ymax=upr,ymin=lwr),alpha=0.3)+
+  geom_line()+
+  labs(y='Response (y)',x='Proportion cover')+#ylim(-1.5,1.5)+
+  annotate('segment',x=0.75,xend=0.75,y=-0.5+0.75,yend=-0.5+1)+
+  annotate('segment',x=0.75,xend=1,y=-0.5+1,yend=-0.5+1)+
+  annotate('segment',x=0.5,xend=0.7,y=-0.3+1,yend=-0.45+1,arrow=arrow())+
+  annotate('text',x=0.4,y=0.7,label='beta == 0.5',parse=TRUE)
+  
+#Actual function: y = -0.5 + 1 * x
+#Inverse: x + 0.5 = y
+
+#Flat line
[…]

### 2020-10-08 manuscript/manuscript_outline.Rmd
Worked on revisions

@@
 Both _Pardosa distincta_ and _Pardosa moesta_ are found in a wide variety of habitats, but are common in ungrazed pastures [@dondale1990; @carcamo2014].
-_P. distincta_ is commonly found in disturbed environments [@collins1996; @wade2010], while _P. moesta_ appear to prefer less frequent disturbances [@graham2003; @kowal2011; but see @dondale1990].
+_P.
+distincta_ is also commonly found in disturbed environments [@collins1996; @wade2010], while _P.
+moesta_ appear to prefer less frequent disturbances [@graham2003; @kowal2011; but see @dondale1990].
 Other _Pardosa_ are known to use road margins and wooded areas as habitat [@buddle2000; @drapela2011].
@@
 
-Functional regression [@ramsay2004; @yen2014] was to incorporate landscape information at different distances, allowing assessment of both local and regional landscape composition [@galpern2020].
+Functional regression [@ramsay2004; @yen2014] was used to incorporate landscape information at different distances, allowing assessment of both local and regional landscape composition [@galpern2020].
 Scalar-on-function regression is a special type of linear regression model ($y=X\beta + e$), where the columns of the model matrix $X$ contain some continuous predictor of the scalar $y$, and the values of the coefficients ($\beta$) are modeled as a smooth function $f(x)$ of the predictors.
@@
 $X\beta$).
-This allows the possibility that the size of the landscape "grain" relevant to a given organism may change over the course of its life stages [@addicott1987; @lima1996; @gardiner2010].
+This allows for the possibility that the size of the landscape "grain" relevant to a given organism may change over the course of its life stages [@addicott1987; @lima1996; @gardiner2010].
 It also allows for the possibility that certain land cover types may be locally beneficial, but detremental at wider scales, indicating that the cover type may not constitute a completely usable habitat.
@@
 ***
-**Box 1: Interpretation of Functional Regression Plots**
+**Box 1: Interpreting Functional Regression Plots**
 
-This box explains how to interpret functional regression plots.
+Functional linear regression is a special case of linear regression, where both the independent variable is predicted by a functional dependent variable, meaning that the slope is a function (vector) rather a fixed (scalar) value [@ramsay2004; @yen2014].
+Therefore, the interpretation of a functional regression plot is very different from that of a simple linear regression plot.
+Figure \@ref(fig:frExample)a shows a simple linear regression plot of a hypothetical relationship between trap _activity density_ (_y_) and a single predictor, _Proportion cover_ (_x_), which is measured in a circle of a fixed radius (_Distance_) surrounding each trap.
+If we suppose that the relationship between _x_ and _y_ is similar at all radii at which _x_ is measured, then Figure \@ref(fig:frExample)b shows the resulting functional linear regression plot, where the slope ($\beta$) is the same at all distances.
+In reality it is more likely that nearby cover will be more influential on activity density than far-away cover, which would result in a relationship similar to Figure \@ref(fig:frExample)c.
+As functional regression takes any continuous predictor of _y_, it is also possible to use proportion cover (measured within a fixed radius) as a predictor of measurements taken across time, allowing the effect of proportion cover to vary over the course of the season (Figure \@ref(fig:frExample)d).
+Finally, proportion cover over distance and time may be combined into a smoothed surface of effects, representing the spatio-temporal influence of landscape cover on activity density.
+
+```{r frExample, echo=FALSE, fig.cap='Examples of (functional) linear regression plots.
+\\textbf{a)} shows a simple linear regression plot, with a single slope value for a single regressor.
+\\textbf{b)} shows the equivalent plot in functional regression form, where the the slope is a smoothed function that maps onto a function-valued regressor.
+\\textbf{c)} and \\textbf{d)} show functional linear regression plots where the slope varies with the location of the regressor.', out.width='100%'}
+  include_graphics('../figures/frExample.png',dpi=NA)
+```
 
@@
 Positive responses to nearby landscape cover classes indicate that the cover class acts as a net source (i.e. arthropods spill over *from* it).
-__Paul, do we need a separate box/figure explaining how to interpret these plots, or should we just include references?__
 However, negative responses to nearby landscape cover classes can indicate one of two things:
@@
 
+```
+
+```{r resultsTab, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
+mytable = data.frame(
+    CoverClass = c("Grassland", "Canola", "Pasture", "Woodland", "Pulses", "Road margins"),
+    PteMel = c('* Local sink (late)','* Local source (early) \n* Landscape sink (early)',' ',' ','* Source (late)',' '),
+    ParDis = c(' ',' ','* Landscape sink',' * Sink (late)',' ',' '),
+    ParMoe = c('* Local sink \n* Landscape source','* Local source (early) \n* Local sink (late)',' ',' ','* Landscape source','* Local source (early) \n*Local sink (late) \n* Landscape sink (early) \n* Landscape source (late)'),
+    Opilio = c('* Local sink (early)',' ',' ','* Local sink (early) \n* Landscape source (mid)',' ',' ')
+    )
+
+names(mytable) <- c('Cover class','_Pterosticus\nmelanarius_','_Pardosa distincta_','_Pardosa moesta_','Phalangium opilio')
+
+pander::pander(mytable, keep.line.breaks = TRUE, style = 'grid', justify = 'left')
 ```

### 2020-10-08 frPlotDemo.R

@@ -25,18 +25,22 @@ expFun <- function(a,b,d,xRange=c(0,1),n=100){
 }
 plot(expFun(1,0.05,-0.1)); abline(h=0)
 
+#Set seed
+set.seed(1)
+
 #Positively sloped line
-p1 <- apply(mapply(lineFun,int=rnorm(1000,0,0.1),slope=rnorm(1000,0.5,0.1),MoreArgs=list(n=1000)),
+p1 <- apply(mapply(lineFun,int=rnorm(1000,1,0.1),slope=rnorm(1000,0.5,0.1),MoreArgs=list(n=1000)),
       1,function(x) quantile(x,c(0.05,0.5,0.95))) %>% t(.) %>% 
   data.frame(x=seq(0,1,length.out=length(.[,1])),.) %>% 
   rename(lwr=`X5.`,med=`X50.`,upr=`X95.`) %>% 
   ggplot(aes(x,med))+geom_ribbon(aes(ymax=upr,ymin=lwr),alpha=0.3)+
   geom_line()+
-  labs(y='Response (y)',x='Proportion cover')+#ylim(-1.5,1.5)+
-  annotate('segment',x=0.75,xend=0.75,y=-0.5+0.75,yend=-0.5+1)+
-  annotate('segment',x=0.75,xend=1,y=-0.5+1,yend=-0.5+1)+
-  annotate('segment',x=0.5,xend=0.7,y=-0.3+1,yend=-0.45+1,arrow=arrow())+
-  annotate('text',x=0.4,y=0.7,label='beta == 0.5',parse=TRUE)
+  labs(y='Activity Density (y)',x='Proportion cover')+#ylim(-1.5,1.5)+
+  annotate('segment',x=0.75,xend=0.75,y=0.5+0.75,yend=0.5+1,linetype='dashed')+
+  annotate('segment',x=0.75,xend=1,y=0.5+1,yend=0.5+1,linetype='dashed')+
+  annotate('segment',x=0.5,xend=0.7,y=0.7+1,yend=0.55+1,arrow=arrow())+
+  annotate('text',x=0.4,y=1.7,label='beta == 0.5',parse=TRUE)+
+  annotate('text',x=0.25,y=1.2,label='hat(y) == alpha + beta %*% Proportion~Cover',parse=TRUE)
   
 #Actual function: y = -0.5 + 1 * x
 #Inverse: x + 0.5 = y
[…]

### 2020-10-09 manuscript/manuscript_outline.Rmd
Updated results table

@@
 
-```{r resultsTab, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
-mytable = data.frame(
+```{r resultsTab, echo=FALSE, message=FALSE, warning=FALSE, out.width='100%'}
+#Based on example from:
+# https://stackoverflow.com/questions/31011265/how-to-write-bullet-lists-in-a-table-using-rmarkdown-and-pandoc
+# #Note: this works, but it's very ugly. Trying kable instead
+# mytable <- data.frame(
+#     CoverClass = c("Grassland", "Canola", "Pasture", "Woodland", "Pulses", "Road margins"),
+#     PteMel = c('* Local sink ','* Local source (early) \n* Landscape sink (early)',' ',' ','* Source (late)',' '),
+#     ParDis = c(' ',' ','* Landscape sink',' * Sink (late)',' ',' '),
+#     ParMoe = c('* Local sink \n* Landscape source','* Local source (early) \n* Local sink (late)',' ',' ','* Landscape source','* Local source (early) \n* Local sink (late) \n* Landscape sink (early) \n* Landscape source (late)'),
+#     Opilio = c('* Local sink (early)',' ',' ','* Local sink (early) \n* Landscape source (mid)',' ',' ')
+#     )
+# colnames(mytable) <- c('Cover class','_Pterosticus_ _melanarius_','_Pardosa_ _distincta_','_Pardosa_ _moesta_','_Phalangium_ _opilio_')
+# pander(mytable, keep.line.breaks = TRUE, style = 'grid', justify = 'left', split.table=1000)
+
+#Based on example from:
+# https://stackoverflow.com/questions/52962411/table-with-long-text-bullet-points-and-specific-table-width
+mytable <- data.frame(
     CoverClass = c("Grassland", "Canola", "Pasture", "Woodland", "Pulses", "Road margins"),
-    PteMel = c('* Local sink (late)','* Local source (early) \n* Landscape sink (early)',' ',' ','* Source (late)',' '),
-    ParDis = c(' ',' ','* Landscape sink',' * Sink (late)',' ',' '),
-    ParMoe = c('* Local sink \n* Landscape source','* Local source (early) \n* Local sink (late)',' ',' ','* Landscape source','* Local source (early) \n*Local sink (late) \n* Landscape sink (early) \n* Landscape source (late)'),
-    Opilio = c('* Local sink (early)',' ',' ','* Local sink (early) \n* Landscape source (mid)',' ',' ')
+    PteMel = c('$\\cdot$ Local -- (late)','$\\cdot$ Local + (early) \n$\\cdot$ Landscape -- (early)',' ',' ','$\\cdot$ Overall + (late)',' '),
+    ParDis = c(' ',' ','$\\cdot$ Landscape --',' $\\cdot$ Overall -- (late)',' ',' '),
+    ParMoe = c('$\\cdot$ Local -- \n$\\cdot$ Landscape +','$\\cdot$ Local + (early) \n$\\cdot$ Local -- (late)',' ',' ','$\\cdot$ Landscape +','$\\cdot$ Local + (early) \n$\\cdot$ Local -- (late) \n$\\cdot$ Landscape -- (early) \n$\\cdot$ Landscape + (late)'),
+    Opilio = c('$\\cdot$ Local -- (early)',' ',' ','$\\cdot$ Local -- (early) \n$\\cdot$ Landscape + (mid)',' ',' ')
     )
 
-names(mytable) <- c('Cover class','_Pterosticus\nmelanarius_','_Pardosa distincta_','_Pardosa moesta_','Phalangium opilio')
-
-pander::pander(mytable, keep.line.breaks = TRUE, style = 'grid', justify = 'left')
+mytable %>%
+  mutate_all(linebreak) %>%  # required for linebreaks to work
+  kable(.,format='latex',caption='Summary of model results. Cover classes with weak effects on activity density are not shown.',
+        col.names=linebreak(x=c('Cover class','\\emph{Pterostichus}\n\\emph{melanarius}','\\emph{Pardosa}\n\\emph{distincta}',
+                              '\\emph{Pardosa}\n\\emph{moesta}','\\emph{Phalangium}\n\\emph{opilio}')),
+        align='rllll',escape=FALSE) %>% 
+  column_spec(1, width = "4em") %>% column_spec(c(2:5), width = "8em") # fix column widths
 ```

### 2020-10-09 frAnalysis.R

@@ -326,12 +326,12 @@ p1 <- data.frame(trapLoc=tempTrap$trapLoc,pred=predict(mod3,type='terms',terms='
   ggplot(aes(x=trapLoc,y=pred))+geom_pointrange(aes(ymax=upr,ymin=lwr))+
   labs(x='Trap location',y='Activity')
 
-#Canola (space + time: weak)
-p2 <- expand.grid(endDayMat=c(173,203,232),distMat=seq(30,1500,30),Canola=1) %>% 
-  smoothPred(mod3,whichSmooth=which(grepl('Canola',sapply(mod3$smooth,function(x) x$label)))) %>% 
-  rename(x=distMat,y=endDayMat) %>% 
-  mutate(y=factor(y,labels=dispDays$date)) %>% 
-  effectPlot(leg=T,cols=smoothCols)+labs(x='Distance (m)',y='Canola effect')
+# #Canola (space + time: weak)
+# p2 <- expand.grid(endDayMat=c(173,203,232),distMat=seq(30,1500,30),Canola=1) %>% 
+#   smoothPred(mod3,whichSmooth=which(grepl('Canola',sapply(mod3$smooth,function(x) x$label)))) %>% 
+#   rename(x=distMat,y=endDayMat) %>% 
+#   mutate(y=factor(y,labels=dispDays$date)) %>% 
+#   effectPlot(leg=T,cols=smoothCols)+labs(x='Distance (m)',y='Canola effect')
 
 #Pasture (space)
 p3 <- expand.grid(distMat=seq(30,1500,30),Pasture=1,y=NA) %>% 
@@ -347,8 +347,8 @@ p4 <- data.frame(endDayMat=149:241,TreeShrub=1,y=NA) %>%
   effectPlot(leg=F)+labs(x='Time of year',y='Woodland effect')
 
 #Plot landscape effects
-fixeffPlot <- ggarrange(p1,p2,p3,p4,
-                        labels=letters[1:4],nrow=2,ncol=2,
+fixeffPlot <- ggarrange(p1,p3,p4,
+                        labels=letters[1:3],nrow=2,ncol=2,
                         legend='bottom',common.legend=T,font.label=list(size=landscapeLabel)) 
 ggsave('./figures/Pardosa_distincta_fixeff.png',fixeffPlot,width=landscapeFigX,height=landscapeFigY,scale=1)
 rm(p1,p2,p3,p4,raneffPlot,fixeffPlot) #Cleanup

### 2020-10-09 manuscript/manuscript_outline.Rmd
Worked on Results section

@@
 csl: ecology-letters.csl
+geometry: "left=3cm,right=3cm,top=3cm,bottom=3cm"
 output: 
@@
 header-includes: 
-  \usepackage{tcolorbox} 
   \usepackage{float} \floatplacement{figure}{H} 
   \newcommand{\beginsupplement}{\setcounter{table}{0} \newpage \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
+  \usepackage{setspace}
+  \linenumbers
 ---
@@
 
+\newpage
+\doublespacing
+
 # Introduction
-
 Arthropods are one of the most influential groups of animals in agricultural systems.
@@
 We used a set of `r sum(NtrapsPer$n)` pitfall traps installed in road margins (minimum of 5 m away from the road edge, `r with(NtrapsPer, sum(n[trapLoc=='ditch']))` traps) and in-field locations (`r with(NtrapsPer, sum(n[trapLoc!='ditch']))`) across southern Alberta, Canada in 2017 (Figure \@ref(fig:siteMap)).
+The sites spanned a west-to-east gradient of four natural subregions, including foothills parkland, foothills fescue, mixedgrass, and dry mixedgrass [@ABRegions2006].
 Traps were placed starting on `r format(as.Date(as.character(min(PteMelMod$tempTrap$startjulian)),format='%j'),format='%B %d')`, and collections ended on `r format(as.Date(as.character(max(PteMelMod$tempTrap$endjulian)),format='%j'),format='%B %d')`, with collection occurring continuously and traps being emptied every `r round(mean(PteMelMod$tempTrap$trapdays),1)` days on average (SD: `r round(sd(PteMelMod$tempTrap$trapdays),1)`).
 This resulted in `r nrow(PteMelMod$tempTrap)` unique collection events, taking place across a total of `r round(sum(PteMelMod$tempTrap$trapdays),1)` trapping days.
-The sites spanned a west-to-east gradient of four natural subregions, including foothills parkland, foothills fescue, mixedgrass, and dry mixedgrass [@ABRegions2006].
 In-field traps were placed in canola crops (`r with(NtrapsPer, sum(n[trapLoc=='canola']))`), wetlands (`r with(NtrapsPer, sum(n[trapLoc=='wetland']))`), grassy field edges (`r with(NtrapsPer, sum(n[trapLoc=='pivot']))`), and remnant prairie grasslands (`r with(NtrapsPer, sum(n[trapLoc=='native']))`).
@@
 Day of year was included as a 1-dimensional smooth, and easting and northing (km east and north of the trap extent centre point) were included as 2-dimensional smooths, in order to account for underlying spatial and temporal autocorrelation in the data.
-The deviance residuals from each model were visually inspected for normality and equal variance [@hilbe2011; @wood2017].
 
@@
 To remove unimportant terms from the model, we used thin-plate regression splines with shrinkage, a continuous analog to stepwise model selection where weaker terms are completely removed from the model rather than reduced to a line [@marra2011].
+The deviance residuals from each model were visually inspected for normality and equal variance [@hilbe2011; @wood2017].
 Finally, we calculated the R$^2$ for each group of terms [@nakagawa2013; @nakagawa2017].
+
 <!-- + Double-penalization gave qualitatively similar results, but required twice the number of penalty terms, and some of the penalty terms were unstable  -->
@@
 Cereal was removed from the model, as it was negatively correlated with canola cover at distances less than 200m and was positively correlated at distances over 500m, reflecting the most common crop rotations (canola $\rightarrow$ wheat $\rightarrow$ barley) and the commonly-used 800 m block structure of farmland in our study region (quarter-sections).
-This resulted in a reduced set of landscape terms, none of which were strongly concurved with each other (grassland, canola, pasture, woodland, pulses, urban; see Figure \@ref(fig:concurvity))
+This resulted in a reduced set of landscape terms, none of which were strongly concurved with each other (grassland, canola, pasture, woodland, pulses, urban; see Figure \@ref(fig:concurvity)).
 
@@
 Alternatively, a cover class could act as a sink by providing high-quality habitat at certain times of the year (e.g. egg laying/feeding), but act as a source at other times (e.g. during emergence).
+For brevity in the subsequent Results section, we refer to "local" and "landscape"-level effects; local refers to the effects of landscape composition at scales of <500m, whereas landscape refers to scales >500 m.
+Similarly, we refer to "early", "mid", and "late"-season effects, where landscape composition affected abundance from June - July, July - August, or August - September.
 
@@
 Sites are represented by individual lines.
-Mean cover for each class is listed in each sub-figure heading.', out.width='100%'}
+Mean cover for each class is listed in each sub-figure heading.', fig.width=5, fig.height=5}
 coverList %>% group_by(cover) %>% mutate(p=sum(prop)) %>% ungroup() %>% mutate(p=100*round(p/sum(unique(p)),4)) %>% 
@@
   ggplot(aes(dist,prop,group=site))+geom_line(alpha=0.2)+
-  facet_wrap(~cover,ncol=4)+theme_classic()+labs(y='Percent cover',x='Inner radius of annuli (m)')
-
+  facet_wrap(~cover,ncol=4)+theme_classic()+theme(axis.text = element_text(size = 8),strip.text=element_text(size=8))+
+  labs(y='Percent cover',x='Inner radius of annuli (m)')
 ```
@@
 Canola crops had a marginally higher activity-density of _P. melanarius_ than other trap locations (Figure \@ref(fig:PteMelLandscape)a).
-Grassland cover was the most important land cover type in explaining in activity-density ($R^2$: 0.104, Table \@ref(tab:rSquared)), and nearby grassland had a neutral effect early in the summer but a negative effect later in the summer (Figure \@ref(fig:PteMelLandscape)b), suggesting that _P.
+Grassland cover was the most important land cover type in explaining in activity-density ($R^2$: 0.104, Table \@ref(tab:rSquared)), and local (<500 m) grassland had a neutral effect early in the summer but a negative effect later in the summer (Figure \@ref(fig:PteMelLandscape)b), suggesting that _P.
 melanarius_ may move into grasslands later in the year.
-Nearby canola had a positive effect in the early summer, but far-away canola (>800 m) had a negative effect, indicating that areas with widespread canola coverage had lower _P.
-melanarius_ activity-density than those with only local canola cover.
+Local canola had a positive effect in the early season, but landscape-level canola (>500 m) had a negative effect, indicating that areas with widespread canola coverage had lower _P.
+melanarius_ activity-density.
 Pulses acted as a late-season source, indicating that _P. melanarius_ may migrate out of the crop after (or during) harvest.
 Finally, _P.
-melanarius_ activity-density had a strong temporal and spatial component (both p<0.001), indicating that phenology and local geographic factors were strong drivers of ground beetle activity-density (Figure \@ref(fig:PteMelSpatiotemporal)).
-The landscape composition and trap location explained `r r2Nakagawa$PteMelMod[1]*100`% of the variance in activity-density, while the spatial and temporal smoothers accounted for `r with(r2Nakagawa,(PteMelMod[2]-PteMelMod[1])*100)`% (Table \@ref(tab:rSquared)).
+melanarius_ activity-density had a strong temporal and spatial component (both p<0.001), indicating that phenology and local geographic factors were important drivers of ground beetle activity-density (Figure \@ref(fig:PteMelSpatiotemporal)).
+Landscape composition and trap location explained `r r2Nakagawa$PteMelMod[1]*100`% of the variance in activity-density, while the spatial and temporal smoothers accounted for `r with(r2Nakagawa,(PteMelMod[2]-PteMelMod[1])*100)`% (Table \@ref(tab:rSquared)).
 
-<!-- Percent signs are escaped in LaTeX, but this causes havoc if used in fig.cap of chunk options (OK if used in internal captions, I think). Yihui uses "text references" instead. -->
+<!-- Percent signs are escaped in LaTeX, but this causes havoc if used in fig.cap of chunk options (OK if used in internal captions, I think). Yihui uses the following "text references" instead. -->
 (ref:PteMelCap) Landscape influence on _Pterostichus melanarius_ activity-density.
@@
 Unlike _P. melanarius_, both _Pardosa_ species had far lower activity-density in canola than any other cover type (Figures \@ref(fig:ParDisLandscape)a, \@ref(fig:ParMoeLandscape)a).
-Nearby canola appeared to act as a source of _P.
-moesta_ and a weak source of _P.
-distincta_, as activity-density was positively related to the local proportion of canola early in the season, but negatively related later in the season (Figures \@ref(fig:ParDisLandscape)b, \@ref(fig:ParMoeLandscape)c, p=`r with(pdisSmTerms,p[Smoother=='ti(Distance,Day):Canola'])`, `r with(pmoeSmTerms,p[Smoother=='ti(Distance,Day):Canola'])`).
-Urban land cover had a similar effect on _P. moesta_, acting as an early source and a late sink (Figure \@ref(fig:ParMoeLandscape)f).
-Trees and shrubs acted as a sink for _P. distincta_ later in the season, and as a weak source early on in the season for _P. moesta_ (Figures \@ref(fig:ParDisLandscape)d, \@ref(fig:ParMoeLandscape)d).
-Grasslands had a local negative effect on _P.
-moesta_, but a positive landscape-level effect, indicating that while these cover types act as a sink, the general amount of grassland in the area had a positive effect on _P.
-moesta_ abundance.
-_P. distincta_ was similarly affected by pulses: landscape-level abundance of pulses had a positive effect, but the local effect was neutral.
-Finally, activity-density of both _Pardosa_ species had a very strong temporal and spatial component, although the temporal component was dominant for _P.
+Activity-density of both _Pardosa_ species had a strong temporal and spatial component, although the temporal component was dominant for _P.
 distincta_, whereas the spatial component was dominant for _P.
-moesta_ (Figures \@ref(fig:ParDisSpatiotemporal) and \@ref(fig:ParMoeSpatiotemporal) ; both p`r with(pmoeSmTerms,p[Smoother=='s(E,N)'])`).
-The landscape composition and trap location explained `r r2Nakagawa$ParDisMod[1]*100`%  and `r r2Nakagawa$ParMoeMod[1]*100`% of variance in activity-density, while the spatial and temporal smoothers accounted for `r with(r2Nakagawa,(ParDisMod[2]-ParDisMod[1])*100)`%  and `r with(r2Nakagawa,(ParMoeMod[2]-ParMoeMod[1])*100)`%, for _P.
-distincta_ and _P.
-moesta_ respectively.
+moesta_ (Figures \@ref(fig:ParDisSpatiotemporal) and \@ref(fig:ParMoeSpatiotemporal); both p`r with(pmoeSmTerms,p[Smoother=='s(E,N)'])`).
+
+_P.
+distincta_ activity density responded to pasture and woodlands; landscape-level pasture cover had a negative effect (Figure \@ref(fig:ParDisLandscape)b), while woodlands had a negative effect late in the season (Figure \@ref(fig:ParDisLandscape)c).
+This suggests that large amounts of pasture are unsuitable habitat for _P. distincta_, and that they may migrate into woodlands later in the season.
+However, trap location and the temporal random effect (Figure \@ref(fig:ParDisSpatiotemporal)a) explained roughly 10 times more variance ($R^2$: `r round(sum(filter(r2Nakagawa2,model=='ParDisMod',terms=='trapLoc'|grepl('day',terms))$r2comp),3)`) than landscape composition ($R^2$: `r round(sum(filter(r2Nakagawa2,model=='ParDisMod',terms!='trapLoc',terms!='sigmaD',!grepl('s\\(',terms))$r2comp),3)`), meaning that while _P.
+distincta_ may be locally abundant in certain cover types, it is very generalistic in its overall habitat preferences.
+
+_P. moesta_ activity density responded to grassland, canola, and road margins.
+Grasslands had a local negative effect, but a positive landscape-level effect, indicating that while these cover types act as a local sink, the general amount of grassland in the area had a positive effect (Figure \@ref(fig:ParMoeLandscape)b).
+Nearby local canola had a positive early effect on activity-density, but a negative local effect later in the season (Figure \@ref(fig:ParMoeLandscape)c).
+Local road margins had a similar effect, acting as an early source and a late sink (Figure \@ref(fig:ParMoeLandscape)d).
+Pulses also had a positive effect at the landscape level (Figure \@ref(fig:ParMoeLandscape)e), but this explained very little variance in _P.
+moesta_ activity density (Table \@ref(tab:rSquared), $R^2$: `r round(filter(r2Nakagawa2,model=="ParMoeMod",terms=="Pulses")$r2comp,3)`).
+Similar to _P.distincta_, trap location and an East-West spatial random effect (Figure \@ref(fig:ParMoeSpatiotemporal)b) explained roughly 5 times more variance ($R^2$: `r round(sum(filter(r2Nakagawa2,model=='ParMoeMod',terms=='trapLoc'|grepl('E,N',terms))$r2comp),3)`) in _P.
+moesta_ activity density than landscape composition ($R^2$: `r round(sum(filter(r2Nakagawa2,model=='ParMoeMod',terms!='trapLoc',terms!='sigmaD',!grepl('s\\(',terms))$r2comp),3)`), meaning that _P.
+moesta_ is also highly generalistic in its overall habitat preferences.
 
@@
 _Phalangium opilio_ activity-density was strongly influenced by trap location, with grassy field edges and wetlands having the highest activity-density (Figure \@ref(fig:OpilioLandscape)a).
-Landscape composition explained `r filter(r2Nakagawa2,grepl('Opilio',model),!grepl('s\\(',terms),terms!='trapLoc',terms!='sigmaD') %>% summarize(s=sum(r2comp)) %>% pull(s) %>% paste(.,collapse=', ')`% of variance in _P.
+Nearby grassland and woodland both had negative effects on _P.
+opilio_ activity-density, but only early in the season (Figures \@ref(fig:OpilioLandscape)b,c), suggesting that either these landscape cover classes
+
+<!-- Landscape composition explained `r filter(r2Nakagawa2,grepl('Opilio',model),!grepl('s\\(',terms),terms!='trapLoc',terms!='sigmaD') %>% summarize(s=sum(r2comp)) %>% pull(s) %>% paste(.,collapse=', ')`% of variance in _P.
 opilio_ activity-density.
-Nearby grassland (p=`r with(opilSmTerms,p[Smoother=='ti(Distance,Day):GrassWetland'])`) and woodland (p=`r with(opilSmTerms,p[Smoother=='s(Distance):TreeShrub'])`) both had negative effects on _P.
-opilio_ activity-density, but only early in the season (Figures \@ref(fig:OpilioLandscape)b,c).
-Compare this to _P. melanarius_, which is also influenced by grassland and woodland, but where the effect was negative _late_ in the season.
+-->
 The temporal and spatial components, as in the other two species, were both very strong (both p`r with(opilSmTerms,p[grepl('E,N',Smoother)])`).
@@
 ```{r rSquared, echo=FALSE, out.width='100%'}  
-
 r2Nakagawa2 %>% select(model,terms,r2comp) %>% mutate(terms=as.character(terms),r2comp=r2comp*1) %>%
@@
                          terms=='Urban' ~ 'Road margins', TRUE ~ terms)) %>%
-  kable(.,format='latex',caption='R$^2_{GLMM}$ for model components, representing the proportion of total variance attributable to each term.',
+  kable(.,format='latex',caption='R$^2_{GLMM}$ for model components, representing the proportion of total variance explained by each term.
+R$^2$ was calculated using methods from Nakagawa et al.
+2013 and Nakagawa et al.
+2017.',
         col.names=linebreak(x=c('Term','\\emph{Pterostichus}\n\\emph{melanarius}','\\emph{Pardosa}\n\\emph{distincta}',
@@
         digits=c(1,3,3,3,3),align='rllll',escape=FALSE)
-
 ```
@@
   mutate_all(linebreak) %>%  # required for linebreaks to work
-  kable(.,format='latex',caption='Summary of model results. Cover classes with weak effects on activity density are not shown.',
+  kable(.,format='latex',caption='Summary of model results.
+\\emph{Local/Landscape} denotes cover classes <500m or >500m away from the trap location, respectively.
++/-- indicates positive or negative effects of the cover class, and \\emph{Early/Mid/Late} denotes whether the effects were present earlier or later during the season.
+Cover classes with weak effects on activity density are not shown.',
         col.names=linebreak(x=c('Cover class','\\emph{Pterostichus}\n\\emph{melanarius}','\\emph{Pardosa}\n\\emph{distincta}',
@@
         align='rllll',escape=FALSE) %>% 
-  column_spec(1, width = "4em") %>% column_spec(c(2:5), width = "8em") # fix column widths
+  column_spec(1, width = "4em") %>% column_spec(c(2:5), width = "9em") # fix column widths
 ```

### 2020-10-09 frAnalysis.R

@@ -438,18 +438,18 @@ p3 <- expand.grid(endDayMat=c(173,203,232),distMat=seq(30,1500,30),Canola=1) %>%
   mutate(y=factor(y,labels=dispDays$date)) %>% 
   effectPlot(cols=smoothCols)+labs(x='Distance (m)',y='Canola effect')
 
-#Pulses (space)
-p4 <- expand.grid(distMat=seq(30,1500,30),Pulses=1,y=NA) %>% 
-  smoothPred(mod3,whichSmooth=which(grepl('Pulses',sapply(mod3$smooth,function(x) x$label)))[1]) %>%
-  rename(x=distMat) %>% 
-  effectPlot(leg=F)+labs(x='Distance (m)',y='Pulse effect')
-
 #Urban effect (space + time)
-p5 <- expand.grid(endDayMat=c(173,203,232),distMat=seq(30,1500,30),Urban=1) %>% 
+p4 <- expand.grid(endDayMat=c(173,203,232),distMat=seq(30,1500,30),Urban=1) %>% 
   smoothPred(mod3,whichSmooth=which(grepl('Urban',sapply(mod3$smooth,function(x) x$label)))) %>%
   rename(x=distMat,y=endDayMat) %>% 
   mutate(y=factor(y,labels=dispDays$date)) %>% 
   effectPlot(cols=smoothCols)+labs(x='Distance (m)',y='Road margin effect')
+
+#Pulses (space)
+p5 <- expand.grid(distMat=seq(30,1500,30),Pulses=1,y=NA) %>% 
+  smoothPred(mod3,whichSmooth=which(grepl('Pulses',sapply(mod3$smooth,function(x) x$label)))[1]) %>%
+  rename(x=distMat) %>% 
+  effectPlot(leg=F)+labs(x='Distance (m)',y='Pulse effect')
 
 #Plot landscape effects
 fixeffPlot <- ggarrange(p1,p2,p3,p4,p5,

### 2020-10-14 manuscript/manuscript_outline.Rmd
Worked on discussion

@@
 1.
-Untilled semi-natural land (SNL) provides egg-laying and feeding areas for predatory arthropods, meaning that SNL should act as a source of arthropods during the early part of the season, and a sink during the later part of the season.
+Untilled semi-natural land provides egg-laying and feeding areas for predatory arthropods, meaning that it should act as a source of arthropods during the early part of the season, and a sink during the later part of the season.
 2.
@@
 Cereal was removed from the model, as it was negatively correlated with canola cover at distances less than 200m and was positively correlated at distances over 500m, reflecting the most common crop rotations (canola $\rightarrow$ wheat $\rightarrow$ barley) and the commonly-used 800 m block structure of farmland in our study region (quarter-sections).
-This resulted in a reduced set of landscape terms, none of which were strongly concurved with each other (grassland, canola, pasture, woodland, pulses, urban; see Figure \@ref(fig:concurvity)).
+This resulted in a reduced set of landscape terms, none of which were strongly concurved with each other (cropland: canola, pulses; SNL: grassland, pasture, woodland, urban; see Figure \@ref(fig:concurvity)).
 
@@
 
-_Phalangium opilio_ activity-density was strongly influenced by trap location, with grassy field edges and wetlands having the highest activity-density (Figure \@ref(fig:OpilioLandscape)a).
-Nearby grassland and woodland both had negative effects on _P.
-opilio_ activity-density, but only early in the season (Figures \@ref(fig:OpilioLandscape)b,c), suggesting that either these landscape cover classes
-
-<!-- Landscape composition explained `r filter(r2Nakagawa2,grepl('Opilio',model),!grepl('s\\(',terms),terms!='trapLoc',terms!='sigmaD') %>% summarize(s=sum(r2comp)) %>% pull(s) %>% paste(.,collapse=', ')`% of variance in _P.
-opilio_ activity-density.
--->
-The temporal and spatial components, as in the other two species, were both very strong (both p`r with(opilSmTerms,p[grepl('E,N',Smoother)])`).
-The landscape composition and trap location explained `r r2Nakagawa$OpilioMod[1]*100`%  of variance in activity-density, while the spatial and temporal smoothers accounted for `r with(r2Nakagawa,(OpilioMod[2]-OpilioMod[1])*100)`%.
+_P.
+opilio_ activity-density was somewhat influenced by trap location, with field edges and wetlands having the highest activity-density (Figure \@ref(fig:OpilioLandscape)a), but this effect was swamped by the effect of landscape and the spatiotemporal random effects (Table \@ref(tab:rSquared)), meaning that _P.
+opilio_ activity density is only mildly influenced by local cover type.
+Nearby grassland and woodland both had negative effects on _Phalangium opilio_ activity-density, but only early in the season (Figures \@ref(fig:OpilioLandscape)b,c), suggesting that _P.
+opilio_ may preferentially migrate to these cover classes.
+The temporal random effect was overwhelmingly the most important predictor of _P.
+opilio_ activity-density ($R^2$: `r round(sum(filter(r2Nakagawa2,model=='OpilioMod',terms=='s(day)')$r2comp),3)`), showing that activity-density increased during the spring, and showed very little decline during the rest of the season (Figure \@ref(fig:OpilioSpatiotemporal)a).
+Similar to _P.
+moesta_, _P.
+opilio_ also showed a distinct East-West spatial random effect (Figure \@ref(fig:OpilioSpatiotemporal)b), indicating that their activity-density is also influenced by larger-scale abiotic factors.
 
@@
 
-The activity-density of _Pterostichus melanarius_ and _Phalangium opilio_ responded to strongly landscape composition, but the response of _Pardosa distincta_ and _Pardosa moesta_ was weaker.
-We found some support for our predictions of SNL (grass and wetland, woodlands, and road margins) acting as a late-season sinks for beneficial arthropods.
-In particular, grass and wetland acted as a sink for _P. melanarius_, woodlands acted as a sink for _P. distincta_, and road margins acted as a sink for _P. moesta_.
-While there was limited evidence of SNL acting as early-season sources, some acted as landscape-level sources (grassland and road margins on _P. moesta_), indicating earlier or wider-scale dispersal.
-Canola and pasture acted as landscape-level sinks for _P. melanarius_ and _P. distincta_, respectively, meaning that these cover types likely represent only partial habitat for these arthropods.
+The activity-density of the four arthropods was influenced by landscape composition, but the response of _Pterostichus melanarius_ and _Phalangium opilio_ was much stronger.
+We found support for our predictions of SNL (grassland, woodlands, and road margins) acting as a late-season sinks for beneficial arthropods.
+In particular, _P. melanarius_ was attracted to grasslands, _P. distincta_ to woodlands, and _P. moesta_ to road margins, all at the end of the season.
+While there was limited evidence of SNL acting as early-season sources, some cover classes had a positive effect at the landscape level (grassland and road margins on _P.
+moesta_), indicating earlier or wider-scale dispersal away from these cover classes.
+Canola and pasture had negative landscape-level effects on _P. melanarius_ and _P. distincta_, respectively, meaning that these cover types likely represent only partial habitat for these arthropods.
 There was also a strong temporal component to most of the landscape effects, meaning that it is important to consider how sinks and sources may change over the season.
@@
 The predatory ground beetle _Pterostichus melanarius_ responded to landscape composition, primarily to canola, pulses, and grass and wetland cover.
-Grassland and wetland cover acted as a late-season sink, suggesting that _P. melanarius_ may migrate into it at the end of the summer.
+Grassland and wetland cover had a negative late-season effect, suggesting that _P. melanarius_ may migrate into it at the end of the summer.
 Other studies have found similar results, suggesting that untilled land is important off-field habitat for carabids [@desender1988; @fournier2002; but see @hatten2007].
-In particular, @purtauf2005 found that carabid density increased with proportion of nearby grasslands, so our finding of grassland as late-season sink may represent _P.
+In particular, @purtauf2005 found that carabid density increased with proportion of nearby grasslands, so our negative late-season effect of grasslands may represent _P.
 melanarius_ moving to overwintering habitat at the end of the season.
 However, _P. melanarius_ is also found in a wide variety of habitats, and tends to prefer agricultural fields [@larsen2003]. 
-Our models also suggest this, as they showed that canola and pulse crops acted as early- and mid-season sources of _P. melanarius_.
-Early in the season, canola crops acted as local source but a landscape-level sink, which may indicate that they provide only temporary feeding habitat.
+Our models also suggest this, as they showed that canola and pulse crops had positive effects on _P. melanarius_ activity-density early in the season.
+Early in the season, canola crops had a local positive effect, but a landscape-level negative effect, which may indicate that they provide only temporary feeding habitat.
 The effect of pulse crops on carabid abundance is not well-studied, but our results suggest that pulses may represent a potential food resource for _P.
@@
 
-The wolf spiders _Pardosa distincta_ and _Pardosa moesta_ both responded to landscape composition, but in slightly different ways.
-Canola acted as an early-season source for both species, indicating that _Pardosa_ and _P. melanarius_ may both use canola as foraging grounds.
-The responses to other landscape cover classes, however, was different between each species of spider.
-The only other landscape classes that influenced _P. distincta_ were pasture and woodland.
-Pasture had a negative effect at the landscape scale, and woodland acted as a late season sink, suggesting that _Pardosa_ use woody shrubs and trees for overwintering or winter foraging [@aitchison1984].
+The wolf spiders _Pardosa distincta_ and _Pardosa moesta_ both responded to landscape composition, but it explained only a small fraction of their activity-density ($R^2$: `r round(sum(filter(r2Nakagawa2,model=='ParDisMod',terms!='trapLoc',terms!='sigmaD',!grepl('s\\(',terms))$r2comp),3)`, `r round(sum(filter(r2Nakagawa2,model=='ParMoeMod',terms!='trapLoc',terms!='sigmaD',!grepl('s\\(',terms))$r2comp),3)`).
+This means that both species of _Pardosa_ appear to have very general habitat preferences, but may be somewhat influenced by certain cover types.
+
+Pasture had a negative effect at the landscape scale, and woodland acted as a late season sink, suggesting that _P.
+distincta_ use shrubs and trees for overwintering or winter foraging [@aitchison1984; @buddle2000].
 _Pardosa_ are found in areas close to disturbed roadside strips [@drapela2008; @drapela2011; @kowal2011], but _P.
@@
 distincta_ tended to have higher activity-density in trap locations with higher grass cover (Figure \@ref(fig:ParDisLandscape)a).
-For _P. moesta_, we found that roads clearly acted as an early source and a late sink [similar to @drapela2008 and @drapela2011]. 
-Grassland and wetland, as well as pulses, also acted as a local sink but a landscape-level source, suggesting that they draw _P.
-moesta_ away from trapping locations but enhance their landscape-level abundance.
+Canola had an early-season positive effect on _P. moesta_, indicating that _P. moesta_ and _P. melanarius_ may both use canola as foraging grounds.
+We also found that road margins had a positive early-season and a negative late-season effect [similar to @drapela2008 and @drapela2011]. 
+Grassland and pulses also had a local negative effect but a positive landscape-level effect; this suggests that they may constitute suitable habitat for _P.
+moesta_ and attract them away from other cover types.
 Lycosids employ a wandering-active predation strategy [@young1990], meaning that nearby landscape composition may be more influential to _Pardosa_ than large-scale composition [@oberg2007; @oberg2008].
 While trapping location explained a large proportion of variance for both species (`r round(filter(r2Nakagawa2,model=='ParDisMod',grepl('trapLoc',terms))$r2comp,2)` and `r round(filter(r2Nakagawa2,model=='ParMoeMod',grepl('trapLoc',terms))$r2comp,2)`), several landscape features were also important at large spatial scales, including grass and wetland, pasture, pulses, and road margins.
-This suggests that _Pardosa_ dispersal distances may be further than previously though, either through ballooning as juveniles [@richter1970; @greenstone1982] or through other long-distance travel.
+Therefore, _Pardosa_ dispersal distances may be further than previously thought, either through ballooning as juveniles [@richter1970; @greenstone1982] or through other long-distance travel.
 
-_Phalangium opilio_ activity-density responded to grass and wetland cover, as well as trees and shrubs, but the trap location and landscape explained only `r r2Nakagawa$OpilioMod[1]*100`% of the variance.
+_Phalangium opilio_ activity-density responded to grass and wetland cover, as well as trees and shrubs.
 Other studies have found that _P. opilio_ is mostly found in human-altered landscapes with a large proportion of farming [@muster2014; @vandepoel2015Msc].
@@
 _P. opilio_ is also found in large numbers at the edges of forests, and may migrate from forests into farmlands [@vandepoel2015Msc].
-We found the opposite pattern: forests act as a weak sink for _P. opilio_, at least early in the year.
+We found the opposite pattern: forests had a weak negative effect on _P. opilio_, at least early in the year.
 Unlike the other arthropods, most of the variation in activity-density for _P.
 opilio_ was explained by day of year (R$^2$ = `r round(filter(r2Nakagawa2,model=='OpilioMod',grepl('day',terms))$r2comp,2)`), indicating strong seasonal emergence cues.
+However, there was also a strong East-West spatial random effect in both _P.
+opilio_ and _P.
+moesta_, meaning that wider-scale geographic patterns (possibly related to rainfall or temperature) also influence their activity-density.
 <!-- Feels like this paragraph ends too soon. Why was there so little variation due to landscape? Link to biology of the critter. -->
@@
 Different types of SNL act as sinks or sources at different times of year, but our results reveal the changes in sinks and sources within an agricultural landscape.
-These patterns imply movement of organisms between landscape features, but since we did not directly measure this, future studies should directly examine arthropod movement, with the goal of integrating landscape ecology and behavioural processes into a single model [@lima1996].
+These patterns imply movement of organisms between landscape features, but since we did not directly measure this, future studies should directly examine arthropod movement and life-history within matrices of cover types, with the goal of integrating landscape ecology and behavioural processes into a single model [@lima1996].
 This would also allow direct inference about landscape categories that were combined in our dataset, allowing us to consider different landscape categories independently.

### 2020-10-14 manuscript/manuscript_outline.Rmd
Worked on discussion

@@
 Functional regression plots of landscape composition reveal which cover classes are acting as sources or sinks of organisms, and at what spatial scale.
-Positive responses to nearby landscape cover classes indicate that the cover class acts as a net source (i.e. arthropods spill over *from* it).
+Positive effects of nearby landscape cover classes indicate that the cover class acts as a net source (i.e. arthropods spill over *from* it).
 However, negative responses to nearby landscape cover classes can indicate one of two things:
@@
 Alternatively, a cover class could act as a sink by providing high-quality habitat at certain times of the year (e.g. egg laying/feeding), but act as a source at other times (e.g. during emergence).
-For brevity in the subsequent Results section, we refer to "local" and "landscape"-level effects; local refers to the effects of landscape composition at scales of <500m, whereas landscape refers to scales >500 m.
+For brevity in the following Results section, we refer to "local" and "landscape"-level effects; local refers to the effects of landscape composition at scales of <500m, whereas landscape refers to scales >500 m.
 Similarly, we refer to "early", "mid", and "late"-season effects, where landscape composition affected abundance from June - July, July - August, or August - September.
-
-<!-- * We used 4 nested models to gauge the relative importance of landscape composition for arthropod activity-density -->
-<!--   + Model 1 consisted of a temporal and spatial smoothers (``random effects"), necessary to account for the underlying spatiotemporal structure of the data  -->
-<!--   + Smoothers can be thought of as random effects, where the coefficients follow a probability distribution defined by a fixed smoothing coefficient $\lambda$ [@wood2017]  -->
-<!--   + Model 2 added a local cover term, to account for the specific effect of local cover on activity-density -->
-<!--   + Model 3 added a smoother term for the landscape rings, modeling the effect of non-crop cover at varying distances on activity-density -->
-<!--   + Model 4, similar to model 3, modeled the effect of all underlying cover classes (crop and non-crop) at varying distances -->
-
-<!-- Model    | Independent variables                                     | $r$ Formula -->
-<!-- -------- | --------------------------------------------------------- | ----------------------------------------------- -->
-<!-- 1        | Phenology + Geography                                     | activity-density ~ s(Day) + s(E,N) -->
-<!-- 2        | Phenology + Geography + Local cover                       | activity-density ~ s(Day) + s(E,N) + Trap Location -->
-<!-- 3        | Phenology + Geography + Local cover + Landscape (general) | activity-density ~ s(Day) + s(E,N) + Trap Location + s(Non-crop Cover)-->
-<!-- 4        | Phenology + Geography + Local cover + Landscape (specific)| activity-density ~ s(Day) + s(E,N) + Trap Location + s(Cover 1) + s(Cover 2) + ... + s(Cover n) -->
 
@@
 
-<!-- + Carabid diversity is higher in no-till agriculture [@bourassa2008, @puech2014] -->
-<!-- Surprisingly, flax acted as a local and landscape level sink for _P.
-melanarius_, and as an overall sink for _P.
-opilio_, suggesting that it may be inappropriate feeding or nesting cover for these beneficial arthropods.
--->
-<!-- Flax is more sensitive to weed competition than other small grains [@friesen1986; @kandel2020], so weed control tends to be more intense. -->
-<!-- Lower weed abundance may cause flax fields to have lower levels of weed seeds to feed on, causing seed-feeding carabids to move to other locations [@trichard2014]. -->
-<!-- Alternatively, it could be that plant structural diversity due to extensive weed control, meaning that carabids have lower amounts of attractive ground cover [@butts2003; @clark1993]. -->
-<!-- Why this occurs in flax fields but not canola or pulse crops is unclear, but may have to do with decreased shading or ground cover being less attractive to carabids [@butts2003]. -->
-<!-- To our knowledge, there is no published research investigating effects of flax cropping on beneficial arthropods, so the causes of this pattern are speculative. -->
-
 The wolf spiders _Pardosa distincta_ and _Pardosa moesta_ both responded to landscape composition, but it explained only a small fraction of their activity-density ($R^2$: `r round(sum(filter(r2Nakagawa2,model=='ParDisMod',terms!='trapLoc',terms!='sigmaD',!grepl('s\\(',terms))$r2comp),3)`, `r round(sum(filter(r2Nakagawa2,model=='ParMoeMod',terms!='trapLoc',terms!='sigmaD',!grepl('s\\(',terms))$r2comp),3)`).
 This means that both species of _Pardosa_ appear to have very general habitat preferences, but may be somewhat influenced by certain cover types.
-
-Pasture had a negative effect at the landscape scale, and woodland acted as a late season sink, suggesting that _P.
-distincta_ use shrubs and trees for overwintering or winter foraging [@aitchison1984; @buddle2000].
+Pasture had a negative effect at the landscape scale, and woodland had a late-season negative effect, suggesting that _P.
+distincta_ move to shrubs and trees for overwintering or winter foraging [@aitchison1984; @buddle2000].
 _Pardosa_ are found in areas close to disturbed roadside strips [@drapela2008; @drapela2011; @kowal2011], but _P.
@@
 Since most of our study area was in or near farmed land, the lack of variation is understandable, but there were a few notable landscape-level patterns that emerged.
-_P. opilio_ activity-density was higher in grassy field edges and wetlands, but grasslands and wetlands acted as a local sink of _P. opilio_ until late in the season.
+_P. opilio_ activity-density was higher in grassy field edges and wetlands, but grasslands and wetlands had a local negative effect on _P. opilio_ until late in the season.
 These indicate that while grass and wetlands could act as a reservoir, spillover into other land cover types may be limited, as _P.
@@
 We have shown how a relatively straightforward statistical technique can be used to consider multiple spatial scales of landscape composition, providing richer inference about the processes acting on beneficial arthropods.
-Different types of SNL act as sinks or sources at different times of year, but our results reveal the changes in sinks and sources within an agricultural landscape.
-These patterns imply movement of organisms between landscape features, but since we did not directly measure this, future studies should directly examine arthropod movement and life-history within matrices of cover types, with the goal of integrating landscape ecology and behavioural processes into a single model [@lima1996].
+Our results show empirical evidence of arthropod migration between cover types at different times of year, which is rarely considered beyond single-field studies.
+Since we did not directly track individual movements, future studies should directly examine arthropod movement and life-history within matrices of cover types, with the goal of integrating landscape ecology and behavioural processes into a single model [@lima1996].
 This would also allow direct inference about landscape categories that were combined in our dataset, allowing us to consider different landscape categories independently.
 Finally, future work should explicitly link landscape structure, arthropod abundance, and ecosystem services [@gagic2017].
+
+# Implications
 

### 2020-10-15 manuscript/manuscript_outline.Rmd
Worked on revisions
- Redid figures

@@
     email: diane.edwards.ca@gmail.com
-    affiliation: University of Calgary
+    affiliation: Ambrose University
   - name: Jess Vickruck
     email: jessica.vickruck@canada.ca
-    affiliation: Agriculture and Agri-Food Canada
+    affiliation: University of Calgary
   - name: Lincoln Best
@@
     address: 2500 University Drive NW, Calgary, AB, Canada
-  - code: Agriculture and Agri-Food Canada
-    address: 850 Lincoln Road, Fredericton, NB, Canada
+  - code: Ambrose University
+    address: 150 Ambrose Circle SW, Calgary, AB
   - code: Oregon State University
@@
 Arthropods are one of the most influential groups of animals in agricultural systems.
-Pest arthropods can cause large reductions in crop yield [@oerke2005], which can result in downstream economic effects, food insecurity, and malnutrition.
+Pest arthropods can cause large reductions in crop yield [@oerke2005], which can result in negative downstream economic effects and food insecurity.
 On the other hand, spillover of beneficial arthropods from adjacent non-crop patches can deliver increased crop yields by providing ecosystem services such as extra pollination or pest suppression [@losey2006; @klein2007; @garibaldi2013].
@@
 Despite what is known about the spatial and temporal aspects of beneficial arthropod spillover, these are rarely considered together.
-First, some habitat types may act as sources of arthropods during some times of the year, but as sinks during other times, meaning that the timing of spillover may not align with key periods in crop development.
+First, some non-crop habitat may act as sources of arthropods during some times of the year, but as sinks during other times, meaning that the timing of spillover from non-crop habitat may not align with important periods in crop development.
 Arthropods can migrate from managed crops back into adjacent SNL at the end of the season [@desender1988; @tscharntke2005b], but this is seldom considered.
 Second, the spatial "grain" of the landscape that is relevant to an organism depends on their traits and life history [@ahrenfeldt2015].
-For instance, bumblebee abundance can be controlled by both local- and landscape-scale SNL abundance [@westphal2006], but this is poorly studied for other groups of beneficial organisms [but see @sander2006].
-Finally, the feeding and life-history characteristics of many predatory ground beetles and spiders is often poorly-documented, especially in North America.
+For instance, bumblebee abundance can be controlled by both nearby and far-away SNL abundance [@westphal2006], but this is poorly studied for other groups of beneficial organisms [but see @sander2006].
+Finally, the feeding and life-history characteristics of many predatory ground beetles and spiders are often poorly-documented, especially in North America.
 This makes it difficult to make generalizations of which habitat types harbour beneficial arthropods, making it even more difficult to provide accurate information to farmers about land management practices.
@@
 
-We used four highly-abundant species of predatory arthropods found in the pitfall traps, as common species are often more important for ecosystem service provision than rare ones [@winfree2015].
-_Pterostichus melanarius_ is an introduced predatory ground beetle (Coleoptera: Carabidae) that is a wide-ranging generalist [@carcamo1994; @larsen2003; @busch_Msc].
+We used four highly-abundant species of predatory arthropods found in the pitfall traps, as common species are often more important for ecosystem service provision than rare species [@winfree2015], but their habitat preferences are still poorly understood.
+_Pterostichus melanarius_ is an introduced predatory ground beetle (Coleoptera: Carabidae) that is a wide-ranging generalist known to prey upon crop pests [@carcamo1994; @larsen2003; @busch_Msc].
 It is commonly found in untilled grasslands [@purtauf2005] and may use grassy field edges as larval habitat [@desender1988].
@@
 Several landscape ``fingerprints" were evident in the landscape annuli, with cereal cover increasing with distance away, along with a corresponding decrease in canola cover.
-Grassland cover was largely constant with distance, although a cluster of sites had uniformly high or low cover of grassland with distance.
+Study sites were originally chosen for sampling arthropods surrounding canola agroecosystems, so canola was a dominant signal in the landscape, but there was also a large amount of variation in grassland and pasture surrounding each site (Figure \@ref(fig:landscapeComp)).
+Grassland cover was largely constant with distance, but a cluster of sites had uniformly high or low cover of grassland with distance.
 The pitfall traps caught a total of `r with(Ncatches,total[spp=='PteMel'])` _Pterostichus melanarius_, `r with(Ncatches,total[spp=='ParDis'])` _Pardosa distincta_, `r with(Ncatches,total[spp=='ParMoe'])` _Pardosa moesta_, and `r with(Ncatches,total[spp=='Opilio'])` _Phalangium opilio_ (mean trapping rates per day: `r with(Ncatches,paste(round(perDayMean,2),collapse=', '))`, SD: `r with(Ncatches,paste(round(perDaySD,2),collapse=', '))`, respectively).
@@
 Canola crops had a marginally higher activity-density of _P. melanarius_ than other trap locations (Figure \@ref(fig:PteMelLandscape)a).
-Grassland cover was the most important land cover type in explaining in activity-density ($R^2$: 0.104, Table \@ref(tab:rSquared)), and local (<500 m) grassland had a neutral effect early in the summer but a negative effect later in the summer (Figure \@ref(fig:PteMelLandscape)b), suggesting that _P.
+Grassland cover was the most important land cover type in explaining activity-density ($R^2$: 0.104, Table \@ref(tab:rSquared)), and local (<500 m) grassland had a negative effect late in the summer (Figure \@ref(fig:PteMelLandscape)b), suggesting that _P.
 melanarius_ may move into grasslands later in the year.
-Local canola had a positive effect in the early season, but landscape-level canola (>500 m) had a negative effect, indicating that areas with widespread canola coverage had lower _P.
+Local canola had a positive effect in the early season, but landscape-level (>500 m) canola had a negative effect, indicating that areas with widespread canola coverage had lower _P.
 melanarius_ activity-density.
@@
 (ref:PteMelCap) Landscape influence on _Pterostichus melanarius_ activity-density.
+a) shows the effect of local trap location, and b-c) are functional regression plots of the proportion grassland and canola at distances away from each trap.
+d) is a functional regression plot over time, showing the effect of pulses at different times of the year.
 Lines and dots represent means, and bars and shaded regions represent 95 % confidence intervals (1.96 x SE).

### 2020-10-15 frPlotDemo.R

@@ -52,7 +52,7 @@ p2 <- apply(mapply(lineFun,int=rnorm(1000,0.5,0.1),slope=rnorm(1000,0,0.1),MoreA
   rename(lwr=`X5.`,med=`X50.`,upr=`X95.`) %>% 
   ggplot(aes(x,med))+geom_ribbon(aes(ymax=upr,ymin=lwr),alpha=0.3)+
   geom_line()+geom_hline(yintercept=0,linetype='dashed')+
-  annotate('text',x=500,y=-0.75,label='Effect of cover is uniform at all distances')+
+  annotate('text',x=500,y=-0.75,label='Effect of cover is positive at all distances')+
   annotate('segment',x=400,xend=300,y=-0.5,yend=0.2,arrow=arrow())+
   annotate('segment',x=600,xend=700,y=-0.5,yend=0.2,arrow=arrow())+
   labs(x='Distance',y=expression(paste('Slope of proportion cover (',beta,')')))+ylim(-1.5,1.5)

### 2020-10-15 frAnalysis.R
Changed date display in figures

@@ -179,8 +179,8 @@ ggsave('./figures/Pterostichus_melanarius_raneff.png',raneffPlot,width=stFigX,he
 #Plot significant landscape effects
 
 #Days to display on plots (early,mid,late)
-dispDays <- data.frame(doy=c(173,203,232)) %>% 
-  mutate(date=c('June 20','July 20','August 20')) #Actually June/July 22, but close enough...
+dispDays <- data.frame(doy=c(173,203,232)) %>% #June 20, July 20, Aug 20 (Actually June/July 22, but close enough...)
+  mutate(date=c('Early','Mid','Late')) 
 
 #Get order of terms to plot
 cbind(1:length(mod3$smooth),sapply(mod3$smooth,function(x) x$label))
@@ -314,8 +314,8 @@ ggsave('./figures/Pardosa_distincta_raneff.png',raneffPlot,width=stFigX,height=s
 data.frame(round(anova(mod3)$s.table,3)) %>% rownames_to_column('smoother')
 
 #Days to display on plots (early,mid,late)
-dispDays <- data.frame(doy=c(173,203,232)) %>% 
-  mutate(date=c('June 20','July 20','August 20')) #Actually June/July 22, but close enough...
+dispDays <- data.frame(doy=c(173,203,232)) %>% #June 20, July 20, Aug 20 (Actually June/July 22, but close enough...)
+  mutate(date=c('Early','Mid','Late')) 
 
 #Trap location - far less in canola
 p1 <- data.frame(trapLoc=tempTrap$trapLoc,pred=predict(mod3,type='terms',terms='trapLoc',se.fit=T)) %>% 
@@ -413,8 +413,8 @@ ggsave('./figures/Pardosa_moesta_raneff.png',raneffPlot,width=stFigX,height=stFi
 data.frame(round(anova(mod3)$s.table,3)) %>% rownames_to_column('smoother')
 
 #Days to display on plots (early,mid,late)
-dispDays <- data.frame(doy=c(173,203,232)) %>% 
-  mutate(date=c('June 20','July 20','August 20')) #Actually June/July 22, but close enough...
+dispDays <- data.frame(doy=c(173,203,232)) %>% #June 20, July 20, Aug 20 (Actually June/July 22, but close enough...)
+  mutate(date=c('Early','Mid','Late')) 
 
 #Trap location - far less in canola
[…]

### 2020-10-21 manuscript/manuscript_outline.Rmd
Worked on revisions

@@
 date: "Spring 2020"
-abstract: Ground-dwelling arthropods are important generalist predators in agro-ecosystems, and can use non-crop features as overwintering habitats.
+abstract: "Ground-dwelling arthropods are important generalist predators in agro-ecosystems, and can use non-crop features as overwintering habitats.
 However, it is unclear which types of landscape features constitute useful non-crop habitat, and at what spatial scale organisms gather resources at.
-Additionally, the same landscape feature may act as a sink or a source of arthropods at different times of the year, but this is rarely considered.
+Additionally, the same landscape feature may act as source of arthropods spill-over at different times of the year, but this is rarely considered.
 We modeled the activity-density of four highly-abundant species of Canadian prairie arthropods, and used functional regression to simultaneously consider both their habitat preferences and the timing of sources and sinks.
-We found that canola crops (_Brassica napus_ L.) acted as early-season sources, and that grasses and wetlands acted as late-season sinks of arthropods.
-Farmers should consider preserving existing grasslands and wetlands to act as reservoir habitats for the surrounding cropland.
+_Pterostichus melanarius_ (Coleoptera: Carabidae) and _Pardosa moesta_ (Arachnida: Lycosidae) appear to be attracted to canola (_Brassica napus_ L.) during the early summer, then disperse to grasslands, wetlands, and grassy road margins during the end of the summer.
+This suggests that grasslands and wetlands act as reservoir habitats for predatory arthropods, and that farmers should consider preserving existing habitat around croplands in order to maintain background levels of pest-control."
 
@@
 At each site, we extracted the proportion of each cover class within 30m annuli (rings), with the inner radius of each annulus ranging from 30 to 1470m in increments of 30m (total of 49 annuli, 1.5 km maximum).
-The ten most-common cover classes surrounding our sites represented 98% of the total land cover in our study region: grassland, cereal, canola, pasture, pulses, wetland, urban, shrubland, flax, and forest (Figure \@ref(fig:landscapeComp)); flax was removed, as only a single site had nearby flax cover.
+The ten most-common cover classes surrounding our sites represented 98% of the total land cover in our study region: grassland, cereal, canola, pasture, pulses, wetland, urban (road margins), shrubland, flax, and forest (Figure \@ref(fig:landscapeComp)); flax was removed, as only a single site had nearby flax cover.
 
-## Statistics
+## Analysis
 
@@
 Cereal was removed from the model, as it was negatively correlated with canola cover at distances less than 200m and was positively correlated at distances over 500m, reflecting the most common crop rotations (canola $\rightarrow$ wheat $\rightarrow$ barley) and the commonly-used 800 m block structure of farmland in our study region (quarter-sections).
-This resulted in a reduced set of landscape terms, none of which were strongly concurved with each other (cropland: canola, pulses; SNL: grassland, pasture, woodland, urban; see Figure \@ref(fig:concurvity)).
+This resulted in a reduced set of landscape terms, none of which were strongly concurved with each other (cropland: canola, pulses; SNL: grassland, pasture, woodland, roadside; see Figure \@ref(fig:concurvity)).
 
@@
 
-Functional regression plots of landscape composition reveal which cover classes are acting as sources or sinks of organisms, and at what spatial scale.
-Positive effects of nearby landscape cover classes indicate that the cover class acts as a net source (i.e. arthropods spill over *from* it).
+Functional regression plots of landscape composition reveal which cover classes are acting as spill-over sources or sinks of a given arthropod, and at what spatial scale.
+Positive effects of nearby landscape cover classes indicate that arthropods are spilling over *from* it.
 However, negative responses to nearby landscape cover classes can indicate one of two things:
-1) It may indicate that the cover class acts as a sink (i.e.
-organisms spill over *into* it) or 2) it may indicate that the cover class acts as a source, but it is unoccupied (i.e.
-no organisms available to spill over).
+1) It may indicate that arthropods are spilling over *into* it (i.e. net sink for spill-over) or 2) it may indicate that no arthropods are available to spill over *from* it.
 We consider 1) to be the more likely scenario, as it is unlikely that any one cover class is *completely* unoccupied.
 <!-- As these data were collected from a single year, this model does not consider the next-generation fitness consequences of spillover. -->
-For example, a cover class with low-quality habitat could act as an ecological trap [@galpern2017] if it acts as a sink but never as a source.
+For example, a cover class with low-quality habitat could act as an ecological trap [@galpern2017] if it acts as a net sink but never acts as a source of spill over.
 Alternatively, a cover class could act as a sink by providing high-quality habitat at certain times of the year (e.g. egg laying/feeding), but act as a source at other times (e.g. during emergence).
-For brevity in the following Results section, we refer to "local" and "landscape"-level effects; local refers to the effects of landscape composition at scales of <500m, whereas landscape refers to scales >500 m.
-Similarly, we refer to "early", "mid", and "late"-season effects, where landscape composition affected abundance from June - July, July - August, or August - September.
+For brevity in the following Results section, we refer to local- and landscape-level effects, where local indicates the effects of landscape composition at scales of <500m, whereas landscape indicates scales >500 m.
+Similarly, we refer to early-, mid-, and late-season effects, where landscape composition affected abundance from June - July, July - August, or August - September, respectively.
 
@@
 Lines and dots represent means, and bars and shaded regions represent 95 % confidence intervals (1.96 x SE).
-Coloured regions represent early-, mid-, and late-season effects (red, purple, blue).
+Coloured regions represent early-, mid-, and late-season effects (blue = August, purple = July, red = June).
 
@@
 
-#Based on example from:
-# https://stackoverflow.com/questions/52962411/table-with-long-text-bullet-points-and-specific-table-width
-mytable <- data.frame(
-    CoverClass = c("Grassland", "Canola", "Pasture", "Woodland", "Pulses", "Road margins"),
-    PteMel = c('$\\cdot$ Local -- (late)','$\\cdot$ Local + (early) \n$\\cdot$ Landscape -- (early)',' ',' ','$\\cdot$ Overall + (late)',' '),
-    ParDis = c(' ',' ','$\\cdot$ Landscape --',' $\\cdot$ Overall -- (late)',' ',' '),
-    ParMoe = c('$\\cdot$ Local -- \n$\\cdot$ Landscape +','$\\cdot$ Local + (early) \n$\\cdot$ Local -- (late)',' ',' ','$\\cdot$ Landscape +','$\\cdot$ Local + (early) \n$\\cdot$ Local -- (late) \n$\\cdot$ Landscape -- (early) \n$\\cdot$ Landscape + (late)'),
-    Opilio = c('$\\cdot$ Local -- (early)',' ',' ','$\\cdot$ Local -- (early) \n$\\cdot$ Landscape + (mid)',' ',' ')
-    )
-
-mytable %>%
-  mutate_all(linebreak) %>%  # required for linebreaks to work
-  kable(.,format='latex',caption='Summary of model results.
+# #Based on example https://stackoverflow.com/questions/52962411/table-with-long-text-bullet-points-and-specific-table-width
+# #Much better than above, but not very easy to absorb. Perhaps there should be some kind of organismal-based synthesis table?
+# summaryTab <- data.frame(
+#     CoverClass = c("Grassland", "Canola", "Pasture", "Woodland", "Pulses", "Road margins"),
+#     PteMel = c('$\\cdot$ Local -- (late)','$\\cdot$ Local + (early) \n$\\cdot$ Landscape -- (early)',' ',' ','$\\cdot$ Overall + (late)',' '),
+#     ParDis = c(' ',' ','$\\cdot$ Landscape --',' $\\cdot$ Overall -- (late)',' ',' '),
+#     ParMoe = c('$\\cdot$ Local -- \n$\\cdot$ Landscape +','$\\cdot$ Local + (early) \n$\\cdot$ Local -- (late)',' ',' ','$\\cdot$ Landscape +','$\\cdot$ Local + (early) \n$\\cdot$ Local -- (late) \n$\\cdot$ Landscape -- (early) \n$\\cdot$ Landscape + (late)'),
+#     Opilio = c('$\\cdot$ Local -- (early)',' ',' ','$\\cdot$ Local -- (early) \n$\\cdot$ Landscape + (mid)',' ',' ')
+#     )
+# 
+# summaryTab %>%
+#   mutate_all(linebreak) %>%  # required for linebreaks to work
+#   kable(.,format='latex',caption='Summary of model results.
 \\emph{Local/Landscape} denotes cover classes <500m or >500m away from the trap location, respectively.
@@
 Cover classes with weak effects on activity density are not shown.',
-        col.names=linebreak(x=c('Cover class','\\emph{Pterostichus}\n\\emph{melanarius}','\\emph{Pardosa}\n\\emph{distincta}',
-                              '\\emph{Pardosa}\n\\emph{moesta}','\\emph{Phalangium}\n\\emph{opilio}')),
-        align='rllll',escape=FALSE) %>% 
-  column_spec(1, width = "4em") %>% column_spec(c(2:5), width = "9em") # fix column widths
+#         col.names=linebreak(x=c('Cover class','\\emph{Pterostichus}\n\\emph{melanarius}','\\emph{Pardosa}\n\\emph{distincta}',
+#                               '\\emph{Pardosa}\n\\emph{moesta}','\\emph{Phalangium}\n\\emph{opilio}')),
+#         align='rllll',escape=FALSE) %>% 
+#   column_spec(1, width = "4em") %>% column_spec(c(2:5), width = "9em") # fix column widths
+
+##Attempt at synthesis table
+mytable <- data.frame(
+  Species = c(' \\emph{Pterostichus}\n\\emph{melanarius}',' \\emph{Pardosa}\n\\emph{distincta}',
+                              ' \\emph{Pardosa}\n\\emph{moesta}',' \\emph{Phalangium}\n\\emph{opilio}'),
+    Summary = as.character(c('$\\cdot$ Aggregates in canola during early season \n$\\cdot$ Disperses to grassland during late season',
+                '$\\cdot$ Negative effect of pasture \n$\\cdot$ May locally aggregate in field edges',
+                '$\\cdot$ Aggregates in canola during early season \n$\\cdot$ Disperses to road margins and grassland during late season \n$\\cdot$Aggregates in grasslands across the season.',
+                '$\\cdot$ Aggregates to grassland early in the season')),
+    BioControl= as.character(c('High','Low','Medium','Low'))
+    )
+# pander(mytable, keep.line.breaks = TRUE, style = 'grid', justify = 'left', split.table=1000)
+mytable %>% mutate_all(linebreak) %>% 
+  kable(.,format='latex',caption='Synthesis of model results. Bio-control potential is based on likely early-season aggregation to canola crops.',escape=FALSE,
+      col.names=c('Species','Summary','Bio-control potential'),align='lll') %>% 
+  column_spec(2,width='15em')
+
 ```
@@
 
-The activity-density of the four arthropods was influenced by landscape composition, but the response of _Pterostichus melanarius_ and _Phalangium opilio_ was much stronger.
-We found support for our predictions of SNL (grassland, woodlands, and road margins) acting as a late-season sinks for beneficial arthropods.
-In particular, _P. melanarius_ was attracted to grasslands, _P. distincta_ to woodlands, and _P. moesta_ to road margins, all at the end of the season.
-While there was limited evidence of SNL acting as early-season sources, some cover classes had a positive effect at the landscape level (grassland and road margins on _P.
-moesta_), indicating earlier or wider-scale dispersal away from these cover classes.
-Canola and pasture had negative landscape-level effects on _P. melanarius_ and _P. distincta_, respectively, meaning that these cover types likely represent only partial habitat for these arthropods.
+<!-- The activity-density of the four arthropods was influenced by landscape composition, but the response of _Pterostichus melanarius_ and _Phalangium opilio_ was much stronger. -->
+We found support for our predictions of SNL having late-season effects on beneficial arthropods; specifically, grassland had a negative effect on _P.
+melanarius_ activity-density, woodlands on _P.
+distincta_ activity density, and road margins on _P.
+moesta_ activity density, all during late summer (August - September).
+This suggests that these arthropods migrate to these habitats at the end of the summer to prepare for oviposition or overwintering.
+However, _P.
+opilio_ showed no evidence of this, instead showing a negative effect of grassland _early_ in the season, suggesting that a) they aggregate in grasslands or b) grasslands do not constitute suitable habitat for _P.
+opilio_, resulting in low spill-over.
+There was little evidence of SNL acting as early-season sources, aside from road margins having a positive early effect on _P. moesta_ activity-density.
+However, some cover classes had a positive effect at the landscape level (grassland and road margins on _P. moesta_), suggesting earlier or wider-scale dispersal away from these cover classes.
+Canola had a positive effect on _P.
+melanarius_ and _P.
+moesta_ in the early season, suggesting that these organisms aggregate to canola crops and disperse at the end of the season [mass effects _sensu_ @shmida1985].
+Canola also had negative landscape-level effects on _P.
+melanarius_ while pasture had negative effects on _P.
+distincta_, meaning that these cover types likely represent only partial habitat for these arthropods.
+Finally, the influence of landscape composition tended to be limited to a radius of about 500m, indicating that large-scale _and_ local land cover can be important to beneficial arthropod abundance.
 There was also a strong temporal component to most of the landscape effects, meaning that it is important to consider how sinks and sources may change over the season.
-Finally, the influence of landscape composition tended to be limited to a radius of about 500m, indicating that large-scale _and_ local land cover can be important to beneficial arthropod abundance.
-These results highlight the seasonal importance of non-crop marginal lands for predatory arthropod abundance.
 
@@
 The predatory ground beetle _Pterostichus melanarius_ responded to landscape composition, primarily to canola, pulses, and grass and wetland cover.
-Grassland and wetland cover had a negative late-season effect, suggesting that _P. melanarius_ may migrate into it at the end of the summer.
+Grassland and wetland cover had a negative late-season effect, suggesting that _P. melanarius_ migrates into it at the end of the summer.
 Other studies have found similar results, suggesting that untilled land is important off-field habitat for carabids [@desender1988; @fournier2002; but see @hatten2007].
@@
 However, _P. melanarius_ is also found in a wide variety of habitats, and tends to prefer agricultural fields [@larsen2003]. 
-Our models also suggest this, as they showed that canola and pulse crops had positive effects on _P. melanarius_ activity-density early in the season.
+Our models confirmed this, as they showed that canola and pulse crops had positive effects on _P. melanarius_ activity-density early in the season.
 Early in the season, canola crops had a local positive effect, but a landscape-level negative effect, which may indicate that they provide only temporary feeding habitat.
@@
 # Implications
+
+Our work suggests that:
+- Grasslands (and possibly wetlands) act as reservoir habitats
+- The role of _P. melanarius_ and _P. moesta_ as predators in canola crops should be investigated
 

### 2020-10-21 manuscript/manuscript_outline.Rmd
Worked on revisions

@@
 However, it is unclear which types of landscape features constitute useful non-crop habitat, and at what spatial scale organisms gather resources at.
-Additionally, the same landscape feature may act as source of arthropods spill-over at different times of the year, but this is rarely considered.
+Additionally, the same landscape feature may act as source of arthropods spillover at different times of the year, but this is rarely considered.
 We modeled the activity-density of four highly-abundant species of Canadian prairie arthropods, and used functional regression to simultaneously consider both their habitat preferences and the timing of sources and sinks.
@@
 
-Functional regression plots of landscape composition reveal which cover classes are acting as spill-over sources or sinks of a given arthropod, and at what spatial scale.
+Functional regression plots of landscape composition reveal which cover classes are acting as spillover sources or sinks of a given arthropod, and at what spatial scale.
 Positive effects of nearby landscape cover classes indicate that arthropods are spilling over *from* it.
 However, negative responses to nearby landscape cover classes can indicate one of two things:
-1) It may indicate that arthropods are spilling over *into* it (i.e. net sink for spill-over) or 2) it may indicate that no arthropods are available to spill over *from* it.
+1) It may indicate that arthropods are spilling over *into* it (i.e. net sink for spillover) or 2) it may indicate that no arthropods are available to spill over *from* it.
 We consider 1) to be the more likely scenario, as it is unlikely that any one cover class is *completely* unoccupied.
@@
 d) is a functional regression plot over time, showing the effect of pulses at different times of the year.
-Lines and dots represent means, and bars and shaded regions represent 95 % confidence intervals (1.96 x SE).
-Coloured regions represent early-, mid-, and late-season effects (blue = August, purple = July, red = June).
+Lines and dots represent means, and bars and shaded regions represent 95 % confidence regions (1.96 x SE).
+Coloured regions represent early-, mid-, and late-season effects (blue = June, purple = July, red = August).
 
@@
 However, trap location and the temporal random effect (Figure \@ref(fig:ParDisSpatiotemporal)a) explained roughly 10 times more variance ($R^2$: `r round(sum(filter(r2Nakagawa2,model=='ParDisMod',terms=='trapLoc'|grepl('day',terms))$r2comp),3)`) than landscape composition ($R^2$: `r round(sum(filter(r2Nakagawa2,model=='ParDisMod',terms!='trapLoc',terms!='sigmaD',!grepl('s\\(',terms))$r2comp),3)`), meaning that while _P.
-distincta_ may be locally abundant in certain cover types, it is very generalistic in its overall habitat preferences.
+distincta_ may be locally abundant in certain cover types, it is highly general in its overall habitat preferences.
+Additionally, the lack of any effect of canola crops suggests that this species does not aggregate to these crops, suggesting that its ecosystem service potential to farmers is limited.
 
@@
 moesta_ activity density than landscape composition ($R^2$: `r round(sum(filter(r2Nakagawa2,model=='ParMoeMod',terms!='trapLoc',terms!='sigmaD',!grepl('s\\(',terms))$r2comp),3)`), meaning that _P.
-moesta_ is also highly generalistic in its overall habitat preferences.
+moesta_ is also fairly general in its overall habitat preferences.
 
 (ref:ParDisCap) Landscape influence on _Pardosa distincta_ activity-density.
-Lines and dots represent means, and bars and shaded regions represent 95 % confidence intervals (1.96 x SE).
-Coloured regions represent early-, mid-, and late-season effects (blue = August, purple = July, red = June).
+a) shows the effect of local trap location, b) is a functional regression plot of the proportion pasture at distances away from each trap, and c) is a functional regression plot over time, showing the effect of woodland at different times of the year.
+Lines and dots represent means, and bars and shaded regions represent 95 % confidence regions (1.96 x SE).
+Coloured regions represent early-, mid-, and late-season effects (blue = June, purple = July, red = August).
 
@@
 (ref:ParMoeCap) Landscape influence on _Pardosa moesta_ activity-density.
-Lines and dots represent means, and bars and shaded regions represent 95 % confidence intervals (1.96 x SE).
-Coloured regions represent early-, mid-, and late-season effects (blue = August, purple = July, red = June).
+a) shows the effect of local trap location, and b-e) are functional regression plots of the proportion grassland, canola, road margins, and pulses at distances away from each trap.
+Lines and dots represent means, and bars and shaded regions represent 95 % confidence regions (1.96 x SE).
+Coloured regions represent early-, mid-, and late-season effects (blue = June, purple = July, red = August).
 
@@
 (ref:OpilioCap) Landscape influence on _Phalangium opilio_ activity-density.
-Lines and dots represent means, and bars and shaded regions represent 95 % confidence intervals (1.96 x SE).
-Coloured regions represent early-, mid-, and late-season effects (blue = August, purple = July, red = June).
+a) shows the effect of local trap location, and b-c) are functional regression plots of the proportion grassland and woodland at distances away from each trap.
+Lines and dots represent means, and bars and shaded regions represent 95 % confidence regions (1.96 x SE).
+Coloured regions represent early-, mid-, and late-season effects (blue = June, purple = July, red = August).
+__SHOULD WE TAKE OUT THE MID (PURPLE) TIME SEQUENCE, IN THE INTEREST OF READABLILITY?
+THIS WOULD WORK FINE FOR ALL OTHER FIGURES, EXCEPT FOR c OF THIS ONE.__
 
@@
 opilio_ showed no evidence of this, instead showing a negative effect of grassland _early_ in the season, suggesting that a) they aggregate in grasslands or b) grasslands do not constitute suitable habitat for _P.
-opilio_, resulting in low spill-over.
+opilio_, resulting in low spillover.
 There was little evidence of SNL acting as early-season sources, aside from road margins having a positive early effect on _P. moesta_ activity-density.
@@
 @moring1994 showed that _P.
-distincta_ were more active in grassy habitats, which we found partial evidence of, as _P.
+distincta_ were active in grassy habitats, which we found partial evidence of, as _P.
 distincta_ tended to have higher activity-density in trap locations with higher grass cover (Figure \@ref(fig:ParDisLandscape)a).
@@
 moesta_ and attract them away from other cover types.
-Lycosids employ a wandering-active predation strategy [@young1990], meaning that nearby landscape composition may be more influential to _Pardosa_ than large-scale composition [@oberg2007; @oberg2008].
+Wolf spiders (Lycosidae) employ a wandering-active predation strategy [@young1990], meaning that nearby landscape composition may be more influential to _Pardosa_ than large-scale composition [@oberg2007; @oberg2008].
 While trapping location explained a large proportion of variance for both species (`r round(filter(r2Nakagawa2,model=='ParDisMod',grepl('trapLoc',terms))$r2comp,2)` and `r round(filter(r2Nakagawa2,model=='ParMoeMod',grepl('trapLoc',terms))$r2comp,2)`), several landscape features were also important at large spatial scales, including grass and wetland, pasture, pulses, and road margins.
@@
 
-# Implications
+# Applications
 
-Our work suggests that:
-- Grasslands (and possibly wetlands) act as reservoir habitats
-- The role of _P. melanarius_ and _P. moesta_ as predators in canola crops should be investigated
+Our work has three main applications.
+First, it adds to the basis of scientific evidence showing that SNL can act as reservoir habitats in intensely-managed agroecosystems.
+Based on our findings, farmers and land managers should consider preserving existing grassland and wetland habitat to act as a background source of pest-control in crop fields.
+While local habitat appears valuable, even landscape-level habitat can be valuable, as it can increase the number of beneficial arthropods at larger spatial scales (e.g.
+Figures \@ref(fig:PteMelLandscape), \@ref(fig:ParMoeLandscape)).
+Secondly, our work suggests that _P. melanarius_ and _P. moesta_ should be investigated for their role as predators in canola crops.
+They appear to aggregate in canola crops early in the season, meaning that they have the potential to provide valuable pest-control services to growers.
+Finally, we demonstrate that timing and spatial scale of spillover should be considered in future landscape studies of ecosystem services.
+We show important differences in the timing of landscape effects on activity-density (early-season vs.
+late-season spillover) that are typically ignored, but should be considered when assessing how SNL can deliver ecosystem services.
 
@@
 
-```{r concurvity, echo=FALSE, fig.cap='Concurvity estimates for reduced cover classes used in models', out.width='100%'}  
+```{r concurvity, echo=FALSE, fig.cap='Concurvity estimates for reduced cover classes used in models.', out.width='100%'}  
   include_graphics('../figures/coverCorPlots/concurvityEstimate_reduced.png',dpi=NA)
@@
 (ref:PteMelSTCap) Temporal and spatial components of _Pterostichus melanarius_ activity-density (after accounting for landscape composition and trap location).
+a) shows the effect of day of year, and b) shows the spatially smoothed effect of site location.
 
@@
 (ref:ParDisSTCap) Temporal and spatial components of _Pardosa distincta_ activity-density (after accounting for landscape composition and trap location).
+a) shows the effect of day of year, and b) shows the spatially smoothed effect of site location.
 
@@
 (ref:ParMoeSTCap) Temporal and spatial components of _Pardosa moesta_ activity-density (after accounting for landscape composition and trap location).
+a) shows the effect of day of year, and b) shows the spatially smoothed effect of site location.
 
@@
 (ref:OpilioSTCap) Temporal and spatial components of _Phalangium opilio_ activity-density (after accounting for landscape composition and trap location).
+a) shows the effect of day of year, and b) shows the spatially smoothed effect of site location.
 
@@
 pmelLinTerms %>% select(-p) %>% 
-  kable(.,caption='Trap location effects for \\emph{Pterostichus melanarius}',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
+  kable(.,caption='Trap location (cover type that trap was located in) intercept estimates for \\emph{Pterostichus melanarius}',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
       digits=c(1,2,2,2,2),align='rrrrl',escape=FALSE)
@@
 pdisLinTerms %>% select(-p) %>% 
-  kable(.,caption='Trap location effects for \\emph{Pardosa distincta}',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
+  kable(.,caption='Trap location (cover type that trap was located in) intercept estimates for \\emph{Pardosa distincta}',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
         digits=c(1,2,2,2,2),align='rrrrl',escape=FALSE)
@@
 pmoeLinTerms %>% select(-p) %>% 
-  kable(.,caption='Trap location effects for \\emph{Pardosa moesta}.',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
+  kable(.,caption='Trap location (cover type that trap was located in) intercept estimates for \\emph{Pardosa moesta}.',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
         digits=c(1,2,2,2,2),align='rrrrl',escape=FALSE)
@@
 opilLinTerms %>% select(-p) %>% 
-  kable(.,caption='Trap location effects for \\emph{Phalangium opilio}',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
+  kable(.,caption='Trap location (cover type that trap was located in) intercept estimates for \\emph{Phalangium opilio}',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
         digits=c(1,2,2,2,2),align='rrrrl',escape=FALSE)

### 2020-10-21 manuscript/manuscript.Rmd
Finished revisions round 1

--- 2020-10-21 manuscript/manuscript_outline.Rmd
@@
 At each site, we extracted the proportion of each cover class within 30m annuli (rings), with the inner radius of each annulus ranging from 30 to 1470m in increments of 30m (total of 49 annuli, 1.5 km maximum).
-The ten most-common cover classes surrounding our sites represented 98% of the total land cover in our study region: grassland, cereal, canola, pasture, pulses, wetland, urban (road margins), shrubland, flax, and forest (Figure \@ref(fig:landscapeComp)); flax was removed, as only a single site had nearby flax cover.
+The ten most-common cover classes surrounding our sites represented 98% of the total land cover in our study region: grassland, cereal, canola, pasture, pulses, wetland, urban (road margins), shrubland, flax, and forests (Figure \@ref(fig:landscapeComp)); flax was removed, as only a single site had nearby flax cover.
 
@@
 The deviance residuals from each model were visually inspected for normality and equal variance [@hilbe2011; @wood2017].
-Finally, we calculated the R$^2$ for each group of terms [@nakagawa2013; @nakagawa2017].
+Finally, we calculated the proportion of explained variance (R$^2$) for each set of terms [@nakagawa2013; @nakagawa2017].
 
@@
 <!-- Some landscape terms were strongly concurved , namely forest and shrubland (max: 0.71), canola and cereal (max: 0.74), and grassland and wetland (max: 0.63). -->
-Trees and shrubs were combined into a single ``woodland" category, and grassland and wetland were combined into a single "grassland" category, as they were strongly positively correlated at all distances, indicating similar feature classes.
+Forests and shrubland were combined into a single ``woodland" category, and grassland and wetland were combined into a single "grassland" category, as they were strongly positively correlated at all distances, indicating similar feature classes.
 Cereal was removed from the model, as it was negatively correlated with canola cover at distances less than 200m and was positively correlated at distances over 500m, reflecting the most common crop rotations (canola $\rightarrow$ wheat $\rightarrow$ barley) and the commonly-used 800 m block structure of farmland in our study region (quarter-sections).
@@
 Canola crops had a marginally higher activity-density of _P. melanarius_ than other trap locations (Figure \@ref(fig:PteMelLandscape)a).
-Grassland cover was the most important land cover type in explaining activity-density ($R^2$: 0.104, Table \@ref(tab:rSquared)), and local (<500 m) grassland had a negative effect late in the summer (Figure \@ref(fig:PteMelLandscape)b), suggesting that _P.
+Grassland cover was the most important land cover type in explaining activity-density ($R^2$: 0.104, Table \@ref(tab:rSquared)), and local grassland had a negative effect late in the summer (Figure \@ref(fig:PteMelLandscape)b), suggesting that _P.
 melanarius_ may move into grasslands later in the year.
-Local canola had a positive effect in the early season, but landscape-level (>500 m) canola had a negative effect, indicating that areas with widespread canola coverage had lower _P.
-melanarius_ activity-density.
-Pulses acted as a late-season source, indicating that _P. melanarius_ may migrate out of the crop after (or during) harvest.
+Local canola had a positive effect in the early season, but landscape-level canola had a negative effect, indicating that areas with widespread canola coverage had lower _P.
+melanarius_ activity-density (Figure \@ref(fig:PteMelLandscape)c).
+Pulses acted as a late-season source, indicating that _P. melanarius_ may migrate out of the crop after (or during) harvest (Figure \@ref(fig:PteMelLandscape)d).
 Finally, _P.
-melanarius_ activity-density had a strong temporal and spatial component (both p<0.001), indicating that phenology and local geographic factors were important drivers of ground beetle activity-density (Figure \@ref(fig:PteMelSpatiotemporal)).
+melanarius_ activity-density had a strong temporal and spatial component (both p `r with(pmelSmTerms,p[Smoother=='s(E,N)'])`), indicating that phenology and local geographic factors were important drivers of ground beetle activity-density (Figure \@ref(fig:PteMelSpatiotemporal)).
 Landscape composition and trap location explained `r r2Nakagawa$PteMelMod[1]*100`% of the variance in activity-density, while the spatial and temporal smoothers accounted for `r with(r2Nakagawa,(PteMelMod[2]-PteMelMod[1])*100)`% (Table \@ref(tab:rSquared)).
@@
 distincta_ and _P.
-moesta_ was influenced by trap location and landscape composition (Tables \@ref(tab:ParDisLinear), \@ref(tab:ParDisSmooth)), but landscape composition had relatively weak effects on both species ($R^2$: `r filter(r2Nakagawa2,grepl('Par',model),!grepl('s\\(',terms),terms!='trapLoc',terms!='sigmaD') %>% group_by(model) %>% summarize(s=sum(r2comp)) %>% pull(s) %>% paste(.,collapse=', ')`).
+moesta_ was influenced by trap location and landscape composition (Tables \@ref(tab:ParDisLinear), \@ref(tab:ParDisSmooth), \@ref(tab:ParMoeLinear), \@ref(tab:ParMoeSmooth)), but landscape composition had relatively weak effects on both species ($R^2$: `r filter(r2Nakagawa2,grepl('Par',model),!grepl('s\\(',terms),terms!='trapLoc',terms!='sigmaD') %>% group_by(model) %>% summarize(s=sum(r2comp)) %>% pull(s) %>% paste(.,collapse=', ')`).
 Unlike _P. melanarius_, both _Pardosa_ species had far lower activity-density in canola than any other cover type (Figures \@ref(fig:ParDisLandscape)a, \@ref(fig:ParMoeLandscape)a).
@@
 _P.
-distincta_ activity density responded to pasture and woodlands; landscape-level pasture cover had a negative effect (Figure \@ref(fig:ParDisLandscape)b), while woodlands had a negative effect late in the season (Figure \@ref(fig:ParDisLandscape)c).
-This suggests that large amounts of pasture are unsuitable habitat for _P. distincta_, and that they may migrate into woodlands later in the season.
-However, trap location and the temporal random effect (Figure \@ref(fig:ParDisSpatiotemporal)a) explained roughly 10 times more variance ($R^2$: `r round(sum(filter(r2Nakagawa2,model=='ParDisMod',terms=='trapLoc'|grepl('day',terms))$r2comp),3)`) than landscape composition ($R^2$: `r round(sum(filter(r2Nakagawa2,model=='ParDisMod',terms!='trapLoc',terms!='sigmaD',!grepl('s\\(',terms))$r2comp),3)`), meaning that while _P.
+distincta_ activity density was negatively affected by landscape-level pasture (Figure \@ref(fig:ParDisLandscape)b), while woodlands had a negative effect late in the season (Figure \@ref(fig:ParDisLandscape)c).
+This suggests that large amounts of pasture are unsuitable habitat for _P. distincta_, and that they migrate into woodlands later in the season.
+However, trap location and the temporal random effect (Figure \@ref(fig:ParDisSpatiotemporal)a) explained roughly 10 times more variance than landscape composition ($R^2$: `r round(sum(filter(r2Nakagawa2,model=='ParDisMod',terms=='trapLoc'|grepl('day',terms))$r2comp),3)` versus `r round(sum(filter(r2Nakagawa2,model=='ParDisMod',terms!='trapLoc',terms!='sigmaD',!grepl('s\\(',terms))$r2comp),3)`), meaning that while _P.
 distincta_ may be locally abundant in certain cover types, it is highly general in its overall habitat preferences.
-Additionally, the lack of any effect of canola crops suggests that this species does not aggregate to these crops, suggesting that its ecosystem service potential to farmers is limited.
+<!-- The weak effect of canola crops (p>0.07) suggests that this species does not aggregate into these crops, meaning that its ecosystem service potential to farmers is limited. -->
 
@@
 Grasslands had a local negative effect, but a positive landscape-level effect, indicating that while these cover types act as a local sink, the general amount of grassland in the area had a positive effect (Figure \@ref(fig:ParMoeLandscape)b).
-Nearby local canola had a positive early effect on activity-density, but a negative local effect later in the season (Figure \@ref(fig:ParMoeLandscape)c).
-Local road margins had a similar effect, acting as an early source and a late sink (Figure \@ref(fig:ParMoeLandscape)d).
+Local canola cover had a positive early effect on activity-density, but a negative local effect later in the season (Figure \@ref(fig:ParMoeLandscape)c).
+Local road margins also had a similar effect, acting as an early source and a late sink (Figure \@ref(fig:ParMoeLandscape)d).
 Pulses also had a positive effect at the landscape level (Figure \@ref(fig:ParMoeLandscape)e), but this explained very little variance in _P.
 moesta_ activity density (Table \@ref(tab:rSquared), $R^2$: `r round(filter(r2Nakagawa2,model=="ParMoeMod",terms=="Pulses")$r2comp,3)`).
-Similar to _P.distincta_, trap location and an East-West spatial random effect (Figure \@ref(fig:ParMoeSpatiotemporal)b) explained roughly 5 times more variance ($R^2$: `r round(sum(filter(r2Nakagawa2,model=='ParMoeMod',terms=='trapLoc'|grepl('E,N',terms))$r2comp),3)`) in _P.
-moesta_ activity density than landscape composition ($R^2$: `r round(sum(filter(r2Nakagawa2,model=='ParMoeMod',terms!='trapLoc',terms!='sigmaD',!grepl('s\\(',terms))$r2comp),3)`), meaning that _P.
-moesta_ is also fairly general in its overall habitat preferences.
+Similar to _P.distincta_, trap location and an East-West spatial random effect (Figure \@ref(fig:ParMoeSpatiotemporal)b) explained roughly 5 times more variance in _P.
+moesta_ activity density than landscape composition ($R^2$: `r round(sum(filter(r2Nakagawa2,model=='ParMoeMod',terms=='trapLoc'|grepl('E,N',terms))$r2comp),3)` versus `r round(sum(filter(r2Nakagawa2,model=='ParMoeMod',terms!='trapLoc',terms!='sigmaD',!grepl('s\\(',terms))$r2comp),3)`), meaning that _P.
+moesta_ is also fairly general in its overall habitat preferences, and is influenced more heavily by larger-scale abiotic factors.
 
@@
 Pasture had a negative effect at the landscape scale, and woodland had a late-season negative effect, suggesting that _P.
-distincta_ move to shrubs and trees for overwintering or winter foraging [@aitchison1984; @buddle2000].
+distincta_ move to woodlands for overwintering or winter foraging [@aitchison1984; @buddle2000].
 _Pardosa_ are found in areas close to disturbed roadside strips [@drapela2008; @drapela2011; @kowal2011], but _P.
@@
 
-_Phalangium opilio_ activity-density responded to grass and wetland cover, as well as trees and shrubs.
+_Phalangium opilio_ activity-density responded to grass and wetland cover, as well as wooded landscapes.
 Other studies have found that _P. opilio_ is mostly found in human-altered landscapes with a large proportion of farming [@muster2014; @vandepoel2015Msc].

### 2020-11-04 manuscript/manuscript.Rmd
Worked on 2nd round of revisions

@@
   - name: Diane Edwards
-    email: diane.edwards.ca@gmail.com
+    email: diane@abienvironmental.ca
     affiliation: Ambrose University
@@
   - code: University of Calgary
-    address: 2500 University Drive NW, Calgary, AB, Canada
+    address: 2500 University Drive NW, Calgary, AB
   - code: Ambrose University
@@
   - code: Oregon State University
-    address: 1500 SW Jefferson Way, Corvallis, OR, USA
+    address: 1500 SW Jefferson Way, Corvallis, OR
 footnote:
@@
 # Introduction
+<!-- DE: BIOCONTROL THEME NEEDS SET-UP IN INTRODUCTION -->
+
 Arthropods are one of the most influential groups of animals in agricultural systems.
@@
 Finding "win-win" practices is of particular importance to land managers and conservationists; that is, practices that result in better conservation outcomes while maintaining or improving crop yields.
-Finally, agricultural land occupies 15 million km$^2$ (~36%) of land globally [@ramankutty2018], suggesting that there remains great potential to achieve conservation outcomes by adjusting agricultural practices.
+<!-- Finally, agricultural land occupies 15 million km$^2$ (~36%) of land globally [@ramankutty2018], suggesting that there remains great potential to achieve conservation outcomes by adjusting agricultural practices.
+-->
 
@@
 For example, carabid beetles are thought to reproduce in field margins, while the adults feed in fields [@desender1988].
-This depends on the life history of the organisms in question, such as the seasonal timing of emergence, feeding, and reproduction, as well as their traits such as dispersal capability.
+Habitat preference also depends on the life history of the organisms in question, such as the seasonal timing of emergence, feeding, and reproduction, as well as their traits such as dispersal capability.
 Non-adjacent cropland can also influence arthropod abundance if the organisms are long-distance dispersers [@oberg2008].
@@
 
-In this study, we used pitfall traps to determine how landscape composition affects the seasonal activity-density of arthropods across a large Canadian prairie agroecosystem.
+In this study, we used pitfall traps to determine how landscape composition affects the seasonal abundance of arthropods across a large Canadian prairie agroecosystem.
 We considered the following hypotheses:
@@
 Traps in canola were installed at 25, 75, and 200 m along a transect heading away from the nearest non-crop feature (wetland, grassy field edges, or remnant prairie), while the trap at 0 m was installed in the non-crop feature itself.
-We used 582 mL Solo® cups buried up to the rim and partially filled with ethylene glycol, with 2 cm wire mesh mounted over the rim to prevent vertebrates from falling into the traps.
+We used 582 mL Solo® cups buried up to the rim and partially filled with propylene glycol, with 2 cm wire mesh mounted over the rim to prevent vertebrates from falling into the traps.
 Specimens were identified to species using appropriate taxonomic literature [@dondale1990; @edgar1990; @vogel2004; @yigit2007].
@@
 This makes it impossible to disentangle arthropod activity from density using single traps [@lang2000; @zhao2013], meaning that counts in the traps represent the "activity-density" of a given organism.
-Despite this disadvantage, activity-density is generally positively related to ecosystem services, at least in carabids [@trichard2014; @boetzl2018; @gonzalez2020], making it acceptable for our study.
+Despite this drawback, activity-density is generally positively related to ecosystem services, at least in carabids [@trichard2014; @boetzl2018; @gonzalez2020], making it acceptable for our study.
 
-```{r siteMap, echo=FALSE, fig.cap='Location of pitfall traps during 2017, and classified cover f.
+```{r siteMap, echo=FALSE, fig.cap='Location of pitfall traps during 2017, and classified land cover.
 Inset map shows study location within Alberta.
@@
 
-We used four highly-abundant species of predatory arthropods found in the pitfall traps, as common species are often more important for ecosystem service provision than rare species [@winfree2015], but their habitat preferences are still poorly understood.
+We used four highly-abundant species of predatory arthropods found in the pitfall traps, as common species are often more important for ecosystem service provision than rare species [@winfree2015].
 _Pterostichus melanarius_ is an introduced predatory ground beetle (Coleoptera: Carabidae) that is a wide-ranging generalist known to prey upon crop pests [@carcamo1994; @larsen2003; @busch_Msc].
 It is commonly found in untilled grasslands [@purtauf2005] and may use grassy field edges as larval habitat [@desender1988].
-_Pardosa_ are wolf spiders (Araneae: Lycosidae) that use an active wandering predation strategy [@young1990], and are common across the Canadian prairies.
+_Pardosa_ are a genus of wolf spiders (Araneae: Lycosidae) that use an active wandering predation strategy [@young1990], and are common across the Canadian prairies.
 Both _Pardosa distincta_ and _Pardosa moesta_ are found in a wide variety of habitats, but are common in ungrazed pastures [@dondale1990; @carcamo2014].
@@
 Other _Pardosa_ are known to use road margins and wooded areas as habitat [@buddle2000; @drapela2011].
-Finally, _Phallangium opilio_ is an introduced harvestman (Opiliones: Phalangiidae) that is found in drier disturbed areas [@bragg2009].
+Finally, _Phalangium opilio_ is an introduced harvestman (Opiliones: Phalangiidae) that is found in drier disturbed areas [@bragg2009].
 Juveniles hatch from eggs during the spring, becoming adults during the summer, and eggs are laid during the fall [adults do not overwinter; @bragg2009].
@@
 This allows for the possibility that the size of the landscape "grain" relevant to a given organism may change over the course of its life stages [@addicott1987; @lima1996; @gardiner2010].
-It also allows for the possibility that certain land cover types may be locally beneficial, but detremental at wider scales, indicating that the cover type may not constitute a completely usable habitat.
+It also allows for the possibility that certain land cover types may be locally beneficial, but detremental at large scales, indicating that the cover type may not constitute a completely usable habitat.
 
@@
 First, we used the proportion cover in the annuli surrounding each trap location (spatial effect of cover class).
-Second, we used the average landcover in all annuli across days of the year (temporal effect of cover class). 
+Second, we used the average proportion cover across days of the year (temporal effect of cover class). 
 Finally, we used a tensor-product interaction of landscape cover and day of year (spatio-temporal interaction of cover class).
 We used 10 basis dimensions for the spatial and temporal landscape smoothers, and 16 basis dimensions for the spatio-temporal interaction.
-This was deemed adequate, as the effective degrees of freedom for all smoothing terms were far below the number of basis dimensions, indicating that no additional basis dimensions were needed (see Tables \@ref(tab:PteMelSmooth), \@ref(tab:ParDisSmooth), \@ref(tab:ParMoeSmooth), \@ref(tab:OpilioSmooth)).
+The effective degrees of freedom for all smoothing terms were far below the number of basis dimensions, indicating that no additional basis dimensions were needed (see Tables \@ref(tab:PteMelSmooth), \@ref(tab:ParDisSmooth), \@ref(tab:ParMoeSmooth), \@ref(tab:OpilioSmooth)).
 To remove unimportant terms from the model, we used thin-plate regression splines with shrinkage, a continuous analog to stepwise model selection where weaker terms are completely removed from the model rather than reduced to a line [@marra2011].
@@
 Therefore, the interpretation of a functional regression plot is very different from that of a simple linear regression plot.
-Figure \@ref(fig:frExample)a shows a simple linear regression plot of a hypothetical relationship between trap _activity density_ (_y_) and a single predictor, _Proportion cover_ (_x_), which is measured in a circle of a fixed radius (_Distance_) surrounding each trap.
+Figure \@ref(fig:frExample)a shows a simple linear regression plot of a hypothetical relationship between trap _activity-density_ (_y_) and a single predictor, _Proportion cover_ (_x_), which is measured in a circle of a fixed radius (_Distance_) surrounding each trap.
 If we suppose that the relationship between _x_ and _y_ is similar at all radii at which _x_ is measured, then Figure \@ref(fig:frExample)b shows the resulting functional linear regression plot, where the slope ($\beta$) is the same at all distances.
-In reality it is more likely that nearby cover will be more influential on activity density than far-away cover, which would result in a relationship similar to Figure \@ref(fig:frExample)c.
+In reality it is more likely that nearby cover will be more influential on activity-density than far-away cover, which would result in a relationship similar to Figure \@ref(fig:frExample)c.
 As functional regression takes any continuous predictor of _y_, it is also possible to use proportion cover (measured within a fixed radius) as a predictor of measurements taken across time, allowing the effect of proportion cover to vary over the course of the season (Figure \@ref(fig:frExample)d).
-Finally, proportion cover over distance and time may be combined into a smoothed surface of effects, representing the spatio-temporal influence of landscape cover on activity density.
+Finally, proportion cover over distance and time may be combined into a smoothed surface of effects, representing the spatio-temporal influence of landscape cover on activity-density.
 
@@
 Alternatively, a cover class could act as a sink by providing high-quality habitat at certain times of the year (e.g. egg laying/feeding), but act as a source at other times (e.g. during emergence).
-For brevity in the following Results section, we refer to local- and landscape-level effects, where local indicates the effects of landscape composition at scales of <500m, whereas landscape indicates scales >500 m.
-Similarly, we refer to early-, mid-, and late-season effects, where landscape composition affected abundance from June - July, July - August, or August - September, respectively.
+In the Results section, we refer to local- and landscape-level effects, where local indicates the effects of landscape composition at scales of <500 m, whereas landscape indicates scales >500 m.
+Similarly, we refer to early- and late-season effects, where landscape composition affected activity-density on June 20th or August 20th, respectively.
 
@@
 Lines and dots represent means, and bars and shaded regions represent 95 % confidence regions (1.96 x SE).
-Coloured regions represent early-, mid-, and late-season effects (blue = June, purple = July, red = August).
+Coloured regions represent early- and late-season effects (blue = June, red = August).
 
@@
 
-Activity density of _P.
+Activity-density of _P.
 distincta_ and _P.
@@
 _P.
-distincta_ activity density was negatively affected by landscape-level pasture (Figure \@ref(fig:ParDisLandscape)b), while woodlands had a negative effect late in the season (Figure \@ref(fig:ParDisLandscape)c).
+distincta_ activity-density was negatively affected by landscape-level pasture (Figure \@ref(fig:ParDisLandscape)b), while woodlands had a negative effect late in the season (Figure \@ref(fig:ParDisLandscape)c).
 This suggests that large amounts of pasture are unsuitable habitat for _P. distincta_, and that they migrate into woodlands later in the season.
@@
 
-_P. moesta_ activity density responded to grassland, canola, and road margins.
+_P. moesta_ activity-density responded to grassland, canola, and road margins.
 Grasslands had a local negative effect, but a positive landscape-level effect, indicating that while these cover types act as a local sink, the general amount of grassland in the area had a positive effect (Figure \@ref(fig:ParMoeLandscape)b).
@@
 Pulses also had a positive effect at the landscape level (Figure \@ref(fig:ParMoeLandscape)e), but this explained very little variance in _P.
-moesta_ activity density (Table \@ref(tab:rSquared), $R^2$: `r round(filter(r2Nakagawa2,model=="ParMoeMod",terms=="Pulses")$r2comp,3)`).
+moesta_ activity-density (Table \@ref(tab:rSquared), $R^2$: `r round(filter(r2Nakagawa2,model=="ParMoeMod",terms=="Pulses")$r2comp,3)`).
 Similar to _P.distincta_, trap location and an East-West spatial random effect (Figure \@ref(fig:ParMoeSpatiotemporal)b) explained roughly 5 times more variance in _P.
-moesta_ activity density than landscape composition ($R^2$: `r round(sum(filter(r2Nakagawa2,model=='ParMoeMod',terms=='trapLoc'|grepl('E,N',terms))$r2comp),3)` versus `r round(sum(filter(r2Nakagawa2,model=='ParMoeMod',terms!='trapLoc',terms!='sigmaD',!grepl('s\\(',terms))$r2comp),3)`), meaning that _P.
+moesta_ activity-density than landscape composition ($R^2$: `r round(sum(filter(r2Nakagawa2,model=='ParMoeMod',terms=='trapLoc'|grepl('E,N',terms))$r2comp),3)` versus `r round(sum(filter(r2Nakagawa2,model=='ParMoeMod',terms!='trapLoc',terms!='sigmaD',!grepl('s\\(',terms))$r2comp),3)`), meaning that _P.
 moesta_ is also fairly general in its overall habitat preferences, and is influenced more heavily by larger-scale abiotic factors.
@@
 Lines and dots represent means, and bars and shaded regions represent 95 % confidence regions (1.96 x SE).
-Coloured regions represent early-, mid-, and late-season effects (blue = June, purple = July, red = August).
 
@@
 opilio_ activity-density was somewhat influenced by trap location, with field edges and wetlands having the highest activity-density (Figure \@ref(fig:OpilioLandscape)a), but this effect was swamped by the effect of landscape and the spatiotemporal random effects (Table \@ref(tab:rSquared)), meaning that _P.
-opilio_ activity density is only mildly influenced by local cover type.
+opilio_ activity-density is only mildly influenced by local cover type.
 Nearby grassland and woodland both had negative effects on _Phalangium opilio_ activity-density, but only early in the season (Figures \@ref(fig:OpilioLandscape)b,c), suggesting that _P.
@@
 Lines and dots represent means, and bars and shaded regions represent 95 % confidence regions (1.96 x SE).
-Coloured regions represent early-, mid-, and late-season effects (blue = June, purple = July, red = August).
-__SHOULD WE TAKE OUT THE MID (PURPLE) TIME SEQUENCE, IN THE INTEREST OF READABLILITY?
-THIS WOULD WORK FINE FOR ALL OTHER FIGURES, EXCEPT FOR c OF THIS ONE.__
+Coloured regions represent early- and late-season effects (blue = June, red = August).
 
@@
 +/-- indicates positive or negative effects of the cover class, and \\emph{Early/Mid/Late} denotes whether the effects were present earlier or later during the season.
-Cover classes with weak effects on activity density are not shown.',
+Cover classes with weak effects on activity-density are not shown.',
 #         col.names=linebreak(x=c('Cover class','\\emph{Pterostichus}\n\\emph{melanarius}','\\emph{Pardosa}\n\\emph{distincta}',
@@
 <!-- The activity-density of the four arthropods was influenced by landscape composition, but the response of _Pterostichus melanarius_ and _Phalangium opilio_ was much stronger. -->
-We found support for our predictions of SNL having late-season effects on beneficial arthropods; specifically, grassland had a negative effect on _P.
+Our prediction of SNL having late-season effects on beneficial arthropods was supported; specifically, grassland had a negative effect on _P.
 melanarius_ activity-density, woodlands on _P.
-distincta_ activity density, and road margins on _P.
-moesta_ activity density, all during late summer (August - September).
+distincta_ activity-density, and road margins on _P.
+moesta_ activity-density, all during late summer (August - September).
 This suggests that these arthropods migrate to these habitats at the end of the summer to prepare for oviposition or overwintering.
@@
 There was little evidence of SNL acting as early-season sources, aside from road margins having a positive early effect on _P. moesta_ activity-density.
-However, some cover classes had a positive effect at the landscape level (grassland and road margins on _P. moesta_), suggesting earlier or wider-scale dispersal away from these cover classes.
+However, some cover classes had a positive effect at the landscape level (grassland and road margins on _P. moesta_), suggesting earlier or larger-scale dispersal away from these cover classes.
 Canola had a positive effect on _P.
@@
 opilio_ and _P.
-moesta_, meaning that wider-scale geographic patterns (possibly related to rainfall or temperature) also influence their activity-density.
+moesta_, meaning that larger-scale geographic patterns (possibly related to rainfall or temperature) also influence their activity-density.
 <!-- Feels like this paragraph ends too soon. Why was there so little variation due to landscape? Link to biology of the critter. -->
@@
 First, it adds to the basis of scientific evidence showing that SNL can act as reservoir habitats in intensely-managed agroecosystems.
-Based on our findings, farmers and land managers should consider preserving existing grassland and wetland habitat to act as a background source of pest-control in crop fields.
+Based on our findings, farmers and land managers should consider preserving existing grassland and wetland habitat to act as a background source of arthropods for pest-control in crops.
 While local habitat appears valuable, even landscape-level habitat can be valuable, as it can increase the number of beneficial arthropods at larger spatial scales (e.g.

### 2020-11-04 frAnalysis.R

@@ -66,7 +66,7 @@ stLegPosX <- 0.85 #Legend position X
 stLegPosY <- 0.3 #Legend position Y
 theme_set(theme_classic()) #Classic theme
 maptheme <- theme(panel.border=element_rect(size=1,fill=NA),axis.line=element_blank()) #Better theme for maps
-smoothCols <- c('blue','purple','red') #Colours for smoothing lines
+smoothCols <- c('blue','red') #Colours for smoothing lines
 
 # Pterostichus melanarius ----------------------------------
 
@@ -101,7 +101,7 @@ tempTrap %>% mutate(resid=resid(mod3)) %>%
   as_Spatial() %>% variogram(resid~1,.) %>% plot()
 
 #Check k values and residual distribution
-par(mfrow=c(2,2)); gam.check(mod3); par(mfrow=c(1,1))
+par(mfrow=c(2,2)); gam.check(mod3); abline(0,1,col='red'); par(mfrow=c(1,1)); 
 plot(mod3,scheme=2,shade=T,pages=1,all.terms=T,rug=F,seWithMean=T)
 
 #Check for concurvity between smoothers
@@ -179,8 +179,9 @@ ggsave('./figures/Pterostichus_melanarius_raneff.png',raneffPlot,width=stFigX,he
 #Plot significant landscape effects
 
 #Days to display on plots (early,mid,late)
-dispDays <- data.frame(doy=c(173,203,232)) %>% #June 20, July 20, Aug 20 (Actually June/July 22, but close enough...)
-  mutate(date=c('Early','Mid','Late')) 
+# c(173,203,232) = June 20, July 20, Aug 20 (Actually June/July 22, but close enough...)
+dispDays <- data.frame(doy=c(173,232)) %>% 
+  mutate(date=c('Early','Late')) 
 
 #Get order of terms to plot
 cbind(1:length(mod3$smooth),sapply(mod3$smooth,function(x) x$label))
@@ -195,18 +196,18 @@ p1 <- data.frame(trapLoc=tempTrap$trapLoc,pred=predict(mod3,type='terms',terms='
   labs(x='Trap location',y='Activity')
 
 #Grass/wetland effect (space + time)
-p2 <- expand.grid(endDayMat=c(173,203,232),distMat=seq(30,1500,30),GrassWetland=1) %>% 
[…]

### 2020-11-04 frPlotDemo.R

@@ -55,7 +55,7 @@ p2 <- apply(mapply(lineFun,int=rnorm(1000,0.5,0.1),slope=rnorm(1000,0,0.1),MoreA
   annotate('text',x=500,y=-0.75,label='Effect of cover is positive at all distances')+
   annotate('segment',x=400,xend=300,y=-0.5,yend=0.2,arrow=arrow())+
   annotate('segment',x=600,xend=700,y=-0.5,yend=0.2,arrow=arrow())+
-  labs(x='Distance',y=expression(paste('Slope of proportion cover (',beta,')')))+ylim(-1.5,1.5)
+  labs(x='Distance from sampling location',y=expression(paste('Slope of proportion cover (',beta,')')))+ylim(-1.5,1.5)
 
 #Exponential
 p3 <- apply(mapply(expFun,a=rnorm(1000,1,0.2),b=rnorm(1000,0.05,0.002),d=rnorm(1000,-0.02,0.1),MoreArgs=list(n=1000)),
@@ -68,7 +68,7 @@ p3 <- apply(mapply(expFun,a=rnorm(1000,1,0.2),b=rnorm(1000,0.05,0.002),d=rnorm(1
   annotate('segment',x=350,xend=100,y=1,yend=0.6,arrow=arrow())+
   annotate('text',x=500,y=-0.75,label='Neutral effect of far-away cover')+
   annotate('segment',x=600,xend=600,y=-0.5,yend=-0.2,arrow=arrow())+
-  labs(x='Distance',y=expression(paste('Slope of proportion cover (',beta,')')))+ylim(-1.5,1.5)
+  labs(x='Distance from sampling location',y=expression(paste('Slope of proportion cover (',beta,')')))+ylim(-1.5,1.5)
 
 #Negatively sloped line
 p4 <- apply(mapply(lineFun,int=rnorm(1000,0,0.1),slope=rnorm(1000,-0.5,0.1),MoreArgs=list(n=1000)),

### 2020-11-04 manuscript/manuscript.Rmd
Revisions round 2

@@
 date: "Spring 2020"
-abstract: "Ground-dwelling arthropods are important generalist predators in agro-ecosystems, and can use non-crop features as overwintering habitats.
-However, it is unclear which types of landscape features constitute useful non-crop habitat, and at what spatial scale organisms gather resources at.
-Additionally, the same landscape feature may act as source of arthropods spillover at different times of the year, but this is rarely considered.
+abstract: "Ground-dwelling arthropods can be important generalist predators in agro-ecosystems, and can use non-crop features as overwintering habitats.
+However, it is unclear which types of landscape features constitute useful non-crop habitat, and at what spatial scale organisms gather resources.
+Additionally, the same landscape feature may act as source of arthropod spillover at different times of the year, but this is rarely considered.
 We modeled the activity-density of four highly-abundant species of Canadian prairie arthropods, and used functional regression to simultaneously consider both their habitat preferences and the timing of sources and sinks.

### 2020-11-04 manuscript/manuscript.Rmd
Updated maps

@@
 _Pterostichus melanarius_ (Coleoptera: Carabidae) and _Pardosa moesta_ (Arachnida: Lycosidae) appear to be attracted to canola (_Brassica napus_ L.) during the early summer, then disperse to grasslands, wetlands, and grassy road margins during the end of the summer.
-This suggests that grasslands and wetlands act as reservoir habitats for predatory arthropods, and that farmers should consider preserving existing habitat around croplands in order to maintain background levels of pest-control."
+This suggests that grasslands and wetlands act as reservoir habitats for predatory arthropods, and that farmers should consider preserving existing habitat in order to maintain pest-control services across the season."
 
@@
 Second, the spatial "grain" of the landscape that is relevant to an organism depends on their traits and life history [@ahrenfeldt2015].
-For instance, bumblebee abundance can be controlled by both nearby and far-away SNL abundance [@westphal2006], but this is poorly studied for other groups of beneficial organisms [but see @sander2006].
+For instance, bumblebee abundance can be influenced by both nearby and far-away SNL abundance [@westphal2006], but this is poorly studied for other groups of beneficial organisms [but see @sander2006].
 Finally, the feeding and life-history characteristics of many predatory ground beetles and spiders are often poorly-documented, especially in North America.
@@
 
-```{r siteMap, echo=FALSE, fig.cap='Location of pitfall traps during 2017, and classified land cover.
-Inset map shows study location within Alberta.
-Roadside traps were installed in road margins, while in-field traps were installed directly in canola fields or in adjacent wetland or grassy field edges.', out.width='100%'}
+```{r siteMap, echo=FALSE, fig.cap='Classified land cover and location of pitfall traps during 2017.
+Inset map shows study location within Alberta provincial boundaries.
+Roadside traps were installed in road margins, while in-field traps were installed directly in canola fields, wetlands, or grassy field edges.', out.width='100%'}
   include_graphics('../figures/maps/PF2017Map.png',dpi=NA)
@@
 Therefore, the interpretation of a functional regression plot is very different from that of a simple linear regression plot.
-Figure \@ref(fig:frExample)a shows a simple linear regression plot of a hypothetical relationship between trap _activity-density_ (_y_) and a single predictor, _Proportion cover_ (_x_), which is measured in a circle of a fixed radius (_Distance_) surrounding each trap.
-If we suppose that the relationship between _x_ and _y_ is similar at all radii at which _x_ is measured, then Figure \@ref(fig:frExample)b shows the resulting functional linear regression plot, where the slope ($\beta$) is the same at all distances.
-In reality it is more likely that nearby cover will be more influential on activity-density than far-away cover, which would result in a relationship similar to Figure \@ref(fig:frExample)c.
-As functional regression takes any continuous predictor of _y_, it is also possible to use proportion cover (measured within a fixed radius) as a predictor of measurements taken across time, allowing the effect of proportion cover to vary over the course of the season (Figure \@ref(fig:frExample)d).
-Finally, proportion cover over distance and time may be combined into a smoothed surface of effects, representing the spatio-temporal influence of landscape cover on activity-density.
+Figure \@ref(fig:frExample)a shows a simple linear regression plot of a hypothetical relationship between trap _activity-density_ (_y_) and a single predictor, _proportion cover_ (_x_), which is measured in a circle of a fixed radius surrounding each trap.
+If we suppose that the relationship between _x_ and _y_ is similar at all radii at which _x_ is measured, then Figure \@ref(fig:frExample)b shows the resulting functional linear regression plot, where the slope ($\beta$) is the same at all distances (we avoid the problem of overlapping concentric circles by using concentric _annuli_).
+In reality, it is more likely that nearby cover will be more influential on activity-density than far-away cover, which could result in a relationship similar to Figure \@ref(fig:frExample)c.
+As functional regression takes any continuous predictor of _y_, it is also possible to use proportion cover (measured within an annulus of a fixed radius) as a predictor of measurements taken across time, allowing the effect of proportion cover to vary over the course of the season (Figure \@ref(fig:frExample)d).
+Finally, the effect of proportion cover over distance and time may be modeled as a smoothed surface, representing the joint spatio-temporal influence of landscape cover on activity-density.
 
@@
 The pitfall traps caught a total of `r with(Ncatches,total[spp=='PteMel'])` _Pterostichus melanarius_, `r with(Ncatches,total[spp=='ParDis'])` _Pardosa distincta_, `r with(Ncatches,total[spp=='ParMoe'])` _Pardosa moesta_, and `r with(Ncatches,total[spp=='Opilio'])` _Phalangium opilio_ (mean trapping rates per day: `r with(Ncatches,paste(round(perDayMean,2),collapse=', '))`, SD: `r with(Ncatches,paste(round(perDaySD,2),collapse=', '))`, respectively).
-
-```{r landscapeComp, echo=FALSE, fig.cap='Landscape composition in annuli surrounding each trap location.
-Sites are represented by individual lines.
-Mean cover for each class is listed in each sub-figure heading.', fig.width=5, fig.height=5}
-coverList %>% group_by(cover) %>% mutate(p=sum(prop)) %>% ungroup() %>% mutate(p=100*round(p/sum(unique(p)),4)) %>% 
-  mutate(cover=paste0(as.character(cover),' (',p,'%)'),prop=prop*100) %>% 
-  mutate(cover=factor(cover,levels=unique(cover))) %>% 
-  ggplot(aes(dist,prop,group=site))+geom_line(alpha=0.2)+
-  facet_wrap(~cover,ncol=4)+theme_classic()+theme(axis.text = element_text(size = 8),strip.text=element_text(size=8))+
-  labs(y='Percent cover',x='Inner radius of annuli (m)')
-```
 
@@
 opilio_ also showed a distinct East-West spatial random effect (Figure \@ref(fig:OpilioSpatiotemporal)b), indicating that their activity-density is also influenced by larger-scale abiotic factors.
+<!-- JV: THIS EAST-WEST PATTERN SHOULD BE MENTIONED IN THE DISCUSSION -->
 
@@
 ```{r resultsTab, echo=FALSE, message=FALSE, warning=FALSE, out.width='100%'}
-#Based on example from:
-# https://stackoverflow.com/questions/31011265/how-to-write-bullet-lists-in-a-table-using-rmarkdown-and-pandoc
-# #Note: this works, but it's very ugly. Trying kable instead
-# mytable <- data.frame(
-#     CoverClass = c("Grassland", "Canola", "Pasture", "Woodland", "Pulses", "Road margins"),
-#     PteMel = c('* Local sink ','* Local source (early) \n* Landscape sink (early)',' ',' ','* Source (late)',' '),
-#     ParDis = c(' ',' ','* Landscape sink',' * Sink (late)',' ',' '),
-#     ParMoe = c('* Local sink \n* Landscape source','* Local source (early) \n* Local sink (late)',' ',' ','* Landscape source','* Local source (early) \n* Local sink (late) \n* Landscape sink (early) \n* Landscape source (late)'),
-#     Opilio = c('* Local sink (early)',' ',' ','* Local sink (early) \n* Landscape source (mid)',' ',' ')
-#     )
-# colnames(mytable) <- c('Cover class','_Pterosticus_ _melanarius_','_Pardosa_ _distincta_','_Pardosa_ _moesta_','_Phalangium_ _opilio_')
-# pander(mytable, keep.line.breaks = TRUE, style = 'grid', justify = 'left', split.table=1000)
 
-# #Based on example https://stackoverflow.com/questions/52962411/table-with-long-text-bullet-points-and-specific-table-width
-# #Much better than above, but not very easy to absorb. Perhaps there should be some kind of organismal-based synthesis table?
-# summaryTab <- data.frame(
-#     CoverClass = c("Grassland", "Canola", "Pasture", "Woodland", "Pulses", "Road margins"),
-#     PteMel = c('$\\cdot$ Local -- (late)','$\\cdot$ Local + (early) \n$\\cdot$ Landscape -- (early)',' ',' ','$\\cdot$ Overall + (late)',' '),
-#     ParDis = c(' ',' ','$\\cdot$ Landscape --',' $\\cdot$ Overall -- (late)',' ',' '),
-#     ParMoe = c('$\\cdot$ Local -- \n$\\cdot$ Landscape +','$\\cdot$ Local + (early) \n$\\cdot$ Local -- (late)',' ',' ','$\\cdot$ Landscape +','$\\cdot$ Local + (early) \n$\\cdot$ Local -- (late) \n$\\cdot$ Landscape -- (early) \n$\\cdot$ Landscape + (late)'),
-#     Opilio = c('$\\cdot$ Local -- (early)',' ',' ','$\\cdot$ Local -- (early) \n$\\cdot$ Landscape + (mid)',' ',' ')
-#     )
-# 
-# summaryTab %>%
-#   mutate_all(linebreak) %>%  # required for linebreaks to work
-#   kable(.,format='latex',caption='Summary of model results.
-\\emph{Local/Landscape} denotes cover classes <500m or >500m away from the trap location, respectively.
-+/-- indicates positive or negative effects of the cover class, and \\emph{Early/Mid/Late} denotes whether the effects were present earlier or later during the season.
-Cover classes with weak effects on activity-density are not shown.',
-#         col.names=linebreak(x=c('Cover class','\\emph{Pterostichus}\n\\emph{melanarius}','\\emph{Pardosa}\n\\emph{distincta}',
-#                               '\\emph{Pardosa}\n\\emph{moesta}','\\emph{Phalangium}\n\\emph{opilio}')),
-#         align='rllll',escape=FALSE) %>% 
-#   column_spec(1, width = "4em") %>% column_spec(c(2:5), width = "9em") # fix column widths
-
-##Attempt at synthesis table
+#Attempt at synthesis table
 mytable <- data.frame(
@@
 <!-- The activity-density of the four arthropods was influenced by landscape composition, but the response of _Pterostichus melanarius_ and _Phalangium opilio_ was much stronger. -->
-Our prediction of SNL having late-season effects on beneficial arthropods was supported; specifically, grassland had a negative effect on _P.
+Our prediction of SNL having late-season effects on beneficial arthropods was supported (Table \@ref(tab:resultsTab)).
+Specifically, grassland had a negative effect on _P.
 melanarius_ activity-density, woodlands on _P.
@@
 We did not consider the influence of previous years' crops, although carabids tend to be more abundant in areas of high crop rotation [@busch_Msc; @bertrand2016].
+Finally, _P.
+melanarius_ has long- and short-winged morphs with very different dispersal abilities [@niemela1999; @bourassa2011], which may influence the degree to which landscape-level proportion cover impacts activity-density.
 
@@
 Figures \@ref(fig:PteMelLandscape), \@ref(fig:ParMoeLandscape)).
-Secondly, our work suggests that _P. melanarius_ and _P. moesta_ should be investigated for their role as predators in canola crops.
+Secondly, our work suggests that _P. melanarius_ and _P. moesta_ should be investigated for their role as predators in canola crops (Table \@ref(tab:resultsTab)).
 They appear to aggregate in canola crops early in the season, meaning that they have the potential to provide valuable pest-control services to growers.
@@
   include_graphics('../figures/coverCorPlots/concurvityEstimate_reduced.png',dpi=NA)
+```
+
+```{r landscapeComp, echo=FALSE, fig.cap='Percent cover of landscape cover classes in annuli surrounding each trap location.
+Sites are represented by individual lines.
+Mean cover for each class is listed in each sub-heading.', fig.width=5, fig.height=5}
+coverList %>% group_by(cover) %>% mutate(p=sum(prop)) %>% ungroup() %>% mutate(p=100*round(p/sum(unique(p)),4)) %>% 
+  mutate(cover=paste0(as.character(cover),' (',p,'%)'),prop=prop*100) %>% 
+  mutate(cover=factor(cover,levels=unique(cover))) %>% 
+  ggplot(aes(dist,prop,group=site))+geom_line(alpha=0.2)+
+  facet_wrap(~cover,ncol=4)+theme_classic()+theme(axis.text = element_text(size = 8),strip.text=element_text(size=8))+
+  labs(y='Percent cover',x='Distance from trap location (m)')
 ```

### 2020-11-04 frPlotDemo.R

@@ -55,7 +55,7 @@ p2 <- apply(mapply(lineFun,int=rnorm(1000,0.5,0.1),slope=rnorm(1000,0,0.1),MoreA
   annotate('text',x=500,y=-0.75,label='Effect of cover is positive at all distances')+
   annotate('segment',x=400,xend=300,y=-0.5,yend=0.2,arrow=arrow())+
   annotate('segment',x=600,xend=700,y=-0.5,yend=0.2,arrow=arrow())+
-  labs(x='Distance from sampling location',y=expression(paste('Slope of proportion cover (',beta,')')))+ylim(-1.5,1.5)
+  labs(x='Distance from sampling location (radius of annulus)',y=expression(paste('Slope of proportion cover (',beta,')')))+ylim(-1.5,1.5)
 
 #Exponential
 p3 <- apply(mapply(expFun,a=rnorm(1000,1,0.2),b=rnorm(1000,0.05,0.002),d=rnorm(1000,-0.02,0.1),MoreArgs=list(n=1000)),
@@ -68,7 +68,7 @@ p3 <- apply(mapply(expFun,a=rnorm(1000,1,0.2),b=rnorm(1000,0.05,0.002),d=rnorm(1
   annotate('segment',x=350,xend=100,y=1,yend=0.6,arrow=arrow())+
   annotate('text',x=500,y=-0.75,label='Neutral effect of far-away cover')+
   annotate('segment',x=600,xend=600,y=-0.5,yend=-0.2,arrow=arrow())+
-  labs(x='Distance from sampling location',y=expression(paste('Slope of proportion cover (',beta,')')))+ylim(-1.5,1.5)
+  labs(x='Distance from sampling location (radius of annulus)',y=expression(paste('Slope of proportion cover (',beta,')')))+ylim(-1.5,1.5)
 
 #Negatively sloped line
 p4 <- apply(mapply(lineFun,int=rnorm(1000,0,0.1),slope=rnorm(1000,-0.5,0.1),MoreArgs=list(n=1000)),

### 2020-11-05 manuscript/manuscript.Rmd
Inserted "origin/destination" wording

@@
 However, it is unclear which types of landscape features constitute useful non-crop habitat, and at what spatial scale organisms gather resources.
-Additionally, the same landscape feature may act as source of arthropod spillover at different times of the year, but this is rarely considered.
-We modeled the activity-density of four highly-abundant species of Canadian prairie arthropods, and used functional regression to simultaneously consider both their habitat preferences and the timing of sources and sinks.
-_Pterostichus melanarius_ (Coleoptera: Carabidae) and _Pardosa moesta_ (Arachnida: Lycosidae) appear to be attracted to canola (_Brassica napus_ L.) during the early summer, then disperse to grasslands, wetlands, and grassy road margins during the end of the summer.
+Additionally, the same landscape feature may act as an origin or destination for arthropods at different times of the year, but this is rarely considered.
+We modeled the activity-density of four highly-abundant species of Canadian prairie arthropods, and used functional regression to simultaneously consider both their habitat preferences and the timing of origins and destinations.
+_Pterostichus melanarius_ (Coleoptera: Carabidae) and _Pardosa moesta_ (Arachnida: Lycosidae) appear to be attracted to canola (_Brassica napus_ L.) during the early summer, then dispersed to grasslands, wetlands, and grassy road margins during the end of the summer.
 This suggests that grasslands and wetlands act as reservoir habitats for predatory arthropods, and that farmers should consider preserving existing habitat in order to maintain pest-control services across the season."
@@
 Pest arthropods can cause large reductions in crop yield [@oerke2005], which can result in negative downstream economic effects and food insecurity.
-On the other hand, spillover of beneficial arthropods from adjacent non-crop patches can deliver increased crop yields by providing ecosystem services such as extra pollination or pest suppression [@losey2006; @klein2007; @garibaldi2013].
-Seasonal "pulses" of food resources from crop fields act as a bottom-up driver of their associated arthropod communities, meaning that agricultural land can act as a source of nutrients and individuals for adjacent non-crop land [@diekotter2010; @galpern2017].
-These important fluxes of mobile arthropods, both to crops and away from them, are key for managing both crop yield and biodiversity in agroecosystems.
-Finding "win-win" practices is of particular importance to land managers and conservationists; that is, practices that result in better conservation outcomes while maintaining or improving crop yields.
+However, beneficial arthropods living in non-crop patches can increase crop yields by providing ecosystem services, such as extra pollination or pest suppression [@losey2006; @klein2007; @garibaldi2013].
+Seasonal "pulses" of food resources act as bottom-up drivers of arthropod communities in crop fields, meaning that agricultural land can increase arthropod abundance in adjacent non-crop land [@diekotter2010; @galpern2017].
+These movements of mobile arthropods in and out of crops are important for managing both crop yield and biodiversity in agroecosystems.
+In this context, finding "win-win" practices -- that is, practices that result in better conservation outcomes while maintaining or improving crop yields -- is of particular importance.
 <!-- Finally, agricultural land occupies 15 million km$^2$ (~36%) of land globally [@ramankutty2018], suggesting that there remains great potential to achieve conservation outcomes by adjusting agricultural practices.
@@
 For example, wild bee abundance in agricultural landscapes is largely driven by flower and nest availability [@roulston2011], and the effect of SNL on bee abundance and diversity is generally positive.
-Predatory arthropods such as beetles or spiders can be limited by water, food, and egg-laying sites [@lovei1996; @purtauf2005; @gardiner2010], but the effect of SNL on their abundance and diversity is less consistent [@macfadyen2013; @shackelford2013] as some taxa may use SNL as a travel corridor or overwintering site, but are not completely dependent on it for reproduction.
+Pest-suppressing predators, such as beetles or spiders, can be limited by water, food, and egg-laying sites [@lovei1996; @purtauf2005; @gardiner2010], but the effect of SNL on their abundance and diversity is less consistent [@macfadyen2013; @shackelford2013] as some taxa may use SNL as a travel corridor or overwintering site, but are not completely dependent on it for reproduction.
 Some taxa are not dependent on SNL at all, and thrive in cultivated landscapes, while others exclusively inhabit SNL and do not venture beyond the edge of cultivated fields.
@@
 Despite what is known about the spatial and temporal aspects of beneficial arthropod spillover, these are rarely considered together.
-First, some non-crop habitat may act as sources of arthropods during some times of the year, but as sinks during other times, meaning that the timing of spillover from non-crop habitat may not align with important periods in crop development.
+First, some non-crop habitat may act as origins of arthropods during some times of the year, but as destinations during other times, meaning that the timing of spillover from non-crop habitat may not align with important periods in crop development.
 Arthropods can migrate from managed crops back into adjacent SNL at the end of the season [@desender1988; @tscharntke2005b], but this is seldom considered.
@@
 
-In this study, we used pitfall traps to determine how landscape composition affects the seasonal abundance of arthropods across a large Canadian prairie agroecosystem.
+In this study, we used pitfall traps to determine how landscape composition affects the seasonal abundance of predatory arthropods in a Canadian prairie agroecosystem.
 We considered the following hypotheses:
 1.
-Untilled semi-natural land provides egg-laying and feeding areas for predatory arthropods, meaning that it should act as a source of arthropods during the early part of the season, and a sink during the later part of the season.
+Untilled semi-natural land provides egg-laying and feeding areas for predatory arthropods, meaning that it should act as an origin of arthropods during the early part of the season, and a destination during the later part of the season.
 2.
-Crops act as sources of food (pest insects) for predatory arthropods during the growing season.
-This should result in agricultural land becoming a sink for predators in the early part of the season as they migrate into the crop, and a source at the end of the season as they migrate out of the crop.
-3. Crops may act as a temporary feeding site for predators. Therefore, crops may act as a local sink for arthropods, but will also be negatively associated at larger (landscape-level) scales.
+Crops provide food (pest insects) for predatory arthropods during the growing season.
+This should result in agricultural land becoming a destination for predators in the early part of the season as they migrate into the crop, and an origin at the end of the season as they migrate out of the crop.
+3. Crops may act as a temporary feeding site for predators. Therefore, crops may act as a local destination for arthropods, but will also be negatively associated at larger (landscape-level) scales.
 Using a large pitfall trapping dataset, we related seasonal changes in arthropod abundance to landscape composition at multiple spatial scales.
@@
 
-We used counts of organisms in our pitfall traps as proxies of ecosystem service provision.
+We used counts of organisms in our pitfall traps as proxies of ecosystem services (specifically, pest control).
 However, increased counts of organisms in pitfall traps can represent higher activity levels (same number of organisms but more mobile) or higher abundances in the vicinity of the trap.
 This makes it impossible to disentangle arthropod activity from density using single traps [@lang2000; @zhao2013], meaning that counts in the traps represent the "activity-density" of a given organism.
-Despite this drawback, activity-density is generally positively related to ecosystem services, at least in carabids [@trichard2014; @boetzl2018; @gonzalez2020], making it acceptable for our study.
+Despite this drawback, activity-density is generally positively related to pest consumption, at least in carabids [@trichard2014; @boetzl2018; @gonzalez2020], making it acceptable for our study.
 
@@
 
-We used four highly-abundant species of predatory arthropods found in the pitfall traps, as common species are often more important for ecosystem service provision than rare species [@winfree2015].
+We used four highly-abundant species of predatory arthropods found in the pitfall traps, as common species are more important for ecosystem service provision than rare species [@winfree2015].
 _Pterostichus melanarius_ is an introduced predatory ground beetle (Coleoptera: Carabidae) that is a wide-ranging generalist known to prey upon crop pests [@carcamo1994; @larsen2003; @busch_Msc].
@@
 
-Functional regression plots of landscape composition reveal which cover classes are acting as spillover sources or sinks of a given arthropod, and at what spatial scale.
-Positive effects of nearby landscape cover classes indicate that arthropods are spilling over *from* it.
+Functional regression plots of landscape composition reveal which cover classes are acting as origins or destinations of a given arthropod, and at what spatial scale.
+Positive effects of nearby landscape cover classes indicate that arthropods are spilling over *from* it, therefore acting as an origin.
 However, negative responses to nearby landscape cover classes can indicate one of two things:
-1) It may indicate that arthropods are spilling over *into* it (i.e. net sink for spillover) or 2) it may indicate that no arthropods are available to spill over *from* it.
+1) It may indicate that arthropods are spilling over *into* it (therefore acting as a destination) or 2) it may indicate that no arthropods are available to spill over *from* it.
 We consider 1) to be the more likely scenario, as it is unlikely that any one cover class is *completely* unoccupied.
 <!-- As these data were collected from a single year, this model does not consider the next-generation fitness consequences of spillover. -->
-For example, a cover class with low-quality habitat could act as an ecological trap [@galpern2017] if it acts as a net sink but never acts as a source of spill over.
-Alternatively, a cover class could act as a sink by providing high-quality habitat at certain times of the year (e.g. egg laying/feeding), but act as a source at other times (e.g. during emergence).
+For example, a cover class with low-quality habitat could act as an ecological trap [@galpern2017] if it acts as a destination but never as an origin.
+Alternatively, a cover class could act as a destination by providing high-quality habitat at certain times of the year (e.g.
+egg laying/feeding), but act as an origin at other times (e.g.
+during emergence).
+
 In the Results section, we refer to local- and landscape-level effects, where local indicates the effects of landscape composition at scales of <500 m, whereas landscape indicates scales >500 m.
@@
 melanarius_ activity-density (Figure \@ref(fig:PteMelLandscape)c).
-Pulses acted as a late-season source, indicating that _P. melanarius_ may migrate out of the crop after (or during) harvest (Figure \@ref(fig:PteMelLandscape)d).
+Pulses acted as a late-season origin, indicating that _P. melanarius_ may migrate out of the crop after (or during) harvest (Figure \@ref(fig:PteMelLandscape)d).
 Finally, _P.
@@
 distincta_ may be locally abundant in certain cover types, it is highly general in its overall habitat preferences.
-<!-- The weak effect of canola crops (p>0.07) suggests that this species does not aggregate into these crops, meaning that its ecosystem service potential to farmers is limited. -->
+<!-- The weak effect of canola crops (p>0.07) suggests that this species does not aggregate into these crops, meaning that its pest suppressing potential for farmers is limited. -->
 
 _P. moesta_ activity-density responded to grassland, canola, and road margins.
-Grasslands had a local negative effect, but a positive landscape-level effect, indicating that while these cover types act as a local sink, the general amount of grassland in the area had a positive effect (Figure \@ref(fig:ParMoeLandscape)b).
+Grasslands had a local negative effect, but a positive landscape-level effect, indicating that while these cover types act as a local destination, the general amount of grassland in the area had a positive effect (Figure \@ref(fig:ParMoeLandscape)b).
 Local canola cover had a positive early effect on activity-density, but a negative local effect later in the season (Figure \@ref(fig:ParMoeLandscape)c).
-Local road margins also had a similar effect, acting as an early source and a late sink (Figure \@ref(fig:ParMoeLandscape)d).
+Local road margins also had a similar effect, acting as an early origin and a late destination (Figure \@ref(fig:ParMoeLandscape)d).
 Pulses also had a positive effect at the landscape level (Figure \@ref(fig:ParMoeLandscape)e), but this explained very little variance in _P.
@@
                               ' \\emph{Pardosa}\n\\emph{moesta}',' \\emph{Phalangium}\n\\emph{opilio}'),
-    Summary = as.character(c('$\\cdot$ Aggregates in canola during early season \n$\\cdot$ Disperses to grassland during late season',
-                '$\\cdot$ Negative effect of pasture \n$\\cdot$ May locally aggregate in field edges',
-                '$\\cdot$ Aggregates in canola during early season \n$\\cdot$ Disperses to road margins and grassland during late season \n$\\cdot$Aggregates in grasslands across the season.',
-                '$\\cdot$ Aggregates to grassland early in the season')),
+    Summary = as.character(c('$\\cdot$ Moves to canola during early season \n$\\cdot$ Disperses to grassland during late season',
+                '$\\cdot$ Negative effect of pasture \n$\\cdot$ May move locally to field edges',
+                '$\\cdot$ Moves to canola during early season \n$\\cdot$ Disperses to road margins and grassland during late season \n$\\cdot$Moves to grasslands across the season.',
+                '$\\cdot$ Moves to grassland early in the season')),
     BioControl= as.character(c('High','Low','Medium','Low'))
@@
 mytable %>% mutate_all(linebreak) %>% 
-  kable(.,format='latex',caption='Synthesis of model results. Bio-control potential is based on likely early-season aggregation to canola crops.',escape=FALSE,
-      col.names=c('Species','Summary','Bio-control potential'),align='lll') %>% 
+  kable(.,format='latex',caption='Synthesis of model results. Pest control potential is based on likelihood of early-season aggregation to canola crops.',escape=FALSE,
+      col.names=c('Species','Summary','Pest control potential'),align='lll') %>% 
   column_spec(2,width='15em')
@@
 opilio_, resulting in low spillover.
-There was little evidence of SNL acting as early-season sources, aside from road margins having a positive early effect on _P. moesta_ activity-density.
+There was little evidence of SNL acting as early-season origins, aside from road margins having a positive early effect on _P. moesta_ activity-density.
 However, some cover classes had a positive effect at the landscape level (grassland and road margins on _P. moesta_), suggesting earlier or larger-scale dispersal away from these cover classes.
@@
 Finally, the influence of landscape composition tended to be limited to a radius of about 500m, indicating that large-scale _and_ local land cover can be important to beneficial arthropod abundance.
-There was also a strong temporal component to most of the landscape effects, meaning that it is important to consider how sinks and sources may change over the season.
+There was also a strong temporal component to most of the landscape effects, meaning that it is important to consider how destinations and origins may change over the season.
 
-<!-- 1. ... nearby SNL should act as a source of arthropods during the early part of the season, and a sink during the later part of the season.  -->
+<!-- 1. ... nearby SNL should act as an origin of arthropods during the early part of the season, and a destination during the later part of the season.  -->
 <!-- 2.
 ...
-should result in agricultural land becoming a sink for predators in the early part of the season as they migrate into the crop, and a source at the end of the season as they migrate out of the crop.
+should result in agricultural land becoming a destination for predators in the early part of the season as they migrate into the crop, and an origin at the end of the season as they migrate out of the crop.
 -->
-<!-- 3. ... crops may act as a local sink for arthropods, but will also be negatively associated at larger (landscape-level) scales. -->
+<!-- 3. ... crops may act as a local destination for arthropods, but will also be negatively associated at larger (landscape-level) scales. -->
 
 The predatory ground beetle _Pterostichus melanarius_ responded to landscape composition, primarily to canola, pulses, and grass and wetland cover.
-Grassland and wetland cover had a negative late-season effect, suggesting that _P. melanarius_ migrates into it at the end of the summer.
+Grassland and wetland cover had a negative late-season effect, suggesting that they act as a destination for _P. melanarius_ at the end of the summer.
 Other studies have found similar results, suggesting that untilled land is important off-field habitat for carabids [@desender1988; @fournier2002; but see @hatten2007].
@@
 
-Many other studies have considered the overall effect of SNL on ecosystem service provision, but we have highlighted the different spatial and temporal aspects of ecosystem service provision.
+Many other studies have considered the overall effect of SNL on ecosystem service provision, but we have highlighted the different spatial and temporal aspects of these services.
 We have shown how a relatively straightforward statistical technique can be used to consider multiple spatial scales of landscape composition, providing richer inference about the processes acting on beneficial arthropods.
@@
 First, it adds to the basis of scientific evidence showing that SNL can act as reservoir habitats in intensely-managed agroecosystems.
-Based on our findings, farmers and land managers should consider preserving existing grassland and wetland habitat to act as a background source of arthropods for pest-control in crops.
+Based on our findings, farmers and land managers should consider preserving existing grassland and wetland habitat to act as habitat for pest-suppressing arthropods in crops.
 While local habitat appears valuable, even landscape-level habitat can be valuable, as it can increase the number of beneficial arthropods at larger spatial scales (e.g.

### 2020-11-06 manuscript/manuscript.Rmd
Changed title and added acknowledgements

@@
 ---
-title: "Beneficial arthropod habitat useage changes within-season: implications for pest control services in croplands"
-#Potential titles: 
-# Non-crop features influence the abundance and timing of beneficial arthropod abundance
-# 1) Cropland ecosystem services in space and time: Beneficial arthropod habitat use shifts within-season.
-# 2) Beneficial arthropod habitat use shifts within-season: implications for pest control services in croplands
-# 
+title: "Non-crop sources of beneficial arthropods vary within-season across a prairie agroecosystem"
 author:
@@
 date: "Spring 2020"
-abstract: "Ground-dwelling arthropods can be important generalist predators in agro-ecosystems, and can use non-crop features as overwintering habitats.
+abstract: "Ground-dwelling arthropods can be important generalist predators in agroecosystems, and can use non-crop features as overwintering habitats.
 However, it is unclear which types of landscape features constitute useful non-crop habitat, and at what spatial scale organisms gather resources.
-Additionally, the same landscape feature may act as an origin or destination for arthropods at different times of the year, but this is rarely considered.
-We modeled the activity-density of four highly-abundant species of Canadian prairie arthropods, and used functional regression to simultaneously consider both their habitat preferences and the timing of origins and destinations.
+Additionally, the same landscape feature may act as a source or destination for arthropods at different times of the year, but this is rarely considered.
+We modeled the abundance of four highly-abundant species of Canadian prairie arthropods caught in pitfall traps, and used functional regression to simultaneously consider both their habitat preferences and the timing of sources and destinations.
 _Pterostichus melanarius_ (Coleoptera: Carabidae) and _Pardosa moesta_ (Arachnida: Lycosidae) appear to be attracted to canola (_Brassica napus_ L.) during the early summer, then dispersed to grasslands, wetlands, and grassy road margins during the end of the summer.
-This suggests that grasslands and wetlands act as reservoir habitats for predatory arthropods, and that farmers should consider preserving existing habitat in order to maintain pest-control services across the season."
+This suggests that grasslands and wetlands act as seasonal reservoir habitats for predatory arthropods, and that farmers should consider preserving existing habitat in order to maintain pest-control services across the season."
 
@@
 
+Key words: beetles; spiders; harvestmen; movement; natural enemies; functional regression
+
 \newpage
@@
 # Introduction
-<!-- DE: BIOCONTROL THEME NEEDS SET-UP IN INTRODUCTION -->
-
 Arthropods are one of the most influential groups of animals in agricultural systems.
@@
 Despite what is known about the spatial and temporal aspects of beneficial arthropod spillover, these are rarely considered together.
-First, some non-crop habitat may act as origins of arthropods during some times of the year, but as destinations during other times, meaning that the timing of spillover from non-crop habitat may not align with important periods in crop development.
+First, some non-crop habitat may act as sources of arthropods during some times of the year, but as destinations during other times, meaning that the timing of spillover from non-crop habitat may not align with important periods in crop development.
 Arthropods can migrate from managed crops back into adjacent SNL at the end of the season [@desender1988; @tscharntke2005b], but this is seldom considered.
@@
 1.
-Untilled semi-natural land provides egg-laying and feeding areas for predatory arthropods, meaning that it should act as an origin of arthropods during the early part of the season, and a destination during the later part of the season.
+Untilled semi-natural land provides egg-laying and feeding areas for predatory arthropods, meaning that it should act as a _source_ of arthropods during the early part of the season, and a _destination_ during the later part of the season.
 2.
 Crops provide food (pest insects) for predatory arthropods during the growing season.
-This should result in agricultural land becoming a destination for predators in the early part of the season as they migrate into the crop, and an origin at the end of the season as they migrate out of the crop.
+This should result in agricultural land becoming a destination for predators in the early part of the season as they migrate into the crop, and a source at the end of the season as they migrate out of the crop.
 3. Crops may act as a temporary feeding site for predators. Therefore, crops may act as a local destination for arthropods, but will also be negatively associated at larger (landscape-level) scales.
@@
 
-```{r siteMap, echo=FALSE, fig.cap='Classified land cover and location of pitfall traps during 2017.
+(ref:siteMapCap) Classified land cover and location of pitfall traps during 2017.
 Inset map shows study location within Alberta provincial boundaries.
-Roadside traps were installed in road margins, while in-field traps were installed directly in canola fields, wetlands, or grassy field edges.', out.width='100%'}
+Roadside traps were installed in road margins, while in-field traps were installed directly in canola fields, wetlands, or grassy field edges.
+
+```{r siteMap, echo=FALSE, fig.cap='(ref:siteMapCap)', out.width='100%'}  
   include_graphics('../figures/maps/PF2017Map.png',dpi=NA)
@@
 
-Functional regression plots of landscape composition reveal which cover classes are acting as origins or destinations of a given arthropod, and at what spatial scale.
-Positive effects of nearby landscape cover classes indicate that arthropods are spilling over *from* it, therefore acting as an origin.
+Functional regression plots of landscape composition reveal which cover classes are acting as sources or destinations of a given arthropod, and at what spatial scale.
+Positive effects of nearby landscape cover classes indicate that arthropods are spilling over *from* it, therefore acting as a source.
 However, negative responses to nearby landscape cover classes can indicate one of two things:
@@
 <!-- As these data were collected from a single year, this model does not consider the next-generation fitness consequences of spillover. -->
-For example, a cover class with low-quality habitat could act as an ecological trap [@galpern2017] if it acts as a destination but never as an origin.
+For example, a cover class with low-quality habitat could act as an ecological trap [@galpern2017] if it acts as a destination but never as a source.
 Alternatively, a cover class could act as a destination by providing high-quality habitat at certain times of the year (e.g.
-egg laying/feeding), but act as an origin at other times (e.g.
+egg laying/feeding), but act as a source at other times (e.g.
 during emergence).
@@
 melanarius_ activity-density (Figure \@ref(fig:PteMelLandscape)c).
-Pulses acted as a late-season origin, indicating that _P. melanarius_ may migrate out of the crop after (or during) harvest (Figure \@ref(fig:PteMelLandscape)d).
+Pulses acted as a late-season source, indicating that _P. melanarius_ may migrate out of the crop after (or during) harvest (Figure \@ref(fig:PteMelLandscape)d).
 Finally, _P.
@@
 Local canola cover had a positive early effect on activity-density, but a negative local effect later in the season (Figure \@ref(fig:ParMoeLandscape)c).
-Local road margins also had a similar effect, acting as an early origin and a late destination (Figure \@ref(fig:ParMoeLandscape)d).
+Local road margins also had a similar effect, acting as an early source and a late destination (Figure \@ref(fig:ParMoeLandscape)d).
 Pulses also had a positive effect at the landscape level (Figure \@ref(fig:ParMoeLandscape)e), but this explained very little variance in _P.
@@
 opilio_, resulting in low spillover.
-There was little evidence of SNL acting as early-season origins, aside from road margins having a positive early effect on _P. moesta_ activity-density.
+There was little evidence of SNL acting as early-season sources, aside from road margins having a positive early effect on _P. moesta_ activity-density.
 However, some cover classes had a positive effect at the landscape level (grassland and road margins on _P. moesta_), suggesting earlier or larger-scale dispersal away from these cover classes.
@@
 Finally, the influence of landscape composition tended to be limited to a radius of about 500m, indicating that large-scale _and_ local land cover can be important to beneficial arthropod abundance.
-There was also a strong temporal component to most of the landscape effects, meaning that it is important to consider how destinations and origins may change over the season.
+There was also a strong temporal component to most of the landscape effects, meaning that it is important to consider how destinations and sources may change over the season.
 
-<!-- 1. ... nearby SNL should act as an origin of arthropods during the early part of the season, and a destination during the later part of the season.  -->
+<!-- 1. ... nearby SNL should act as a source of arthropods during the early part of the season, and a destination during the later part of the season.  -->
 <!-- 2.
 ...
-should result in agricultural land becoming a destination for predators in the early part of the season as they migrate into the crop, and an origin at the end of the season as they migrate out of the crop.
+should result in agricultural land becoming a destination for predators in the early part of the season as they migrate into the crop, and a source at the end of the season as they migrate out of the crop.
 -->
@@
 late-season spillover) that are typically ignored, but should be considered when assessing how SNL can deliver ecosystem services.
+
+# Acknowledgements
+
+Many thanks to the farmers who gave us access to their land for this study.
+This also would not have been possible without the help of Michael Gavin, Jennifer Retzlaff, and Mugunzal Abarmayan, and John Swann.
+Funding for this research was provided by Ducks Unlimited Canada's Institute for Wetland and waterfowl Research, the Alberta Canola Producers Commission, Manitoba Canola Growers Association, SaskCanola, the Alberta Biodiversity Monitoring Institute, the Alberta Conservation Association.
 

### 2020-11-09 manuscript/manuscript.Rmd
Minor changes to wording

--- 2020-11-05 manuscript/manuscript.Rmd
@@
 Therefore, landscape management is a strategy to increase beneficial arthropod abundance in crops [@albrecht2010; @landis2000; @martin2020; but see @tscharntke2016; @karp2018].
-For example, wild bee abundance in agricultural landscapes is largely driven by flower and nest availability [@roulston2011], and the effect of SNL on bee abundance and diversity is generally positive.
+For example, wild bee abundance in agricultural landscapes is driven by food and nest availability [@roulston2011], and the effect of SNL on bee abundance and diversity is generally positive.
 Pest-suppressing predators, such as beetles or spiders, can be limited by water, food, and egg-laying sites [@lovei1996; @purtauf2005; @gardiner2010], but the effect of SNL on their abundance and diversity is less consistent [@macfadyen2013; @shackelford2013] as some taxa may use SNL as a travel corridor or overwintering site, but are not completely dependent on it for reproduction.
@@
 <!-- Small patches of SNL can have a large effect if overall landscape lacks SNL (landscape contrast [@boetzl2020; @vanSchalkwyk2020]) -->
-In this way, the spillover of beneficial arthropods into crops depends not only on the amount of adjacent SNL, but the specific habitat type, the time of the year, and the spatial scale at which an organism gathers resources.
+In this way, the spillover of beneficial arthropods into crops depends not only on the amount of adjacent SNL, but the specific habitat type, the time of the year, and the spatial scale at which an organism forages.
 
 Despite what is known about the spatial and temporal aspects of beneficial arthropod spillover, these are rarely considered together.
-First, some non-crop habitat may act as origins of arthropods during some times of the year, but as destinations during other times, meaning that the timing of spillover from non-crop habitat may not align with important periods in crop development.
-Arthropods can migrate from managed crops back into adjacent SNL at the end of the season [@desender1988; @tscharntke2005b], but this is seldom considered.
+First, non-crop habitat may act as an origin of arthropods during some times of the year, but as a destination during other times, meaning that the timing of spillover from non-crop habitat may not align with important periods of crop growth.
+Arthropods can move from crops back into SNL at the end of the season [@desender1988; @tscharntke2005b], but this is seldom considered.
 Second, the spatial "grain" of the landscape that is relevant to an organism depends on their traits and life history [@ahrenfeldt2015].
@@
 1.
-Untilled semi-natural land provides egg-laying and feeding areas for predatory arthropods, meaning that it should act as an origin of arthropods during the early part of the season, and a destination during the later part of the season.
+Untilled semi-natural land provides egg-laying and feeding areas for predatory arthropods, meaning that it should act as an _origin_ of arthropods during the early part of the season, and a _destination_ during the later part of the season.
 2.
@@
 However, increased counts of organisms in pitfall traps can represent higher activity levels (same number of organisms but more mobile) or higher abundances in the vicinity of the trap.
-This makes it impossible to disentangle arthropod activity from density using single traps [@lang2000; @zhao2013], meaning that counts in the traps represent the "activity-density" of a given organism.
+This makes it impossible to disentangle arthropod activity from density using single traps [@lang2000; @zhao2013], meaning that counts from traps represent the "activity-density" of a given organism, not absolute density.
 Despite this drawback, activity-density is generally positively related to pest consumption, at least in carabids [@trichard2014; @boetzl2018; @gonzalez2020], making it acceptable for our study.

### 2020-11-09 manuscript/manuscript.Rmd
Fixed merge

--- 2020-11-06 manuscript/manuscript.Rmd
@@
 <!-- Small patches of SNL can have a large effect if overall landscape lacks SNL (landscape contrast [@boetzl2020; @vanSchalkwyk2020]) -->
-In this way, the spillover of beneficial arthropods into crops depends not only on the amount of adjacent SNL, but the specific habitat type, the time of the year, and the spatial scale at which an organism gathers resources.
+In this way, the spillover of beneficial arthropods into crops depends not only on the amount of adjacent SNL, but the specific habitat type, the time of the year, and the spatial scale at which an organism forages.
 

### 2020-11-10 manuscript/abstract.Rmd
Updated manuscript
- Moved abstract to separate file
- Moved Supplemental to separate file

1. Ground-dwelling arthropods can be important generalist predators in agroecosystems, and can use non-crop features as overwintering habitats. However, it is unclear which types of landscape features constitute useful non-crop habitat, and at what spatial scale organisms gather resources. Additionally, the same landscape feature may act as a source or a destination for arthropods at different times of the year, but this is rarely considered. \\newline
2. We modeled the abundance of four common species of Canadian prairie arthropods caught in a set of 198 in-field and roadside pitfall traps (June to August of 2017). Functional regression was used in order to simultaneously consider both the habitat preferences and the timing of movement from the land cover classes. \\newline
3. _Pterostichus melanarius_ (Coleoptera: Carabidae) and _Pardosa moesta_ (Araneae: Lycosidae) were attracted to canola (_Brassica napus_) during the early summer, then dispersed to grasslands, wetlands, and grassy road margins at the end of the summer. In particular, _Pterostichus melanarius_ aggregated in canola early in the growing season, suggesting that its role in suppressing crop pests may be underestimated. _Pardosa moesta_ (Araneae: Lycosidae) and _Phalangium opilio_ (Opiliones: Opilionidae) showed weak patterns of seasonal migration, and were more influenced by large-scale geographic patterns rather than landscape composition. \\newline
4. Synthesis and applications: Our results suggest that predatory arthropods migrate into canola crops during the early summer, and that grasslands and wetlands act as seasonal reservoir habitats. Farmers and land managers should consider preserving existing habitat in order to maintain pest-control services across the season.

### 2020-11-10 manuscript/manuscript.Rmd
Updated manuscript
- Moved abstract to separate file
- Moved Supplemental to separate file

@@
 author:
-  - name: Samuel Robinson
+  - name: Samuel V. J. Robinson
     email: samuel.robinson@ucalgary.ca
@@
     affiliation: Ambrose University
-  - name: Jess Vickruck
+  - name: Jess L. Vickruck
     email: jessica.vickruck@canada.ca
     affiliation: University of Calgary
-  - name: Lincoln Best
+  - name: Lincoln R. Best
     email: lincoln.best@oregonstate.edu
@@
 date: "Spring 2020"
-abstract: "Ground-dwelling arthropods can be important generalist predators in agroecosystems, and can use non-crop features as overwintering habitats.
-However, it is unclear which types of landscape features constitute useful non-crop habitat, and at what spatial scale organisms gather resources.
-Additionally, the same landscape feature may act as a source or destination for arthropods at different times of the year, but this is rarely considered.
-We modeled the abundance of four highly-abundant species of Canadian prairie arthropods caught in pitfall traps, and used functional regression to simultaneously consider both their habitat preferences and the timing of sources and destinations.
-_Pterostichus melanarius_ (Coleoptera: Carabidae) and _Pardosa moesta_ (Arachnida: Lycosidae) appear to be attracted to canola (_Brassica napus_ L.) during the early summer, then dispersed to grasslands, wetlands, and grassy road margins during the end of the summer.
-This suggests that grasslands and wetlands act as seasonal reservoir habitats for predatory arthropods, and that farmers should consider preserving existing habitat in order to maintain pest-control services across the season."
-
+abstract: "`r paste(readLines('abstract.Rmd'), collapse = ' ')`"
+keep_tex: true
+keywords:
+  - beetles;
+  - spiders;
+  - harvestmen;
+  - movement;
+  - ecosystem services;
+  - natural enemy;
+  - functional data analysis;
+  - seminatural land
 bibliography: refs.bib
-csl: ecology-letters.csl
 geometry: "left=3cm,right=3cm,top=3cm,bottom=3cm"
@@
     fig_caption: true
+csl: journal-of-applied-ecology.csl    
 header-includes:
+  \makeatletter \def\ps@pprintTitle{  \let\@oddhead\@empty  \let\@evenhead\@empty  \def\@oddfoot{\centerline{\thepage}} \let\@evenfoot\@oddfoot} \makeatother
   \usepackage{float} \floatplacement{figure}{H} 
-  \newcommand{\beginsupplement}{\setcounter{table}{0} \newpage \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
+  \newcommand{\beginsupplement}{\setcounter{table}{0} \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
   \usepackage{setspace}
@@
 ---
-
-<!-- This argument in YAML header adds "manuscript_appendix.md" after document -->
-<!-- output: -->
-<!--   bookdown::html_document2: -->
-<!--     pandoc_args: ["--include-after-body=manuscript_appendix.md"] -->
 
@@
 
-Key words: beetles; spiders; harvestmen; movement; natural enemies; functional regression
-
 \newpage
@@
 We used 582 mL Solo® cups buried up to the rim and partially filled with propylene glycol, with 2 cm wire mesh mounted over the rim to prevent vertebrates from falling into the traps.
-Specimens were identified to species using appropriate taxonomic literature [@dondale1990; @edgar1990; @vogel2004; @yigit2007].
+Specimens were identified to species using appropriate taxonomic literature [@lindroth1966; @dondale1990; @edgar1990; @vogel2004; @yigit2007].
 
@@
 This allows for the possibility that the size of the landscape "grain" relevant to a given organism may change over the course of its life stages [@addicott1987; @lima1996; @gardiner2010].
-It also allows for the possibility that certain land cover types may be locally beneficial, but detremental at large scales, indicating that the cover type may not constitute a completely usable habitat.
+It also allows for the possibility that certain land cover types may be locally beneficial, but detrimental at large scales, indicating that the cover type may not constitute a completely usable habitat.
 
@@
 
-# Applications
-
 Our work has three main applications.
@@
 
+# Authors' contributions
+
+SVJR and PG conceived of the project.
+JV, DE, and LB conducted field work and taxonomic work.
+SVJR designed the statistical analysis and wrote the manuscript.
+JV, DE, LB, and PG all gave critical feedback on the manuscript, and give their approval for the final version.
+
 # Acknowledgements
@@
 Many thanks to the farmers who gave us access to their land for this study.
-This also would not have been possible without the help of Michael Gavin, Jennifer Retzlaff, and Mugunzal Abarmayan, and John Swann.
-Funding for this research was provided by Ducks Unlimited Canada's Institute for Wetland and waterfowl Research, the Alberta Canola Producers Commission, Manitoba Canola Growers Association, SaskCanola, the Alberta Biodiversity Monitoring Institute, the Alberta Conservation Association.
+This project would not have been possible without the help of Michael Gavin, Jennifer Retzlaff, Mugunzal Abarmayan, Riley Waytes, Natasha Morden, and Amy Krause, who helped with field work, and John Swann, who providing lab space for sorting and identification.
+Funding for this research was provided by Ducks Unlimited Canada's Institute for Wetland and Waterfowl Research, the Alberta Canola Producers Commission, Manitoba Canola Growers Association, SaskCanola, the Alberta Biodiversity Monitoring Institute, and the Alberta Conservation Association.
 
-\newpage
+# References {-}
 
-# Supplementary Material {-}
+<div id="refs"></div>
 
-\beginsupplement
-
-```{r concurvity, echo=FALSE, fig.cap='Concurvity estimates for reduced cover classes used in models.', out.width='100%'}  
-  include_graphics('../figures/coverCorPlots/concurvityEstimate_reduced.png',dpi=NA)
+```{r child = 'supplemental.Rmd'}
 ```
-
-```{r landscapeComp, echo=FALSE, fig.cap='Percent cover of landscape cover classes in annuli surrounding each trap location.
-Sites are represented by individual lines.
-Mean cover for each class is listed in each sub-heading.', fig.width=5, fig.height=5}
-coverList %>% group_by(cover) %>% mutate(p=sum(prop)) %>% ungroup() %>% mutate(p=100*round(p/sum(unique(p)),4)) %>% 
-  mutate(cover=paste0(as.character(cover),' (',p,'%)'),prop=prop*100) %>% 
-  mutate(cover=factor(cover,levels=unique(cover))) %>% 
-  ggplot(aes(dist,prop,group=site))+geom_line(alpha=0.2)+
-  facet_wrap(~cover,ncol=4)+theme_classic()+theme(axis.text = element_text(size = 8),strip.text=element_text(size=8))+
-  labs(y='Percent cover',x='Distance from trap location (m)')
-```
-
-(ref:PteMelSTCap) Temporal and spatial components of _Pterostichus melanarius_ activity-density (after accounting for landscape composition and trap location).
-a) shows the effect of day of year, and b) shows the spatially smoothed effect of site location.
-
-```{r PteMelSpatiotemporal, echo=FALSE, fig.cap='(ref:PteMelSTCap)', out.width='100%'}
-  include_graphics('../figures/Pterostichus_melanarius_raneff.png',dpi=NA)
-```
-
-(ref:ParDisSTCap) Temporal and spatial components of _Pardosa distincta_ activity-density (after accounting for landscape composition and trap location).
-a) shows the effect of day of year, and b) shows the spatially smoothed effect of site location.
-
-```{r ParDisSpatiotemporal, echo=FALSE, fig.cap='(ref:ParDisSTCap)', out.width='100%'}
-  include_graphics('../figures/Pardosa_distincta_raneff.png',dpi=NA)
-```
-
-(ref:ParMoeSTCap) Temporal and spatial components of _Pardosa moesta_ activity-density (after accounting for landscape composition and trap location).
-a) shows the effect of day of year, and b) shows the spatially smoothed effect of site location.
-
-```{r ParMoeSpatiotemporal, echo=FALSE, fig.cap='(ref:ParMoeSTCap)', out.width='100%'}
-  include_graphics('../figures/Pardosa_moesta_raneff.png',dpi=NA)
-```
-
-(ref:OpilioSTCap) Temporal and spatial components of _Phalangium opilio_ activity-density (after accounting for landscape composition and trap location).
-a) shows the effect of day of year, and b) shows the spatially smoothed effect of site location.
-
-```{r OpilioSpatiotemporal, echo=FALSE, fig.cap='(ref:OpilioSTCap)', out.width='100%'}
-  include_graphics('../figures/Opiliones_raneff.png',dpi=NA)
-```
-
-```{r PteMelLinear, echo=FALSE, warning=FALSE}
-pmelLinTerms %>% select(-p) %>% 
-  kable(.,caption='Trap location (cover type that trap was located in) intercept estimates for \\emph{Pterostichus melanarius}',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
-      digits=c(1,2,2,2,2),align='rrrrl',escape=FALSE)
-```
-
-```{r PteMelSmooth, echo=FALSE, warning=FALSE}
-pmelSmTerms %>% select(-Ref.df,-p) %>% 
-  kable(.,caption='Smooth terms for \\emph{Pterostichus melanarius}.
-\\emph{s} indicates a thin-plate spline, \\emph{ti} indicates a tensor-product interaction.
-All terms except for day and (E,N) are functional regression fits.',
-      col.names=c('Smoothing term','E.d.f.','$\\chi^2$','p'),
-      digits=c(1,2,2,2),align='rrll',escape=FALSE)
-```
-
-```{r ParDisLinear, echo=FALSE, warning=FALSE}
-pdisLinTerms %>% select(-p) %>% 
-  kable(.,caption='Trap location (cover type that trap was located in) intercept estimates for \\emph{Pardosa distincta}',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
-        digits=c(1,2,2,2,2),align='rrrrl',escape=FALSE)
-```
-
-```{r ParDisSmooth, echo=FALSE, warning=FALSE}
-pdisSmTerms %>% select(-Ref.df,-p) %>% 
-  kable(.,caption='Smooth terms for \\emph{Pardosa distincta}.
-\\emph{s} indicates a thin-plate spline, \\emph{ti} indicates a tensor-product interaction.
-All terms except for day and (E,N) are functional regression fits.',
-        col.names=c('Smoothing term','E.d.f.','$\\chi^2$','p'),
-        digits=c(1,2,2,2),align='rrll',escape=FALSE)
-```
-
-```{r ParMoeLinear, echo=FALSE, warning=FALSE}
-pmoeLinTerms %>% select(-p) %>% 
-  kable(.,caption='Trap location (cover type that trap was located in) intercept estimates for \\emph{Pardosa moesta}.',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
-        digits=c(1,2,2,2,2),align='rrrrl',escape=FALSE)
-```
-
-```{r ParMoeSmooth, echo=FALSE, warning=FALSE}
-pmoeSmTerms %>% select(-Ref.df,-p) %>% 
-  kable(.,caption='Smooth terms for \\emph{Pardosa moesta}.
-\\emph{s} indicates a thin-plate spline, \\emph{ti} indicates a tensor-product interaction.
-All terms except for day and (E,N) are functional regression fits.',
-        col.names=c('Smoothing term','E.d.f.','$\\chi^2$','p'),
-        digits=c(1,2,2,2),align='rrll',escape=FALSE)
-```
-
-```{r OpilioLinear, echo=FALSE, warning=FALSE}
-opilLinTerms %>% select(-p) %>% 
-  kable(.,caption='Trap location (cover type that trap was located in) intercept estimates for \\emph{Phalangium opilio}',col.names=c('Trap location','$\\beta$','S.E.','Z','p'),
-        digits=c(1,2,2,2,2),align='rrrrl',escape=FALSE)
-```
-
-```{r OpilioSmooth, echo=FALSE, warning=FALSE}
-opilSmTerms %>% select(-Ref.df,-p) %>% 
-  kable(.,caption='Smooth terms for \\emph{Phalangium opilio}.
-\\emph{s} indicates a thin-plate spline, \\emph{ti} indicates a tensor-product interaction.
-All terms except for day and (E,N) are functional regression fits.',
-        col.names=c('Smoothing term','E.d.f.','$\\chi^2$','p'),
-        digits=c(1,2,2,2),align='rrll',escape=FALSE)
-```
-
-# References

### 2020-11-10 manuscript/supplemental.Rmd
Updated manuscript
- Moved abstract to separate file
- Moved Supplemental to separate file

--- 2020-10-15 manuscript/manuscript_outline.Rmd
@@
----
-title: "Beneficial arthropod habitat useage changes within-season: implications for pest control services in croplands"
-#Potential titles: 
-# Non-crop features influence the abundance and timing of beneficial arthropod abundance
-# 1) Cropland ecosystem services in space and time: Beneficial arthropod habitat use shifts within-season.
-# 2) Beneficial arthropod habitat use shifts within-season: implications for pest control services in croplands
-# 
-author:
-  - name: Samuel Robinson
-    email: samuel.robinson@ucalgary.ca
-    affiliation: University of Calgary
-    footnote: 1
-  - name: Diane Edwards
-    email: diane.edwards.ca@gmail.com
-    affiliation: Ambrose University
-  - name: Jess Vickruck
-    email: jessica.vickruck@canada.ca
-    affiliation: University of Calgary
-  - name: Lincoln Best
-    email: lincoln.best@oregonstate.edu
-    affiliation: Oregon State University
-  - name: Paul Galpern
-    email: paul.galpern@ucalgary.ca
-    affiliation: University of Calgary
-address:
-  - code: University of Calgary
-    address: 2500 University Drive NW, Calgary, AB, Canada
-  - code: Ambrose University
-    address: 150 Ambrose Circle SW, Calgary, AB
-  - code: Oregon State University
-    address: 1500 SW Jefferson Way, Corvallis, OR, USA
-footnote:
-  - code: 1
-    text: "Corresponding Author"
-date: "Spring 2020"
-abstract: Ground-dwelling arthropods are important generalist predators in agro-ecosystems, and can use non-crop features as overwintering habitats.
-However, it is unclear which types of landscape features constitute useful non-crop habitat, and at what spatial scale organisms gather resources at.
-Additionally, the same landscape feature may act as a sink or a source of arthropods at different times of the year, but this is rarely considered.
-We modeled the activity-density of four highly-abundant species of Canadian prairie arthropods, and used functional regression to simultaneously consider both their habitat preferences and the timing of sources and sinks.
-We found that canola crops (_Brassica napus_ L.) acted as early-season sources, and that grasses and wetlands acted as late-season sinks of arthropods.
-Farmers should consider preserving existing grasslands and wetlands to act as reservoir habitats for the surrounding cropland.
-
-bibliography: refs.bib
-csl: ecology-letters.csl
-geometry: "left=3cm,right=3cm,top=3cm,bottom=3cm"
-output: 
-  bookdown::pdf_book:
-    base_format: rticles::elsevier_article
-    toc: false
-    fig_caption: true
-header-includes: 
-  \usepackage{float} \floatplacement{figure}{H} 
-  \newcommand{\beginsupplement}{\setcounter{table}{0} \newpage \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
-  \usepackage{setspace}
-  \linenumbers
----
-
-<!-- This argument in YAML header adds "manuscript_appendix.md" after document -->
-<!-- output: -->
-<!--   bookdown::html_document2: -->
-<!--     pandoc_args: ["--include-after-body=manuscript_appendix.md"] -->
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-library(knitr)
-library(kableExtra)
-library(tidyverse)
-library(mgcv)
-
-#Load models
-load('../data/PteMelMod.Rdata')
-load('../data/ParDisMod.Rdata')
-load('../data/ParMoeMod.Rdata')
-load('../data/OpilioMod.Rdata')
-
-source('../helperFunctions.R') #Load helper functions
-
-#Forces numbers displayed in inline hooks to be rounded
-inline_hook <- function(x) {
-  if (is.numeric(x)) {
-    format(x, digits = 2)
-  } else x
-}
-knitr::knit_hooks$set(inline = inline_hook)
-
-#Get landscape % cover for each cover class
-coverList <- PteMelMod$datList[9:25]
-siteID <- as.numeric(rownames(unique(cbind(PteMelMod$datList$E,PteMelMod$datList$N))))
-coverList <- lapply(coverList,function(x){
-  data.frame(site=as.character(siteID),x[siteID,]) %>%  #Get unique sites only, convert to DF
-  pivot_longer(cols=d30:d1500,names_to='dist',values_to='prop') %>% 
-  mutate(dist=as.numeric(gsub('d','',dist)))
-})
-coverList <- data.frame(cover=rep(names(coverList),each=nrow(coverList[[1]])),do.call('rbind',coverList))
-
-#Calculate marginal and conditional R2 (Nakagawa and Schielzeth 2013)
-
-#Overall R2 (conditional/marginal)
-r2Nakagawa <- sapply(list(PteMelMod=PteMelMod,ParDisMod=ParDisMod,ParMoeMod=ParMoeMod,OpilioMod=OpilioMod), function(modList){
-  with(modList,getR2Terms(mod3,intVal=exp(mod1$coefficients[[1]]),thetaVal=mod1$family$getTheta(TRUE)))
-}) %>% round(.,3) %>% as.data.frame()
-
-#Piecewise R2
-r2Nakagawa2 <- lapply(list(PteMelMod=PteMelMod,ParDisMod=ParDisMod,ParMoeMod=ParMoeMod,OpilioMod=OpilioMod), function(modList){
-  with(modList,getR2Terms(mod3,intVal=exp(mod1$coefficients[[1]]),thetaVal=mod1$family$getTheta(TRUE),individual=TRUE)) %>%
-    mutate(fixed=!grepl('(day|E,N|sigmaD)',terms),random=grepl('(day|E,N)',terms)) %>% 
-    mutate(r2comp=round(var/sum(var),4))
-}) %>% do.call('rbind',.) %>% rownames_to_column('model') %>% mutate(model=gsub('.[0-9]{1,2}','',model))
-
-#Extract Pterostichus melanarius results
-pmelRes <- summary(PteMelMod$mod3)
-pmelLinTerms <- pmelRes$p.table %>% as.data.frame() %>% 
-  rownames_to_column('loc') %>% 
-  mutate(loc=gsub('trapLoc','',loc)) %>% 
-  mutate(loc=gsub('ditch','road margin',loc),loc=gsub('native','grassland',loc),loc=firstUpper(gsub('pivot','field edge',loc))) %>%
-  rename(p='Pr(>|z|)') %>% mutate(p=roundLess(p,3)) %>% 
-  mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
-  mutate(pTable=ifelse(sig,boldLaTeX(p),p)) %>% select(-sig) #Make text bold
-
-pmelSmTerms <- pmelRes$s.table %>% as.data.frame() %>% 
-  rownames_to_column('Smoother') %>% 
-  mutate(Smoother=gsub('distMat','Distance',Smoother),Smoother=gsub('endDayMat','Day',Smoother),Smoother=gsub('day','Day',Smoother)) %>%
-  mutate(Smoother=gsub('GrassWetland','Grassland',Smoother),Smoother=gsub('TreeShrub','Woodland',Smoother)) %>% 
-  rename(p='p-value') %>% mutate(p=roundLess(p,3)) %>% mutate_at(vars(2:4),roundLess,dig=2) %>% 
-  mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
-  mutate(pTable=ifelse(sig,boldLaTeX(p),p)) %>% select(-sig) #Make text bold
-
-#Extract Pardosa distincta results
-pdisRes <- summary(ParDisMod$mod3)
-pdisLinTerms <- pdisRes$p.table %>% as.data.frame() %>% 
-  rownames_to_column('loc') %>% 
-  mutate(loc=gsub('trapLoc','',loc)) %>% 
-  mutate(loc=gsub('ditch','road margin',loc),loc=gsub('native','grassland',loc),loc=firstUpper(gsub('pivot','field edge',loc))) %>%
-  rename(p='Pr(>|z|)') %>% mutate(p=roundLess(p,3)) %>% 
-  mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
-  mutate(pTable=ifelse(sig,boldLaTeX(p),p)) %>% select(-sig) #Make text bold
-pdisSmTerms <- pdisRes$s.table %>% as.data.frame() %>% 
-  rownames_to_column('Smoother') %>% 
-  mutate(Smoother=gsub('distMat','Distance',Smoother),Smoother=gsub('endDayMat','Day',Smoother),Smoother=gsub('day','Day',Smoother)) %>% 
-  mutate(Smoother=gsub('GrassWetland','Grassland',Smoother),Smoother=gsub('TreeShrub','Woodland',Smoother)) %>% 
-  rename(p='p-value') %>% mutate(p=roundLess(p,3)) %>% mutate_at(vars(2:4),roundLess,dig=2) %>% 
-  mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
-  mutate(pTable=ifelse(sig,boldLaTeX(p),p)) %>% select(-sig) #Make text bold
-
-#Extract Pardosa moesta results
-pmoeRes <- summary(ParMoeMod$mod3)
-pmoeLinTerms <- pmoeRes$p.table %>% as.data.frame() %>% 
-  rownames_to_column('loc') %>% 
-  mutate(loc=gsub('trapLoc','',loc)) %>% 
-  mutate(loc=gsub('ditch','road margin',loc),loc=gsub('native','grassland',loc),loc=firstUpper(gsub('pivot','field edge',loc))) %>%
-  rename(p='Pr(>|z|)') %>% mutate(p=roundLess(p,3)) %>% 
-  mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
-  mutate(pTable=ifelse(sig,boldLaTeX(p),p)) %>% select(-sig) #Make text bold
-pmoeSmTerms <- pmoeRes$s.table %>% as.data.frame() %>% 
-  rownames_to_column('Smoother') %>% 
-  mutate(Smoother=gsub('distMat','Distance',Smoother),Smoother=gsub('endDayMat','Day',Smoother),Smoother=gsub('day','Day',Smoother)) %>% 
-  mutate(Smoother=gsub('GrassWetland','Grassland',Smoother),Smoother=gsub('TreeShrub','Woodland',Smoother)) %>% 
-  rename(p='p-value') %>% mutate(p=roundLess(p,3)) %>% mutate_at(vars(2:4),roundLess,dig=2) %>% 
-  mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
-  mutate(pTable=ifelse(sig,boldLaTeX(p),p)) %>% select(-sig) #Make text bold
-
-#Extract Phalangium opilio results
-opilRes <- summary(OpilioMod$mod3)
-opilLinTerms <- opilRes$p.table %>% as.data.frame() %>% 
-  rownames_to_column('loc') %>% 
-  mutate(loc=gsub('trapLoc','',loc)) %>% 
-  mutate(loc=gsub('ditch','road margin',loc),loc=gsub('native','grassland',loc),loc=firstUpper(gsub('pivot','field edge',loc))) %>%
-  rename(p='Pr(>|z|)') %>% mutate(p=roundLess(p,3)) %>% 
-  mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
-  mutate(pTable=ifelse(sig,boldLaTeX(p),p)) %>% select(-sig) #Make text bold
-opilSmTerms <- opilRes$s.table %>% as.data.frame() %>% 
-  rownames_to_column('Smoother') %>% 
-  mutate(Smoother=gsub('distMat','Distance',Smoother),Smoother=gsub('endDayMat','Day',Smoother),Smoother=gsub('day','Day',Smoother)) %>% 
-  mutate(Smoother=gsub('GrassWetland','Grassland',Smoother),Smoother=gsub('TreeShrub','Woodland',Smoother)) %>% 
-  rename(p='p-value') %>% mutate(p=roundLess(p,3)) %>% mutate_at(vars(2:4),roundLess,dig=2) %>% 
-  mutate(sig=is.na(as.numeric(p))|as.numeric(p)<0.05) %>% #If p<0.05
-  mutate(pTable=ifelse(sig,boldLaTeX(p),p)) %>% select(-sig) #Make text bold
-
-# #Extract concurvity from PteMel model
-# mod3concurv <- concurvity(PteMelMod$mod3,FALSE)$estimate
-
-#Get variance components
-varComp <- rownames_to_column(data.frame(gam.vcomp(PteMelMod$mod3),spp='Pterostichus melanarius'),'term') %>% 
-  bind_rows(rownames_to_column(data.frame(gam.vcomp(ParDisMod$mod3),spp='Pardosa distincta'),'term')) %>% 
-  bind_rows(rownames_to_column(data.frame(gam.vcomp(OpilioMod$mod3),spp='Phalangium opilio'),'term')) %>%
-  mutate(term=factor(term,levels=names(PteMelMod$mod3$sp)))
-
-#Get number of traps in each location
-NtrapsPer <- select(PteMelMod$tempTrap,ID,trapLoc,distFrom) %>% data.frame() %>% distinct() %>% group_by(trapLoc) %>% summarize(n=n())
-
-#Get average catch rates per spp
-Ncatches <- lapply(list(PteMelMod,ParDisMod,ParMoeMod,OpilioMod),function(x){
-  with(data.frame(x$datList), data.frame(perDayMean=mean(count/trapdays),perDayMedian=median(count/trapdays),total=sum(count),perDaySD=sd(count/trapdays)))
-}) %>% do.call('rbind',.) %>% mutate(spp=c('PteMel','ParDis','ParMoe','Opilio'))
-
-```
-
-\newpage
-\doublespacing
-
-# Introduction
-Arthropods are one of the most influential groups of animals in agricultural systems.
-Pest arthropods can cause large reductions in crop yield [@oerke2005], which can result in negative downstream economic effects and food insecurity.
-On the other hand, spillover of beneficial arthropods from adjacent non-crop patches can deliver increased crop yields by providing ecosystem services such as extra pollination or pest suppression [@losey2006; @klein2007; @garibaldi2013].
-Seasonal "pulses" of food resources from crop fields act as a bottom-up driver of their associated arthropod communities, meaning that agricultural land can act as a source of nutrients and individuals for adjacent non-crop land [@diekotter2010; @galpern2017].
-These important fluxes of mobile arthropods, both to crops and away from them, are key for managing both crop yield and biodiversity in agroecosystems.
-Finding "win-win" practices is of particular importance to land managers and conservationists; that is, practices that result in better conservation outcomes while maintaining or improving crop yields.
-Finally, agricultural land occupies 15 million km$^2$ (~36%) of land globally [@ramankutty2018], suggesting that there remains great potential to achieve conservation outcomes by adjusting agricultural practices.
-
-Uncultivated semi-natural land (SNL) can act as important habitat for beneficial arthropods [@duelli2003], which may spill over into adjacent cropland.
-Therefore, landscape management is a strategy to increase beneficial arthropod abundance in crops [@albrecht2010; @landis2000; @martin2020; but see @tscharntke2016; @karp2018].
-For example, wild bee abundance in agricultural landscapes is largely driven by flower and nest availability [@roulston2011], and the effect of SNL on bee abundance and diversity is generally positive.
-Predatory arthropods such as beetles or spiders can be limited by water, food, and egg-laying sites [@lovei1996; @purtauf2005; @gardiner2010], but the effect of SNL on their abundance and diversity is less consistent [@macfadyen2013; @shackelford2013] as some taxa may use SNL as a travel corridor or overwintering site, but are not completely dependent on it for reproduction.
-Some taxa are not dependent on SNL at all, and thrive in cultivated landscapes, while others exclusively inhabit SNL and do not venture beyond the edge of cultivated fields.
-For example, carabid beetles are thought to reproduce in field margins, while the adults feed in fields [@desender1988].
-This depends on the life history of the organisms in question, such as the seasonal timing of emergence, feeding, and reproduction, as well as their traits such as dispersal capability.
-Non-adjacent cropland can also influence arthropod abundance if the organisms are long-distance dispersers [@oberg2008].
-<!-- Small patches of SNL can have a large effect if overall landscape lacks SNL (landscape contrast [@boetzl2020; @vanSchalkwyk2020]) -->
-In this way, the spillover of beneficial arthropods into crops depends not only on the amount of adjacent SNL, but the specific habitat type, the time of the year, and the spatial scale at which an organism gathers resources.
-
-Despite what is known about the spatial and temporal aspects of beneficial arthropod spillover, these are rarely considered together.
-First, some non-crop habitat may act as sources of arthropods during some times of the year, but as sinks during other times, meaning that the timing of spillover from non-crop habitat may not align with important periods in crop development.
-Arthropods can migrate from managed crops back into adjacent SNL at the end of the season [@desender1988; @tscharntke2005b], but this is seldom considered.
-Second, the spatial "grain" of the landscape that is relevant to an organism depends on their traits and life history [@ahrenfeldt2015].
-For instance, bumblebee abundance can be controlled by both nearby and far-away SNL abundance [@westphal2006], but this is poorly studied for other groups of beneficial organisms [but see @sander2006].
-Finally, the feeding and life-history characteristics of many predatory ground beetles and spiders are often poorly-documented, especially in North America.
-This makes it difficult to make generalizations of which habitat types harbour beneficial arthropods, making it even more difficult to provide accurate information to farmers about land management practices.
-
-In this study, we used pitfall traps to determine how landscape composition affects the seasonal activity-density of arthropods across a large Canadian prairie agroecosystem.
-We considered the following hypotheses:
-1.
-Untilled semi-natural land provides egg-laying and feeding areas for predatory arthropods, meaning that it should act as a source of arthropods during the early part of the season, and a sink during the later part of the season.
-2.
-Crops act as sources of food (pest insects) for predatory arthropods during the growing season.
-This should result in agricultural land becoming a sink for predators in the early part of the season as they migrate into the crop, and a source at the end of the season as they migrate out of the crop.
-3. Crops may act as a temporary feeding site for predators. Therefore, crops may act as a local sink for arthropods, but will also be negatively associated at larger (landscape-level) scales.
-Using a large pitfall trapping dataset, we related seasonal changes in arthropod abundance to landscape composition at multiple spatial scales.
-
-# Methods
-
-## Data collection
-We used a set of `r sum(NtrapsPer$n)` pitfall traps installed in road margins (minimum of 5 m away from the road edge, `r with(NtrapsPer, sum(n[trapLoc=='ditch']))` traps) and in-field locations (`r with(NtrapsPer, sum(n[trapLoc!='ditch']))`) across southern Alberta, Canada in 2017 (Figure \@ref(fig:siteMap)).
-The sites spanned a west-to-east gradient of four natural subregions, including foothills parkland, foothills fescue, mixedgrass, and dry mixedgrass [@ABRegions2006].
-Traps were placed starting on `r format(as.Date(as.character(min(PteMelMod$tempTrap$startjulian)),format='%j'),format='%B %d')`, and collections ended on `r format(as.Date(as.character(max(PteMelMod$tempTrap$endjulian)),format='%j'),format='%B %d')`, with collection occurring continuously and traps being emptied every `r round(mean(PteMelMod$tempTrap$trapdays),1)` days on average (SD: `r round(sd(PteMelMod$tempTrap$trapdays),1)`).
-This resulted in `r nrow(PteMelMod$tempTrap)` unique collection events, taking place across a total of `r round(sum(PteMelMod$tempTrap$trapdays),1)` trapping days.
-In-field traps were placed in canola crops (`r with(NtrapsPer, sum(n[trapLoc=='canola']))`), wetlands (`r with(NtrapsPer, sum(n[trapLoc=='wetland']))`), grassy field edges (`r with(NtrapsPer, sum(n[trapLoc=='pivot']))`), and remnant prairie grasslands (`r with(NtrapsPer, sum(n[trapLoc=='native']))`).
-Traps in canola were installed at 25, 75, and 200 m along a transect heading away from the nearest non-crop feature (wetland, grassy field edges, or remnant prairie), while the trap at 0 m was installed in the non-crop feature itself.
-We used 582 mL Solo® cups buried up to the rim and partially filled with ethylene glycol, with 2 cm wire mesh mounted over the rim to prevent vertebrates from falling into the traps.
-Specimens were identified to species using appropriate taxonomic literature [@dondale1990; @edgar1990; @vogel2004; @yigit2007].
-
-We used counts of organisms in our pitfall traps as proxies of ecosystem service provision.
-However, increased counts of organisms in pitfall traps can represent higher activity levels (same number of organisms but more mobile) or higher abundances in the vicinity of the trap.
-This makes it impossible to disentangle arthropod activity from density using single traps [@lang2000; @zhao2013], meaning that counts in the traps represent the "activity-density" of a given organism.
-Despite this disadvantage, activity-density is generally positively related to ecosystem services, at least in carabids [@trichard2014; @boetzl2018; @gonzalez2020], making it acceptable for our study.
-
-```{r siteMap, echo=FALSE, fig.cap='Location of pitfall traps during 2017, and classified cover f.
-Inset map shows study location within Alberta.
-Roadside traps were installed in road margins, while in-field traps were installed directly in canola fields or in adjacent wetland or grassy field edges.', out.width='100%'}
-  include_graphics('../figures/maps/PF2017Map.png',dpi=NA)
-```
-
-We used four highly-abundant species of predatory arthropods found in the pitfall traps, as common species are often more important for ecosystem service provision than rare species [@winfree2015], but their habitat preferences are still poorly understood.
-_Pterostichus melanarius_ is an introduced predatory ground beetle (Coleoptera: Carabidae) that is a wide-ranging generalist known to prey upon crop pests [@carcamo1994; @larsen2003; @busch_Msc].
-It is commonly found in untilled grasslands [@purtauf2005] and may use grassy field edges as larval habitat [@desender1988].
-_Pardosa_ are wolf spiders (Araneae: Lycosidae) that use an active wandering predation strategy [@young1990], and are common across the Canadian prairies.
-Both _Pardosa distincta_ and _Pardosa moesta_ are found in a wide variety of habitats, but are common in ungrazed pastures [@dondale1990; @carcamo2014].
-_P.
-distincta_ is also commonly found in disturbed environments [@collins1996; @wade2010], while _P.
-moesta_ appear to prefer less frequent disturbances [@graham2003; @kowal2011; but see @dondale1990].
-Other _Pardosa_ are known to use road margins and wooded areas as habitat [@buddle2000; @drapela2011].
-Finally, _Phallangium opilio_ is an introduced harvestman (Opiliones: Phalangiidae) that is found in drier disturbed areas [@bragg2009].
-Juveniles hatch from eggs during the spring, becoming adults during the summer, and eggs are laid during the fall [adults do not overwinter; @bragg2009].
-They are commonly found in human-altered landscapes [@muster2014; @vandepoel2015Msc] and are nocturnal generalist hunters and scavengers [@halaj2000; @allard2005; @allard2005b], mainly eating small soft-bodied invertebrates [@acosta2007].
-
-To characterize landscape composition surrounding the traps, we used publicly available classified landscape data [30 m resolution; @AAFC_data].
-AAFC cropland landscape classifications from 2017 were very accurate for cultivated fields (~90%), but were less accurate for non-crop areas (~70%).
-We combined functionally similar landscape categories (cereals: _Triticum aestivum_ and _Hordeum vulgare_, pulses: _Pisum sativum_ and _Lens culinaris_, forest: coniferous and broadleaf). 
-<!-- The radius of the circle necessary to characterize the landscape depends on the scale of the landscape that matters to a given organism [@addicott1987]. -->
-At each site, we extracted the proportion of each cover class within 30m annuli (rings), with the inner radius of each annulus ranging from 30 to 1470m in increments of 30m (total of 49 annuli, 1.5 km maximum).
-The ten most-common cover classes surrounding our sites represented 98% of the total land cover in our study region: grassland, cereal, canola, pasture, pulses, wetland, urban, shrubland, flax, and forest (Figure \@ref(fig:landscapeComp)); flax was removed, as only a single site had nearby flax cover.
-
-## Statistics
-
-Functional regression [@ramsay2004; @yen2014] was used to incorporate landscape information at different distances, allowing assessment of both local and regional landscape composition [@galpern2020].
-Scalar-on-function regression is a special type of linear regression model ($y=X\beta + e$), where the columns of the model matrix $X$ contain some continuous predictor of the scalar $y$, and the values of the coefficients ($\beta$) are modeled as a smooth function $f(x)$ of the predictors.
-<!-- As an example of scalar-on-function regression, biomass in a plot (scalar) could be modeled as a smoothed function of monthly average temperatures at that plot (function), meaning that the effect of monthly temperatures would also be a function of time.
--->
-In our case, the proportion of landscape cover ($X$) within each annulus surrounding the trap is a function of distance away from the trap, meaning that the coefficients are a smoothed function of distance ($\beta_i = f(distance_i)$), and represent the additive effect of a given type of landscape cover at distances away from the trap (i.e.
-$X\beta$).
-This allows for the possibility that the size of the landscape "grain" relevant to a given organism may change over the course of its life stages [@addicott1987; @lima1996; @gardiner2010].
-It also allows for the possibility that certain land cover types may be locally beneficial, but detremental at wider scales, indicating that the cover type may not constitute a completely usable habitat.
-
-Scalar-on-function regression of activity-density was fit using generalized additive models [_mgcv_ version `r packageVersion('mgcv')`; @wood2017]. 
-Count data of arthropods were modeled using a negative binomial distribution with a log-link function and a single dispersion parameter ($\theta$).
-To account for different lengths of trap exposure, log-days since trap placement were used as a fixed effect with their slope held at 1 ("offset" variable).
-Trapping location was included as a fixed effect with 5 levels (canola, field edge, grassland, road margin, and wetlands) to account for the effect of local cover independent of the surrounding landscape composition.
-Day of year was included as a 1-dimensional smooth, and easting and northing (km east and north of the trap extent centre point) were included as 2-dimensional smooths, in order to account for underlying spatial and temporal autocorrelation in the data.
-
-For each landscape cover class, we used three scalar-on-function terms.
-First, we used the proportion cover in the annuli surrounding each trap location (spatial effect of cover class).
-Second, we used the average landcover in all annuli across days of the year (temporal effect of cover class). 
-Finally, we used a tensor-product interaction of landscape cover and day of year (spatio-temporal interaction of cover class).
-We used 10 basis dimensions for the spatial and temporal landscape smoothers, and 16 basis dimensions for the spatio-temporal interaction.
-This was deemed adequate, as the effective degrees of freedom for all smoothing terms were far below the number of basis dimensions, indicating that no additional basis dimensions were needed (see Tables \@ref(tab:PteMelSmooth), \@ref(tab:ParDisSmooth), \@ref(tab:ParMoeSmooth), \@ref(tab:OpilioSmooth)).
-To remove unimportant terms from the model, we used thin-plate regression splines with shrinkage, a continuous analog to stepwise model selection where weaker terms are completely removed from the model rather than reduced to a line [@marra2011].
-The deviance residuals from each model were visually inspected for normality and equal variance [@hilbe2011; @wood2017].
-Finally, we calculated the R$^2$ for each group of terms [@nakagawa2013; @nakagawa2017].
-
-<!-- + Double-penalization gave qualitatively similar results, but required twice the number of penalty terms, and some of the penalty terms were unstable  -->
-
-Preliminary model fits revealed that some of the landscape terms in our model were strongly concurved with each other, so we removed them from the model or combined them.
-Concurvity is a nonlinear analogue of multicollinearity which can bias estimates of standard errors [@buja1989].
-There is no agreed-upon threshold of "unacceptable" concurvity, but 0.5 is commonly used [@dominici2002; @ramsay2003]. 
-<!-- Some landscape terms were strongly concurved , namely forest and shrubland (max: 0.71), canola and cereal (max: 0.74), and grassland and wetland (max: 0.63). -->
-Trees and shrubs were combined into a single ``woodland" category, and grassland and wetland were combined into a single "grassland" category, as they were strongly positively correlated at all distances, indicating similar feature classes.
-Cereal was removed from the model, as it was negatively correlated with canola cover at distances less than 200m and was positively correlated at distances over 500m, reflecting the most common crop rotations (canola $\rightarrow$ wheat $\rightarrow$ barley) and the commonly-used 800 m block structure of farmland in our study region (quarter-sections).
-This resulted in a reduced set of landscape terms, none of which were strongly concurved with each other (cropland: canola, pulses; SNL: grassland, pasture, woodland, urban; see Figure \@ref(fig:concurvity)).
-
-***
-**Box 1: Interpreting Functional Regression Plots**
-
-Functional linear regression is a special case of linear regression, where both the independent variable is predicted by a functional dependent variable, meaning that the slope is a function (vector) rather a fixed (scalar) value [@ramsay2004; @yen2014].
-Therefore, the interpretation of a functional regression plot is very different from that of a simple linear regression plot.
-Figure \@ref(fig:frExample)a shows a simple linear regression plot of a hypothetical relationship between trap _activity density_ (_y_) and a single predictor, _Proportion cover_ (_x_), which is measured in a circle of a fixed radius (_Distance_) surrounding each trap.
-If we suppose that the relationship between _x_ and _y_ is similar at all radii at which _x_ is measured, then Figure \@ref(fig:frExample)b shows the resulting functional linear regression plot, where the slope ($\beta$) is the same at all distances.
-In reality it is more likely that nearby cover will be more influential on activity density than far-away cover, which would result in a relationship similar to Figure \@ref(fig:frExample)c.
-As functional regression takes any continuous predictor of _y_, it is also possible to use proportion cover (measured within a fixed radius) as a predictor of measurements taken across time, allowing the effect of proportion cover to vary over the course of the season (Figure \@ref(fig:frExample)d).
-Finally, proportion cover over distance and time may be combined into a smoothed surface of effects, representing the spatio-temporal influence of landscape cover on activity density.
-
-```{r frExample, echo=FALSE, fig.cap='Examples of (functional) linear regression plots.
-\\textbf{a)} shows a simple linear regression plot, with a single slope value for a single regressor.
-\\textbf{b)} shows the equivalent plot in functional regression form, where the the slope is a smoothed function that maps onto a function-valued regressor.
-\\textbf{c)} and \\textbf{d)} show functional linear regression plots where the slope varies with the location of the regressor.', out.width='100%'}
-  include_graphics('../figures/frExample.png',dpi=NA)
-```
-
-***
-
-Functional regression plots of landscape composition reveal which cover classes are acting as sources or sinks of organisms, and at what spatial scale.
-Positive effects of nearby landscape cover classes indicate that the cover class acts as a net source (i.e. arthropods spill over *from* it).
-However, negative responses to nearby landscape cover classes can indicate one of two things:
-1) It may indicate that the cover class acts as a sink (i.e.
-organisms spill over *into* it) or 2) it may indicate that the cover class acts as a source, but it is unoccupied (i.e.
-no organisms available to spill over).
-We consider 1) to be the more likely scenario, as it is unlikely that any one cover class is *completely* unoccupied.
-<!-- As these data were collected from a single year, this model does not consider the next-generation fitness consequences of spillover. -->
-For example, a cover class with low-quality habitat could act as an ecological trap [@galpern2017] if it acts as a sink but never as a source.
-Alternatively, a cover class could act as a sink by providing high-quality habitat at certain times of the year (e.g. egg laying/feeding), but act as a source at other times (e.g. during emergence).
-For brevity in the following Results section, we refer to "local" and "landscape"-level effects; local refers to the effects of landscape composition at scales of <500m, whereas landscape refers to scales >500 m.
-Similarly, we refer to "early", "mid", and "late"-season effects, where landscape composition affected abundance from June - July, July - August, or August - September.
-
-# Results
-
-## Landscape composition and trap catches
-
-Grassland, cereal, and canola were the three most-abundant landcover classes surrounding our traps, accounting for `r coverList %>% group_by(cover) %>% summarize(p=sum(prop)) %>% ungroup() %>% arrange(desc(p)) %>% mutate(prop=round(100*p/sum(p),2)) %>% slice(1:3) %>% pull(prop) %>% sum `% of land cover (Figure \@ref(fig:landscapeComp)).
-Several landscape ``fingerprints" were evident in the landscape annuli, with cereal cover increasing with distance away, along with a corresponding decrease in canola cover.
-Study sites were originally chosen for sampling arthropods surrounding canola agroecosystems, so canola was a dominant signal in the landscape, but there was also a large amount of variation in grassland and pasture surrounding each site (Figure \@ref(fig:landscapeComp)).
-Grassland cover was largely constant with distance, but a cluster of sites had uniformly high or low cover of grassland with distance.
-The pitfall traps caught a total of `r with(Ncatches,total[spp=='PteMel'])` _Pterostichus melanarius_, `r with(Ncatches,total[spp=='ParDis'])` _Pardosa distincta_, `r with(Ncatches,total[spp=='ParMoe'])` _Pardosa moesta_, and `r with(Ncatches,total[spp=='Opilio'])` _Phalangium opilio_ (mean trapping rates per day: `r with(Ncatches,paste(round(perDayMean,2),collapse=', '))`, SD: `r with(Ncatches,paste(round(perDaySD,2),collapse=', '))`, respectively).
-
-```{r landscapeComp, echo=FALSE, fig.cap='Landscape composition in annuli surrounding each trap location.
-Sites are represented by individual lines.
-Mean cover for each class is listed in each sub-figure heading.', fig.width=5, fig.height=5}
-coverList %>% group_by(cover) %>% mutate(p=sum(prop)) %>% ungroup() %>% mutate(p=100*round(p/sum(unique(p)),4)) %>% 
-  mutate(cover=paste0(as.character(cover),' (',p,'%)'),prop=prop*100) %>% 
-  mutate(cover=factor(cover,levels=unique(cover))) %>% 
-  ggplot(aes(dist,prop,group=site))+geom_line(alpha=0.2)+
-  facet_wrap(~cover,ncol=4)+theme_classic()+theme(axis.text = element_text(size = 8),strip.text=element_text(size=8))+
-  labs(y='Percent cover',x='Inner radius of annuli (m)')
-```
-
-## *Ground beetle:* Pterostichus melanarius
-
-_P. melanarius_ activity-density was strongly influenced by trap location and landscape composition (Tables \@ref(tab:PteMelLinear), \@ref(tab:PteMelSmooth)).
-Canola crops had a marginally higher activity-density of _P. melanarius_ than other trap locations (Figure \@ref(fig:PteMelLandscape)a).
-Grassland cover was the most important land cover type in explaining activity-density ($R^2$: 0.104, Table \@ref(tab:rSquared)), and local (<500 m) grassland had a negative effect late in the summer (Figure \@ref(fig:PteMelLandscape)b), suggesting that _P.
-melanarius_ may move into grasslands later in the year.
-Local canola had a positive effect in the early season, but landscape-level (>500 m) canola had a negative effect, indicating that areas with widespread canola coverage had lower _P.
-melanarius_ activity-density.
-Pulses acted as a late-season source, indicating that _P. melanarius_ may migrate out of the crop after (or during) harvest.
-Finally, _P.
-melanarius_ activity-density had a strong temporal and spatial component (both p<0.001), indicating that phenology and local geographic factors were important drivers of ground beetle activity-density (Figure \@ref(fig:PteMelSpatiotemporal)).
-Landscape composition and trap location explained `r r2Nakagawa$PteMelMod[1]*100`% of the variance in activity-density, while the spatial and temporal smoothers accounted for `r with(r2Nakagawa,(PteMelMod[2]-PteMelMod[1])*100)`% (Table \@ref(tab:rSquared)).
-
-<!-- Percent signs are escaped in LaTeX, but this causes havoc if used in fig.cap of chunk options (OK if used in internal captions, I think). Yihui uses the following "text references" instead. -->
-(ref:PteMelCap) Landscape influence on _Pterostichus melanarius_ activity-density.
-a) shows the effect of local trap location, and b-c) are functional regression plots of the proportion grassland and canola at distances away from each trap.
-d) is a functional regression plot over time, showing the effect of pulses at different times of the year.
-Lines and dots represent means, and bars and shaded regions represent 95 % confidence intervals (1.96 x SE).
-Coloured regions represent early-, mid-, and late-season effects (red, purple, blue).
-
-```{r PteMelLandscape, echo=FALSE, fig.cap='(ref:PteMelCap)', out.width='100%'}  
-  include_graphics('../figures/Pterostichus_melanarius_fixeff.png',dpi=NA)
-```
-
-## *Wolf spiders:* Pardosa distincta *and* Pardosa moesta
-
-Activity density of _P.
-distincta_ and _P.
-moesta_ was influenced by trap location and landscape composition (Tables \@ref(tab:ParDisLinear), \@ref(tab:ParDisSmooth)), but landscape composition had relatively weak effects on both species ($R^2$: `r filter(r2Nakagawa2,grepl('Par',model),!grepl('s\\(',terms),terms!='trapLoc',terms!='sigmaD') %>% group_by(model) %>% summarize(s=sum(r2comp)) %>% pull(s) %>% paste(.,collapse=', ')`).
-Unlike _P. melanarius_, both _Pardosa_ species had far lower activity-density in canola than any other cover type (Figures \@ref(fig:ParDisLandscape)a, \@ref(fig:ParMoeLandscape)a).
-Activity-density of both _Pardosa_ species had a strong temporal and spatial component, although the temporal component was dominant for _P.
-distincta_, whereas the spatial component was dominant for _P.
-moesta_ (Figures \@ref(fig:ParDisSpatiotemporal) and \@ref(fig:ParMoeSpatiotemporal); both p`r with(pmoeSmTerms,p[Smoother=='s(E,N)'])`).
-
-_P.
-distincta_ activity density responded to pasture and woodlands; landscape-level pasture cover had a negative effect (Figure \@ref(fig:ParDisLandscape)b), while woodlands had a negative effect late in the season (Figure \@ref(fig:ParDisLandscape)c).
-This suggests that large amounts of pasture are unsuitable habitat for _P. distincta_, and that they may migrate into woodlands later in the season.
-However, trap location and the temporal random effect (Figure \@ref(fig:ParDisSpatiotemporal)a) explained roughly 10 times more variance ($R^2$: `r round(sum(filter(r2Nakagawa2,model=='ParDisMod',terms=='trapLoc'|grepl('day',terms))$r2comp),3)`) than landscape composition ($R^2$: `r round(sum(filter(r2Nakagawa2,model=='ParDisMod',terms!='trapLoc',terms!='sigmaD',!grepl('s\\(',terms))$r2comp),3)`), meaning that while _P.
-distincta_ may be locally abundant in certain cover types, it is very generalistic in its overall habitat preferences.
-
-_P. moesta_ activity density responded to grassland, canola, and road margins.
-Grasslands had a local negative effect, but a positive landscape-level effect, indicating that while these cover types act as a local sink, the general amount of grassland in the area had a positive effect (Figure \@ref(fig:ParMoeLandscape)b).
-Nearby local canola had a positive early effect on activity-density, but a negative local effect later in the season (Figure \@ref(fig:ParMoeLandscape)c).
-Local road margins had a similar effect, acting as an early source and a late sink (Figure \@ref(fig:ParMoeLandscape)d).
-Pulses also had a positive effect at the landscape level (Figure \@ref(fig:ParMoeLandscape)e), but this explained very little variance in _P.
-moesta_ activity density (Table \@ref(tab:rSquared), $R^2$: `r round(filter(r2Nakagawa2,model=="ParMoeMod",terms=="Pulses")$r2comp,3)`).
-Similar to _P.distincta_, trap location and an East-West spatial random effect (Figure \@ref(fig:ParMoeSpatiotemporal)b) explained roughly 5 times more variance ($R^2$: `r round(sum(filter(r2Nakagawa2,model=='ParMoeMod',terms=='trapLoc'|grepl('E,N',terms))$r2comp),3)`) in _P.
-moesta_ activity density than landscape composition ($R^2$: `r round(sum(filter(r2Nakagawa2,model=='ParMoeMod',terms!='trapLoc',terms!='sigmaD',!grepl('s\\(',terms))$r2comp),3)`), meaning that _P.
-moesta_ is also highly generalistic in its overall habitat preferences.
-
-(ref:ParDisCap) Landscape influence on _Pardosa distincta_ activity-density.
-Lines and dots represent means, and bars and shaded regions represent 95 % confidence intervals (1.96 x SE).
-Coloured regions represent early-, mid-, and late-season effects (red, purple, blue).
-
-```{r ParDisLandscape, echo=FALSE, fig.cap='(ref:ParDisCap)', out.width='100%'}  
-  include_graphics('../figures/Pardosa_distincta_fixeff.png',dpi=NA)
-```
-
-(ref:ParMoeCap) Landscape influence on _Pardosa moesta_ activity-density.
-Lines and dots represent means, and bars and shaded regions represent 95 % confidence intervals (1.96 x SE).
-Coloured regions represent early-, mid-, and late-season effects (red, purple, blue).
-
-```{r ParMoeLandscape, echo=FALSE, fig.cap='(ref:ParMoeCap)', out.width='100%'}  
-  include_graphics('../figures/Pardosa_moesta_fixeff.png',dpi=NA)
-```
-
-## *Harvestman:* Phalangium opilio
-
-_P.
-opilio_ activity-density was somewhat influenced by trap location, with field edges and wetlands having the highest activity-density (Figure \@ref(fig:OpilioLandscape)a), but this effect was swamped by the effect of landscape and the spatiotemporal random effects (Table \@ref(tab:rSquared)), meaning that _P.
-opilio_ activity density is only mildly influenced by local cover type.
-Nearby grassland and woodland both had negative effects on _Phalangium opilio_ activity-density, but only early in the season (Figures \@ref(fig:OpilioLandscape)b,c), suggesting that _P.
-opilio_ may preferentially migrate to these cover classes.
-The temporal random effect was overwhelmingly the most important predictor of _P.
-opilio_ activity-density ($R^2$: `r round(sum(filter(r2Nakagawa2,model=='OpilioMod',terms=='s(day)')$r2comp),3)`), showing that activity-density increased during the spring, and showed very little decline during the rest of the season (Figure \@ref(fig:OpilioSpatiotemporal)a).
-Similar to _P.
-moesta_, _P.
-opilio_ also showed a distinct East-West spatial random effect (Figure \@ref(fig:OpilioSpatiotemporal)b), indicating that their activity-density is also influenced by larger-scale abiotic factors.
-
-(ref:OpilioCap) Landscape influence on _Phalangium opilio_ activity-density.
-Lines and dots represent means, and bars and shaded regions represent 95 % confidence intervals (1.96 x SE).
-Coloured regions represent early-, mid-, and late-season effects (red, purple, blue).
-
-```{r OpilioLandscape, echo=FALSE, fig.cap='(ref:OpilioCap)', out.width='100%'}  
-  include_graphics('../figures/Opiliones_fixeff.png',dpi=NA)
-```
-
-```{r rSquared, echo=FALSE, out.width='100%'}  
-r2Nakagawa2 %>% select(model,terms,r2comp) %>% mutate(terms=as.character(terms),r2comp=r2comp*1) %>%
-  pivot_wider(names_from=model,values_from=r2comp) %>%
-  mutate(terms=case_when(terms=='trapLoc' ~ 'Trap Location', terms=='s(day)' ~ 'Day of Year',
-                         terms=='s(E,N)' ~ 'Spatial Location', terms=='GrassWetland' ~ 'Grassland',
-                         terms=='TreeShrub' ~ 'Woodland', terms=='sigmaD' ~ 'Residual',
-                         terms=='Urban' ~ 'Road margins', TRUE ~ terms)) %>%
-  kable(.,format='latex',caption='R$^2_{GLMM}$ for model components, representing the proportion of total variance explained by each term.
-R$^2$ was calculated using methods from Nakagawa et al.
-2013 and Nakagawa et al.
-2017.',
-        col.names=linebreak(x=c('Term','\\emph{Pterostichus}\n\\emph{melanarius}','\\emph{Pardosa}\n\\emph{distincta}',
-                              '\\emph{Pardosa}\n\\emph{moesta}','\\emph{Phalangium}\n\\emph{opilio}'),align='l'),
-        digits=c(1,3,3,3,3),align='rllll',escape=FALSE)
-```
-
-```{r resultsTab, echo=FALSE, message=FALSE, warning=FALSE, out.width='100%'}
-#Based on example from:
-# https://stackoverflow.com/questions/31011265/how-to-write-bullet-lists-in-a-table-using-rmarkdown-and-pandoc
-# #Note: this works, but it's very ugly. Trying kable instead
-# mytable <- data.frame(
-#     CoverClass = c("Grassland", "Canola", "Pasture", "Woodland", "Pulses", "Road margins"),
-#     PteMel = c('* Local sink ','* Local source (early) \n* Landscape sink (early)',' ',' ','* Source (late)',' '),
-#     ParDis = c(' ',' ','* Landscape sink',' * Sink (late)',' ',' '),
-#     ParMoe = c('* Local sink \n* Landscape source','* Local source (early) \n* Local sink (late)',' ',' ','* Landscape source','* Local source (early) \n* Local sink (late) \n* Landscape sink (early) \n* Landscape source (late)'),
-#     Opilio = c('* Local sink (early)',' ',' ','* Local sink (early) \n* Landscape source (mid)',' ',' ')
-#     )
-# colnames(mytable) <- c('Cover class','_Pterosticus_ _melanarius_','_Pardosa_ _distincta_','_Pardosa_ _moesta_','_Phalangium_ _opilio_')
-# pander(mytable, keep.line.breaks = TRUE, style = 'grid', justify = 'left', split.table=1000)
-
-#Based on example from:
-# https://stackoverflow.com/questions/52962411/table-with-long-text-bullet-points-and-specific-table-width
-mytable <- data.frame(
-    CoverClass = c("Grassland", "Canola", "Pasture", "Woodland", "Pulses", "Road margins"),
-    PteMel = c('$\\cdot$ Local -- (late)','$\\cdot$ Local + (early) \n$\\cdot$ Landscape -- (early)',' ',' ','$\\cdot$ Overall + (late)',' '),
-    ParDis = c(' ',' ','$\\cdot$ Landscape --',' $\\cdot$ Overall -- (late)',' ',' '),
-    ParMoe = c('$\\cdot$ Local -- \n$\\cdot$ Landscape +','$\\cdot$ Local + (early) \n$\\cdot$ Local -- (late)',' ',' ','$\\cdot$ Landscape +','$\\cdot$ Local + (early) \n$\\cdot$ Local -- (late) \n$\\cdot$ Landscape -- (early) \n$\\cdot$ Landscape + (late)'),
-    Opilio = c('$\\cdot$ Local -- (early)',' ',' ','$\\cdot$ Local -- (early) \n$\\cdot$ Landscape + (mid)',' ',' ')
-    )
-
-mytable %>%
-  mutate_all(linebreak) %>%  # required for linebreaks to work
-  kable(.,format='latex',caption='Summary of model results.
-\\emph{Local/Landscape} denotes cover classes <500m or >500m away from the trap location, respectively.
-+/-- indicates positive or negative effects of the cover class, and \\emph{Early/Mid/Late} denotes whether the effects were present earlier or later during the season.
-Cover classes with weak effects on activity density are not shown.',
-        col.names=linebreak(x=c('Cover class','\\emph{Pterostichus}\n\\emph{melanarius}','\\emph{Pardosa}\n\\emph{distincta}',
-                              '\\emph{Pardosa}\n\\emph{moesta}','\\emph{Phalangium}\n\\emph{opilio}')),
-        align='rllll',escape=FALSE) %>% 
-  column_spec(1, width = "4em") %>% column_spec(c(2:5), width = "9em") # fix column widths
-```
-
-# Discussion
-
-The activity-density of the four arthropods was influenced by landscape composition, but the response of _Pterostichus melanarius_ and _Phalangium opilio_ was much stronger.
-We found support for our predictions of SNL (grassland, woodlands, and road margins) acting as a late-season sinks for beneficial arthropods.
-In particular, _P. melanarius_ was attracted to grasslands, _P. distincta_ to woodlands, and _P. moesta_ to road margins, all at the end of the season.
-While there was limited evidence of SNL acting as early-season sources, some cover classes had a positive effect at the landscape level (grassland and road margins on _P.
-moesta_), indicating earlier or wider-scale dispersal away from these cover classes.
-Canola and pasture had negative landscape-level effects on _P. melanarius_ and _P. distincta_, respectively, meaning that these cover types likely represent only partial habitat for these arthropods.
-There was also a strong temporal component to most of the landscape effects, meaning that it is important to consider how sinks and sources may change over the season.
-Finally, the influence of landscape composition tended to be limited to a radius of about 500m, indicating that large-scale _and_ local land cover can be important to beneficial arthropod abundance.
-These results highlight the seasonal importance of non-crop marginal lands for predatory arthropod abundance.
-
-<!-- 1. ... nearby SNL should act as a source of arthropods during the early part of the season, and a sink during the later part of the season.  -->
-<!-- 2.
-...
-should result in agricultural land becoming a sink for predators in the early part of the season as they migrate into the crop, and a source at the end of the season as they migrate out of the crop.
--->
-<!-- 3. ... crops may act as a local sink for arthropods, but will also be negatively associated at larger (landscape-level) scales. -->
-
-The predatory ground beetle _Pterostichus melanarius_ responded to landscape composition, primarily to canola, pulses, and grass and wetland cover.
-Grassland and wetland cover had a negative late-season effect, suggesting that _P. melanarius_ may migrate into it at the end of the summer.
-Other studies have found similar results, suggesting that untilled land is important off-field habitat for carabids [@desender1988; @fournier2002; but see @hatten2007].
-In particular, @purtauf2005 found that carabid density increased with proportion of nearby grasslands, so our negative late-season effect of grasslands may represent _P.
-melanarius_ moving to overwintering habitat at the end of the season.
-However, _P. melanarius_ is also found in a wide variety of habitats, and tends to prefer agricultural fields [@larsen2003]. 
-Our models also suggest this, as they showed that canola and pulse crops had positive effects on _P. melanarius_ activity-density early in the season.
-Early in the season, canola crops had a local positive effect, but a landscape-level negative effect, which may indicate that they provide only temporary feeding habitat.
-The effect of pulse crops on carabid abundance is not well-studied, but our results suggest that pulses may represent a potential food resource for _P.
-melanarius_, albeit a weak one (Table \@ref(tab:rSquared)).
-Carabids are predators of pea-leaf weevils (_Sitona lineatus_) on other Fabaceae [@hamon1990], and _P.
-melanarius_ can prey upon other carabids that are predators of _S.
-lineatus_, such as _Bembidion quadrimaculatum_ [@vankosky2011], so this effect may be direct or indirect.
-We did not consider the influence of previous years' crops, although carabids tend to be more abundant in areas of high crop rotation [@busch_Msc; @bertrand2016].
-
-The wolf spiders _Pardosa distincta_ and _Pardosa moesta_ both responded to landscape composition, but it explained only a small fraction of their activity-density ($R^2$: `r round(sum(filter(r2Nakagawa2,model=='ParDisMod',terms!='trapLoc',terms!='sigmaD',!grepl('s\\(',terms))$r2comp),3)`, `r round(sum(filter(r2Nakagawa2,model=='ParMoeMod',terms!='trapLoc',terms!='sigmaD',!grepl('s\\(',terms))$r2comp),3)`).
-This means that both species of _Pardosa_ appear to have very general habitat preferences, but may be somewhat influenced by certain cover types.
-Pasture had a negative effect at the landscape scale, and woodland had a late-season negative effect, suggesting that _P.
-distincta_ move to shrubs and trees for overwintering or winter foraging [@aitchison1984; @buddle2000].
-_Pardosa_ are found in areas close to disturbed roadside strips [@drapela2008; @drapela2011; @kowal2011], but _P.
-distincta_ appears to be less sensitive to disturbances than _P.
-moesta_ [@collins1996; @wade2010].
-@moring1994 showed that _P.
-distincta_ were more active in grassy habitats, which we found partial evidence of, as _P.
-distincta_ tended to have higher activity-density in trap locations with higher grass cover (Figure \@ref(fig:ParDisLandscape)a).
-Canola had an early-season positive effect on _P. moesta_, indicating that _P. moesta_ and _P. melanarius_ may both use canola as foraging grounds.
-We also found that road margins had a positive early-season and a negative late-season effect [similar to @drapela2008 and @drapela2011]. 
-Grassland and pulses also had a local negative effect but a positive landscape-level effect; this suggests that they may constitute suitable habitat for _P.
-moesta_ and attract them away from other cover types.
-Lycosids employ a wandering-active predation strategy [@young1990], meaning that nearby landscape composition may be more influential to _Pardosa_ than large-scale composition [@oberg2007; @oberg2008].
-While trapping location explained a large proportion of variance for both species (`r round(filter(r2Nakagawa2,model=='ParDisMod',grepl('trapLoc',terms))$r2comp,2)` and `r round(filter(r2Nakagawa2,model=='ParMoeMod',grepl('trapLoc',terms))$r2comp,2)`), several landscape features were also important at large spatial scales, including grass and wetland, pasture, pulses, and road margins.
-Therefore, _Pardosa_ dispersal distances may be further than previously thought, either through ballooning as juveniles [@richter1970; @greenstone1982] or through other long-distance travel.
-
-_Phalangium opilio_ activity-density responded to grass and wetland cover, as well as trees and shrubs.
-Other studies have found that _P. opilio_ is mostly found in human-altered landscapes with a large proportion of farming [@muster2014; @vandepoel2015Msc].
-Since most of our study area was in or near farmed land, the lack of variation is understandable, but there were a few notable landscape-level patterns that emerged.
-_P. opilio_ activity-density was higher in grassy field edges and wetlands, but grasslands and wetlands had a local negative effect on _P. opilio_ until late in the season.
-These indicate that while grass and wetlands could act as a reservoir, spillover into other land cover types may be limited, as _P.
-opilio_ avoids heavily grazed areas, possibly due to low humidity [@sajna2011].
-_P. opilio_ is also found in large numbers at the edges of forests, and may migrate from forests into farmlands [@vandepoel2015Msc].
-We found the opposite pattern: forests had a weak negative effect on _P. opilio_, at least early in the year.
-Unlike the other arthropods, most of the variation in activity-density for _P.
-opilio_ was explained by day of year (R$^2$ = `r round(filter(r2Nakagawa2,model=='OpilioMod',grepl('day',terms))$r2comp,2)`), indicating strong seasonal emergence cues.
-However, there was also a strong East-West spatial random effect in both _P.
-opilio_ and _P.
-moesta_, meaning that wider-scale geographic patterns (possibly related to rainfall or temperature) also influence their activity-density.
-<!-- Feels like this paragraph ends too soon. Why was there so little variation due to landscape? Link to biology of the critter. -->
-
-Many other studies have considered the overall effect of SNL on ecosystem service provision, but we have highlighted the different spatial and temporal aspects of ecosystem service provision.
-We have shown how a relatively straightforward statistical technique can be used to consider multiple spatial scales of landscape composition, providing richer inference about the processes acting on beneficial arthropods.
-Our results show empirical evidence of arthropod migration between cover types at different times of year, which is rarely considered beyond single-field studies.
-Since we did not directly track individual movements, future studies should directly examine arthropod movement and life-history within matrices of cover types, with the goal of integrating landscape ecology and behavioural processes into a single model [@lima1996].
-This would also allow direct inference about landscape categories that were combined in our dataset, allowing us to consider different landscape categories independently.
-Finally, future work should explicitly link landscape structure, arthropod abundance, and ecosystem services [@gagic2017].
-
-# Implications
-
 \newpage
@@
 
+```{r landscapeComp, echo=FALSE, fig.cap='Percent cover of landscape cover classes in annuli surrounding each trap location.
+Sites are represented by individual lines.
+Mean cover for each class is listed in each sub-heading.', fig.width=5, fig.height=5}
+coverList %>% group_by(cover) %>% mutate(p=sum(prop)) %>% ungroup() %>% mutate(p=100*round(p/sum(unique(p)),4)) %>% 
+  mutate(cover=paste0(as.character(cover),' (',p,'%)'),prop=prop*100) %>% 
+  mutate(cover=factor(cover,levels=unique(cover))) %>% 
+  ggplot(aes(dist,prop,group=site))+geom_line(alpha=0.2)+
+  facet_wrap(~cover,ncol=4)+theme_classic()+theme(axis.text = element_text(size = 8),strip.text=element_text(size=8))+
+  labs(y='Percent cover',x='Distance from trap location (m)')
+```
+
 (ref:PteMelSTCap) Temporal and spatial components of _Pterostichus melanarius_ activity-density (after accounting for landscape composition and trap location).
+a) shows the effect of day of year, and b) shows the spatially smoothed effect of site location.
 
@@
 ```
-
-# References

### 2020-11-10 manuscript/manuscript.Rmd
Ran into word length problem. Need to prune.

@@
     fig_caption: true
-csl: journal-of-applied-ecology.csl    
+csl: ecology-letters.csl    
 header-includes:

### 2020-11-12 manuscript/manuscript.Rmd
Moved Box 1 to Supplemental

@@
 However, increased counts of organisms in pitfall traps can represent higher activity levels (same number of organisms but more mobile) or higher abundances in the vicinity of the trap.
-This makes it impossible to disentangle arthropod activity from density using single traps [@lang2000; @zhao2013], meaning that counts from traps represent the "activity-density" of a given organism, not absolute density.
+This makes it impossible to disentangle arthropod activity from density using single traps [@lang2000], meaning that counts from traps represent the "activity-density" of a given organism, not absolute density.
 Despite this drawback, activity-density is generally positively related to pest consumption, at least in carabids [@trichard2014; @boetzl2018; @gonzalez2020], making it acceptable for our study.
@@
 Juveniles hatch from eggs during the spring, becoming adults during the summer, and eggs are laid during the fall [adults do not overwinter; @bragg2009].
-They are commonly found in human-altered landscapes [@muster2014; @vandepoel2015Msc] and are nocturnal generalist hunters and scavengers [@halaj2000; @allard2005; @allard2005b], mainly eating small soft-bodied invertebrates [@acosta2007].
+They are commonly found in human-altered landscapes [@muster2014; @vandepoel2015Msc] and are nocturnal generalist hunters and scavengers [@halaj2000; @allard2005b], mainly eating small soft-bodied invertebrates [@allard2005; @acosta2007].
 
@@
 
-***
-**Box 1: Interpreting Functional Regression Plots**
-
-Functional linear regression is a special case of linear regression, where both the independent variable is predicted by a functional dependent variable, meaning that the slope is a function (vector) rather a fixed (scalar) value [@ramsay2004; @yen2014].
-Therefore, the interpretation of a functional regression plot is very different from that of a simple linear regression plot.
-Figure \@ref(fig:frExample)a shows a simple linear regression plot of a hypothetical relationship between trap _activity-density_ (_y_) and a single predictor, _proportion cover_ (_x_), which is measured in a circle of a fixed radius surrounding each trap.
-If we suppose that the relationship between _x_ and _y_ is similar at all radii at which _x_ is measured, then Figure \@ref(fig:frExample)b shows the resulting functional linear regression plot, where the slope ($\beta$) is the same at all distances (we avoid the problem of overlapping concentric circles by using concentric _annuli_).
-In reality, it is more likely that nearby cover will be more influential on activity-density than far-away cover, which could result in a relationship similar to Figure \@ref(fig:frExample)c.
-As functional regression takes any continuous predictor of _y_, it is also possible to use proportion cover (measured within an annulus of a fixed radius) as a predictor of measurements taken across time, allowing the effect of proportion cover to vary over the course of the season (Figure \@ref(fig:frExample)d).
-Finally, the effect of proportion cover over distance and time may be modeled as a smoothed surface, representing the joint spatio-temporal influence of landscape cover on activity-density.
-
-```{r frExample, echo=FALSE, fig.cap='Examples of (functional) linear regression plots.
-\\textbf{a)} shows a simple linear regression plot, with a single slope value for a single regressor.
-\\textbf{b)} shows the equivalent plot in functional regression form, where the the slope is a smoothed function that maps onto a function-valued regressor.
-\\textbf{c)} and \\textbf{d)} show functional linear regression plots where the slope varies with the location of the regressor.', out.width='100%'}
-  include_graphics('../figures/frExample.png',dpi=NA)
-```
-
-***
-
-Functional regression plots of landscape composition reveal which cover classes are acting as sources or destinations of a given arthropod, and at what spatial scale.
+Functional regression plots of landscape composition reveal which cover classes are acting as sources or destinations of a given arthropod, and at what spatial scale (Figure \@ref(fig:frExample)).
 Positive effects of nearby landscape cover classes indicate that arthropods are spilling over *from* it, therefore acting as a source.
@@
 opilio_ also showed a distinct East-West spatial random effect (Figure \@ref(fig:OpilioSpatiotemporal)b), indicating that their activity-density is also influenced by larger-scale abiotic factors.
-<!-- JV: THIS EAST-WEST PATTERN SHOULD BE MENTIONED IN THE DISCUSSION -->
 
@@
 opilio_ and _P.
-moesta_, meaning that larger-scale geographic patterns (possibly related to rainfall or temperature) also influence their activity-density.
+moesta_, meaning that larger-scale geographic patterns (rainfall or temperature) are more important influences on their activity-density.
 <!-- Feels like this paragraph ends too soon. Why was there so little variation due to landscape? Link to biology of the critter. -->

### 2020-11-12 manuscript/supplemental.Rmd
Moved Box 1 to Supplemental

@@
 
-# Supplementary Material {-}
+# Appendix A: Supplementary Material {-}
 
@@
 ```
+
+\newpage
+
+# Appendix B: Interpreting Functional Regression Plots {-}
+
+Functional linear regression is a special case of linear regression, where both the independent variable is predicted by a functional dependent variable, meaning that the slope is a function (vector) rather a fixed (scalar) value [@ramsay2004; @yen2014].
+Therefore, the interpretation of a functional regression plot is very different from that of a simple linear regression plot.
+Figure \@ref(fig:frExample)a shows a simple linear regression plot of a hypothetical relationship between trap _activity-density_ (_y_) and a single predictor, _proportion cover_ (_x_), which is measured in a circle of a fixed radius surrounding each trap.
+If we suppose that the relationship between _x_ and _y_ is similar at all radii at which _x_ is measured, then Figure \@ref(fig:frExample)b shows the resulting functional linear regression plot, where the slope ($\beta$) is the same at all distances (we avoid the problem of overlapping concentric circles by using concentric _annuli_).
+In reality, it is more likely that nearby cover will be more influential on activity-density than far-away cover, which could result in a relationship similar to Figure \@ref(fig:frExample)c.
+As functional regression takes any continuous predictor of _y_, it is also possible to use proportion cover (measured within an annulus of a fixed radius) as a predictor of measurements taken across time, allowing the effect of proportion cover to vary over the course of the season (Figure \@ref(fig:frExample)d).
+Finally, the effect of proportion cover over distance and time may be modeled as a smoothed surface, representing the joint spatio-temporal influence of landscape cover on activity-density.
+
+```{r frExample, echo=FALSE, fig.cap='Examples of (functional) linear regression plots.
+\\textbf{a)} shows a simple linear regression plot, with a single slope value for a single regressor.
+\\textbf{b)} shows the equivalent plot in functional regression form, where the the slope is a smoothed function that maps onto a function-valued regressor.
+\\textbf{c)} and \\textbf{d)} show functional linear regression plots where the slope varies with the location of the regressor.', out.width='100%'}
+  include_graphics('../figures/frExample.png',dpi=NA)
+```

### 2020-12-22 manuscript/abstract.Rmd
Submitted to AEE

@@
-1.
 Ground-dwelling arthropods can be important generalist predators in agroecosystems, and can use non-crop features as overwintering habitats.
@@
 Additionally, the same landscape feature may act as a source or a destination for arthropods at different times of the year, but this is rarely considered.
-\\newline
-2.
 We modeled the abundance of four common species of Canadian prairie arthropods caught in a set of 198 in-field and roadside pitfall traps (June to August of 2017).
 Functional regression was used in order to simultaneously consider both the habitat preferences and the timing of movement from the land cover classes.
-\\newline
-3.
 _Pterostichus melanarius_ (Coleoptera: Carabidae) and _Pardosa moesta_ (Araneae: Lycosidae) were attracted to canola (_Brassica napus_) during the early summer, then dispersed to grasslands, wetlands, and grassy road margins at the end of the summer.
 In particular, _Pterostichus melanarius_ aggregated in canola early in the growing season, suggesting that its role in suppressing crop pests may be underestimated.
-_Pardosa moesta_ (Araneae: Lycosidae) and _Phalangium opilio_ (Opiliones: Opilionidae) showed weak patterns of seasonal migration, and were more influenced by large-scale geographic patterns rather than landscape composition.
-\\newline
-4.
-Synthesis and applications: Our results suggest that predatory arthropods migrate into canola crops during the early summer, and that grasslands and wetlands act as seasonal reservoir habitats.
+_Pardosa distincta_ (Araneae: Lycosidae) and _Phalangium opilio_ (Opiliones: Opilionidae) showed weak patterns of seasonal migration, and were more influenced by large-scale geographic patterns rather than landscape composition.
+Our results suggest that predatory arthropods migrate into canola crops during the early summer, and that grasslands and wetlands act as seasonal reservoir habitats.
 Farmers and land managers should consider preserving existing habitat in order to maintain pest-control services across the season.

### 2020-12-22 manuscript/manuscript.Rmd
Submitted to AEE

--- 2020-11-10 manuscript/manuscript.Rmd
@@
     affiliation: University of Calgary
+    footnote: 2
   - name: Lincoln R. Best
     email: lincoln.best@oregonstate.edu
-    affiliation: Oregon State University
+    affiliation: University of Calgary
+    footnote: 3
   - name: Paul Galpern
@@
     address: 150 Ambrose Circle SW, Calgary, AB
-  - code: Oregon State University
-    address: 1500 SW Jefferson Way, Corvallis, OR
 footnote:
@@
     text: "Corresponding Author"
+  - code: 2
+    text: "Present address: Fredericton Research and Development Centre, 850 Lincoln Road, Fredericton, NB"
+  - code: 3
+    text: "Present address: Oregon State University; 1500 SW Jefferson Way, Corvallis, OR, USA"
 date: "Spring 2020"
@@
   - harvestmen;
-  - movement;
   - ecosystem services;
-  - natural enemy;
   - functional data analysis;
@@
 In this context, finding "win-win" practices -- that is, practices that result in better conservation outcomes while maintaining or improving crop yields -- is of particular importance.
-<!-- Finally, agricultural land occupies 15 million km$^2$ (~36%) of land globally [@ramankutty2018], suggesting that there remains great potential to achieve conservation outcomes by adjusting agricultural practices.
--->
 
@@
 
-***
-**Box 1: Interpreting Functional Regression Plots**
+----
+
+Box 1: Intepreting Functional Regression Plots
 
@@
 
-***
+-----
 
-Functional regression plots of landscape composition reveal which cover classes are acting as sources or destinations of a given arthropod, and at what spatial scale.
+Functional regression plots of landscape composition reveal which cover classes are acting as sources or destinations of a given arthropod, and at what spatial scale (Figure \@ref(fig:frExample)).
 Positive effects of nearby landscape cover classes indicate that arthropods are spilling over *from* it, therefore acting as a source.
@@
 
-# Authors' contributions
+<!-- # Authors' contributions -->
 
-SVJR and PG conceived of the project.
-JV, DE, and LB conducted field work and taxonomic work.
-SVJR designed the statistical analysis and wrote the manuscript.
-JV, DE, LB, and PG all gave critical feedback on the manuscript, and give their approval for the final version.
+<!-- SVJR and PG conceived of the project. -->
+<!-- JV, DE, and LB conducted field work and taxonomic work. -->
+<!-- SVJR designed the statistical analysis and wrote the manuscript. -->
+<!-- JV, DE, LB, and PG all gave critical feedback on the manuscript, and give their approval for the final version. -->
 
@@
 This project would not have been possible without the help of Michael Gavin, Jennifer Retzlaff, Mugunzal Abarmayan, Riley Waytes, Natasha Morden, and Amy Krause, who helped with field work, and John Swann, who providing lab space for sorting and identification.
-Funding for this research was provided by Ducks Unlimited Canada's Institute for Wetland and Waterfowl Research, the Alberta Canola Producers Commission, Manitoba Canola Growers Association, SaskCanola, the Alberta Biodiversity Monitoring Institute, and the Alberta Conservation Association.
+Funding for this research was provided by Ducks Unlimited Canada's Institute for Wetland and Waterfowl Research, the Alberta Canola Producers Commission, Manitoba Canola Growers Association, SaskCanola, the Alberta Biodiversity Monitoring Institute, and the Alberta Conservation Association (funding sources had no involvement in the data collection, analysis, or writing of the manuscript).
 

### 2021-05-18 manuscript/manuscript.Rmd
Started on revisions

@@
 For instance, bumblebee abundance can be influenced by both nearby and far-away SNL abundance [@westphal2006], but this is poorly studied for other groups of beneficial organisms [but see @sander2006].
-Finally, the feeding and life-history characteristics of many predatory ground beetles and spiders are often poorly-documented, especially in North America.
+<!-- Finally, the feeding and life-history characteristics of many predatory ground beetles and spiders are often poorly-documented, especially in North America. -->
 This makes it difficult to make generalizations of which habitat types harbour beneficial arthropods, making it even more difficult to provide accurate information to farmers about land management practices.
@@
 This resulted in `r nrow(PteMelMod$tempTrap)` unique collection events, taking place across a total of `r round(sum(PteMelMod$tempTrap$trapdays),1)` trapping days.
+These data were collected as a continuation of an earlier study that examined pollination services in crops [@vickruck2019], and here we use pitfall trap data to examine the predatory arthropod community with a focus on canola crops (\emph{Brassica napus} L.).
+Canola is one of the most common crops grown in southern Alberta, 
 In-field traps were placed in canola crops (`r with(NtrapsPer, sum(n[trapLoc=='canola']))`), wetlands (`r with(NtrapsPer, sum(n[trapLoc=='wetland']))`), grassy field edges (`r with(NtrapsPer, sum(n[trapLoc=='pivot']))`), and remnant prairie grasslands (`r with(NtrapsPer, sum(n[trapLoc=='native']))`).

### 2021-05-18 prelimAnalysis.R

@@ -41,6 +41,7 @@ arth %>% filter(grepl('PF',BTID),arthOrder=='Araneae') %>%
   theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
 #Lots of Pardosa distincta and moesta. Could try all lycosids or Pardosa at once, but this might be a stretch
 
+
 # Basic maps of sites/trap distribution -----------------------------------
 
 #Calgary-centred projection from Paul - seems to be problems when using this

### 2021-05-19 manuscript/manuscript.Rmd
Started revisions

@@
 The sites spanned a west-to-east gradient of four natural subregions, including foothills parkland, foothills fescue, mixedgrass, and dry mixedgrass [@ABRegions2006].
+These data were collected as a continuation of an earlier study that examined pollination services in crops [@vickruck2019], and here we use pitfall trap data to examine the predatory arthropod community with a focus on canola crops (\emph{Brassica napus} L.).
+Canola is one of the most commonly-grown crops in southern Alberta, and represented 15\% of the total land cover within the spatial extent of our sampling region during 2017 (Figure \@ref(fig:siteMap)).
+We did not collect information on soil fertilization, pesticide application, mowing, or tillage (approximately 82% of planting in Vulcan County was done with zero-till in 2016; [@statscan_tillage2016]).
+Diverse crop rotations may increase predatory arthropod abundance [@busch_Msc; @bertrand2016], but this was beyond the scope of the study.
+
 Traps were placed starting on `r format(as.Date(as.character(min(PteMelMod$tempTrap$startjulian)),format='%j'),format='%B %d')`, and collections ended on `r format(as.Date(as.character(max(PteMelMod$tempTrap$endjulian)),format='%j'),format='%B %d')`, with collection occurring continuously and traps being emptied every `r round(mean(PteMelMod$tempTrap$trapdays),1)` days on average (SD: `r round(sd(PteMelMod$tempTrap$trapdays),1)`).
 This resulted in `r nrow(PteMelMod$tempTrap)` unique collection events, taking place across a total of `r round(sum(PteMelMod$tempTrap$trapdays),1)` trapping days.
-These data were collected as a continuation of an earlier study that examined pollination services in crops [@vickruck2019], and here we use pitfall trap data to examine the predatory arthropod community with a focus on canola crops (\emph{Brassica napus} L.).
-Canola is one of the most common crops grown in southern Alberta, 
 In-field traps were placed in canola crops (`r with(NtrapsPer, sum(n[trapLoc=='canola']))`), wetlands (`r with(NtrapsPer, sum(n[trapLoc=='wetland']))`), grassy field edges (`r with(NtrapsPer, sum(n[trapLoc=='pivot']))`), and remnant prairie grasslands (`r with(NtrapsPer, sum(n[trapLoc=='native']))`).

### 2021-05-19 frAnalysis.R

@@ -15,6 +15,33 @@ load('./data/geoDataAAFC.Rdata') #Load oring data extracted from AAFC data
 
 source('helperFunctions.R') #Load helper functions
 
+#Select critters of interest
+tempArth <- arth %>% mutate(genSpp=paste(genus,species,sep=' ')) %>%
+  filter(genSpp=='Pterostichus melanarius'|genSpp=='Pardosa distincta'|
+           genSpp=='Pardosa moesta'|genSpp=='Phalangium opilio') %>%
+  filter(year==2017) %>% group_by(BTID,genSpp) %>% summarize(n=n()) %>%
+  pivot_wider(names_from=genSpp,values_from=n)
+
+#Only use pitfall traps from 2017
+tempTrap <- trap %>% filter(startYear==2017,grepl('PF',BTID)) %>%
+  # filter(!grepl('PF',BTID)) %>% #Some ditch sites don't have cover properly digitized at further distances, but it's OK for now
+  select(BLID,BTID,pass,contains('julian'),deployedhours,trapLoc,distFrom,dist,lonTrap,latTrap,lonSite:ID) %>%
+  mutate(trapdays=deployedhours/24) %>% select(-deployedhours) %>% 
+  left_join(rownames_to_column(data.frame(nnDistMat),'ID'),by='ID') %>% 
+  left_join(tempArth,by='BTID') %>% filter(!is.na(grass)) %>% 
+  mutate(across(c(`Pterostichus melanarius`,`Pardosa distincta`,`Pardosa moesta`,`Phalangium opilio`), ~ifelse(is.na(.x),0,.x))) %>% 
+  arrange(BLID,dist,pass) %>% mutate(BLID=factor(BLID)) %>% 
+  mutate_at(vars(ephemeral:noncrop),function(x) ifelse(x>1500,1500,x)) %>% 
+  # rename('count'='n') %>% 
+  #Converts 0 dist trapLoc to distFrom (pitfall traps at 0 m are "inside of" feature)
+  mutate(trapLoc=ifelse(dist==0 & distFrom!='control',distFrom,trapLoc)) %>% 
+  mutate(trapLoc=factor(ifelse(trapLoc=='pivot','ditch',trapLoc))) %>% #TEST: Changes all pivot features to ditch, as per reviewer 1's comment
+  #Get UTM coordinates for traps
[…]

### 2021-05-19 helperFunctions.R

@@ -48,27 +48,9 @@ matrixplot <- function(m,nam=NULL,mar=NULL,numSize=1,numCol='red'){
 #fitFam = family of distribution to use
 #basisFun = name of basis function to be used ('ts' = thin plate spline with extra shrinkage)
 #doublePenalize = should gam use double-penalization? (don't use if using 'ts' or 'cr' as basis functions)
-runMods <- function(tempArth,trap,nnDistMat,oRingMat2,formulas=NULL,
-                    fitMethod='REML',fitFam='nb',basisFun='ts',doublePenalize=F){
+runMods <- function(tempTrap,nnDistMat,oRingMat2,formulas=NULL,
+                    fitMethod='REML',fitFam='nb',basisFun='ts',doublePenalize=FALSE){
   if(is.null(formulas)) stop('No gam formulas provided')
-  
-  #Only use pitfall traps from 2017
-  tempTrap <- trap %>% filter(startYear==2017,grepl('PF',BTID)) %>%
-    # filter(!grepl('PF',BTID)) %>% #Some ditch sites don't have cover properly digitized at further distances, but it's OK for now
-    select(BLID,BTID,pass,contains('julian'),deployedhours,trapLoc,distFrom,dist,lonTrap,latTrap,lonSite:ID) %>%
-    mutate(trapdays=deployedhours/24) %>% select(-deployedhours) %>% 
-    left_join(rownames_to_column(data.frame(nnDistMat),'ID'),by='ID') %>% 
-    left_join(tempArth,by='BTID') %>% mutate(n=ifelse(is.na(n),0,n)) %>% filter(!is.na(grass)) %>% 
-    arrange(BLID,dist,pass) %>% mutate(BLID=factor(BLID)) %>% 
-    mutate_at(vars(ephemeral:noncrop),function(x) ifelse(x>1500,1500,x)) %>% 
-    rename('count'='n') %>% 
-    #Converts 0 dist trapLoc to distFrom (pitfall traps at 0 m are "inside of" feature)
-    mutate(trapLoc=factor(ifelse(dist==0 & distFrom!='control',distFrom,trapLoc))) %>% 
-    #Get UTM coordinates for traps
-    mutate(lonTrap2=lonTrap,latTrap2=latTrap) %>% #Duplicate columns
-    st_as_sf(coords=c('lonTrap2','latTrap2'),crs=4326) %>% 
[…]

### 2021-05-19 frAnalysis.R
Tried model with reduced cover classes
- Combined ditch + pivot corner
- Updated map

@@ -98,10 +98,10 @@ smoothCols <- c('blue','red') #Colours for smoothing lines
 # Pterostichus melanarius ----------------------------------
 
 
-# PteMelMod <- runMods(rename(tempTrap,count=`Pterostichus melanarius`),nnDistMat,oRingMat2Prop,
-#                      formulas=modFormulas,basisFun='ts',doublePenalize=FALSE)
+PteMelMod <- runMods(rename(tempTrap,count=`Pterostichus melanarius`),nnDistMat,oRingMat2Prop,
+                     formulas=modFormulas,basisFun='ts',doublePenalize=FALSE)
 # beep(1)
-# save(PteMelMod,file='./data/PteMelMod.Rdata')
+# save(PteMelMod,file='./data/PteMelMod2.Rdata')
 load('./data/PteMelMod.Rdata')
 
 #Tried running this with double-penalization instead of shrinkage. Results were similar, but some of the shrinkage 
@@ -109,9 +109,24 @@ load('./data/PteMelMod.Rdata')
 
 #Check models
 attach(PteMelMod)
+# detach(PteMelMod)
 
 # detach(PteMelMod)
 AIC(mod1,mod2,mod3,mod4) #Best model has separate land cover types + SpatioTemporal effect
+
+#Original models
+#            df      AIC
+# mod1 48.00979 4779.429
+# mod2 51.27912 4732.102
+# mod3 67.62359 4722.432
+# mod4 57.57936 4740.469
+
+#Updated models - field margin/road margins combined
+#            df      AIC
+# mod1 48.00979 4779.429
+# mod2 50.29594 4732.312
+# mod3 69.61288 4722.696
+# mod4 55.73488 4736.132
 
 #Model 3 - landscape effects matter quite a bit
 summary(mod3); AIC(mod3)
@@ -148,7 +163,7 @@ termNames <- gsub('TreeShrub','Woodland',termNames)
 N <- 1:nrow(checkMC) #Plot all smooth terms
 # N <- 4:nrow(checkMC) #Plot with only landscape smoothers
 lN <- length(N)
-png('./figures/coverCorPlots/concurvityEstimate_reduced.png',1200,1000,pointsize=20)
+png('./figures/coverCorPlots/concurvityEstimate_reduced2.png',1200,1000,pointsize=20)
[…]

### 2021-05-21 manuscript/manuscript.Rmd
Worked on revisions

@@
 First, some non-crop habitat may act as sources of arthropods during some times of the year, but as destinations during other times, meaning that the timing of spillover from non-crop habitat may not align with important periods in crop development.
-Arthropods can migrate from managed crops back into adjacent SNL at the end of the season [@desender1988; @tscharntke2005b], but this is seldom considered.
+Arthropods can disperse from managed crops back into adjacent SNL at the end of the season [@desender1988; @tscharntke2005b], but this is seldom considered.
 Second, the spatial "grain" of the landscape that is relevant to an organism depends on their traits and life history [@ahrenfeldt2015].
@@
 Crops provide food (pest insects) for predatory arthropods during the growing season.
-This should result in agricultural land becoming a destination for predators in the early part of the season as they migrate into the crop, and a source at the end of the season as they migrate out of the crop.
-3. Crops may act as a temporary feeding site for predators. Therefore, crops may act as a local destination for arthropods, but will also be negatively associated at larger (landscape-level) scales.
+This should result in agricultural land becoming a destination for predators in the early part of the season as they disperse into the crop, and a source at the end of the season as they disperse out of the crop.
+3. Crops may act as a temporary feeding site for predators. Therefore, crops may act as a nearby destination for arthropods, but will also be negatively associated at more-distant scales.
 Using a large pitfall trapping dataset, we related seasonal changes in arthropod abundance to landscape composition at multiple spatial scales.
@@
 
-Functional regression [@ramsay2004; @yen2014] was used to incorporate landscape information at different distances, allowing assessment of both local and regional landscape composition [@galpern2020].
+Functional regression [@ramsay2004; @yen2014] was used to incorporate landscape information at different distances, allowing assessment of both nearby and far-away landscape composition [@galpern2020].
 Scalar-on-function regression is a special type of linear regression model ($y=X\beta + e$), where the columns of the model matrix $X$ contain some continuous predictor of the scalar $y$, and the values of the coefficients ($\beta$) are modeled as a smooth function $f(x)$ of the predictors.
@@
 This allows for the possibility that the size of the landscape "grain" relevant to a given organism may change over the course of its life stages [@addicott1987; @lima1996; @gardiner2010].
-It also allows for the possibility that certain land cover types may be locally beneficial, but detrimental at large scales, indicating that the cover type may not constitute a completely usable habitat.
+It also allows for the possibility that small amounts of certain land cover types may be beneficial, but are detrimental at large scales, indicating that the cover type may not constitute a completely usable habitat.
 
@@
 Concurvity is a nonlinear analogue of multicollinearity which can bias estimates of standard errors [@buja1989].
-There is no agreed-upon threshold of "unacceptable" concurvity, but 0.5 is commonly used [@dominici2002; @ramsay2003]. 
+There is no agreed-upon threshold of ``unacceptable" concurvity, but 0.5 is commonly used [@dominici2002; @ramsay2003]. 
 <!-- Some landscape terms were strongly concurved , namely forest and shrubland (max: 0.71), canola and cereal (max: 0.74), and grassland and wetland (max: 0.63). -->
-Forests and shrubland were combined into a single ``woodland" category, and grassland and wetland were combined into a single "grassland" category, as they were strongly positively correlated at all distances, indicating similar feature classes.
-Cereal was removed from the model, as it was negatively correlated with canola cover at distances less than 200m and was positively correlated at distances over 500m, reflecting the most common crop rotations (canola $\rightarrow$ wheat $\rightarrow$ barley) and the commonly-used 800 m block structure of farmland in our study region (quarter-sections).
+For highly concurved classes, we examined the spatial nature of the concurvity using scatterplots of proportion cover within each annulus to determine whether the cover classes should be merged (if classes were consistently related) or removed (if classes were inversely related to one another).
+Forests and shrubland were combined into a single ``woodland" category, and grassland and wetland were combined into a single ``grassland" category, as they were strongly positively related to each other at all distances of annuli, indicating similar feature classes.
+Cereal was removed from the model, as it was highly concurved with canola; in particular, it was negatively associated with canola cover at annulus distances of less than 200m and was positively associated at distances over 500m, reflecting the most common crop rotations (canola $\rightarrow$ wheat $\rightarrow$ barley) and the commonly-used 800 m block structure of farmland in our study region (quarter-sections).
 This resulted in a reduced set of landscape terms, none of which were strongly concurved with each other (cropland: canola, pulses; SNL: grassland, pasture, woodland, roadside; see Figure \@ref(fig:concurvity)).
@@
 
-Functional linear regression is a special case of linear regression, where both the independent variable is predicted by a functional dependent variable, meaning that the slope is a function (vector) rather a fixed (scalar) value [@ramsay2004; @yen2014].
+Functional linear regression is a special case of linear regression, where the independent variable is predicted by a functional dependent variable, meaning that the slope is a function (vector) rather a fixed (scalar) value [@ramsay2004; @yen2014].
 Therefore, the interpretation of a functional regression plot is very different from that of a simple linear regression plot.
@@
 
-In the Results section, we refer to local- and landscape-level effects, where local indicates the effects of landscape composition at scales of <500 m, whereas landscape indicates scales >500 m.
+In the Results section, we refer to ``near" and ``far" landscape effects, where near indicates the effects of landscape composition at scales of <500 m, and far indicates scales of >500 m.
 Similarly, we refer to early- and late-season effects, where landscape composition affected activity-density on June 20th or August 20th, respectively.
@@
 Canola crops had a marginally higher activity-density of _P. melanarius_ than other trap locations (Figure \@ref(fig:PteMelLandscape)a).
-Grassland cover was the most important land cover type in explaining activity-density ($R^2$: 0.104, Table \@ref(tab:rSquared)), and local grassland had a negative effect late in the summer (Figure \@ref(fig:PteMelLandscape)b), suggesting that _P.
+Grassland cover was the most important land cover type in explaining activity-density ($R^2$: 0.104, Table \@ref(tab:rSquared)), and near grassland had a negative effect late in the summer (Figure \@ref(fig:PteMelLandscape)b), suggesting that _P.
 melanarius_ may move into grasslands later in the year.
-Local canola had a positive effect in the early season, but landscape-level canola had a negative effect, indicating that areas with widespread canola coverage had lower _P.
+Near canola had a positive effect in the early season, but landscape-level canola had a negative effect, indicating that areas with widespread canola coverage had lower _P.
 melanarius_ activity-density (Figure \@ref(fig:PteMelLandscape)c).
-Pulses acted as a late-season source, indicating that _P. melanarius_ may migrate out of the crop after (or during) harvest (Figure \@ref(fig:PteMelLandscape)d).
+Pulses acted as a late-season source, indicating that _P. melanarius_ may disperse out of pulses after (or during) harvest (Figure \@ref(fig:PteMelLandscape)d).
 Finally, _P.
-melanarius_ activity-density had a strong temporal and spatial component (both p `r with(pmelSmTerms,p[Smoother=='s(E,N)'])`), indicating that phenology and local geographic factors were important drivers of ground beetle activity-density (Figure \@ref(fig:PteMelSpatiotemporal)).
+melanarius_ activity-density had a strong temporal and spatial component (both p `r with(pmelSmTerms,p[Smoother=='s(E,N)'])`), indicating that phenology and large-scale geographic factors were important drivers of ground beetle activity-density (Figure \@ref(fig:PteMelSpatiotemporal)).
 Landscape composition and trap location explained `r r2Nakagawa$PteMelMod[1]*100`% of the variance in activity-density, while the spatial and temporal smoothers accounted for `r with(r2Nakagawa,(PteMelMod[2]-PteMelMod[1])*100)`% (Table \@ref(tab:rSquared)).
@@
 (ref:PteMelCap) Landscape influence on _Pterostichus melanarius_ activity-density.
-a) shows the effect of local trap location, and b-c) are functional regression plots of the proportion grassland and canola at distances away from each trap.
+a) shows the effect of trap location, and b-c) are functional regression plots of the proportion grassland and canola at distances away from each trap.
 d) is a functional regression plot over time, showing the effect of pulses at different times of the year.
@@
 
-_P.
-distincta_ activity-density was negatively affected by landscape-level pasture (Figure \@ref(fig:ParDisLandscape)b), while woodlands had a negative effect late in the season (Figure \@ref(fig:ParDisLandscape)c).
-This suggests that large amounts of pasture are unsuitable habitat for _P. distincta_, and that they migrate into woodlands later in the season.
+_P. distincta_ activity-density was negatively affected by far pasture (Figure \@ref(fig:ParDisLandscape)b), suggesting that large amounts of pasture are unsuitable habitat for _P. distincta_.
+There was also a negative effect of woodlands late in the summer (Figure \@ref(fig:ParDisLandscape)c) that did not depend on spatial scale, indicating that _P.
+distincta_ may disperse into woodlands at this time.
 However, trap location and the temporal random effect (Figure \@ref(fig:ParDisSpatiotemporal)a) explained roughly 10 times more variance than landscape composition ($R^2$: `r round(sum(filter(r2Nakagawa2,model=='ParDisMod',terms=='trapLoc'|grepl('day',terms))$r2comp),3)` versus `r round(sum(filter(r2Nakagawa2,model=='ParDisMod',terms!='trapLoc',terms!='sigmaD',!grepl('s\\(',terms))$r2comp),3)`), meaning that while _P.
-distincta_ may be locally abundant in certain cover types, it is highly general in its overall habitat preferences.
+distincta_ may be abundant in certain cover types, its overall habitat preferences are fairly general.
 <!-- The weak effect of canola crops (p>0.07) suggests that this species does not aggregate into these crops, meaning that its pest suppressing potential for farmers is limited. -->
@@
 _P. moesta_ activity-density responded to grassland, canola, and road margins.
-Grasslands had a local negative effect, but a positive landscape-level effect, indicating that while these cover types act as a local destination, the general amount of grassland in the area had a positive effect (Figure \@ref(fig:ParMoeLandscape)b).
-Local canola cover had a positive early effect on activity-density, but a negative local effect later in the season (Figure \@ref(fig:ParMoeLandscape)c).
-Local road margins also had a similar effect, acting as an early source and a late destination (Figure \@ref(fig:ParMoeLandscape)d).
+Grasslands had a near negative effect, but a positive far effect, indicating that these cover types act as a local destination, the general amount of grassland in the area had a positive effect (Figure \@ref(fig:ParMoeLandscape)b).
+Near canola cover had a positive early effect on activity-density, but a negative effect later in the season (Figure \@ref(fig:ParMoeLandscape)c).
+Near road margins also had a similar effect, acting as an early source and a late destination (Figure \@ref(fig:ParMoeLandscape)d).
 Pulses also had a positive effect at the landscape level (Figure \@ref(fig:ParMoeLandscape)e), but this explained very little variance in _P.
@@
 (ref:ParDisCap) Landscape influence on _Pardosa distincta_ activity-density.
-a) shows the effect of local trap location, b) is a functional regression plot of the proportion pasture at distances away from each trap, and c) is a functional regression plot over time, showing the effect of woodland at different times of the year.
+a) shows the effect of trap location, b) is a functional regression plot of the proportion pasture at distances away from each trap, and c) is a functional regression plot over time, showing the effect of woodland at different times of the year.
 Lines and dots represent means, and bars and shaded regions represent 95 % confidence regions (1.96 x SE).
@@
 (ref:ParMoeCap) Landscape influence on _Pardosa moesta_ activity-density.
-a) shows the effect of local trap location, and b-e) are functional regression plots of the proportion grassland, canola, road margins, and pulses at distances away from each trap.
+a) shows the effect of trap location, and b-e) are functional regression plots of the proportion grassland, canola, road margins, and pulses at distances away from each trap.
 Lines and dots represent means, and bars and shaded regions represent 95 % confidence regions (1.96 x SE).
@@
 opilio_ activity-density was somewhat influenced by trap location, with field edges and wetlands having the highest activity-density (Figure \@ref(fig:OpilioLandscape)a), but this effect was swamped by the effect of landscape and the spatiotemporal random effects (Table \@ref(tab:rSquared)), meaning that _P.
-opilio_ activity-density is only mildly influenced by local cover type.
-Nearby grassland and woodland both had negative effects on _Phalangium opilio_ activity-density, but only early in the season (Figures \@ref(fig:OpilioLandscape)b,c), suggesting that _P.
-opilio_ may preferentially migrate to these cover classes.
+opilio_ activity-density is only mildly influenced by near cover type.
+Nearby grassland and woodland both had negative effects on _Phalangium opilio_ activity-density Figures \@ref(fig:OpilioLandscape)b,c), but the effect of grassland was negative only early in the season (only weakly for woodland: p=0.07), suggesting that _P.
+opilio_ may preferentially disperse to these cover classes.
 The temporal random effect was overwhelmingly the most important predictor of _P.
@@
 (ref:OpilioCap) Landscape influence on _Phalangium opilio_ activity-density.
-a) shows the effect of local trap location, and b-c) are functional regression plots of the proportion grassland and woodland at distances away from each trap.
+a) shows the effect of trap location, and b-c) are functional regression plots of the proportion grassland and woodland at distances away from each trap.
 Lines and dots represent means, and bars and shaded regions represent 95 % confidence regions (1.96 x SE).
@@
 moesta_ activity-density, all during late summer (August - September).
-This suggests that these arthropods migrate to these habitats at the end of the summer to prepare for oviposition or overwintering.
+This suggests that these arthropods disperse to these habitats at the end of the summer to prepare for oviposition or overwintering.
 However, _P.
@@
 distincta_, meaning that these cover types likely represent only partial habitat for these arthropods.
-Finally, the influence of landscape composition tended to be limited to a radius of about 500m, indicating that large-scale _and_ local land cover can be important to beneficial arthropod abundance.
+Finally, the influence of landscape composition tended to be limited to a radius of about 500m, indicating that nearby _and_ far-away landscape are associated with beneficial arthropod abundance.
 There was also a strong temporal component to most of the landscape effects, meaning that it is important to consider how destinations and sources may change over the season.
@@
 ...
-should result in agricultural land becoming a destination for predators in the early part of the season as they migrate into the crop, and a source at the end of the season as they migrate out of the crop.
+should result in agricultural land becoming a destination for predators in the early part of the season as they disperse into the crop, and a source at the end of the season as they disperse out of the crop.
 -->
-<!-- 3. ... crops may act as a local destination for arthropods, but will also be negatively associated at larger (landscape-level) scales. -->
+<!-- 3. ... crops may act as a nearby destination for arthropods, but will also be negatively associated at far-away scales. -->
 
@@
 Our models confirmed this, as they showed that canola and pulse crops had positive effects on _P. melanarius_ activity-density early in the season.
-Early in the season, canola crops had a local positive effect, but a landscape-level negative effect, which may indicate that they provide only temporary feeding habitat.
+Early in the season, canola crops had a near positive effect, but a landscape-level negative effect, which may indicate that they provide only temporary feeding habitat.
 The effect of pulse crops on carabid abundance is not well-studied, but our results suggest that pulses may represent a potential food resource for _P.
@@
 We also found that road margins had a positive early-season and a negative late-season effect [similar to @drapela2008 and @drapela2011]. 
-Grassland and pulses also had a local negative effect but a positive landscape-level effect; this suggests that they may constitute suitable habitat for _P.
+Grassland and pulses also had a negative nearby effect but a positive faraway effect; this suggests that they may constitute suitable habitat for _P.
 moesta_ and attract them away from other cover types.
@@
 Since most of our study area was in or near farmed land, the lack of variation is understandable, but there were a few notable landscape-level patterns that emerged.
-_P. opilio_ activity-density was higher in grassy field edges and wetlands, but grasslands and wetlands had a local negative effect on _P. opilio_ until late in the season.
+_P. opilio_ activity-density was higher in grassy field edges and wetlands, but grasslands and wetlands had a negative nearby effect on _P. opilio_ until late in the season.
 These indicate that while grass and wetlands could act as a reservoir, spillover into other land cover types may be limited, as _P.
 opilio_ avoids heavily grazed areas, possibly due to low humidity [@sajna2011].
-_P. opilio_ is also found in large numbers at the edges of forests, and may migrate from forests into farmlands [@vandepoel2015Msc].
+_P. opilio_ is also found in large numbers at the edges of forests, and may disperse from forests into farmlands [@vandepoel2015Msc].
 We found the opposite pattern: forests had a weak negative effect on _P. opilio_, at least early in the year.
@@
 We have shown how a relatively straightforward statistical technique can be used to consider multiple spatial scales of landscape composition, providing richer inference about the processes acting on beneficial arthropods.
-Our results show empirical evidence of arthropod migration between cover types at different times of year, which is rarely considered beyond single-field studies.
+Our results show empirical evidence of arthropod movement between cover types at different times of year, which is rarely considered beyond single-field studies.
 Since we did not directly track individual movements, future studies should directly examine arthropod movement and life-history within matrices of cover types, with the goal of integrating landscape ecology and behavioural processes into a single model [@lima1996].
@@
 Based on our findings, farmers and land managers should consider preserving existing grassland and wetland habitat to act as habitat for pest-suppressing arthropods in crops.
-While local habitat appears valuable, even landscape-level habitat can be valuable, as it can increase the number of beneficial arthropods at larger spatial scales (e.g.
+While nearby habitat appears valuable, even faraway habitat can be valuable, as it can increase the number of beneficial arthropods at larger spatial scales (e.g.
 Figures \@ref(fig:PteMelLandscape), \@ref(fig:ParMoeLandscape)).

### 2021-05-21 frAnalysis.R

@@ -35,7 +35,7 @@ tempTrap <- trap %>% filter(startYear==2017,grepl('PF',BTID)) %>%
   # rename('count'='n') %>% 
   #Converts 0 dist trapLoc to distFrom (pitfall traps at 0 m are "inside of" feature)
   mutate(trapLoc=ifelse(dist==0 & distFrom!='control',distFrom,trapLoc)) %>% 
-  mutate(trapLoc=factor(ifelse(trapLoc=='pivot','ditch',trapLoc))) %>% #TEST: Changes all pivot features to ditch, as per reviewer 1's comment
+  # mutate(trapLoc=factor(ifelse(trapLoc=='pivot','ditch',trapLoc))) %>% #TEST: Changes all pivot features to ditch, as per reviewer 1's comment
   #Get UTM coordinates for traps
   mutate(lonTrap2=lonTrap,latTrap2=latTrap) %>% #Duplicate columns
   st_as_sf(coords=c('lonTrap2','latTrap2'),crs=4326) %>% 
@@ -60,6 +60,8 @@ oRingMat2Prop$TreeShrub <- oRingMat2Prop$Shrubland + oRingMat2Prop$Forest
 #Grassland + Wetland
 oRingMat2Prop$GrassWetland <- oRingMat2Prop$Wetland + oRingMat2Prop$Grassland
 # oRingMat2Prop$Wetland <- NULL; oRingMat2Prop$Grassland <- NULL
+
+
 
 #Create model formulas
 modFormulas <- 'count~offset(log(trapdays))+s(day,k=10,bs=basisFun)+s(E,N,k=50,bs=basisFun)' #Temporal + spatial
@@ -95,11 +97,13 @@ theme_set(theme_classic()) #Classic theme
 maptheme <- theme(panel.border=element_rect(size=1,fill=NA),axis.line=element_blank()) #Better theme for maps
 smoothCols <- c('blue','red') #Colours for smoothing lines
 
+ylimRaneffPlots <- c(-5,2.7) #Y-limits for random effects smoothers (everything on the same scale)
+
 # Pterostichus melanarius ----------------------------------
 
 
-PteMelMod <- runMods(rename(tempTrap,count=`Pterostichus melanarius`),nnDistMat,oRingMat2Prop,
-                     formulas=modFormulas,basisFun='ts',doublePenalize=FALSE)
[…]

### 2021-05-21 manuscript/manuscript.Rmd
Worked on revisions

@@
 Arthropods can disperse from managed crops back into adjacent SNL at the end of the season [@desender1988; @tscharntke2005b], but this is seldom considered.
-Second, the spatial "grain" of the landscape that is relevant to an organism depends on their traits and life history [@ahrenfeldt2015].
+Second, the scale at which the landscape is relevant to an organism depends on their traits and life history [@ahrenfeldt2015].
 For instance, bumblebee abundance can be influenced by both nearby and far-away SNL abundance [@westphal2006], but this is poorly studied for other groups of beneficial organisms [but see @sander2006].
@@
 
-We used four highly-abundant species of predatory arthropods found in the pitfall traps, as common species are more important for ecosystem service provision than rare species [@winfree2015].
+We used four highly-abundant species of predatory arthropods found in the pitfall traps, as common species are more important for ecosystem service provision than rare species [@winfree2015; @kleijn2015; but see @winfree2018].
 _Pterostichus melanarius_ is an introduced predatory ground beetle (Coleoptera: Carabidae) that is a wide-ranging generalist known to prey upon crop pests [@carcamo1994; @larsen2003; @busch_Msc].
@@
 $X\beta$).
-This allows for the possibility that the size of the landscape "grain" relevant to a given organism may change over the course of its life stages [@addicott1987; @lima1996; @gardiner2010].
+This allows for the possibility that the scale of landscape relevant to a given organism may change over the course of its life [@addicott1987; @lima1996; @gardiner2010].
 It also allows for the possibility that small amounts of certain land cover types may be beneficial, but are detrimental at large scales, indicating that the cover type may not constitute a completely usable habitat.
@@
 For each landscape cover class, we used three scalar-on-function terms.
-First, we used the proportion cover in the annuli surrounding each trap location (spatial effect of cover class).
-Second, we used the average proportion cover across days of the year (temporal effect of cover class). 
-Finally, we used a tensor-product interaction of landscape cover and day of year (spatio-temporal interaction of cover class).
+First, we used the proportion cover in the annuli surrounding each trap location (spatial effect of cover class - _i.e._ does the effect of cover differ with distance?).
+Second, we used the average proportion cover in all annuli across days of the year (temporal effect of cover class - _i.e._ does the effect of cover differ with time?). 
+Finally, we used a tensor-product interaction of landscape cover and day of year (spatio-temporal interaction of cover class - _i.e._ does the effect of cover differ with distance and time?).
 We used 10 basis dimensions for the spatial and temporal landscape smoothers, and 16 basis dimensions for the spatio-temporal interaction.
 The effective degrees of freedom for all smoothing terms were far below the number of basis dimensions, indicating that no additional basis dimensions were needed (see Tables \@ref(tab:PteMelSmooth), \@ref(tab:ParDisSmooth), \@ref(tab:ParMoeSmooth), \@ref(tab:OpilioSmooth)).
-To remove unimportant terms from the model, we used thin-plate regression splines with shrinkage, a continuous analog to stepwise model selection where weaker terms are completely removed from the model rather than reduced to a line [@marra2011].
-The deviance residuals from each model were visually inspected for normality and equal variance [@hilbe2011; @wood2017].
+To remove unimportant terms from the model, we used thin-plate regression splines with extra shrinkage, a continuous analog to stepwise model selection where weaker terms are completely removed from the model rather than reduced to a line [@marra2011].
+Deviance residuals from each model were visually inspected for normality and equal variance [@hilbe2011; @wood2017].
 Finally, we calculated the proportion of explained variance (R$^2$) for each set of terms [@nakagawa2013; @nakagawa2017].
@@
 In reality, it is more likely that nearby cover will be more influential on activity-density than far-away cover, which could result in a relationship similar to Figure \@ref(fig:frExample)c.
-As functional regression takes any continuous predictor of _y_, it is also possible to use proportion cover (measured within an annulus of a fixed radius) as a predictor of measurements taken across time, allowing the effect of proportion cover to vary over the course of the season (Figure \@ref(fig:frExample)d).
+As functional regression takes any continuous predictor of _y_, it is also possible to use proportion cover as a predictor of measurements taken across time, allowing the effect of a (fixed) proportion cover on activity density to vary over the course of the season (Figure \@ref(fig:frExample)d).
 Finally, the effect of proportion cover over distance and time may be modeled as a smoothed surface, representing the joint spatio-temporal influence of landscape cover on activity-density.
@@
 Lines and dots represent means, and bars and shaded regions represent 95 % confidence regions (1.96 x SE).
-Coloured regions represent early- and late-season effects (blue = June, red = August).
+Coloured regions represent early- and late-season effects (blue = June 20, red = August 20).
 

### 2021-05-21 manuscript/supplemental.Rmd
Worked on revisions

--- 2020-11-10 manuscript/supplemental.Rmd
@@
 ```
+
+Model formula:
+
+gam( count ~ offset(log(trapdays)) + trapLoc + s(day) + s(E,N)+ 
+    s(distanceMatrix,by=GrassWetland) + s(dayMatrix,by=GrassWetland) + ti(distanceMatrix,dayMatrix,by=GrassWetland) + 
+    s(distanceMatrix,by=Canola) + s(dayMatrix,by=Canola) + ti(distanceMatrix,dayMatrix,by=Canola) + 
+    s(distanceMatrix,by=Pasture)+ s(dayMatrix,by=Pasture) + ti(distanceMatrix,dayMatrix,by=Pasture) + 
+    s(distanceMatrix,by=TreeShrub) + s(dayMatrix,by=TreeShrub)+ ti(distanceMatrix,dayMatrix,by=TreeShrub) + 
+    s(distanceMatrix,by=Pulses) + s(dayMatrix,by=Pulses)+ ti(distanceMatrix,dayMatrix,by=Pulses) + 
+    s(distanceMatrix,by=Urban) + s(dayMatrix,by=Urban)+ ti(distanceMatrix,dayMatrix,by=Urban),
+    family= 'nb'
+)
+
+where:
+count = N x 1 vector of activity density from traps (count)
+trapdays = N x 1 vector of number of days that the trap was installed for (numeric)
+trapLoc = N x 1 vector of trap location type (factor)
+day = N x 1 vector of day of year that the trap was installed on (numeric)
+E,N = N x 1 vector(s) of Easting and Northing (numeric)
+distanceMatrix = N x M matrix of distances, where the Nth row contains a vector of distances to the annuli (numeric)
+dayMatrix = N x M matrix of days, where the Nth row contains a vector of days that spans the range of days of the year (numeric)
+GrassWetland,Canola,... = N x M matrix of cover measurements, where the Nth row contains a vector of proportion cover measurements within each annulus (numeric)
 

### 2021-05-21 frAnalysis.R

@@ -96,14 +96,20 @@ stLegPosY <- 0.3 #Legend position Y
 theme_set(theme_classic()) #Classic theme
 maptheme <- theme(panel.border=element_rect(size=1,fill=NA),axis.line=element_blank()) #Better theme for maps
 smoothCols <- c('blue','red') #Colours for smoothing lines
-
 ylimRaneffPlots <- c(-5,2.7) #Y-limits for random effects smoothers (everything on the same scale)
+#Days to display on plots (early,mid,late)
+# c(171,201,232) = June 20, July 20, Aug 20
+
+#Changed to c(153,232) to show effects at the extreme ends of the season
+
+dispDays <- data.frame(doy=c(153,232)) %>% 
+  mutate(date=c('Early','Late')) 
+
 
 # Pterostichus melanarius ----------------------------------
 
-
-# PteMelMod <- runMods(rename(tempTrap,count=`Pterostichus melanarius`),nnDistMat,oRingMat2Prop,
-#                      formulas=modFormulas,basisFun='ts',doublePenalize=FALSE)
+PteMelMod <- runMods(rename(tempTrap,count=`Pterostichus melanarius`),nnDistMat,oRingMat2Prop,
+                     formulas=modFormulas,basisFun='ts',doublePenalize=FALSE)
 # beep(1)
 # save(PteMelMod,file='./data/PteMelMod2.Rdata')
 load('./data/PteMelMod.Rdata')
@@ -218,28 +224,25 @@ ggsave('./figures/Pterostichus_melanarius_raneff.png',raneffPlot,width=stFigX,he
 
 #Plot significant landscape effects: GrassWetland, Canola, Pulses
 
-#Days to display on plots (early,mid,late)
-# c(173,203,232) = June 20, July 20, Aug 20 (Actually June/July 22, but close enough...)
-dispDays <- data.frame(doy=c(173,232)) %>% 
-  mutate(date=c('Early','Late')) 
-
 #Get order of terms to plot
 cbind(1:length(mod3$smooth),sapply(mod3$smooth,function(x) x$label))
 
 #Trap location
[…]

### 2021-05-21 helperFunctions.R

@@ -280,7 +280,8 @@ boldLaTeX <- function(x) paste0('\\textbf{',x,'}')
 #ylab = custom y label
 #showLegend = show legend for "both" plots?
 makeFRplot <- function(mod,term=NULL,type=NULL,days=NULL,dists=seq(30,1500,30),ylab=NULL,dateLabs=NULL,showLegend=F){
-  if(is.null(days)|is.null(dateLabs)){
+  if(xor(is.null(days),is.null(dateLabs))) stop('Must specify days and dateLabs, or neither')
+  if(is.null(days)&is.null(dateLabs)){
     if(type=='time'){
       days <- 149:241
     } else {
@@ -313,3 +314,25 @@ makeFRplot <- function(mod,term=NULL,type=NULL,days=NULL,dists=seq(30,1500,30),y
   }
   return(p)
 }
+
+#Get compact letter display from GAM linear terms
+#Idea from: 
+# https://stats.stackexchange.com/questions/376237/correcting-for-multiple-pairwise-comparisons-with-gam-objects-mgcv-in-r
+cldGam <- function(mod){ 
+  require(multcomp)
+  coefNames <- names(coef(mod)[1:5])
+  comparisons <- rep('',sum(seq(length(coefNames)-1)))
+  n <- 1
+  for(i in 1:(length(coefNames)-1)){
+    for(j in (i+1):length(coefNames)){
+      comparisons[n] <- paste0(coefNames[i],' - ',coefNames[j],' = 0') 
+      n <- n+1
+    }
+  }
+  modcomp <- glht(mod,linfct=comparisons)
+  # summary(mod3comp)
+  modcomp$focus <- 'trapLoc' #Trick to get CLD from GAM
+  letDisp <- cld(modcomp)$mcletters$Letters
+  data.frame(trapLoc=names(letDisp),labs=unname(letDisp))
+}
+

### 2021-05-25 manuscript/manuscript.Rmd
Worked on revisions

@@
   mutate(Smoother=gsub('GrassWetland','Grassland',Smoother),Smoother=gsub('TreeShrub','Woodland',Smoother)) %>%
+  mutate(Smoother=gsub('Urban','Roads',Smoother)) %>% 
   rename(p='p-value') %>% mutate(p=roundLess(p,3)) %>% mutate_at(vars(2:4),roundLess,dig=2) %>% 
@@
   mutate(Smoother=gsub('GrassWetland','Grassland',Smoother),Smoother=gsub('TreeShrub','Woodland',Smoother)) %>% 
+  mutate(Smoother=gsub('Urban','Roads',Smoother)) %>% 
   rename(p='p-value') %>% mutate(p=roundLess(p,3)) %>% mutate_at(vars(2:4),roundLess,dig=2) %>% 
@@
 }) %>% do.call('rbind',.) %>% mutate(spp=c('PteMel','ParDis','ParMoe','Opilio'))
+
+#Compare annular and radial models 
+compareMods <- list(PteMelMod,ParDisMod,ParMoeMod,OpilioMod) %>% 
+  sapply(.,function(x){
+    with(x,c(mod2AIC=AIC(mod2),mod2df=attr(logLik(mod2),'df'),
+      mod3AIC=AIC(mod3),mod3df=attr(logLik(mod3),'df'),
+      mod5AIC=AIC(mod5),mod5df=attr(logLik(mod5),'df'),bestDist=mod5info$radiusDist[which.min(mod5info$AIC)]))
+  }) %>% t() %>% data.frame() %>% 
+  mutate(spp=c('Pterostichus melanarius','Pardosa distincta','Pardosa moesta','Phalangium opilio')) %>% 
+  column_to_rownames('spp')
 
@@
 
+Traps in canola were installed in 27 fields at 25, 75, and 200 m along a transect heading away from the nearest non-crop feature (wetland, grassy field edges, or remnant prairie), while the trap at 0 m was installed in the non-crop feature itself.
+The remaining 90 sites had only a single trap.
+In-field traps were placed in canola crops (`r with(NtrapsPer, sum(n[trapLoc=='canola']))`), wetlands (`r with(NtrapsPer, sum(n[trapLoc=='wetland']))`), grassy field edges (`r with(NtrapsPer, sum(n[trapLoc=='pivot']))`), and remnant prairie grasslands (`r with(NtrapsPer, sum(n[trapLoc=='native']))`).
 Traps were placed starting on `r format(as.Date(as.character(min(PteMelMod$tempTrap$startjulian)),format='%j'),format='%B %d')`, and collections ended on `r format(as.Date(as.character(max(PteMelMod$tempTrap$endjulian)),format='%j'),format='%B %d')`, with collection occurring continuously and traps being emptied every `r round(mean(PteMelMod$tempTrap$trapdays),1)` days on average (SD: `r round(sd(PteMelMod$tempTrap$trapdays),1)`).
 This resulted in `r nrow(PteMelMod$tempTrap)` unique collection events, taking place across a total of `r round(sum(PteMelMod$tempTrap$trapdays),1)` trapping days.
-In-field traps were placed in canola crops (`r with(NtrapsPer, sum(n[trapLoc=='canola']))`), wetlands (`r with(NtrapsPer, sum(n[trapLoc=='wetland']))`), grassy field edges (`r with(NtrapsPer, sum(n[trapLoc=='pivot']))`), and remnant prairie grasslands (`r with(NtrapsPer, sum(n[trapLoc=='native']))`).
-Traps in canola were installed at 25, 75, and 200 m along a transect heading away from the nearest non-crop feature (wetland, grassy field edges, or remnant prairie), while the trap at 0 m was installed in the non-crop feature itself.
 We used 582 mL Solo® cups buried up to the rim and partially filled with propylene glycol, with 2 cm wire mesh mounted over the rim to prevent vertebrates from falling into the traps.
@@
 Trapping location was included as a fixed effect with 5 levels (canola, field edge, grassland, road margin, and wetlands) to account for the effect of local cover independent of the surrounding landscape composition.
-Day of year was included as a 1-dimensional smooth, and easting and northing (km east and north of the trap extent centre point) were included as 2-dimensional smooths, in order to account for underlying spatial and temporal autocorrelation in the data.
+Day of year was included as a 1-dimensional smooth, and easting and northing (km east and north of the trap extent centroid) were included as 2-dimensional smooths in order to account for underlying spatial and temporal autocorrelation in the data.
 
@@
 Finally, we calculated the proportion of explained variance (R$^2$) for each set of terms [@nakagawa2013; @nakagawa2017].
+
+To compare scalar-on-function (annular) regression to the more traditional (radial) regression approach, we also fit radial models of abundance using the same cover classes.
+We fit models using proportion cover in radii of increasing distances around each trap location (30 - 1500m, as above), and chose the model with the lowest AIC as the ``best" model. 
+As in the annular regression model, trapping location, log-days of trap placement, day of year, and easting and northing were also included in the radial models.
 
@@
 distincta_ may disperse into woodlands at this time.
-However, trap location and the temporal random effect (Figure \@ref(fig:ParDisSpatiotemporal)a) explained roughly 10 times more variance than landscape composition ($R^2$: `r round(sum(filter(r2Nakagawa2,model=='ParDisMod',terms=='trapLoc'|grepl('day',terms))$r2comp),3)` versus `r round(sum(filter(r2Nakagawa2,model=='ParDisMod',terms!='trapLoc',terms!='sigmaD',!grepl('s\\(',terms))$r2comp),3)`), meaning that while _P.
+However, trap location and the temporal smoother (Figure \@ref(fig:ParDisSpatiotemporal)a) explained roughly 10 times more variance than landscape composition ($R^2$: `r round(sum(filter(r2Nakagawa2,model=='ParDisMod',terms=='trapLoc'|grepl('day',terms))$r2comp),3)` versus `r round(sum(filter(r2Nakagawa2,model=='ParDisMod',terms!='trapLoc',terms!='sigmaD',!grepl('s\\(',terms))$r2comp),3)`), meaning that while _P.
 distincta_ may be abundant in certain cover types, its overall habitat preferences are fairly general.
@@
 moesta_ activity-density (Table \@ref(tab:rSquared), $R^2$: `r round(filter(r2Nakagawa2,model=="ParMoeMod",terms=="Pulses")$r2comp,3)`).
-Similar to _P.distincta_, trap location and an East-West spatial random effect (Figure \@ref(fig:ParMoeSpatiotemporal)b) explained roughly 5 times more variance in _P.
+Similar to _P.distincta_, trap location and an East-West spatial smoother (Figure \@ref(fig:ParMoeSpatiotemporal)b) explained roughly 5 times more variance in _P.
 moesta_ activity-density than landscape composition ($R^2$: `r round(sum(filter(r2Nakagawa2,model=='ParMoeMod',terms=='trapLoc'|grepl('E,N',terms))$r2comp),3)` versus `r round(sum(filter(r2Nakagawa2,model=='ParMoeMod',terms!='trapLoc',terms!='sigmaD',!grepl('s\\(',terms))$r2comp),3)`), meaning that _P.
@@
 _P.
-opilio_ activity-density was somewhat influenced by trap location, with field edges and wetlands having the highest activity-density (Figure \@ref(fig:OpilioLandscape)a), but this effect was swamped by the effect of landscape and the spatiotemporal random effects (Table \@ref(tab:rSquared)), meaning that _P.
-opilio_ activity-density is only mildly influenced by near cover type.
+opilio_ activity-density was somewhat influenced by trap location, with field edges and wetlands having the highest activity-density (Figure \@ref(fig:OpilioLandscape)a), but this effect was dwarfed by the spatial and temporal smoothers (Table \@ref(tab:rSquared)), meaning that _P.
+opilio_ activity-density is only mildly influenced by landscape composition.
 Nearby grassland and woodland both had negative effects on _Phalangium opilio_ activity-density Figures \@ref(fig:OpilioLandscape)b,c), but the effect of grassland was negative only early in the season (only weakly for woodland: p=0.07), suggesting that _P.
 opilio_ may preferentially disperse to these cover classes.
-The temporal random effect was overwhelmingly the most important predictor of _P.
+The temporal smoother was overwhelmingly the most important predictor of _P.
 opilio_ activity-density ($R^2$: `r round(sum(filter(r2Nakagawa2,model=='OpilioMod',terms=='s(day)')$r2comp),3)`), showing that activity-density increased during the spring, and showed very little decline during the rest of the season (Figure \@ref(fig:OpilioSpatiotemporal)a).
@@
 moesta_, _P.
-opilio_ also showed a distinct East-West spatial random effect (Figure \@ref(fig:OpilioSpatiotemporal)b), indicating that their activity-density is also influenced by larger-scale abiotic factors.
+opilio_ also showed a distinct East-West spatial smoother (Figure \@ref(fig:OpilioSpatiotemporal)b), indicating that their activity-density is also influenced by larger-scale abiotic factors.
 
@@
 
+## Comparison of annular and radial models
+
+Functional regression provided a better abundance model for two out of the four species (_P.
+melanarius_ and _P.
+distincta_), while radial regression performed better for _P.
+moesta_, and the null model (no landscape terms) was the best model for _P.
+opilio_ (Table \@ref(tab:compareModels)).
+The best radial model of _P.
+melanarius_ used a landscape radius of 1230 m, lending strength to the interpretation of the functional model where far-away landscapes have an influence on _P.
+melanarius_ abundance.
+The best landscape radii identified for _P.
+distincta_ and _P.
+moesta_ were much smaller (270 and 180 m, respectively), so it may be that the functional regression incorrectly identified effects of far-away land cover classes on abundance.
+However, none of the radial models accounted for the temporal effects of specific land cover classes, so it is difficult to compare the models directly.
+Interestingly, the radial model of _P.
+moesta_ provided a much better fit than the functional regression model ($\delta$AIC: `r round(with(compareMods, mod5AIC[3]-mod3AIC[3]),2)`), suggesting that a simpler model may be more appropriate for some species than others.
+Finally, the null model (no landscape terms) provided the best model of _P. opilio_ abundance, indicating that the organism has very general landscape preferences.
+
+```{r compareModels, echo=FALSE, message=FALSE, warning=FALSE, out.width='100%'}
+
+compareMods %>% #select(-bestDist) %>% 
+  rownames_to_column(var='Species') %>% 
+  kable(.,format='latex',caption='Comparison of models.
+The null model includes trap location and a spatial and a temporal smoother, but contains no landscape terms.
+The annular model includes the terms in the null model plus scalar-on-function landscape terms.
+The radial model includes the terms the null model plus radial landscape smoothers.
+Radius indicates the radius of landscape composition used in the best-fitting radial model.',escape=FALSE,
+      col.names=c('Species','AIC','edf','AIC','edf','AIC','edf','Radius (m)'),digits=1) %>% 
+  add_header_above(c(' '=1,'Null Model'=2,'Annular Model'=2,'Radial Model'=3)) %>% 
+  column_spec(1,italic=TRUE)
+```
+
 # Discussion
@@
 distincta_, meaning that these cover types likely represent only partial habitat for these arthropods.
-Finally, the influence of landscape composition tended to be limited to a radius of about 500m, indicating that nearby _and_ far-away landscape are associated with beneficial arthropod abundance.
+Finally, the influence of landscape composition tended to be limited to a radius of about 500m, indicating that nearby landscapes are associated with beneficial arthropod abundance.
 There was also a strong temporal component to most of the landscape effects, meaning that it is important to consider how destinations and sources may change over the season.
@@
 opilio_ was explained by day of year (R$^2$ = `r round(filter(r2Nakagawa2,model=='OpilioMod',grepl('day',terms))$r2comp,2)`), indicating strong seasonal emergence cues.
-However, there was also a strong East-West spatial random effect in both _P.
+However, there was also a strong East-West pattern in the spatial smoother for both _P.
 opilio_ and _P.
@@
 ```
+
+```{r child = 'supplemental2.Rmd'}
+```

### 2021-05-25 manuscript/supplemental2.Rmd
Worked on revisions

\newpage

# Appendix B: R Code {-}

```{r modelFormula, eval=FALSE}

#Code to run functional regression using gam function from mgcv 1.8-35

gam(count ~ offset(log(trapdays)) + trapLoc + s(day) + s(E,N)+ 
      #Canola
      s(distanceMatrix,by=Canola) + #Functional regression of distance
      s(dayMatrix,by=Canola) + #FR of time
      ti(distanceMatrix,dayMatrix,by=Canola) + #FR of distance and time
      #Pasture
      s(distanceMatrix,by=Pasture)+ #Functional regression of distance
      s(dayMatrix,by=Pasture) + #FR of time 
      ti(distanceMatrix,dayMatrix,by=Pasture) + #FR of distance and time
      #Other land cover classes here
      #...
      #...
      #...
      s(distanceMatrix,by=Roads) + 
      s(dayMatrix,by=Roads)+ 
      ti(distanceMatrix,dayMatrix,by=Roads),
    family= 'nb'
)
# where:
#
# count = N x 1 vector of activity density from traps (count)
# trapdays = N x 1 vector of number of days that the trap was installed for (numeric)
# trapLoc = N x 1 vector of trap location type (factor)
# day = N x 1 vector of day of year that the trap was installed on (numeric)
# E,N = N x 1 vector(s) of Easting and Northing (numeric)
# distanceMatrix = N x M matrix of distances, where the Nth row contains a vector
#     of distances to the annuli (numeric)
# dayMatrix = N x M matrix of days, where the Nth row contains a vector of days 
#     that spans the range of days of the year (numeric)
# Canola, Pasture, ... = N x M matrix of cover measurements, where the Nth row
#     contains a vector of proportion cover measurements within each annulus (numeric)
# 'nb' = Negative binomial family
```

### 2021-05-25 frAnalysis.R

@@ -61,12 +61,10 @@ oRingMat2Prop$TreeShrub <- oRingMat2Prop$Shrubland + oRingMat2Prop$Forest
 oRingMat2Prop$GrassWetland <- oRingMat2Prop$Wetland + oRingMat2Prop$Grassland
 # oRingMat2Prop$Wetland <- NULL; oRingMat2Prop$Grassland <- NULL
 
-
-
 #Create model formulas
 modFormulas <- 'count~offset(log(trapdays))+s(day,k=10,bs=basisFun)+s(E,N,k=50,bs=basisFun)' #Temporal + spatial
 # modFormulas <- paste0(modFormulas,'+ti(N,E,day,k=5,bs=basisFun)') # Add spatiotemporal interaction
-modFormulas[c(2,3,4)] <- paste0(modFormulas[1],'+trapLoc-1')
+modFormulas[c(2,3,4,5,6)] <- paste0(modFormulas[1],'+trapLoc-1')
 mod3Vars <- c('GrassWetland','Canola','Pasture','TreeShrub','Pulses','Urban') #Variables for mod3
 # mod3Vars <- c('GrassWetland','Cereal','Canola','Pasture','TreeShrub','Pulses','Flax','Urban') #As above, but includes cereal, flax
 # mod3Vars <- c('Grassland','Cereal','Canola','Pasture','Pulses','Wetland','Urban','Shrubland','Flax','Forest') #Expanded variables for mod3 - adding Water causes problems
@@ -80,8 +78,10 @@ for(i in 1:length(mod3Vars)){ #Add in specified terms (s and ti)
   modFormulas[3] <- paste0(modFormulas[3],"+ ti(distMat,endDayMat,by=",mod3Vars[i],",bs=basisFun)")
   # #Full interaction (te)
   # modFormulas[3] <- paste0(modFormulas[3],"+ te(distMat,endDayMat,by=",mod3Vars[i],",bs=basisFun)")
+  modFormulas[5] <- paste0(modFormulas[5],"+ s(",mod3Vars[i],",bs=basisFun,k=5)")
 }
 modFormulas[4] <- paste0(modFormulas[2],'+s(distMat,by=NonCrop,bs=basisFun)+s(endDayMat,by=NonCrop,bs=basisFun)+ti(distMat,endDayMat,by=NonCrop,bs=basisFun)')
+modFormulas[6] <- paste0(modFormulas[2],'+s(NonCrop,bs=basisFun)')
 
 #Parameters for multiplot figures
 #Landscape-level parameters
[…]

### 2021-05-25 helperFunctions.R

@@ -44,26 +44,37 @@ matrixplot <- function(m,nam=NULL,mar=NULL,numSize=1,numCol='red'){
 }
 
 #Takes a df of arthropod counts at each site (unique to each spp), then runs 4 landscape-level models of abundance
+#tempTrap = df of data to be used
+#oRingMatA = matrix of o-ring proportion cover
 #fitMethod = 'ML' or 'REML'
 #fitFam = family of distribution to use
 #basisFun = name of basis function to be used ('ts' = thin plate spline with extra shrinkage)
 #doublePenalize = should gam use double-penalization? (don't use if using 'ts' or 'cr' as basis functions)
-runMods <- function(tempTrap,nnDistMat,oRingMat2,formulas=NULL,
+runMods <- function(tempTrap,oRingMatA,formulas=NULL,
                     fitMethod='REML',fitFam='nb',basisFun='ts',doublePenalize=FALSE){
+  # #Test
+  # tempTrap <- rename(tempTrap,count=`Pterostichus melanarius`)
+  # oRingMatA <- oRingMat2Prop
+  # formulas <- modFormulas
+  # fitMethod <- 'REML'
+  # fitFam <- 'nb'
+  # basisFun <- 'ts'
+  # doublePenalize <- FALSE
+  
   if(is.null(formulas)) stop('No gam formulas provided')
   
-  #Arrange matrices from oRingMat2 to correspond with rows of tempTrap
-  oRingMat2 <- lapply(oRingMat2,function(x){
+  #Arrange matrices from oRingMatA to correspond with rows of tempTrap
+  oRingMatA <- lapply(oRingMatA,function(x){
     x %>% as.data.frame() %>% rownames_to_column('ID') %>% 
       right_join(st_drop_geometry(select(tempTrap,ID)),by='ID') %>% 
       select(-ID) %>% as.matrix() })
   
   #Distance matrix to use in functional regression
-  distMat <- matrix(rep(as.numeric(gsub('d','',colnames(oRingMat2[[1]]))),each=nrow(oRingMat2[[1]])),
-                    ncol=ncol(oRingMat2[[1]]))
+  distMat <- matrix(rep(as.numeric(gsub('d','',colnames(oRingMatA[[1]]))),each=nrow(oRingMatA[[1]])),
+                    ncol=ncol(oRingMatA[[1]]))
   #Matrix of end ("julian") days
[…]

### 2021-06-10 manuscript/manuscript.Rmd
Finished revisions and sent to journal

@@
 
-#Load models
+#Load ML model
+load('../data/PteMelMod_ML.Rdata')
+load('../data/ParDisMod_ML.Rdata')
+load('../data/ParMoeMod_ML.Rdata')
+load('../data/OpilioMod_ML.Rdata')
+
+#Compare annular and radial models 
+compareMods <- list(PteMelMod,ParDisMod,ParMoeMod,OpilioMod) %>% 
+  sapply(.,function(x){
+    with(x,c(mod2AIC=AIC(mod2),mod2df=attr(logLik(mod2),'df'),
+      mod3AIC=AIC(mod3),mod3df=attr(logLik(mod3),'df'),
+      mod5AIC=AIC(mod5),mod5df=attr(logLik(mod5),'df'),bestDist=mod5info$radiusDist[which.min(mod5info$AIC)]))
+  }) %>% t() %>% data.frame() %>% 
+  mutate(spp=c('Pterostichus melanarius','Pardosa distincta','Pardosa moesta','Phalangium opilio')) %>% 
+  column_to_rownames('spp')
+
+#Load REML models
+
 load('../data/PteMelMod.Rdata')
@@
 
-#Compare annular and radial models 
-compareMods <- list(PteMelMod,ParDisMod,ParMoeMod,OpilioMod) %>% 
-  sapply(.,function(x){
-    with(x,c(mod2AIC=AIC(mod2),mod2df=attr(logLik(mod2),'df'),
-      mod3AIC=AIC(mod3),mod3df=attr(logLik(mod3),'df'),
-      mod5AIC=AIC(mod5),mod5df=attr(logLik(mod5),'df'),bestDist=mod5info$radiusDist[which.min(mod5info$AIC)]))
-  }) %>% t() %>% data.frame() %>% 
-  mutate(spp=c('Pterostichus melanarius','Pardosa distincta','Pardosa moesta','Phalangium opilio')) %>% 
-  column_to_rownames('spp')
-
 ```
@@
 Pest arthropods can cause large reductions in crop yield [@oerke2005], which can result in negative downstream economic effects and food insecurity.
-However, beneficial arthropods living in non-crop patches can increase crop yields by providing ecosystem services, such as extra pollination or pest suppression [@losey2006; @klein2007; @garibaldi2013].
+However, beneficial arthropods living in non-crop areas can increase crop yields by providing ecosystem services, such as pollination or pest suppression [@losey2006; @klein2007; @garibaldi2013].
 Seasonal "pulses" of food resources act as bottom-up drivers of arthropod communities in crop fields, meaning that agricultural land can increase arthropod abundance in adjacent non-crop land [@diekotter2010; @galpern2017].
@@
 ## Data collection
-We used a set of `r sum(NtrapsPer$n)` pitfall traps installed in road margins (minimum of 5 m away from the road edge, `r with(NtrapsPer, sum(n[trapLoc=='ditch']))` traps) and in-field locations (`r with(NtrapsPer, sum(n[trapLoc!='ditch']))`) across southern Alberta, Canada in 2017 (Figure \@ref(fig:siteMap)).
+We used a set of `r sum(NtrapsPer$n)` pitfall traps across southern Alberta, Canada in 2017 (Figure \@ref(fig:siteMap)).
 The sites spanned a west-to-east gradient of four natural subregions, including foothills parkland, foothills fescue, mixedgrass, and dry mixedgrass [@ABRegions2006].
-These data were collected as a continuation of an earlier study that examined pollination services in crops [@vickruck2019], and here we use pitfall trap data to examine the predatory arthropod community with a focus on canola crops (\emph{Brassica napus} L.).
+The data were collected as an offshoot of an earlier study that examined pollination services in crops [@vickruck2019], and here we use pitfall trap data to examine the predatory arthropod community with a focus on canola crops (\emph{Brassica napus} L.).
 Canola is one of the most commonly-grown crops in southern Alberta, and represented 15\% of the total land cover within the spatial extent of our sampling region during 2017 (Figure \@ref(fig:siteMap)).
 We did not collect information on soil fertilization, pesticide application, mowing, or tillage (approximately 82% of planting in Vulcan County was done with zero-till in 2016; [@statscan_tillage2016]).
-Diverse crop rotations may increase predatory arthropod abundance [@busch_Msc; @bertrand2016], but this was beyond the scope of the study.
+Diverse crop rotations may also increase predatory arthropod abundance [@busch_Msc; @bertrand2016], but this was beyond the scope of the study.
 
-Traps in canola were installed in 27 fields at 25, 75, and 200 m along a transect heading away from the nearest non-crop feature (wetland, grassy field edges, or remnant prairie), while the trap at 0 m was installed in the non-crop feature itself.
-The remaining 90 sites had only a single trap.
-In-field traps were placed in canola crops (`r with(NtrapsPer, sum(n[trapLoc=='canola']))`), wetlands (`r with(NtrapsPer, sum(n[trapLoc=='wetland']))`), grassy field edges (`r with(NtrapsPer, sum(n[trapLoc=='pivot']))`), and remnant prairie grasslands (`r with(NtrapsPer, sum(n[trapLoc=='native']))`).
+Pitfall traps were installed in road margins (minimum of 5 m away from the road edge, `r with(NtrapsPer, sum(n[trapLoc=='ditch']))` traps) and in-field in canola crops (`r with(NtrapsPer, sum(n[trapLoc!='ditch']))`).
+Traps in canola were installed in 27 separate fields at 25, 75, and 200 m along a transect heading away from the nearest non-crop feature (wetland, grassy field edges, or remnant prairie), while the trap at 0 m was installed in the non-crop feature itself (see Figure \@ref(fig:siteMap) inset maps).
+The remaining 5 sites had only a single trap.
+In total, in-field traps were placed in canola crops (`r with(NtrapsPer, sum(n[trapLoc=='canola']))`), wetlands (`r with(NtrapsPer, sum(n[trapLoc=='wetland']))`), grassy field edges (`r with(NtrapsPer, sum(n[trapLoc=='pivot']))`), and remnant prairie grasslands (`r with(NtrapsPer, sum(n[trapLoc=='native']))`).
+"Wetlands" were permanent (non-ephemeral) flooded areas, "field edges" were the grassy corners of central-pivot irrigated fields, and "remnant prairie" were uncultivated grasslands composed of native grasses and herbs.
+We used 582 mL Solo® cups buried up to the rim and partially filled with propylene glycol, with 2 cm wire mesh mounted over the rim to prevent small vertebrates from falling into the traps.
+
 Traps were placed starting on `r format(as.Date(as.character(min(PteMelMod$tempTrap$startjulian)),format='%j'),format='%B %d')`, and collections ended on `r format(as.Date(as.character(max(PteMelMod$tempTrap$endjulian)),format='%j'),format='%B %d')`, with collection occurring continuously and traps being emptied every `r round(mean(PteMelMod$tempTrap$trapdays),1)` days on average (SD: `r round(sd(PteMelMod$tempTrap$trapdays),1)`).
 This resulted in `r nrow(PteMelMod$tempTrap)` unique collection events, taking place across a total of `r round(sum(PteMelMod$tempTrap$trapdays),1)` trapping days.
-We used 582 mL Solo® cups buried up to the rim and partially filled with propylene glycol, with 2 cm wire mesh mounted over the rim to prevent vertebrates from falling into the traps.
 Specimens were identified to species using appropriate taxonomic literature [@lindroth1966; @dondale1990; @edgar1990; @vogel2004; @yigit2007].
 
-We used counts of organisms in our pitfall traps as proxies of ecosystem services (specifically, pest control).
-However, increased counts of organisms in pitfall traps can represent higher activity levels (same number of organisms but more mobile) or higher abundances in the vicinity of the trap.
+We used counts of organisms in our pitfall traps as proxies of pest control service.
+However, increased counts of organisms in pitfall traps may represent higher activity levels (same number of organisms but more mobile) or higher abundances in the vicinity of the trap.
 This makes it impossible to disentangle arthropod activity from density using single traps [@lang2000], meaning that counts from traps represent the "activity-density" of a given organism, not absolute density.
@@
 (ref:siteMapCap) Classified land cover and location of pitfall traps during 2017.
-Inset map shows study location within Alberta provincial boundaries.
 Roadside traps were installed in road margins, while in-field traps were installed directly in canola fields, wetlands, or grassy field edges.
+Inset maps show study location within Alberta provincial boundaries, as well as examples of trap placement at two in-field sites.
 
@@
 Finally, _Phalangium opilio_ is an introduced harvestman (Opiliones: Phalangiidae) that is found in drier disturbed areas [@bragg2009].
-Juveniles hatch from eggs during the spring, becoming adults during the summer, and eggs are laid during the fall [adults do not overwinter; @bragg2009].
+Juveniles hatch from eggs during the spring, becoming adults during the summer, and eggs are laid during the fall (adults do not overwinter; @bragg2009).
 They are commonly found in human-altered landscapes [@muster2014; @vandepoel2015Msc] and are nocturnal generalist hunters and scavengers [@halaj2000; @allard2005b], mainly eating small soft-bodied invertebrates [@allard2005; @acosta2007].
 
-To characterize landscape composition surrounding the traps, we used publicly available classified landscape data [30 m resolution; @AAFC_data].
-AAFC cropland landscape classifications from 2017 were very accurate for cultivated fields (~90%), but were less accurate for non-crop areas (~70%).
+To characterize landscape composition surrounding the traps, we used 30 m resolution classified landscape data [@AAFC_data].
+Cropland classifications from 2017 were very accurate for cultivated fields (~90%), but were less accurate for non-crop areas (~70%).
 We combined functionally similar landscape categories (cereals: _Triticum aestivum_ and _Hordeum vulgare_, pulses: _Pisum sativum_ and _Lens culinaris_, forest: coniferous and broadleaf). 
 <!-- The radius of the circle necessary to characterize the landscape depends on the scale of the landscape that matters to a given organism [@addicott1987]. -->
-At each site, we extracted the proportion of each cover class within 30m annuli (rings), with the inner radius of each annulus ranging from 30 to 1470m in increments of 30m (total of 49 annuli, 1.5 km maximum).
+At each site, we extracted the proportion of each cover class within 30 m annuli (rings), with the inner radius of each annulus ranging from 30 to 1470 m in increments of 30 m (total of 49 annuli, 1.5 km maximum).
 The ten most-common cover classes surrounding our sites represented 98% of the total land cover in our study region: grassland, cereal, canola, pasture, pulses, wetland, urban (road margins), shrubland, flax, and forests (Figure \@ref(fig:landscapeComp)); flax was removed, as only a single site had nearby flax cover.
@@
 To account for different lengths of trap exposure, log-days since trap placement were used as a fixed effect with their slope held at 1 ("offset" variable).
-Trapping location was included as a fixed effect with 5 levels (canola, field edge, grassland, road margin, and wetlands) to account for the effect of local cover independent of the surrounding landscape composition.
+Trapping location was included as a fixed effect with 5 levels (canola, field edge, grassland, road margin, and wetlands) to account for the effect of local cover independent of the effect of surrounding landscape composition (described below).
 Day of year was included as a 1-dimensional smooth, and easting and northing (km east and north of the trap extent centroid) were included as 2-dimensional smooths in order to account for underlying spatial and temporal autocorrelation in the data.
@@
 
-To compare scalar-on-function (annular) regression to the more traditional (radial) regression approach, we also fit radial models of abundance using the same cover classes.
-We fit models using proportion cover in radii of increasing distances around each trap location (30 - 1500m, as above), and chose the model with the lowest AIC as the ``best" model. 
+To compare scalar-on-function (annular) regression to the more traditional (radial) regression approach, we also fit radial models of arthropod counts using the same cover classes.
+We fit count models using a smooth effect of proportion cover of radii of increasing distances around each trap location (30 - 1500 m, as above), and chose the model with the lowest AIC as the "best" model.
+Radial models reveal nothing about changes in the effect of land cover classes with distance or time, but serves to highlight differences in the predictive capability of the two methods.
 As in the annular regression model, trapping location, log-days of trap placement, day of year, and easting and northing were also included in the radial models.
@@
 Concurvity is a nonlinear analogue of multicollinearity which can bias estimates of standard errors [@buja1989].
-There is no agreed-upon threshold of ``unacceptable" concurvity, but 0.5 is commonly used [@dominici2002; @ramsay2003]. 
+There is no agreed-upon threshold of "unacceptable" concurvity, but 0.5 is commonly used [@dominici2002; @ramsay2003]. 
 <!-- Some landscape terms were strongly concurved , namely forest and shrubland (max: 0.71), canola and cereal (max: 0.74), and grassland and wetland (max: 0.63). -->
 For highly concurved classes, we examined the spatial nature of the concurvity using scatterplots of proportion cover within each annulus to determine whether the cover classes should be merged (if classes were consistently related) or removed (if classes were inversely related to one another).
-Forests and shrubland were combined into a single ``woodland" category, and grassland and wetland were combined into a single ``grassland" category, as they were strongly positively related to each other at all distances of annuli, indicating similar feature classes.
+Forests and shrubland were combined into a single "woodland" category, and grassland and wetland were combined into a single "grassland" category, as they were strongly positively related to each other at all distances of annuli, indicating similar feature classes.
 Cereal was removed from the model, as it was highly concurved with canola; in particular, it was negatively associated with canola cover at annulus distances of less than 200m and was positively associated at distances over 500m, reflecting the most common crop rotations (canola $\rightarrow$ wheat $\rightarrow$ barley) and the commonly-used 800 m block structure of farmland in our study region (quarter-sections).
@@
 
-Box 1: Intepreting Functional Regression Plots
+Box 1: Interpreting Functional Regression Plots
 
@@
 In reality, it is more likely that nearby cover will be more influential on activity-density than far-away cover, which could result in a relationship similar to Figure \@ref(fig:frExample)c.
-As functional regression takes any continuous predictor of _y_, it is also possible to use proportion cover as a predictor of measurements taken across time, allowing the effect of a (fixed) proportion cover on activity density to vary over the course of the season (Figure \@ref(fig:frExample)d).
+As functional regression takes any continuous predictor of _y_, it is also possible to use proportion cover as a predictor of measurements taken across time, allowing the effect of a (fixed) proportion cover on activity-density to vary over the course of the season (Figure \@ref(fig:frExample)d).
 Finally, the effect of proportion cover over distance and time may be modeled as a smoothed surface, representing the joint spatio-temporal influence of landscape cover on activity-density.
@@
 during emergence).
+As mentioned above, abundance and activity are confounded within activity-density, meaning that our method cannot explicitly say whether changes in counts are due to changes in abundance (_i.e._ migration or reproduction) or changes in activity (_i.e._ foraging).
+However, we consider it more likely that changes in activity-density related to landscape components are caused by changes in abundance, not activity, as there is no mechanism by which distant parts of landscape could alter activity.
+<!-- Changes in activity-density due to seasonal changes in foraging will be accounted for by the overall temporal smoother  -->
 
-In the Results section, we refer to ``near" and ``far" landscape effects, where near indicates the effects of landscape composition at scales of <500 m, and far indicates scales of >500 m.
-Similarly, we refer to early- and late-season effects, where landscape composition affected activity-density on June 20th or August 20th, respectively.
+In the Results section, we refer to "near" and "far" landscape effects, where near indicates the effects of landscape composition at scales of <500 m, and far indicates scales of >500 m.
+Similarly, we refer to "early" and "late"-season effects, where landscape composition affected activity-density in early June or late August, respectively.
 
@@
 Grassland, cereal, and canola were the three most-abundant landcover classes surrounding our traps, accounting for `r coverList %>% group_by(cover) %>% summarize(p=sum(prop)) %>% ungroup() %>% arrange(desc(p)) %>% mutate(prop=round(100*p/sum(p),2)) %>% slice(1:3) %>% pull(prop) %>% sum `% of land cover (Figure \@ref(fig:landscapeComp)).
-Several landscape ``fingerprints" were evident in the landscape annuli, with cereal cover increasing with distance away, along with a corresponding decrease in canola cover.
+Several landscape "fingerprints" were evident in the landscape annuli, with cereal cover increasing with distance away, along with a corresponding decrease in canola cover.
 Study sites were originally chosen for sampling arthropods surrounding canola agroecosystems, so canola was a dominant signal in the landscape, but there was also a large amount of variation in grassland and pasture surrounding each site (Figure \@ref(fig:landscapeComp)).
@@
 Lines and dots represent means, and bars and shaded regions represent 95 % confidence regions (1.96 x SE).
-Coloured regions represent early- and late-season effects (blue = June 20, red = August 20).
+Coloured regions represent early- and late-season effects (blue = June 2, red = August 20).
 
@@
 opilio_ activity-density was somewhat influenced by trap location, with field edges and wetlands having the highest activity-density (Figure \@ref(fig:OpilioLandscape)a), but this effect was dwarfed by the spatial and temporal smoothers (Table \@ref(tab:rSquared)), meaning that _P.
-opilio_ activity-density is only mildly influenced by landscape composition.
+opilio_ activity-density is weakly influenced by landscape composition.
 Nearby grassland and woodland both had negative effects on _Phalangium opilio_ activity-density Figures \@ref(fig:OpilioLandscape)b,c), but the effect of grassland was negative only early in the season (only weakly for woodland: p=0.07), suggesting that _P.
@@
                          terms=='TreeShrub' ~ 'Woodland', terms=='sigmaD' ~ 'Residual',
-                         terms=='Urban' ~ 'Road margins', TRUE ~ terms)) %>%
+                         terms=='Urban' ~ 'Road Margins', TRUE ~ terms)) %>%
   kable(.,format='latex',caption='R$^2_{GLMM}$ for model components, representing the proportion of total variance explained by each term.
+Trap Location refers to the individual cover type that the trap was installed in, Spatial Location and Day of Year refer to the overall spatial and temporal smoothers, Grassland through Road Margins refers to the functional smoothers over different surrounding land cover types, and Residual represents unexplained variation.
 R$^2$ was calculated using methods from Nakagawa et al.
@@
                               ' \\emph{Pardosa}\n\\emph{moesta}',' \\emph{Phalangium}\n\\emph{opilio}'),
-    Summary = as.character(c('$\\cdot$ Moves to canola during early season \n$\\cdot$ Disperses to grassland during late season',
+    Summary = as.character(c('$\\cdot$ Likely oves to canola during early season \n$\\cdot$ May disperse to grassland during late season',
                 '$\\cdot$ Negative effect of pasture \n$\\cdot$ May move locally to field edges',
-                '$\\cdot$ Moves to canola during early season \n$\\cdot$ Disperses to road margins and grassland during late season \n$\\cdot$Moves to grasslands across the season.',
-                '$\\cdot$ Moves to grassland early in the season')),
+                '$\\cdot$ Likely moves to canola during early season \n$\\cdot$ May disperse to road margins and grassland during late season \n$\\cdot$May disperse to grasslands across the season.',
+                '$\\cdot$ Likely moves to grassland early in the season')),
     BioControl= as.character(c('High','Low','Medium','Low'))
@@
 mytable %>% mutate_all(linebreak) %>% 
-  kable(.,format='latex',caption='Synthesis of model results. Pest control potential is based on likelihood of early-season aggregation to canola crops.',escape=FALSE,
+  kable(.,format='latex',caption='Synthesis of model results. Pest control potential is based on likelihood of early-season activity-density in canola crops.',escape=FALSE,
       col.names=c('Species','Summary','Pest control potential'),align='lll') %>% 
@@
 
-Functional regression provided a better abundance model for two out of the four species (_P.
+Functional regression provided a more parsimonious (lower AIC) activity-density model for _P.
+melanarius_, radial regression performed better for _P.
+moesta_ and _P.
+opilio_, and _P.
+distincta_ was modeled approximately equally by both model types (Table \@ref(tab:compareModels)).
+The best radial model of _P.
+distincta_ used a landscape radius of 1410 m, adding weight to the interpretation of the functional regression model where far-away landscapes have an influence on _P.
+distincta_ activity-density, while the best landscape radii identified for _P.
 melanarius_ and _P.
-distincta_), while radial regression performed better for _P.
-moesta_, and the null model (no landscape terms) was the best model for _P.
-opilio_ (Table \@ref(tab:compareModels)).
-The best radial model of _P.
-melanarius_ used a landscape radius of 1230 m, lending strength to the interpretation of the functional model where far-away landscapes have an influence on _P.
-melanarius_ abundance.
-The best landscape radii identified for _P.
-distincta_ and _P.
-moesta_ were much smaller (270 and 180 m, respectively), so it may be that the functional regression incorrectly identified effects of far-away land cover classes on abundance.
+moesta_ were much smaller (`r compareMods$bestDist[grepl('melanarius',rownames(compareMods))]` and `r compareMods$bestDist[grepl('moesta',rownames(compareMods))]` m, respectively).
+Interestingly, the radial models of _P.
+moesta_ and _P.
+opilio_ had lower AIC scores than the functional regression model ($\Delta$AIC: `r with(compareMods,round(mod5AIC[3]-mod3AIC[3],3))`, `r with(compareMods,round(mod5AIC[4]-mod3AIC[4],3))`), suggesting that a simpler model may be more appropriate for some species than others (if the goal is purely prediction with the least number of variables).
 However, none of the radial models accounted for the temporal effects of specific land cover classes, so it is difficult to compare the models directly.
-Interestingly, the radial model of _P.
-moesta_ provided a much better fit than the functional regression model ($\delta$AIC: `r round(with(compareMods, mod5AIC[3]-mod3AIC[3]),2)`), suggesting that a simpler model may be more appropriate for some species than others.
-Finally, the null model (no landscape terms) provided the best model of _P. opilio_ abundance, indicating that the organism has very general landscape preferences.
+All models had a lower AIC score than the null model, indicating that landscape composition is at least somewhat important for predicting activity-density.
 
@@
   rownames_to_column(var='Species') %>% 
+  # rowwise() %>% mutate(whichMin=which.min(c(mod2AIC,mod3AIC,mod5AIC))) %>%
   kable(.,format='latex',caption='Comparison of models.
@@
 Radius indicates the radius of landscape composition used in the best-fitting radial model.',escape=FALSE,
-      col.names=c('Species','AIC','edf','AIC','edf','AIC','edf','Radius (m)'),digits=1) %>% 
+      col.names=c('Species','AIC','Edf','AIC','Edf','AIC','Edf','Radius (m)'),digits=1) %>% 
   add_header_above(c(' '=1,'Null Model'=2,'Annular Model'=2,'Radial Model'=3)) %>% 
@@
 distincta_, meaning that these cover types likely represent only partial habitat for these arthropods.
-Finally, the influence of landscape composition tended to be limited to a radius of about 500m, indicating that nearby landscapes are associated with beneficial arthropod abundance.
+The influence of landscape composition tended to be limited to a radius of about 500m, indicating that nearby landscapes are associated with beneficial arthropod abundance.
 There was also a strong temporal component to most of the landscape effects, meaning that it is important to consider how destinations and sources may change over the season.
+Finally, the functional regression technique provided a more parsimonious model for _P. distincta_, highlighting its potential value for future work in landscape ecology.
+<!-- In particular, functional regression provided inference about how landscape cover influences the spatio-temporal distribution of ecosystem services within agroecosystems. -->
 
@@
 Many other studies have considered the overall effect of SNL on ecosystem service provision, but we have highlighted the different spatial and temporal aspects of these services.
-We have shown how a relatively straightforward statistical technique can be used to consider multiple spatial scales of landscape composition, providing richer inference about the processes acting on beneficial arthropods.
-Our results show empirical evidence of arthropod movement between cover types at different times of year, which is rarely considered beyond single-field studies.
-Since we did not directly track individual movements, future studies should directly examine arthropod movement and life-history within matrices of cover types, with the goal of integrating landscape ecology and behavioural processes into a single model [@lima1996].
+We have shown how a relatively novel statistical technique can be used to consider multiple spatial scales of landscape composition, providing richer inference about the processes acting on beneficial arthropods.
+Our results show indirect empirical evidence of arthropod movement between cover types at different times of year, which is rarely considered beyond single-field studies.
+Since we tracked activity-density and not individual movements, future studies should directly examine arthropod movement and life-history within matrices of cover types, with the goal of integrating landscape ecology and behavioural processes into a single model [@lima1996].
 This would also allow direct inference about landscape categories that were combined in our dataset, allowing us to consider different landscape categories independently.
@@
 Based on our findings, farmers and land managers should consider preserving existing grassland and wetland habitat to act as habitat for pest-suppressing arthropods in crops.
-While nearby habitat appears valuable, even faraway habitat can be valuable, as it can increase the number of beneficial arthropods at larger spatial scales (e.g.
+While nearby habitat appears valuable, even far-away habitat can be valuable, as it can increase the number of beneficial arthropods at larger spatial scales (e.g.
 Figures \@ref(fig:PteMelLandscape), \@ref(fig:ParMoeLandscape)).
-Secondly, our work suggests that _P. melanarius_ and _P. moesta_ should be investigated for their role as predators in canola crops (Table \@ref(tab:resultsTab)).
+Second, our work suggests that _P. melanarius_ and _P. moesta_ should be investigated for their role as predators in canola crops (Table \@ref(tab:resultsTab)).
 They appear to aggregate in canola crops early in the season, meaning that they have the potential to provide valuable pest-control services to growers.

### 2021-06-10 manuscript/supplemental2.Rmd
Finished revisions and sent to journal

@@
 #Code to run functional regression using gam function from mgcv 1.8-35 
+#See section 7.11 (p. 390) in Wood 2017 for more details
 
@@
       ti(distanceMatrix,dayMatrix,by=Pasture) + #FR of distance and time
-      #Other land cover classes here
+      #Other land cover classes go here 
       #...
@@
       #...
+      #Roads
       s(distanceMatrix,by=Roads) + 

### 2021-06-10 frAnalysis.R

@@ -35,12 +35,18 @@ tempTrap <- trap %>% filter(startYear==2017,grepl('PF',BTID)) %>%
   # rename('count'='n') %>% 
   #Converts 0 dist trapLoc to distFrom (pitfall traps at 0 m are "inside of" feature)
   mutate(trapLoc=ifelse(dist==0 & distFrom!='control',distFrom,trapLoc)) %>% 
-  # mutate(trapLoc=factor(ifelse(trapLoc=='pivot','ditch',trapLoc))) %>% #TEST: Changes all pivot features to ditch, as per reviewer 1's comment
+  mutate(trapLoc=factor(trapLoc)) %>% 
   #Get UTM coordinates for traps
   mutate(lonTrap2=lonTrap,latTrap2=latTrap) %>% #Duplicate columns
   st_as_sf(coords=c('lonTrap2','latTrap2'),crs=4326) %>% 
   st_transform(3403) %>% mutate(easting=st_coordinates(.)[,1],northing=st_coordinates(.)[,2]) %>% 
   mutate(easting=(easting-mean(easting))/1000,northing=(northing-mean(northing))/1000) #Center and scale coordinates to km
+
+# tempTrap %>% st_drop_geometry() %>% group_by(ID) %>% #Write tempTrap df to a csv (for mapping)
+#   summarize(BLID=first(BLID),nPasses=length(unique(pass)),totalDays=sum(trapdays),trapLoc=first(trapLoc),distFrom=first(distFrom),dist=first(dist),
+#             latitude=first(latTrap),longitude=first(lonTrap),sumPteMel=sum(`Pterostichus melanarius`),
+#             sumParDis=sum(`Pardosa distincta`),sumParMoe=sum(`Pardosa moesta`),sumOpilio=sum(`Phalangium opilio`)) %>% 
+#   write.csv('./data/trapLocs.csv',row.names = FALSE)
 
 #Arrange oRing data
 oRingMat2 <- lapply(oRingMat2,function(x) x[,-1]) #Remove distance=0 measurements (already in trapLoc category)
@@ -105,13 +111,58 @@ ylimRaneffPlots <- c(-5,2.7) #Y-limits for random effects smoothers (everything 
 dispDays <- data.frame(doy=c(153,232)) %>% 
   mutate(date=c('Early','Late')) 
 
-# Pterostichus melanarius ----------------------------------
+# Load/run models ----------------------------------------
 
[…]

### 2021-06-10 helperFunctions.R

@@ -66,8 +66,23 @@ runMods <- function(tempTrap,oRingMatA,formulas=NULL,
   #Arrange matrices from oRingMatA to correspond with rows of tempTrap
   oRingMatA <- lapply(oRingMatA,function(x){
     x %>% as.data.frame() %>% rownames_to_column('ID') %>% 
-      right_join(st_drop_geometry(select(tempTrap,ID)),by='ID') %>% 
-      select(-ID) %>% as.matrix() })
+      left_join(st_drop_geometry(select(tempTrap,ID)),.,by='ID') %>% 
+      # select(-ID) %>%
+      mutate(ID=paste0(ID,'.',1:nrow(.))) %>% column_to_rownames(var='ID') %>% 
+      as.matrix() })
+  
+  # oRingMatA$GrassWetland %>% head()
+  # oRingMatB$GrassWetland %>% head(10)
+  # st_drop_geometry(select(tempTrap,ID)) %>% head(10)
+  # oRingMatA$GrassWetland[which(rownames(oRingMatA$GrassWetland)=='10092-0-2017'),]
+  # 
+  # oRingMatA$GrassWetland[1,]-oRingMatB$GrassWetland[1,]
+  # 
+  # oRingMatA$GrassWetland %>% as.data.frame() %>% rownames_to_column('ID') %>% 
+  #   left_join(st_drop_geometry(select(tempTrap,ID)),.,by='ID') %>% 
+  #   # select(-ID) %>%
+  #   mutate(ID=paste0(ID,'.',1:nrow(.))) %>% column_to_rownames(var='ID') %>% 
+  #   as.matrix()
   
   #Distance matrix to use in functional regression
   distMat <- matrix(rep(as.numeric(gsub('d','',colnames(oRingMatA[[1]]))),each=nrow(oRingMatA[[1]])),
@@ -363,6 +378,11 @@ cldGam <- function(mod){
   letDisp <- cld(modcomp)$mcletters$Letters
   data.frame(trapLoc=names(letDisp),labs=unname(letDisp))
 }
+# 
+# debugonce(cldGam)
+# cldGam(mod3)
+
+
 
 #Function to convert o-ring matrix to circle matrix
 #o-ring = matrix with values for each ring in columns
